### 2015-08-16 paper_outline.tex
First -> just added the paper and the outline latex files.

%\documentclass[aps,floatfix,11pt,twocolumn]{revtex4-1}
\documentclass[aps,floatfix,11pt]{revtex4-1}
\usepackage{bm}%bold math
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{scalerel}
\epstopdfsetup{update} % only regenerate pdf files when eps file is newer
\linespread{1}
\usepackage[export]{adjustbox}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

    \begin{itemize}
        \item Topological Order that can not be described with Landau symmetry breaking.
        \item Robust ground state degeneracy.
        \item Fractional excitations.
        \item Toric code is a well studied exactly solvable model exhibitying topological order.
        \item Dimer models $\rightarrow$ more physical and some display topological order.
        \item Dimer models must be studied numerically.
    \end{itemize}

    \subsection{In this paper we... }
        \begin{itemize}
            \item In this paper we study the quantum dimer pentamer model (QDPM) on the square
                lattice at the RK point.
            \item Believe it may exhibit $Z_3$ topological order.
            \item Different than $Z_3$ toric code because only Ising degrees of freedom on the links.
            \item Study dimer correlations showing a liquid dimer pentamer phase at RK point with
                exponentially decaying dimer correlations.
            \item Estimate the dimer and vison gap.
        \end{itemize}

\section{Backround}

    \subsection{$Z_2$ Toric Code on Square Lattice}
        \begin{itemize}
        \item Hamiltonian.
        \item All terms commute $\rightarrow$ can solve exactly.
        \item Ground state is uniquely determined. 
        \item String operators.
        \item On torus conserved numbers, winding numbers $\rightarrow$ write in terms of string
            operators.
        \item 4 fold degenerate ground state.
        \item broken string operators give you electric and magnetic excitations.
        \item Exact local gauge symmetry on square lattice.
        \item $Z_2$ topological order $\rightarrow$ known exactly. 
        \end{itemize}

    \subsection{$Z_3$ Toric Code}
        \subsubsection{Hamiltonian Gauge symmetry }
            \begin{itemize}
                \item $Z_3$ algebra.
                \item Hamiltonian. Write the Hamiltonian in terms of $P$ and $Q$ operators. 
                \item \textcolor{red}{Figure} of vertex and plaquette labeling.
                \item Hamiltonian has local symmetry. 
                \item Specifically Hamiltonian obeys this local $Z_3$ gauge symmetry. Define the gauge operator. 
                \item Discus gauge symmetry connection to the Hilbert space.
                %\item express gauge operator in terms of electric flux $G_i =
                %    exp{[\frac{i2\pi}{3}\sum_{l\in v}\mathrm{sign}(l)E_l]}$
            \end{itemize}
        \subsubsection{String operators}
            \begin{itemize}
                \item String net $E$, $Q$ and $P$ operators and how they operate on links with three degrees of
                    freedom.
                \item Define string operators.
            \end{itemize}

        \subsubsection{properties of $Z_3$ string operators}
            \begin{itemize}
                \item \textcolor{red}{Figure} of the magnetic and electric string operator 
                    acting on a configuration (open ends).
                \item Use figure to highlight the fact that the $Z_3$ electric string operator with open ends
                    has a positive charge at one end and a negative charge at the other.
                \item Visons live at the ends of magnetic string with open ends.
                \item $Z_3$ vison $\rightarrow$ three values.
                \item Discuss $Z_3$ vison phase change when a closed electric string operator encloses a vison.
                \item Visons are the most ``physical'' excitations $\rightarrow$ explain. 
            \end{itemize}

        \subsubsection{Winding Numbers}
                \begin{itemize}
                    \item Winding operator in terms of magnetic string operator $\rightarrow$ commutes
                        with Hamiltonian.
                    \item Changing the topological sector with a non-trivial electric
                        string.
                    \item On a torus 9-fold degenerate ground state, each corresponding to a
                        different topological sector.
                \end{itemize}

    \subsection{QDM on Square lattice}
        \begin{itemize}
            \item Hamiltonian.
            \item RK point and Hilbert space.
            \item Dimer correlation's algebraic decay.
            \item Gapless.
            \item Discus $U(1)$ symmetry of QDM on square lattice.
            \item Winding number.
            \item Dimers as flux lines.
            \item Introduction of dynamical charges reduces $U(1) \rightarrow Z_N$ where $N$ is
                charge of itinerant objects.
        \end{itemize}

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Quantum Dimer Pentamer Model}

    \subsection{How to get local $Z_3$ symmetry in square lattice dimer model}
        \begin{itemize}
            \item Define pentamer.
            \item When charge 3 is introduced pentamers are the flux from the vertices with
                additional charge 3.
            \item $U(1) \rightarrow Z_3$ through the relaxation of constraints.
            \item \textit{Exact} local gauge symmetry.
        \end{itemize}

    \subsection{QDPM Hamiltonian}
        \begin{itemize}
            \item QDM Hamiltonian + pentamer terms.
            \item Like the QDM pentamer terms will consist of the smallest local moves that conserve
                the constraints.
            \item Introduce the pentamer terms. \textcolor{red}{Figure} of pentamer dynamics.
            \item We study this model at the RK point $t/v = 1$ where the wave function is just the
                equal weighted superposition of all classical dimer pentamer configurations.
        \end{itemize}

    \subsection{Winding operators}
        \begin{itemize}
            \item Make conection with $Z_3$ toric code. Can use same string operators $\rightarrow$
                all QDPM configurations can be written as $Z_3$ toric code configurations (but not
                the other way around).
            \item QDPM winding operator in terms of magnetic string operator $\rightarrow$ commutes
                with Hamiltonian.
            \item QDPM simplified winding operator (mod 3).
            \item In QDPM model the QDM winding operator is no longer conserved and does not commute with the
                Hamiltonian.
            \item In QDPM on a torus 9-fold degenerate ground state, each corresponding to a
                different topological sector.
        \end{itemize}

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Dimer Correlation Results}
    \subsection{Correlation functions}
        \begin{itemize}
            \item By measuring the dimer correlations between the link at the origin and all other
                links on the lattice we find no obvious broken symmetries.
            \item List all of the correlation functions measured. Such as: parallel dimers along
                horizontal and vertical directions, perpendicular dimers along horizontal and
                vertical directions ...
            \item \textcolor{red}{Figure} of the correlation functions. If possible, one figure
                containing all of the important ones. Log linear plot with a linear linear inset.
        \end{itemize}

    \subsection{Liquid}
        \begin{itemize}
            \item The exponential decaying correlations mean a liquid state with a finite gap.
            \item The correlation length is...
        \end{itemize}

    \subsection{Comparison to other models}
        \begin{itemize}
            \item Take the parallel dimer correlation function and compare these results in the QDM,
                the QDPM, and the toric code.
            \item \textcolor{red}{Figure} with the dimer correlations of the three models listed
                above.
        \end{itemize}

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Estimating the Gap}
    \subsection{Imaginary time vison correlations}
        \begin{itemize}
            \item The $Z_3$ Vison gap should be the smallest if there is $Z_3$ topological order.
            \item We can estimate the vison gap by calculating the imaginary time correlation
                functions - present correlation function formally.
            \item Should we discuss the subtleties of the imaginary time vison correlation function?
            \item We investigate three particular points $\rightarrow$ origin, $(L/2,0)$, $(L/2,L/2)$.
            \item \textcolor{red}{Figure} containing the $Z_3$ vison imaginary time correlations at all three
                of the points listed above.
            \item Estimate of the vison gap is ...
            \item Compare single and double vison correlations.
        \end{itemize}

    \subsection{Imaginary time dimer correlations}
        \begin{itemize}
            \item Same thing for the dimer gap $\rightarrow$ define correlation function.
            \item investigate the same 3 points.
            \item \textcolor{red}{Figure} of the imaginary time dimer correlations.
            \item Estimate of the dimer gap is ...
        \end{itemize}

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
    \begin{itemize}
        \item `` We present the QDPM ...''
        \item We show the string-net representation of the QDPM, introduce string operators and
            discus $Z_3$ excitations
        \item By calculating the dimer correlations we show QDPM is in liquid state at RK point.
        \item By calculating the imaginary time dimer and vison correlation functions we show ...
            hopefully show vison gap is smaller and thus this is indicative of $Z_3$ topological
            order.
    \end{itemize}

\end{document}

### 2015-08-16 qdpm_paper.tex
First -> just added the paper and the outline latex files.

\documentclass[aps,floatfix,11pt,twocolumn]{revtex4-1}
\usepackage{bm}%bold math
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{scalerel}
\epstopdfsetup{update} % only regenerate pdf files when eps file is newer
\linespread{1}
\usepackage[export]{adjustbox}

%\newcommand*\bplqt{\includegraphics[height=1.6ex] {Symbols/blank_plqt}}
%\newcommand*\bhrzmv{\includegraphics[height=1.6ex]{Symbols/blank_hrzmv}}
%\newcommand*\bdiag{\includegraphics[height=1.6ex] {Symbols/blank_diag}}
%\newcommand*\bstr{\includegraphics[height=1.6ex] {Symbols/blank_str}}

\newcommand*{\bplqt}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.2ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/blank_plqt} }
}
\newcommand*{\bhrzmv}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.2ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/blank_hrzmv} }
}
\newcommand*{\bdiag}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.2ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/blank_diag} }
}
\newcommand*{\bstr}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.2ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/blank_str} }
}
\newcommand*{\vvemptylink}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.8ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/string_net_link_sym0} }
}
\newcommand*{\emptylink}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.5ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/string_net_link_sym1} }
}
\newcommand*{\rightarrowlink}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.5ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/string_net_link_sym2} }
}
\newcommand*{\leftarrowlink}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.5ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/string_net_link_sym3} }
}
\newcommand*{\twointwoout}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.5ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/two_in_two_out} }
}
\newcommand*{\oneinoneout}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.5ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/one_in_one_out} }
}
\newcommand*{\threeinzeroout}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.5ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/three_in_zero_out} }
}
\newcommand*{\threeoutzeroin}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.5ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/three_out_zero_in} }
}
\newcommand*{\zerooutzeroin}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.5ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/zero_out_zero_in} }
}
\newcommand*{\hrzplqt}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.5ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/hrzplqt.pdf} }
}
\newcommand*{\vrtplqt}{%
  \text{% change size in subscripts or superscripts
    \includegraphics[
      height=1.5ex,% adjust to suit
      valign=M,% center vertically
      raise=\fontdimen22\textfont2,% but raise it to the formula axis
    ]{Symbols/vrtplqt.pdf} }
}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

    It became apparent in the 80's and early 90's that the Landau theory of symmetry breaking did not
    encompass all possible types of order possible in the groundstate of a condensed matter system. 
    In fact it was found that the symmetry of a system
    could increase as a system was cooled past a critical tempature and a phase transition occured
    that did not fit into Landau's theory. In these cases oder was found
    that could not be described with an order
    parameters \cite{wen_1990} which was a topological order does not fit in to Landau's
    theory of symmetry breaking. Though the discovery of topological order was originally thought
    to help understand superconductivity in the context of chiral spin systems \cite{HERE} it was
    not able to do so. However, due to the robust ground state degeneracy of systems exhibiting
    topological order they have become candidates for methods of storing and manipulating
    quantum information.  Also important to the field of quantum information, but interesting in
    its own right, is that topologically ordered systems exhibit fractal excitations.

    One of the simplest and most well studied models that exhibits topological order is the
    toric code. The toric code is also an exactly solvable model. Unfortunately it is
    a difficult model to physically realize. Another class of models that are well studied are
    the quantum dimer models (QDM).  These models can exhibit topological order and are also
    easier to experimentally realize, for example some short range resonating valence bond
    systems can be approximated with a QDM that provides a low energy effective description of
    the frustrated spins. Some correlation functions in QDMs are solvable using Pfaffian models
    but in general they must be studied numerically.

    In this paper we numerically study the quantum dimer pentamer model (QDPM) on the square
    lattice at the RK point.  The QDPM contains an exact $Z_3$ local gauge symmetry due to the
    introduction of pentamer objects and we believe it exhibits $Z_3$ topological order.
    Pentamers are objects consisting of four dimers touching a vertex.  The Hilbert space
    comprises all fully packed dimer and pentamer coverings. The presence or absence of a dimer
    may be defined in terms of Ising degrees of freedom that live on the links of the square
    lattice and this distinguishes it from the $Z_3$ toric code with three degrees of freedom on
    the links. We show numerically that a liquid dimer pentamer phase exists at the RK point
    with exponentially decaying dimer correlations. We also estimate the dimer and vison gaps
    showing that the $Z_3$ visons are the lowest lying and most fundamental excitations.

\section{Background}

    Now we will introduce the toric code on the square lattice in some detail to sever as a point of reference and
    comparison for the following discussion of the $Z_3$ case. The toric code Hamiltonian is given by
    %
    \begin{equation}
        H_t = -J_e\sum_v A_v - J_m\sum_p B_p
        \label{eqn:toric_code_ham}
    \end{equation}
    %
    where the operator $A_v$ acts on the vertex $v$ and the sum over $v$ is the sum over all vertices. 
    The operator $B_p$ acts on a plaquette $p$ and the sum over $p$ is the sum over all
    plaquettes. In the $Z_2$ toric code, Ising degrees of freedom live on the links of the
    lattice. Explicitly the operators $A_v$ and $B_p$ can be expressed as
    %
    \begin{equation}
        A_v = \prod_{i\in v} \sigma^x_i
        ,
    \end{equation}
    %
    and
    \begin{equation}
        B_p = \prod_{i\in p} \sigma^z_i
        .
    \end{equation}
    %
    The products are over the links adjacent to vertex $v$ and on the edges of plaquette $p$ for
    $A_v$ and $B_p$ respectively. Since all $A_v$ operators commute with each other, all
    $B_p$ operators commute with each other and $A_v$ commutes with $B_p$ even if they share
    links (commute because they
    can only share an even number of links) then the Hamiltonian can be solved term by term.

    Without a rigorous solution it is possible to guess at the form of the Toric code
    ground state wave function. The first term in \ref{eqn:toric_code_ham} is maximized ($H_t$
    minimized) when an even number of links touching a vertex are spin up or down in the
    $\sigma^z$ basis. By coloring the links of all down spins the groundstate will
    contain closed loops. The second term in \ref{eqn:toric_code_ham} is maximized for a
    superposition of loops since $B_p$ flips the spins around a plaquette $p$. The ground state
    wave function is then a superposition of all possible closed loop configurations. 
    %Since $B_p$ is a local operator
    %though the alowed loop configurations are determined by how the sytem in initilized.

    NEED HERE Some stuff about plaquette flux ?? -> $B_p | \Psi \rangle = | \Psi \rangle$ -> only true if
    grnd state as no vortices

    NEED HERE String operators. The electric and magnetic string operators are respectively
    \begin{equation}
        S^e_{\Gamma} = \prod_{i\in\Gamma_e} \sigma^x_i
        ,
    \end{equation}
    \begin{equation}
        S^m_{\Gamma} = \prod_{i\in\Gamma_m} \sigma^z_i
        ,
    \end{equation}
    where the path is denoted by $\Gamma$. The path of the electric string operator is along the
    links of the lattice and if this path is not closed then the operator
    creates a pair of excitations. These excitations are defects in the system 
    that can be thought of as electric charges that live at the
    end of the unclosed string. Each of these electric defects has an energy costs of $2J_e$. 
    The path of the magnetic string operator runs perpendicular to the links
    and starts and ends on the dual lattice. An unclosed magnetic path results in two magnetic
    excitations on the at the ends of the magnetic string each costing $2J_m$ each.

    Using a nontrivial path (genus of system $>0$) one can move between topological sectors using $S_e$ and determine
    the topological sector the system is in using $S_m$. On a torus, acting with $S_e$ along a
    path that encloses either the major or minor axis of the torus changes the topological sector.
    In general there are $4^g$ topological sectors where $g$ is the
    genus of the system. For a torus then there are four topological sectors. If These can be
    measuerd using the $S_m$ operator on a ...

    \subsection{$Z_3$ Toric Code}
        We can represent the $Z_3$ algebra through the following expressions
        %
        %Z_N
        %\begin{equation}
        %    E |n\rangle = n |n\rangle, ~ n=0,1,2,...,N-1
        %    \\
        %    e^{iA} |n\rangle = |n+1 \rangle, ~ n=0,1,2,...,N-2
        %    \\
        %    e^{iA} |N-1\rangle = |0\rangle
        %    %\label{eqn:}
        %\end{equation}
        %Z_3
        %
        \begin{equation}
            \begin{split}
            & E_l |n_l\rangle = n_l |n_l\rangle, ~ n_l=0,1,2
            \\
            & e^{iA_l} |n_l \rangle = |n_l+1 \rangle, ~ n_l =0,1
            \\ 
            & e^{iA_l} |2 \rangle = |0\rangle
            \end{split}
            ,
            %\label{eqn:}
        \end{equation}
        %
        where the operators $E_l$ and $A_l$ act on a given link $l$ and are analogous to the electric field and vector potential
        respectively. 
        By assigning orientations to the links between two vertices we can define 3 unique
        link ``values'' pictorially. 
        %
        \begin{itemize}
            \item $\vvemptylink$ 
            \item $\rightarrowlink$ 
            \item $\leftarrowlink$ 
        \end{itemize}
        % 
        In this way we can define $e^{iA_l}$ as the operator $Q$ which acts on the links in the
        following way
        \begin{equation}
            \begin{split}
                & Q^\dagger_{vv'}  | \vvemptylink \rangle = | \rightarrowlink \rangle
                ,
                \\
                & Q^\dagger_{vv'}  | \rightarrowlink \rangle = | \leftarrowlink \rangle
                ,
                \\
                & Q^\dagger_{vv'}  | \leftarrowlink \rangle = | \emptylink \rangle
                ,
            \end{split}
            %\label{eqn:}
        \end{equation}
        where the link is specified by the two vertices it connects and the operator
        $Q^\dagger_{vv'}$ acts in a direction from vertex $v$ to vertex $v'$. By changing the
        direction in which $Q$ operates we can express it in terms of its hermitian conjugate. 
        %
        \begin{equation}
            (Q^\dagger_{vv'})^\dagger = Q_{vv'}^\dagger
            .
            %\label{eqn:}
        \end{equation}

        The operator $E$ The operator $E_{vv'}$ can be defined in a similar way as
        %
        \begin{equation}
            \begin{split}
                & E^\dagger_{vv'}  | \vvemptylink \rangle = 0
                ,
                \\
                & E^\dagger_{vv'}  | \rightarrowlink \rangle = | \rightarrowlink \rangle
                ,
                \\
                & E^\dagger_{vv'}  | \leftarrowlink \rangle = 2| \leftarrowlink \rangle
                ,
            \end{split}
            %\label{eqn:}
        \end{equation}
        and with it we can define.
        %
        \begin{equation}
            P_{vv'}^\dagger \equiv e^{i2\pi E_{vv'}/3}
            .
            %\label{eqn:}
        \end{equation}
        %
        Now how $P_{vv'}^\dagger$ acts on the links: 
        %
        \begin{equation}
            \begin{split}
                & P^\dagger_{vv'}  | \vvemptylink \rangle = | \vvemptylink \rangle
                ,
                \\
                & P^\dagger_{vv'}  | \rightarrowlink \rangle = e^{i2\pi/3} | \rightarrowlink \rangle
                ,
                \\
                & P^\dagger_{vv'}  | \leftarrowlink \rangle = e^{-i2\pi/3} | \leftarrowlink \rangle
                .
            \end{split}
            %\label{eqn:}
        \end{equation}
        %

        The $Z_3$ toric code Hamiltonian can now be written in terms of the $P$ and $Q$ operators. The
        usual string net Hamiltonian is written as 
        \begin{equation}
            H = - J_e \sum_v A_v - J_m \sum_p B_p
            %\label{eqn:}
        \end{equation}
        where the sum over $v$ and the sum over $p$ are the sums over all vertices and plaquettes on
        the lattice respectively and 
        \begin{equation}
            A_v = \prod_{i\in v} P^\dagger_{vv_i}~,~ B_p \prod_{i\in p} Q^\dagger_{v_iv_{i+1}}
            .
            %\label{eqn:}
        \end{equation}
        The specific vertex and plaquette labeling scheme is shown in Fig.~\ref{fig:vertex_link_labels}.
        %
        \begin{figure}[htpb]
            \centering
            \includegraphics[width=0.8\linewidth]{vertex_link_gauge_def}
            \caption{Notation of vertex and plaquette labels}
            \label{fig:vertex_link_labels}
        \end{figure}
        %
        For the ground state of this Hamiltonian there is a local symmetry corresponding to the
        minimization of the first term. The model has an exactly local gauge symmetry that can be
        expressed as
        \begin{equation}
            G_v | \psi \rangle= | \psi \rangle
            %\label{eqn:}
        \end{equation}
        where $G_v$ = $A_v$.

        \subsubsection{Hamiltonian Gauge symmetry }

        \subsubsection{String operators}
            With the above notation we can write down the string operators. The electric string operator along
            the path $\Gamma_{v_b v_e}$ between the two vertices $v_0$ (beginning) and $v_N$ (end) is written
            %
            \begin{equation}
                S^e_{\Gamma} = \prod_{l=0}^{N-2} Q_{v_lv_{l+1}}^\dagger
                %\label{eqn:}
                ,
            \end{equation}
            %
            where $v_l \in \Gamma$ and $N$ is the number of vertices in $\Gamma$. We show an example of an
            electric string operator operation on an example configuration in Fig.~\ref{fig:example_elec_string}.
            %
            %
            \begin{figure}[htpb]
                \centering
                \includegraphics[width=0.8\linewidth]{example_elec_string.pdf}
                \caption{The grey line is the path $\Gamma$ on which the string operator acts. The operator acts
            in the direction from the vertex labeled in red to the one labeled in blue.}
                \label{fig:example_elec_string}
            \end{figure}
            %
            %
            The magnetic string operator can be written as
            \begin{equation}
                S^m_{\Gamma} = \prod_{l=0}^{N-1} Q_{v_{2l}v_{2l+1}}^\dagger
                %\label{eqn:}
            \end{equation}
            %
            where $v_l$ are the vertices adjacent to the links in $\Gamma$ and $N$ is the number of
            vertices
            on the \textit{left} side of the path when looking along the path from red to blue. 
            An example of this operator acting
            on a configuration is shown in Fig.~\ref{fig:example_mag_string} along with the vertex labeling
            scheme.
            %
            %
            \begin{figure}[htpb]
                \centering
                \includegraphics[width=0.8\linewidth]{example_mag_string.pdf}
                \caption{The grey line is the path $\Gamma$ on which the string operator acts. The magnetic
                    string operator acts in the 
                    direction from the plaquette labeled in red to the one labeled in blue.}
                \label{fig:example_mag_string}
            \end{figure}
            %
            The magnetic string operator acting on path $\Gamma$ in Fig.~\ref{fig:example_mag_string} is
            explicitly
            %
            \begin{multline}
                S^m_{\Gamma} (\mathrm{~Fig.~\ref{fig:example_mag_string}~config})
                = P_{v_0v_1}^\dagger P_{v_2v_3}^\dagger P_{v_4v_5}^\dagger
                \\
                = \exp{[0 - \frac{i2\pi}{3} + \frac{i2\pi}{3} ]} 
                = 1 (\mathrm{~Fig.~\ref{fig:example_mag_string}~config})
                .
            \end{multline}
            %

            An interesting property of the electric string string operators in the $Z_3$ toric code is
            that they produce two defects, one having positive charge and the other having negative
            charge. This is most easily see by looking at Fig.~\ref{fig:example_elec_string}. The
            configuration in Fig.~\ref{fig:example_elec_string}(a) obeys the local gauge symmetry and
            when the electric string operator acts on path $\Gamma$ it results in two defects at the
            end points of $\Gamma$. At the first $v_0$ (red) the local constraint is broken and
            $G_{v_0} = e^{i2\pi /3}$ as shown in Fig.~\ref{fig:example_elec_string}(b), whereas
            $G_{v_3} = e^{-i2\pi /3}$ which can be thought of as negative and positive gauge charges
            at $v_0$ and $v_3$ respectively.

            The magnetic excitations, or $Z_3$ visons live at the endpoints of a path created with the magnetic
            string operator. These visons can take three different values which can be changed by
            operating with the electric operator on a path that encircles one endpoint of the
            magnetic string path.

        \subsubsection{String operators}

        \subsubsection{properties of $Z_3$ string operators}

        \subsubsection{Winding Numbers}

            The ground state of the $Z_3$ toric code on the torus is nine-fold degenerate because of
            the nine different topological sectors in this topology. One can move between the
            topological sectors with a nontrivial closed electric string which wraps around either
            the major axis or the minor axis of the torus. We will call the electric winding
            operator that acts around the major axis $W^e_y$ and around the minor axis $W^e_x$.
            A given topological sector can be distinguish 
            by acting around the minor and major axes with the magnetic string operator $W^m_y$ and
            $W^m_x$. All of the aforementioned winding operators commute with the Hamiltonian and
            therefore share the same eigenvalues. The operator $W^m_{x}$ ($W^m_{y}$) can 
            have three different values depending on how many electric strings enclose the minor
            (major) axis. Since there are three different
            possible values for each winding number around each axis there are nine distinct
            topological sectors.

    \subsection{QDM on Square lattice}
        Here we will review the relevant
        properties and attributes of the QDM on the square lattice for which the Hamiltonian is.
        \begin{equation}
            \label{}
            H_{\mathrm{QDM}} = -t\sum_{\bplqt} 
                \left(
                    \left|
                        \vrtplqt
                    \right\rangle
                    \left\langle
                        \hrzplqt
                    \right|
                    +
                    \mathrm{h.c.}
                \right)
            - v\sum_{\bplqt}
                \left(
                    \left|
                        \vrtplqt
                    \right\rangle
                    \left\langle
                        \vrtplqt
                    \right|
                    +
                    \left|
                        \hrzplqt{}
                    \right\rangle
                    \left\langle
                        \hrzplqt
                    \right|
                \right)
                .
        \end{equation}
        This model can be defined in terms of a single parameter $t/v$ for which the wave function is
        known exactly at the Rokhsar and Kivelson (RK) point, the point where $t/v =1$. At the RK
        point the wave function is the equal weighted superposition over all dimer configurations.
        HERE

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Quantum Dimer Pentamer Model}

    \subsection{How to get local $Z_3$ symmetry in square lattice dimer model}

    \subsection{QDPM Hamiltonian}

    \subsection{Winding operators}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Dimer Correlation Results}
    \subsection{Correlation functions}

    \subsection{Liquid}

    \subsection{Comparison to other models}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Estimating the Gap}
    \subsection{Imaginary time vison correlations}

    \subsection{Imaginary time dimer correlations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

\end{document}

### 2015-08-24 qdpm_paper.tex
Included some information of the QDPM hamiltonian and the Z3 local gauge symetry of the QDPM.

@@
 %\newcommand*\bstr{\includegraphics[height=1.6ex] {Symbols/blank_str}}
+
+\newcommand*{\hprs}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.2ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/hrzprestar} }
+}
+\newcommand*{\hspr}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.2ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/hrzstarpair} }
+}
 
@@
     It became apparent in the 80's and early 90's that the Landau theory of symmetry breaking did not
-    encompass all possible types of order possible in the groundstate of a condensed matter system. 
+    encompass all possible types of order that can be found in the groundstate of a condensed matter system. 
     In fact it was found that the symmetry of a system
     could increase as a system was cooled past a critical tempature and a phase transition occured
-    that did not fit into Landau's theory. In these cases oder was found
+    that did not fit into Landau's theory. In these cases the odering 
     that could not be described with an order
-    parameters \cite{wen_1990} which was a topological order does not fit in to Landau's
-    theory of symmetry breaking. Though the discovery of topological order was originally thought
+    parameters \cite{wen_1990} was a topological order. Though the discovery of topological order was originally thought
     to help understand superconductivity in the context of chiral spin systems \cite{HERE} it was
@@
 
-        \subsubsection{String operators}
-
         \subsubsection{properties of $Z_3$ string operators}
@@
             the nine different topological sectors in this topology. One can move between the
-            topological sectors with a nontrivial closed electric string which wraps around either
+            topological sectors with a nontrivial closed electric string wraps around either
             the major axis or the minor axis of the torus. We will call the electric winding
@@
 
-    \subsection{How to get local $Z_3$ symmetry in square lattice dimer model}
+    \subsection{Local $Z_3$ Gauge Symmetry}
+
+        In the QDPM Ising degrees of freedom live on the links of the lattice.
+        The operator $\hat{\sigma}^x_l$ acts on these links and has 
+        eigenvalues $\sigma_l = \pm 1$, where $\sigma_l$ is the
+        Ising variables of the $l^{\mathrm{th}}$ link on the lattice. The number operator for a give link is
+        defined as $\hat{n}_l \equiv (1+\hat{\sigma}_x)/2$ and counts the number of dimers on link $l$.
+        An exactl local gauge symetry exsists on the lattice due to the contraint that either one or
+        four dimers touch any give vertex. In terms of $n_l$ we can define an operator that counts the
+        number of dimers touching a given vertex $v$ as $n_v = \sum_{l\in v} n_l$.
+
+        the local gauge transformation $G_v$ acting on a give vertex $v$ for the quantum dimer model
+        can be expressed as
+        %
+        \begin{equation}
+            \label{}
+            G_v=e^{i \alpha (n_v - n_0)}
+        \end{equation}
+        %
+        where $n_0$ is the constrained number of dimers touching a vertex, $n_0=1$ in the QDM model,
+        The operator $G_v$ then acts in such a
+        way that only the physical states, states satisfying the local constraint 
+        are invariant. For the QDM $G_v =
+        e^{i\alpha (0)}$ and therefore $G_v$ leaves a physical state unchanged for any
+        $\alpha$ making the local gauge symetry $U(1)$. The local gauge transformation that leaves
+        only configurations contaiing dimers and pentamers invarient is
+        %
+        \begin{equation}
+            \label{eqn:gauge_trans}
+            G_v = e^{i (\hat{n}_v -1) 2\pi/3}    
+        \end{equation}
+        %
+        For the QDPM $\alpha$ is must be $2\pi/3$ due to the relaxed contraint of the QDM
+        model that alows for pentamers. Relaxing the contraint of the QDM brings the local gauge
+        symetry from $U(1)$ to $Z(3)$.
 
     \subsection{QDPM Hamiltonian}
+
+        We work specificly at the RK point at wich the ground state wave function
+        is an equal weighted superposition of fully packed dimer pentamer configurations
+        %
+        \begin{equation}
+            \label{}
+            \left| \Psi \right\rangle = \frac{1}{\sqrt{N}}\sum_{\{C\}} \left| C \right\rangle
+            ,
+        \end{equation}
+        %
+        where $\{C\}$ is the set of fully packed configurations. The Hilbert space can be defined
+        using the gauge trasformation in Eq.~\ref{eqn:gauge_trans} as all $\left| C \right\rangle$
+        satisfying $G \left| C \right\rangle = \left| C \right\rangle$.
+
+        The QDPM Hamiltonian
+        \begin{equation}
+            H_{\mathrm{QDPM}} = H_{\mathrm{QDM}} + \mathrm{pentamer\ terms}
+        \end{equation}
+
+        The pentamer terms in the Hamiltonian can be constructed with the dynamics shown in
+        Fig.~\ref{fig:pentamer_moves}.  
+        \begin{figure}[htpb]
+            \centering
+            \includegraphics[width=0.8\linewidth]{pentamer_moves.pdf}
+            \caption{a) Horizontal criation an anihilation, b) horizontal move, c) and d) are two
+            differen possible diagonal moves in the same direction.}
+            \label{fig:pentamer_moves}
+        \end{figure}
+        Each of the  moves shown in Fig.~\ref{fig:pentamer_moves} can be
+        rotated to produce the symetry related counterpart (eg. vertical creation and anihilation). 
+        As an example the creation and anhilation term in the Hamiltonian is
+        \begin{multline}
+        H_{\mathrm{pentamer\ creation}} = t_{\mathrm{create}}
+            \sum_{\bstr}
+            \left(
+                \left|
+                    \hprs
+                \right\rangle
+                \left\langle
+                    \hspr
+                \right|
+                +
+                \mathrm{h.c.}
+            \right)
+            \\
+            - v_{\mathrm{create}}
+            \sum_{\bstr}
+                \left(
+                    \left|
+                        \hprs
+                    \right\rangle
+                    \left\langle
+                        \hprs
+                    \right|
+                    +
+                    \left|
+                        \hspr
+                    \right\rangle
+                    \left\langle
+                        \hspr
+                    \right|
+                \right)
+        \end{multline}
+        where the factors $t_{\mathrm{create}}$ and $v_{\mathrm{create}}$ are the coefficients of
+        the penamer pair creation and anihilation respectivly. At the RK point
+        $t/v=1$ for each all the petamer terms. 
+        Writing the kinetic and potential energy terms as done above for all the dynamics shown in
+        Fig.~\ref{fig:pentamer_moves} and all of their symetry related counterparts comprise the
+        the pentamer terms of the Hamiltonian.
 
@@
 \section{Dimer Correlation Results}
+
+    \subsection{Liquid}
+
     \subsection{Correlation functions}
 
-    \subsection{Liquid}
+    \begin{equation}
+        C_{\mathrm{dimer}} = \langle d_0 d_r \rangle - \langle d_0 \rangle   \langle d_r \rangle   
+    \end{equation}
+
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=0.8\linewidth]{spacial_dmr_cor.pdf}
+        \caption{(Note: This figure was made using equal probabilities of plaquette filps and
+        pentamer moves) Spacial correlation function of parralel dimers for the two different
+        sublattices distiguesed by their color (red, green).}
+        \label{fig:spacial_dmr_cor}
+    \end{figure}
 
@@
     \subsection{Imaginary time vison correlations}
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=0.8\linewidth]{z2_origin_vison_time_cor.pdf}
+        \caption{Imaginary time $z_2$ \textit{single} vison correlations at the origin in the QDM model (red) and QDPM
+        model (green) on an $8\times$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$.}
+        \label{fig:name}
+    \end{figure}
 
     \subsection{Imaginary time dimer correlations}
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=0.8\linewidth]{dimer_origin_time_cor.pdf}
+        \caption{Imaginary time dimer correlations of a single dimer in the QDM model (red) and QDPM
+        model (green) on an $8\times$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$. }
+        \label{fig:}
+
+    \end{figure}
 

### 2015-08-27 qdpm_paper.tex
added all images and a table to the paper with some of the gap info

@@
     One of the simplest and most well studied models that exhibits topological order is the
-    toric code. The toric code is also an exactly solvable model. Unfortunately it is
+    toric code, an exactly solvable model. Unfortunately it is
     a difficult model to physically realize. Another class of models that are well studied are
@@
         defined as $\hat{n}_l \equiv (1+\hat{\sigma}_x)/2$ and counts the number of dimers on link $l$.
-        An exactl local gauge symetry exsists on the lattice due to the contraint that either one or
+        An exactly local gauge symmetry exists on the lattice due to the constraint that either one or
         four dimers touch any give vertex. In terms of $n_l$ we can define an operator that counts the
@@
         e^{i\alpha (0)}$ and therefore $G_v$ leaves a physical state unchanged for any
-        $\alpha$ making the local gauge symetry $U(1)$. The local gauge transformation that leaves
-        only configurations contaiing dimers and pentamers invarient is
+        $\alpha$ making the local gauge symmetry $U(1)$. The local gauge transformation that leaves
+        only configurations containing dimers and pentamers invariant is
         %
@@
         %
-        For the QDPM $\alpha$ is must be $2\pi/3$ due to the relaxed contraint of the QDM
-        model that alows for pentamers. Relaxing the contraint of the QDM brings the local gauge
-        symetry from $U(1)$ to $Z(3)$.
+        For the QDPM $\alpha$ is must be $2\pi/3$ due to the relaxed constraint of the QDM
+        model that allows for pentamers. Relaxing the constraint of the QDM brings the local gauge
+        symmetry from $U(1)$ to $Z(3)$.
 
@@
 
-        We work specificly at the RK point at wich the ground state wave function
+        We work specifically at the RK point at which the ground state wave function
         is an equal weighted superposition of fully packed dimer pentamer configurations
@@
         where $\{C\}$ is the set of fully packed configurations. The Hilbert space can be defined
-        using the gauge trasformation in Eq.~\ref{eqn:gauge_trans} as all $\left| C \right\rangle$
+        using the gauge transformation in Eq.~\ref{eqn:gauge_trans} as all $\left| C \right\rangle$
         satisfying $G \left| C \right\rangle = \left| C \right\rangle$.
@@
             \includegraphics[width=0.8\linewidth]{pentamer_moves.pdf}
-            \caption{a) Horizontal criation an anihilation, b) horizontal move, c) and d) are two
-            differen possible diagonal moves in the same direction.}
+            \caption{a) Horizontal creation an annihilation, b) horizontal move, c) and d) are two
+            different possible diagonal moves in the same direction.}
             \label{fig:pentamer_moves}
@@
         Each of the  moves shown in Fig.~\ref{fig:pentamer_moves} can be
-        rotated to produce the symetry related counterpart (eg. vertical creation and anihilation). 
-        As an example the creation and anhilation term in the Hamiltonian is
+        rotated to produce the symmetry related counterpart (eg. vertical creation and annihilation). 
+        As an example the creation and annihilation term in the Hamiltonian is
         \begin{multline}
@@
         where the factors $t_{\mathrm{create}}$ and $v_{\mathrm{create}}$ are the coefficients of
-        the penamer pair creation and anihilation respectivly. At the RK point
-        $t/v=1$ for each all the petamer terms. 
+        the pentamer pair creation and annihilation respectively. At the RK point
+        $t/v=1$ for each all the pentamer terms. 
         Writing the kinetic and potential energy terms as done above for all the dynamics shown in
-        Fig.~\ref{fig:pentamer_moves} and all of their symetry related counterparts comprise the
+        Fig.~\ref{fig:pentamer_moves} and all of their symmetry related counterparts comprise the
         the pentamer terms of the Hamiltonian.
@@
     \subsection{Winding operators}
+
+        In the QDPM there is a conserved winding operator in a given topological sector
+        \begin{equation}
+            W_{x,y} = (N_A - N_B)\mod{3} = n
+            .
+        \end{equation}
+        For $W_y$ ($W_x$), $N_A$ is the number of dimers crossed on a vertical (horizontal) cut and
+        $n=0$, $1$, or $2$ depending on the topological sector. The winding operator commutes with
+        the Hamiltonian and therefore share the same eigenvalues. Since there are three winding numbers in
+        each direction then the ground state is ninefold degenerate.
 
@@
         \includegraphics[width=0.8\linewidth]{spacial_dmr_cor.pdf}
-        \caption{(Note: This figure was made using equal probabilities of plaquette filps and
-        pentamer moves) Spacial correlation function of parralel dimers for the two different
-        sublattices distiguesed by their color (red, green).}
+        \caption{(Note: This figure was made using equal probabilities of plaquette flips and
+        pentamer moves) Spacial correlation function of parallel dimers for the two different
+        sublattices distinguished by their color (red, green).}
         \label{fig:spacial_dmr_cor}
@@
 \section{Estimating the Gap}
+
+    \begin{table}[htpb]
+        \centering
+        \caption{$\Delta \tau = 150$}
+        \label{tab:label}
+        \begin{tabular}{c c c}
+            \hline\hline
+         L            & 8x8 Gap  & 16x16  \\ 
+            \hline
+         frac 1.0     &          & \\
+            \hline
+         Dimer origin &  0.03230 & 0.00806 \\
+         $Z_2$ origin &  0.00787 & 0.00198  \\
+         $Z_3$ origin &  NA      & NA \\
+            \hline
+         frac 0.9     &          & \\
+            \hline
+         Dimer origin &  0.00419 & 0.00429 \\
+         $Z_2$ origin &  0.00216 & 0.00129  \\
+         $Z_3$ origin &  0.00346 & 0.00359 \\
+            \hline
+         frac 0.5     &          & \\
+            \hline
+         Dimer origin &          & 0.02049 \\
+         $Z_2$ origin &          & 0.00614  \\
+         $Z_3$ origin &          & 0.01927  
+        \end{tabular}
+    \end{table}
+
     \subsection{Imaginary time vison correlations}
@@
         \caption{Imaginary time $z_2$ \textit{single} vison correlations at the origin in the QDM model (red) and QDPM
-        model (green) on an $8\times$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$.}
+        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$.}
         \label{fig:name}
@@
         \caption{Imaginary time dimer correlations of a single dimer in the QDM model (red) and QDPM
-        model (green) on an $8\times$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$. }
+        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$. }
         \label{fig:}

### 2015-09-01 qdpm_paper.tex
Added error to the gap estimates in the table
Added the gap info for 12x12.

@@
         \label{tab:label}
-        \begin{tabular}{c c c}
+        \begin{tabular}{c c c c}
             \hline\hline
-         L            & 8x8 Gap  & 16x16  \\ 
+         L            & 8x8 Gap                               & 12x12                            & 16x16                              \\ 
             \hline
-         frac 1.0     &          & \\
+         frac 1.0     &                                       &                                  &                                    \\
             \hline
-         Dimer origin &  0.03230 & 0.00806 \\
-         $Z_2$ origin &  0.00787 & 0.00198  \\
-         $Z_3$ origin &  NA      & NA \\
+         Dimer        &  $ 0.03230 \pm 0.01142$               & $ 0.01430 \pm 0.00034 $          & $0.00806 \pm 0.00023$ \\
+         $Z_2$ origin &  $ 0.00787 \pm 5.3\times 10^{-6} $    & $ 0.00344 \pm 9.0\times 10^{-7}$ & $0.00198 \pm 3.8\times 10^{-6} $   \\
+         $Z_3$ origin &  NA                                   & NA                               & NA \\
             \hline
-         frac 0.9     &          & \\
+         frac 0.9     &                                       &                                  & \\
             \hline
-         Dimer origin &  0.00419 & 0.00429 \\
-         $Z_2$ origin &  0.00216 & 0.00129  \\
-         $Z_3$ origin &  0.00346 & 0.00359 \\
+         Dimer origin &  $ 0.00419 \pm 8.1\times 10^{-6} $    & $ 0.00406 \pm 1.7\times 10^{-5} $ & $0.00429 \pm 6.6\times 10^{-6} $   \\
+         $Z_2$ origin &  $ 0.00216 \pm 1.5\times 10^{-6} $    & $ 0.00141 \pm 8.4\times 10^{-7} $ & $0.00129 \pm 1.8\times 10^{-6} $   \\
+         $Z_3$ origin &  $ 0.00346 \pm 3.8\times 10^{-6} $    & $ 0.00348 \pm 5.1\times 10^{-6} $ & $0.00359 \pm 3.5\times 10^{-6} $   \\
             \hline
-         frac 0.5     &          & \\
+         frac 0.5     &                                       &                                   & \\
             \hline
-         Dimer origin &          & 0.02049 \\
-         $Z_2$ origin &          & 0.00614  \\
-         $Z_3$ origin &          & 0.01927  
+         Dimer origin &                                       & $ 0.02075 \pm 8.9\times 10^{-5} $ & $0.02049 \pm 0.00011 $\\
+         $Z_2$ origin &                                       & $ 0.00615 \pm 2.2\times 10^{-6} $ & $0.00614 \pm 2.8\times 10^{-6} $   \\
+         $Z_3$ origin &                                       & $ 0.01939 \pm 2.2\times 10^{-5} $ & $0.01927 \pm 0.00002 $ 
         \end{tabular}

### 2015-09-04 qdpm_paper.tex
tried to fix permisions

--- 2015-08-27 qdpm_paper.tex
@@
         \label{tab:label}
-        \begin{tabular}{c c c}
+        \begin{tabular}{c c c c}
             \hline\hline
-         L            & 8x8 Gap  & 16x16  \\ 
+         L            & 8x8 Gap                               & 12x12                            & 16x16                               & 18x18 \\ 
             \hline                                                                                                                           
-         frac 1.0     &          & \\
+         frac 1.0     &                                       &                                  &                                     &  \\
             \hline                                                                                                                           
-         Dimer origin &  0.03230 & 0.00806 \\
-         $Z_2$ origin &  0.00787 & 0.00198  \\
-         $Z_3$ origin &  NA      & NA \\
+         Dimer        &  $ 0.03230 \pm 0.01142$               & $ 0.01430 \pm 0.00034 $          & $0.00806 \pm 0.00023$               & \\
+         $Z_2$ origin &  $ 0.00787 \pm 5.3\times 10^{-6} $    & $ 0.00344 \pm 9.0\times 10^{-7}$ & $0.00198 \pm 3.8\times 10^{-6} $    &  \\
+         $Z_3$ origin &  NA                                   & NA                               & NA                                  & \\
             \hline                                                                                                                         
-         frac 0.9     &          & \\
+         frac 0.9     &                                       &                                  &                                     &  \\
             \hline                                                                                                                          
-         Dimer origin &  0.00419 & 0.00429 \\
-         $Z_2$ origin &  0.00216 & 0.00129  \\
-         $Z_3$ origin &  0.00346 & 0.00359 \\
+         Dimer origin &  $ 0.00419 \pm 8.1\times 10^{-6} $    & $ 0.00406 \pm 1.7\times 10^{-5} $ & $0.00429 \pm 6.6\times 10^{-6} $   &  $ 0.00405 \pm 1.6\times 10^{-5} $\\
+         $Z_2$ origin &  $ 0.00216 \pm 1.5\times 10^{-6} $    & $ 0.00141 \pm 8.4\times 10^{-7} $ & $0.00129 \pm 1.8\times 10^{-6} $   &  $ 0.00126 \pm 1.7\times 10^{-6} $\\
+         $Z_3$ origin &  $ 0.00346 \pm 3.8\times 10^{-6} $    & $ 0.00348 \pm 5.1\times 10^{-6} $ & $0.00359 \pm 3.5\times 10^{-6} $   &  $ 0.00355 \pm 3.3\times 10^{-6}$\\
             \hline                                                                                                                          
-         frac 0.5     &          & \\
+         frac 0.5     &                                       &                                   &                                    & \\
             \hline                                                                                                                          
-         Dimer origin &          & 0.02049 \\
-         $Z_2$ origin &          & 0.00614  \\
-         $Z_3$ origin &          & 0.01927  
+         Dimer origin &                                       & $ 0.02075 \pm 8.9\times 10^{-5} $ & $0.02049 \pm 0.00011 $             &  $ $ \\
+         $Z_2$ origin &                                       & $ 0.00615 \pm 2.2\times 10^{-6} $ & $0.00614 \pm 2.8\times 10^{-6} $   &  $ $ \\
+         $Z_3$ origin &                                       & $ 0.01939 \pm 2.2\times 10^{-5} $ & $0.01927 \pm 0.00002 $             &  $ $  
         \end{tabular}

### 2015-09-04 qdpm_paper.tex
Started formatting paper

--- 2015-09-01 qdpm_paper.tex
@@
-\documentclass[aps,floatfix,11pt,twocolumn]{revtex4-1}
+\documentclass[twocolumn,prb,aps,floatfix,superscriptaddress]{revtex4-1}
+
 \usepackage{bm}%bold math
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
+
+\title{Topological order in the quantum dimer-pentamer model}
+
+\author{Owen Myers}
+\email{omyers@uvm.edu}
+\affiliation{Department of Physics, University of Vermont, Burlington, VT 05405, USA}
+
+\author{C. M. Herdman}
+\affiliation{Institute for Quantum Computing, University of Waterloo, Ontario, N2L 3G1, Canada}
+\affiliation{Department of Physics \& Astronomy, University of Waterloo, Ontario, N2L 3G1, Canada}
+\affiliation{Department of Chemistry,  University of Waterloo, Ontario, N2L 3G1, Canada}
+
+\begin{abstract}
+
+\end{abstract}
+
+\maketitle
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     that could not be described with an order
-    parameters \cite{wen_1990} was a topological order. Though the discovery of topological order was originally thought
+    parameters~\cite{Wen1990} was a topological order. Though the discovery of topological order was originally thought
     to help understand superconductivity in the context of chiral spin systems \cite{HERE} it was
@@
 
+\bibliographystyle{apsrev4-1}
+\bibliography{QDPM}
+
 \end{document}

### 2015-09-09 qdpm_paper.tex
Reformatted gap table.
Worked on introduction. Added placeholder figure 1.

@@
 %\newcommand*\bstr{\includegraphics[height=1.6ex] {Symbols/blank_str}}
+
+\newcommand{\figref}[1]{Fig. \ref{#1}}
+\newcommand{\secref}[1]{Sec. \ref{#1}}
 
@@
 \begin{abstract}
-
+We study the ground state of the quantum dimer-pentamer model (QDPM) on the square lattice.
+This model is a generalization of the square lattice quantum dimer model (QDM) as its configuration space comprises fully-packed hard-core dimer coverings as well as configurations containing pentamers, where four dimers touch a vertex.
+Thus in the QDPM, the fully-packed, hard-core constraint of the QDM is relaxed such that the local dimer number at each vertex is fixed modulo 3; correspondingly, the local $U(1)$ gauge symmetry of the QDM Hilbert space is reduced to a local $Z_3$ gauge symmetry in the QDPM.
+We construct a local Hamiltonian for which the Rokhsar-Kivelson (RK) state (the equal superposition of all configurations in a topological sector) is the exact ground state and has a 9-fold topological degeneracy on the torus.
+Using Monte Carlo calculations, we find no spontaneous symmetry breaking in the RK wavefunction and that its dimer-dimer correlation function decays exponentially.
+Additionally, we discuss the possibility of $Z_3$ topological order in the ground state of the QDPM.
 \end{abstract}
@@
 
-    It became apparent in the 80's and early 90's that the Landau theory of symmetry breaking did not
-    encompass all possible types of order that can be found in the groundstate of a condensed matter system. 
-    In fact it was found that the symmetry of a system
-    could increase as a system was cooled past a critical tempature and a phase transition occured
-    that did not fit into Landau's theory. In these cases the odering 
-    that could not be described with an order
-    parameters~\cite{Wen1990} was a topological order. Though the discovery of topological order was originally thought
-    to help understand superconductivity in the context of chiral spin systems \cite{HERE} it was
-    not able to do so. However, due to the robust ground state degeneracy of systems exhibiting
-    topological order they have become candidates for methods of storing and manipulating
-    quantum information.  Also important to the field of quantum information, but interesting in
-    its own right, is that topologically ordered systems exhibit fractal excitations.
+Over the last several decades, experimental and theoretical work has demonstrated that strongly interacting quantum many-body systems support exotic quantum phases phases of matter not described by the Landau symmetry breaking paradigm.
+One class of such quantum phases of matter are topologically ordered quantum liquids~\cite{Wen1990}, first realized experimentally via the fractional quantum Hall effect~\cite{FQHE????}.
+Despite the absence of conventional symmetry breaking and a local order parameter, topological quantum liquids possess a non-trivial quantum order that distinguishes them from trivial liquid phases~\cite{Nayak2008}.
+Although not detectable by local operators, topological order arises due to a non-local entanglement structure that leaves a signatures in the bipartite entanglement entropy~\cite{Levin2006a,Kitaev2006b}.
+Such topological phases provide the basis for a proposal for fault-tolerant quantum information processing~\cite{Freedman2001,Kitaev2003}.
 
-    One of the simplest and most well studied models that exhibits topological order is the
-    toric code, an exactly solvable model. Unfortunately it is
-    a difficult model to physically realize. Another class of models that are well studied are
-    the quantum dimer models (QDM).  These models can exhibit topological order and are also
-    easier to experimentally realize, for example some short range resonating valence bond
-    systems can be approximated with a QDM that provides a low energy effective description of
-    the frustrated spins. Some correlation functions in QDMs are solvable using Pfaffian models
-    but in general they must be studied numerically.
+Because of the exotic nature of topological phases and their potential use for quantum information processing, there is great interest in the development of theoretical models which display these phases.
+Such models offer the possibility of furthering the understanding of these phases as well as providing possibly candidate experimental systems in which to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Martinis2015}.
+A variety of exactly soluble lattice models are known to support ground states with topological order that ranges from the simplest variety, so-called $Z_2$ topological order~\cite{Kitaev2003,Wen2003}, to those with non-Abelian anyonic excitations~\cite{Levin2005a,Kitaev2006a}.
+These exactly soluble models generally involve complex many-body interactions, and thus it is desirable to find simpler models supporting topological order that are closer to what is accessible experimentally.
 
-    In this paper we numerically study the quantum dimer pentamer model (QDPM) on the square
-    lattice at the RK point.  The QDPM contains an exact $Z_3$ local gauge symmetry due to the
-    introduction of pentamer objects and we believe it exhibits $Z_3$ topological order.
-    Pentamers are objects consisting of four dimers touching a vertex.  The Hilbert space
-    comprises all fully packed dimer and pentamer coverings. The presence or absence of a dimer
-    may be defined in terms of Ising degrees of freedom that live on the links of the square
-    lattice and this distinguishes it from the $Z_3$ toric code with three degrees of freedom on
-    the links. We show numerically that a liquid dimer pentamer phase exists at the RK point
-    with exponentially decaying dimer correlations. We also estimate the dimer and vison gaps
-    showing that the $Z_3$ visons are the lowest lying and most fundamental excitations.
+Among the simplest class of models displaying topological quantum liquid phases are those with local geometric constraints; the frustration inherent in these constraints inhibits the formation of symmetry breaking local order and given sufficient dynamics, such models may have symmetric liquid ground states.
+The simplest such geometrically constrained model is the quantum dimer model (QDM) describing dimer degrees of freedom living on the links of a lattice~\cite{Rokhsar1988,Moessner2008}; the hard-core, fully-packed QDM has a local constraint that requires exactly one dimer touching each vertex.
 
+\begin{figure}[b!]
+    \centering
+    \includegraphics[width=0.5\columnwidth]{QDPM_ex_config.pdf}
+    \caption{Example of an allowed configuration in the quantum dimer-pentamer model.}
+    \label{fig:QDPMex}
+\end{figure}
+
+While on non-bipartite lattices, the QDM posses a topologically ordered ground state~\cite{Moessner2001a,Fendley2002}, on the square lattice there is only a liquid ground state at an isolated critical quantum point~\cite{Leung1996,Syljuasen2006}.
+If the hard-core constraint of the QDM is relaxed to a parity constraint such that each vertex much have an even (odd) number of dimers touching each vertex, the simplest non-trivial dynamics lead to the (odd) toric code which has a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
+
+The existence of topologically ordered ground states in dimer-based models is intimately related to the local constraint which imposes a local gauge symmetry in the low energy Hilbert space; the topological order that arises is directly related to a discrete gauge theory with the appropriate local gauge constraint~\cite{Moessner2001}.
+
+Given that these models with dimer degrees of freedom and local constraints posses the simplest non-trivial local (Ising) Hilbert space at each link, they provide a (possibly) simpler route to engineering exotic phases; the local constraints constraint can often be enforced by a local potential energy penalty and the required dynamics are generally expected to arise at the lowest order non-trivial order in perturbation theory.
+Previous work as demonstrated that GQDM on the square lattice support gapped $Z_2$ topologically ordered phases as well as gapless quantum critical points.
+On non-bipartite lattices GQDM supported $Z_2$ topological order~\cite{Moessner2001a,Misguich2002} as well as doubled-semion phases~\cite{Qi2014,Buerschaper2014a}.
+A full characterization of all exotic phases that can exist within this framework is thus desirable.
+
+In this work we extend this paradigm to a new GQDM on the square lattice, what we term the quantum dimer-pentamer model (QDPM).
+In the QDPM, the local constraint is relaxed from that of the QDM to require that either $1$ or $4$ dimers to touching each vertex, as shown in figure \figref{fig:QDPMex}.
+Correspondingly, the QDPM extends the Hilbert space of the QDM to include both fully-packed hard-core dimer configurations, as well as those pentamers, four dimers touch a vertex.
+To give the system dynamics, the Hamiltonian includes terms that incorporate the simplest non-trivial dynamics that don't violate the local constraint.
+
+We present a numerical study of the ground state of the QDPM at an exactly soluble point and demonstrate the the soluble point represents a gapped, disordered quantum liquid phase.
+Using Monte Carlo calculations, we explicitly demonstrate the absence of symmetry breaking order and the exponential decay of correlation functions; by computing imaginary-time correlation functions, we find that the RK point is gapped in the thermodynamic limit.
+By construction the QDPM has an exact local $Z_3$ symmetry and conserves a $Z_3$ topological winding number.
+Thus the QDPM has a 9-fold topological degeneracy on the torus.
+Thus we argue that the ground state of the QDPM posses $Z_3$ topological order.
+
+This this paper is organized as follows.
+In \secref{sec:Background} we provide relevant background for the QDM and related models.
+In \secref{sec:QDPM} we present the details of the QPDM.
+\secref{sec:MC} provides the results of a Monte Carlo study of the ground state of the QDPM at its exactly soluble point.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Background}
+\label{sec:Background}
+
+\subsection{Generalized quantum dimer models}
+\label{sec:GQDM}
+
+Here we will provide background about generalized quantum dimer models on the square lattice.
+We consider systems with Ising-like dimer degrees of freedom on each link, such that each link has either $0$ or $1$ dimers.
+The Hilbert space consists of configurations of dimers on the square lattice that satisfy a local constraint at each vertex; the simplest constraint is that of the hard-core fully-packed QDM where a single dimer must touch each vertex.
+We write this constraint as $n_v = 1$, where $n_v$ is the number of dimers that touch a vertex.
+Other unique, non-trivial constraints are $n_v=2$ and the parity constraints $n_v\mod2 =0$ and  $n_v\mod2 =1$ (see \figref{fig:GQDMexamples}).
+
+The Hamiltonian of a GQDM is of the form
+\begin{equation}
+H_{\rm{GQDM}} = -t \hat{T} + v \hat{V}
+\end{equation}
+where $\hat{T}$ is an off-diagonal kinetic term that preserves the constraint, $\hat{V}$ is a local potential energy term, and $v$ and $t$ are the strength of each term.
 
@@
 
-    \begin{table}[htpb]
+    \begin{table*}[htpb]
+    \setlength\tabcolsep{0.3cm}
         \centering
@@
         \label{tab:label}
-        \begin{tabular}{c c c c}
+        \begin{tabular}{l l l l l}
             \hline\hline
-         L            & 8x8 Gap                               & 12x12                            & 16x16                               & 18x18 \\ 
+         L            		& 8x8                               		& 12x12                            		& 16x16					& 18x18 \\ 
             \hline                                                                                                                           
@@
             \hline                                                                                                                           
-         Dimer        &  $ 0.03230 \pm 0.01142$               & $ 0.01430 \pm 0.00034 $          & $0.00806 \pm 0.00023$               & \\
-         $Z_2$ origin &  $ 0.00787 \pm 5.3\times 10^{-6} $    & $ 0.00344 \pm 9.0\times 10^{-7}$ & $0.00198 \pm 3.8\times 10^{-6} $    &  \\
+         Dimer        	&  $ 3(1) \times 10^{-2}$        	& $ 1.43(3) \times 10^{-2}$	& $0.81(2)\times 10^{-2}$  	& \\
+         $Z_2$ origin 	&  $ 0.787?(5)\times 10^{-2} $ 	& $ 0.344? (1)\times 10^{-2}$ 	& $0.198? (4)\times 10^{-2} $ 	&  \\
          $Z_3$ origin 	&  NA                                   	& NA                               		& NA                                  	& \\
@@
             \hline                                                                                                                          
-         Dimer origin &  $ 0.00419 \pm 8.1\times 10^{-6} $    & $ 0.00406 \pm 1.7\times 10^{-5} $ & $0.00429 \pm 6.6\times 10^{-6} $   &  $ 0.00405 \pm 1.6\times 10^{-5} $\\
-         $Z_2$ origin &  $ 0.00216 \pm 1.5\times 10^{-6} $    & $ 0.00141 \pm 8.4\times 10^{-7} $ & $0.00129 \pm 1.8\times 10^{-6} $   &  $ 0.00126 \pm 1.7\times 10^{-6} $\\
-         $Z_3$ origin &  $ 0.00346 \pm 3.8\times 10^{-6} $    & $ 0.00348 \pm 5.1\times 10^{-6} $ & $0.00359 \pm 3.5\times 10^{-6} $   &  $ 0.00355 \pm 3.3\times 10^{-6}$\\
+         Dimer origin 	&  $ 0.419(1)\times 10^{-2} $    	& $ 0.406(2)\times 10^{-2} $ 	& $0.429(1)\times 10^{-2} $   	&  $ 0.405(2)\times 10^{-2} $\\
+         $Z_2$ origin 	&  $ 0.216?(2)\times 10^{-2} $ 	& $ 0.141?(1)\times 10^{-2} $ 	& $0.129?(2)\times 10^{-2} $	&  $ 0.126?(2)\times 10^{-2} $\\
+         $Z_3$ origin 	&  $ 0.346?(4)\times 10^{-2} $ 	& $ 0.348(1)\times 10^{-2} $ 	& $0.359?(4)\times 10^{-2} $	&  $ 0.355?(3)\times 10^{-2}$\\
             \hline                                                                                                                          
@@
             \hline                                                                                                                          
-         Dimer origin &                                       & $ 0.02075 \pm 8.9\times 10^{-5} $ & $0.02049 \pm 0.00011 $             &  $ $ \\
-         $Z_2$ origin &                                       & $ 0.00615 \pm 2.2\times 10^{-6} $ & $0.00614 \pm 2.8\times 10^{-6} $   &  $ $ \\
-         $Z_3$ origin &                                       & $ 0.01939 \pm 2.2\times 10^{-5} $ & $0.01927 \pm 0.00002 $             &  $ $  
+         Dimer origin 	&                                       		& $ 2.075(9)\times 10^{-2} $ 	& $2.05(1) \times 10^{-2}$		&  $ $ \\
+         $Z_2$ origin 	&                                       		& $ 0.615?(2)\times 10^{-2} $ 	& $0.614?(3)\times 10^{-2} $	&  $ $ \\
+         $Z_3$ origin 	&                                       		& $ 1.939(2)\times 10^{-2} $ 	& $1.927(2)\times 10^{-2} $	&  $ $  
         \end{tabular}
-    \end{table}
+    \end{table*}
 

### 2015-09-09 qdpm_paper.tex
Worked on section II

@@
 We write this constraint as $n_v = 1$, where $n_v$ is the number of dimers that touch a vertex.
-Other unique, non-trivial constraints are $n_v=2$ and the parity constraints $n_v\mod2 =0$ and  $n_v\mod2 =1$ (see \figref{fig:GQDMexamples}).
+We can distinguish between number constraints of the form $n_v = n_0$ and parity constraints of the form $n_v \mod 2 = 0,1$.
+The unique, non-trivial constraints of this form are the number constraints $n_v=1,2$ and the parity constraints $n_v\mod2 =0,1$ and  $n_v\mod2 =1$ (see \figref{fig:GQDMexamples}).
+
+The presence of such local constraints implies all physical states in the Hilbert space are invariant under local gauge transformations at each vertex, $G_v$.
 
@@
 \end{equation}
-where $\hat{T}$ is an off-diagonal kinetic term that preserves the constraint, $\hat{V}$ is a local potential energy term, and $v$ and $t$ are the strength of each term.
+where $\hat{T}$ is an off-diagonal kinetic term that preserves the constraint, $\hat{V}$ is a local potential energy term, and $v$ and $t$ parametrize the strength of each term.
+We will take the kinetic term $\hat{T}$ to be the dynamics which preserved the constraint; for example in the QDM $\hat{T}$ is the sum of all possible ``plaquette" flip terms acting on plaquettes with parallel dimers.
+\begin{equation}
+    \label{}
+    \hat{T} = \sum_{\bplqt} 
+            \left|
+                \vrtplqt
+            \right\rangle
+            \left\langle
+                \hrzplqt
+            \right|
+            +
+            \mathrm{h.c.}
+\end{equation}
 

### 2015-09-16 qdpm_paper.tex
pulling
added U(1) winding number measured on qdpm, a figure of gray heat map of dimer correlations, qdpm example config, table moddifications

@@
 
+            \begin{figure}[htpb]
+                \centering
+                \includegraphics[width=0.8\linewidth]{u1_wind_qdpm.pdf}
+                \caption{The $U(1)$ winding number as measured in the QDPM on a $8\times8$ lattice
+                with a dimer to pentamer move fraction (need a name for this fraction HERE) of 0.5.}
+                \label{fig:u1_wind_qdpm}
+            \end{figure}
+
     \subsection{QDM on Square lattice}
@@
     \subsection{Liquid}
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=0.8\linewidth]{dimer_gry_scale_qdpm.pdf}
+        \caption{Gray scale (actualy data) of the dimer corelation between the dimer in the upper
+        left corner and other dimers on a $16\times16$ lattice.}
+        \label{fig:dimer_gry_scale_qdpm}
+    \end{figure}
 
@@
 
+    \begin{table*}[htpb]
+    \setlength\tabcolsep{0.3cm}
+        \centering
+        \caption{$\Delta \tau = 150$}
+        \label{tab:label}
+        \begin{tabular}{l l l l}
+            \hline\hline
+                        & Dimer                 & $Z_2$ double ($L/2$)  &  $Z_3$ single (origin)     \\   
+            \hline
+            frac 1.0    &  &  & \\
+            $8\times8$  &                       &                       &                            \\
+            $12\times12$&                       &                       &                            \\
+            $16\times16$&                       &                       &                            \\
+            $18\times18$&                       &                       &                            \\
+            \hline
+            frac 0.9    &  &  & \\
+            $8\times8$  & $3.5(3)\times10^{-3}$ & $1.02(8)\times10^{-3}$&  $3.07(4)\times10^{-3}$    \\
+            $12\times12$&                       &                       &                            \\
+            $16\times16$&                       &                       &                            \\
+            $18\times18$&                       &                       &                            \\
+            \hline
+            frac 0.5    &  &  & \\
+            $8\times8$  & $1.(8)\times10^{-2}$  &  $5.(6)\times10^{-4}$ & $1.7(5)\times10^{-2}$      \\
+            $12\times12$& $1.4(8)\times10^{-2}$ &                       &                            \\
+            $16\times16$&                       &                       &                            \\
+            $18\times18$&                       &                       &                            \\
+        \end{tabular}
+    \end{table*}
+
     \subsection{Imaginary time vison correlations}

### 2015-09-28 qdpm_paper.tex
a few minor chages. Gap estimates should be more correct
better images

--- 2015-09-09 qdpm_paper.tex
@@
 \label{sec:GQDM}
+
+\begin{figure}[htpb]
+    \centering
+    \includegraphics[width=0.8\linewidth]{example_local_constraints.pdf}
+    \caption{Clockwise from the upper left panel we show an example of a QDM with constraints: one
+    dimer, two dimers, an even number of dimers, and and odd number of dimers touching each vertex.}
+    \label{fig:example_local_constraints}
+\end{figure}
 
@@
 
+            \begin{figure}[htpb]
+                \centering
+                \includegraphics[width=0.8\linewidth]{u1_wind_qdpm.pdf}
+                \caption{The $U(1)$ winding number as measured in the QDPM on a $16\times16$ lattice
+                with a dimer to pentamer move fraction (need a name for this fraction HERE) of 0.5.}
+                \label{fig:u1_wind_qdpm}
+            \end{figure}
+
     \subsection{QDM on Square lattice}
@@
 
+%    \begin{table*}[htpb]
+%    \setlength\tabcolsep{0.3cm}
+%        \centering
+%        \caption{$\Delta \tau = 150$}
+%        \label{tab:label}
+%        \begin{tabular}{l l l l l}
+%            \hline\hline
+%         L            		& 8x8                               		& 12x12                            		& 16x16					& 18x18 \\ 
+%            \hline                                                                                                                           
+%         frac 1.0     	&                                       		&                                  		&                                    		&  \\
+%            \hline                                                                                                                           
+%         Dimer        	&  $ 3(1) \times 10^{-2}$        	& $ 1.43(3) \times 10^{-2}$	& $0.81(2)\times 10^{-2}$  	& \\
+%         $Z_2$ origin 	&  $ 0.787?(5)\times 10^{-2} $ 	& $ 0.344? (1)\times 10^{-2}$ 	& $0.198? (4)\times 10^{-2} $ 	&  \\
+%         $Z_3$ origin 	&  NA                                   	& NA                               		& NA                                  	& \\
+%            \hline                                                                                                                         
+%         frac 0.9     	&                                       		&                                  		&                                     		&  \\
+%            \hline                                                                                                                          
+%         Dimer origin 	&  $ 0.419(1)\times 10^{-2} $    	& $ 0.406(2)\times 10^{-2} $ 	& $0.429(1)\times 10^{-2} $   	&  $ 0.405(2)\times 10^{-2} $\\
+%         $Z_2$ origin 	&  $ 0.216?(2)\times 10^{-2} $ 	& $ 0.141?(1)\times 10^{-2} $ 	& $0.129?(2)\times 10^{-2} $	&  $ 0.126?(2)\times 10^{-2} $\\
+%         $Z_3$ origin 	&  $ 0.346?(4)\times 10^{-2} $ 	& $ 0.348(1)\times 10^{-2} $ 	& $0.359?(4)\times 10^{-2} $	&  $ 0.355?(3)\times 10^{-2}$\\
+%            \hline                                                                                                                          
+%         frac 0.5     	&                                       		&                                   		&                                    		& \\
+%            \hline                                                                                                                          
+%         Dimer origin 	&                                       		& $ 2.075(9)\times 10^{-2} $ 	& $2.05(1) \times 10^{-2}$		&  $ $ \\
+%         $Z_2$ origin 	&                                       		& $ 0.615?(2)\times 10^{-2} $ 	& $0.614?(3)\times 10^{-2} $	&  $ $ \\
+%         $Z_3$ origin 	&                                       		& $ 1.939(2)\times 10^{-2} $ 	& $1.927(2)\times 10^{-2} $	&  $ $  
+%        \end{tabular}
+%    \end{table*}
+
     \begin{table*}[htpb]
@@
         \centering
-        \caption{$\Delta \tau = 150$}
+        \caption{$\Delta \tau = 250$}
         \label{tab:label}
-        \begin{tabular}{l l l l l}
+        \begin{tabular}{l l l l}
             \hline\hline
-         L            		& 8x8                               		& 12x12                            		& 16x16					& 18x18 \\ 
+                        & Dimer                 & $Z_2$ double ($L/2$)  &  $Z_3$ single (origin)     \\   
             \hline
-         frac 1.0     	&                                       		&                                  		&                                    		&  \\
+            frac 1.0    &  &  & \\
+            $8\times8$  & $3.(3)\times10^{-2}$  &                       &                            \\
+            $12\times12$& $1.4(5)\times10^{-2}$ &                       &                            \\
+            $16\times16$&                       &                       &                            \\
+            $18\times18$&                       &                       &                            \\
             \hline
-         Dimer        	&  $ 3(1) \times 10^{-2}$        	& $ 1.43(3) \times 10^{-2}$	& $0.81(2)\times 10^{-2}$  	& \\
-         $Z_2$ origin 	&  $ 0.787?(5)\times 10^{-2} $ 	& $ 0.344? (1)\times 10^{-2}$ 	& $0.198? (4)\times 10^{-2} $ 	&  \\
-         $Z_3$ origin 	&  NA                                   	& NA                               		& NA                                  	& \\
+            frac 0.9    &  &  & \\
+            $8\times8$  & $0.35(6)\times10^{-2}$&$0.102(1)\times10^{-2}$& $0.306(3)\times10^{-2}$     \\
+            $12\times12$& $0.35(7)\times10^{-2}$&$0.25(5)\times10^{-2}$ & $0.316(4)\times10^{-2}$    \\
+            $16\times16$& $0.35(7)\times10^{-2}$&$0.36(3)\times10^{-2}$ & $0.316(8)\times10^{-2}$    \\
+            $18\times18$&                       &                       &                            \\
             \hline
-         frac 0.9     	&                                       		&                                  		&                                     		&  \\
-            \hline                                                                                                                          
-         Dimer origin 	&  $ 0.419(1)\times 10^{-2} $    	& $ 0.406(2)\times 10^{-2} $ 	& $0.429(1)\times 10^{-2} $   	&  $ 0.405(2)\times 10^{-2} $\\
-         $Z_2$ origin 	&  $ 0.216?(2)\times 10^{-2} $ 	& $ 0.141?(1)\times 10^{-2} $ 	& $0.129?(2)\times 10^{-2} $	&  $ 0.126?(2)\times 10^{-2} $\\
-         $Z_3$ origin 	&  $ 0.346?(4)\times 10^{-2} $ 	& $ 0.348(1)\times 10^{-2} $ 	& $0.359?(4)\times 10^{-2} $	&  $ 0.355?(3)\times 10^{-2}$\\
-            \hline                                                                                                                          
-         frac 0.5     	&                                       		&                                   		&                                    		& \\
-            \hline                                                                                                                          
-         Dimer origin 	&                                       		& $ 2.075(9)\times 10^{-2} $ 	& $2.05(1) \times 10^{-2}$		&  $ $ \\
-         $Z_2$ origin 	&                                       		& $ 0.615?(2)\times 10^{-2} $ 	& $0.614?(3)\times 10^{-2} $	&  $ $ \\
-         $Z_3$ origin 	&                                       		& $ 1.939(2)\times 10^{-2} $ 	& $1.927(2)\times 10^{-2} $	&  $ $  
+            frac 0.5    &  &  & \\
+            $8\times8$  & $1.0(6)\times10^{-2}$ &$0.05(5)\times10^{-2}$ & $1.7(1)\times10^{-2}$     \\
+            $12\times12$& $1.5(7)\times10^{-2}$ &                       & $1.9(7)\times10^{-2}$      \\
+            $16\times16$&                       &                       &                            \\
+            $18\times18$&                       &                       &                            \\
         \end{tabular}

### 2015-10-07 qdpm_paper.tex
quick
Started appedix on gap calculations

@@
         In the QDPM Ising degrees of freedom live on the links of the lattice.
-        The operator $\hat{\sigma}^x_l$ acts on these links and has 
+        The operator $\hat{\sigma}^x_l$ acts on these links with 
         eigenvalues $\sigma_l = \pm 1$, where $\sigma_l$ is the
@@
 
-        We work specifically at the RK point at which the ground state wave function
+        We work specifically at the RK point where the ground state wave function
         is an equal weighted superposition of fully packed dimer pentamer configurations
@@
 
-        The QDPM Hamiltonian
+        The QDPM Hamiltonian comprises the QDM Hamiltonian pluss additional terms coresponding to
+        the pentamer dynamics.
         \begin{equation}
@@
         \end{equation}
-
-        The pentamer terms in the Hamiltonian can be constructed with the dynamics shown in
+        Specificaly the penatamers pentamer terms are constructed with the dynamics shown in
         Fig.~\ref{fig:pentamer_moves}.  
@@
 \section{Estimating the Gap}
+    An exponetial decay of the spacial correlations shown in the previous sections 
+    suggeste a gap in the spectrum. However we would like to know if the lowest lying excitations are in the vison
+    or the dimer sector.  The energy gap of the dimer and vison exsitations can be estimated by investigating the dimer and
+    vison imaginary time correlations respectivly as outlined by Henley \cite{Henley2004a}. 
+    One changlenge in the gap estimates from the imaginary time correlations is going far enough out
+    in imaginary time. In appendix \ref{appendix_gap_err} we discuss our proccess in determining
+    that this systematic error is sufficinetly small which is necissary when compairing gap
+    estimates for different excitatoins.
 
-%    \begin{table*}[htpb]
-%    \setlength\tabcolsep{0.3cm}
-%        \centering
-%        \caption{$\Delta \tau = 150$}
-%        \label{tab:label}
-%        \begin{tabular}{l l l l l}
-%            \hline\hline
-%         L            		& 8x8                               		& 12x12                            		& 16x16					& 18x18 \\ 
-%            \hline                                                                                                                           
-%         frac 1.0     	&                                       		&                                  		&                                    		&  \\
-%            \hline                                                                                                                           
-%         Dimer        	&  $ 3(1) \times 10^{-2}$        	& $ 1.43(3) \times 10^{-2}$	& $0.81(2)\times 10^{-2}$  	& \\
-%         $Z_2$ origin 	&  $ 0.787?(5)\times 10^{-2} $ 	& $ 0.344? (1)\times 10^{-2}$ 	& $0.198? (4)\times 10^{-2} $ 	&  \\
-%         $Z_3$ origin 	&  NA                                   	& NA                               		& NA                                  	& \\
-%            \hline                                                                                                                         
-%         frac 0.9     	&                                       		&                                  		&                                     		&  \\
-%            \hline                                                                                                                          
-%         Dimer origin 	&  $ 0.419(1)\times 10^{-2} $    	& $ 0.406(2)\times 10^{-2} $ 	& $0.429(1)\times 10^{-2} $   	&  $ 0.405(2)\times 10^{-2} $\\
-%         $Z_2$ origin 	&  $ 0.216?(2)\times 10^{-2} $ 	& $ 0.141?(1)\times 10^{-2} $ 	& $0.129?(2)\times 10^{-2} $	&  $ 0.126?(2)\times 10^{-2} $\\
-%         $Z_3$ origin 	&  $ 0.346?(4)\times 10^{-2} $ 	& $ 0.348(1)\times 10^{-2} $ 	& $0.359?(4)\times 10^{-2} $	&  $ 0.355?(3)\times 10^{-2}$\\
-%            \hline                                                                                                                          
-%         frac 0.5     	&                                       		&                                   		&                                    		& \\
-%            \hline                                                                                                                          
-%         Dimer origin 	&                                       		& $ 2.075(9)\times 10^{-2} $ 	& $2.05(1) \times 10^{-2}$		&  $ $ \\
-%         $Z_2$ origin 	&                                       		& $ 0.615?(2)\times 10^{-2} $ 	& $0.614?(3)\times 10^{-2} $	&  $ $ \\
-%         $Z_3$ origin 	&                                       		& $ 1.939(2)\times 10^{-2} $ 	& $1.927(2)\times 10^{-2} $	&  $ $  
-%        \end{tabular}
-%    \end{table*}
+    %At the RK point the Hamiltonian is proportional to the matrix of transitions rates the eigen modes of wich describe the time evolution of the
+    %system. Since the Hamiltonian and the rate matrix share eigenvalues the lowest energy can be
+    %found by looking at the fit of the imaginary time correlations far out in imaginary time where
+    %the smalles exponetial dominates.
 
+    In this paper we only investigate the high symetry points in the Brillouin zone.
+
+    In Table~\ref{tab:gap_table} we show the estimates of the dimer gap, the double $Z_2$ vison gap
+    at $L/2$ and the $Z_3$ vison gap.
     \begin{table*}[htpb]
@@
         \caption{$\Delta \tau = 250$}
-        \label{tab:label}
+        \label{tab:gap_table}
         \begin{tabular}{l l l l}
@@
             frac 1.0    &  &  & \\
-            $8\times8$  & $3.(3)\times10^{-2}$  &                       &                            \\
-            $12\times12$& $1.4(5)\times10^{-2}$ &                       &                            \\
+            $8\times8$  & $3.24(5)\times10^{-2}$  &                       &                            \\
+            $12\times12$& $1.47(5)\times10^{-2}$ &                       &                            \\
             $16\times16$&                       &                       &                            \\
@@
             frac 0.9    &  &  & \\
-            $8\times8$  & $0.35(6)\times10^{-2}$&$0.102(1)\times10^{-2}$& $0.306(3)\times10^{-2}$     \\
-            $12\times12$& $0.35(7)\times10^{-2}$&$0.25(5)\times10^{-2}$ & $0.316(4)\times10^{-2}$    \\
-            $16\times16$& $0.35(7)\times10^{-2}$&$0.36(3)\times10^{-2}$ & $0.316(8)\times10^{-2}$    \\
-            $18\times18$&                       &                       &                            \\
+            $8\times8$  & $0.3549(9)\times10^{-2}$&$0.0993(3)\times10^{-2}$& $0.3069(3)\times10^{-2}$     \\
+            $12\times12$& $0.357(2)\times10^{-2} $&$0.256(2)\times10^{-2} $ & $0.3164(7)\times10^{-2}$    \\
+            $16\times16$& $0.357(3)\times10^{-2} $&$0.363(5)\times10^{-2} $ & $0.3170(9)\times10^{-2}$    \\
+            $18\times18$& $0.352(2)\times10^{-2} $&$0.419(3)\times10^{-2} $ & $0.3167(7)\times10^{-2}$    \\
             \hline
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+\section{Error in the Gap Estimations}
+\label{appendix_gap_err}
+
+When estimating the gap by calculating correlations in imaginary time one has to be sure
+that the range of imaginary time is appropriate otherwise it is not meaningful to compare the relative 
+sizes of the vison and dimer gaps. In
+%Fig.~\ref{fig:HERE} 
+we show the finite size scaling of the different gaps. For each gap estimation we wanted to reduce
+if not eliminate the systematic error due to and inadiquate range of imaginary time. This was
+accived by investegating the gap as a fuction of the lower cutoff in the exponential fit of. We
+extended the range of $\tau$ until the gap plataued and had little dependence on the cutoff. We show an
+example of the estimate of the $Z_3$ vison gap dependence on the lower cutoff of the fit for the
+$HERE\times HERE$ lattice with a fraction (HERE) of $0.9$ in 
+%Fig.~\ref{fig:}
+%\begin{figure}[htpb]
+%    \centering
+%    \includegraphics[width=0.8\linewidth]{name.ext}
+%    \caption{Name}
+%    \label{fig:name}
+%\end{figure}
+
+NOTE: There is also some systematic error in the discritization of time. This error falls off in the QDM
+as the number of flippable plaquestts. We assume this error it is small compared to the
+statistical error.
+
+\section{Imaginary time Vison Correlations}
+\label{appendix_tau_corr}
+
+    \subsection{$Z_2$ Single and Double Visons}
+
+        \subsubsection{Single Vison}
+            First we distiguish between the single and double vison correlation fuctions. We start with the
+            the described by Ivanov \cite{Ivanov2004} for rewriting the single vison correlation function in a
+            convieient form to implement numericaly. 
+            The correlation function between two point visons $V(\bm{x}_1,\tau_1)$, and $V(\bm{x}_2,\tau_2)$ at 
+            points in space $\bm{x}_1$, $\bm{x}_2$ and in imaginary time $\tau_1$ and $\tau_2$ can be writen as
+            \begin{equation}
+                C_{\mathrm{single}}(\bm{x}_2-\bm{x}_1,\tau_2 - \tau_1) = \langle V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_2) \rangle
+            \end{equation}
+            For the $Z_2$ vison $V(\bm{x}_i,\tau_j)^2=1$ and inserting this for $i=2$ and $j=1$ between the two vison
+            operators in the above equation we get 
+            \begin{equation}
+                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_2) = \big(V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_1)\big)
+                \big( V(\bm{x}_2,\tau_1) V(\bm{x}_2,\tau_2) \big),
+                \label{eqn:expanded_z2_v_tau_cor}
+            \end{equation}
+
+            The first product in Eq.~\ref{eqn:expanded_z2_v_tau_cor} on the RHS is a 
+            string operator between two points on the lattice at a given imaginary time $\tau_2$ 
+            \begin{equation}
+                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_1) = (-1)^{n},
+                \label{eqn:simp_z2_vison_phase}
+            \end{equation}
+            $n$ being the number of dimers intersecting the path between $\bm{x}_1$ and $\bm{x}_1$. This number
+            can not depend on the path so one must choose a meathod of ``gauge fixing''. This can be done
+            by choosing an imutable bacround configureation which also changes the phase of the
+            operator $V_{12}(\tau)$ in the same way as the dynamic dimers. 
+            Including the gauge fixing Eqn.~\ref{eqn:simp_z2_vison_phase} becomes
+            \begin{equation}
+                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_1) = (-1)^{n+n_{\mathrm{backround}}}.
+            \end{equation}
+
+            The second product in Eq.~\ref{eqn:expanded_z2_v_tau_cor} on the RHS is a string operator 
+            between two points at the location but at different imaginary time $\tau_2$. 
+            In order for the full path in space and
+            imaginary time to maintain its path independece it can be shown that the phase 
+            changes with every plaquet flip at $\bm{x}_2$. So
+            \begin{equation}
+                V(\bm{x}_2,\tau_1) V(\bm{x}_2,\tau_2) = (-1)^{n_{\mathrm{flipped}}},
+            \end{equation}
+            where $n_{\mathrm{flipped}}$ is the number of times the plaquette at $\bm{x}_2$ is flipped.
+            Finaly Eq.~\ref{eqn:expanded_z2_v_tau_cor} can be expresed as 
+            \begin{equation}
+                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_2) =
+                (-1)^{n+n_{\mathrm{backround}+n_{\mathrm{flipped}}}}.
+            \end{equation}
+            The gap that is being estimated by looking at the single vison correlatoin function is
+            the energy gap of a single vison exciation, only physical when the system has
+            boundries but measureable in any system topology.
+
+        \subsubsection{Double Vison}
+            Calculating the doublue vison imaginary time correlation funciton
+            \begin{equation}
+                C_{\mathrm{double}}(\bm{x}_{12},\tau_2 - \tau_1) = \langle V(\bm{x}_1,\tau_1)V(\bm{x}_2,\tau_1) V(\bm{x}_1,\tau_2)V(\bm{x}_2,\tau_2) \rangle
+            \end{equation}
+            where the first product on the RHS is the string operator acting along path between points
+            $\bm{x}_1$ and $\bm{x}_1$ at imaginary time $\tau_1$ and the second product is the
+            string operator along a path between the same points but at $\tau_2$.
+
+            by looking at the double vison correlation function in imaginary time the gap of a pair
+            of visons is extracted.
+
+    \subsection{$Z_3$ Single and Double Visons}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{apsrev4-1}

### 2015-10-14 qdpm_paper.tex
Minor changes and a figure of QDM and QDPM finite size scaling of dimer gap

@@
         \begin{equation}
-            H_{\mathrm{QDPM}} = H_{\mathrm{QDM}} + \mathrm{pentamer\ terms}
+            H_{\mathrm{QDPM}} = H_{\mathrm{QDM}} + (1-\gamma)\mathrm{pentamer\ terms}
+            ,
         \end{equation}
-        Specificaly the penatamers pentamer terms are constructed with the dynamics shown in
+        where $\gamma$ is a single parameter that tunes the relative energy scale of the petamer
+        terms to the QDM terms in the Hamiltonian.
+
+        The penatamers pentamer terms are constructed with the dynamics shown in
         Fig.~\ref{fig:pentamer_moves}.  
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Dimer Correlation Results}
+\section{Spacial Dimer Correlation Results}
 
+    In this section we discuss the dimer dimer correlation function
+    \begin{equation}
+        C_{\mathrm{dimer}} = \langle d_0 d_r \rangle - \langle d_0 \rangle   \langle d_r \rangle   
+        ,
+    \end{equation}
+    where $d_i$ is the ising degrees of freedom on link i.
+    In order for the QDPM to exhibit topological order there we must find that it is in a gaped
+    dimer liquid phase. It is likely that the QDPM in a liquid phase at the RK point because there 
+    we find no evedence of broken symmetries in the system sizes up to $32x32$. As an example of the
+    absence of broken symmetries we show
+    the dimer correlation function measuered between a single dimer and all other dimers on the
+    lattice in Fig.~\ref{fig:fig:dimer_gry_scale_qdpm} for a $16x16$ lattice.
     \subsection{Liquid}
@@
         \caption{Gray scale (actualy data) of the dimer corelation between the dimer in the upper
-        left corner and other dimers on a $16\times16$ lattice.}
+        left corner (colored red) and other dimers on a $16\times16$ lattice.}
         \label{fig:dimer_gry_scale_qdpm}
@@
 
-    \subsection{Correlation functions}
-
-    \begin{equation}
-        C_{\mathrm{dimer}} = \langle d_0 d_r \rangle - \langle d_0 \rangle   \langle d_r \rangle   
-    \end{equation}
-
+    We also find exponetialy decaying dimer correlations 
+    In Fig.~\ref{fig:fig:spacial_dmr_cor} we show the dimer correlations between horizontal dimers
+    in a vertical column. We find the correlation length to be $HERE$.
     \begin{figure}[htpb]
@@
 \section{Estimating the Gap}
-    An exponetial decay of the spacial correlations shown in the previous sections 
-    suggeste a gap in the spectrum. However we would like to know if the lowest lying excitations are in the vison
-    or the dimer sector.  The energy gap of the dimer and vison exsitations can be estimated by investigating the dimer and
+    The exponetial decay of the spacial correlations shown in the previous sections 
+    suggest a gap in the spectrum though it is important to determine if the lowest lying
+    excitations are in the vison-like
+    or the dimer-like.  The energy gap of the dimer-like and vison-like excitations can be estimated 
+    by investigating the dimer and
     vison imaginary time correlations respectivly as outlined by Henley \cite{Henley2004a}. 
-    One changlenge in the gap estimates from the imaginary time correlations is going far enough out
-    in imaginary time. In appendix \ref{appendix_gap_err} we discuss our proccess in determining
-    that this systematic error is sufficinetly small which is necissary when compairing gap
-    estimates for different excitatoins.
+    One changlenge in this type of gap estimate is in resloving the correlation functions far enough out
+    in imaginary time. In appendix \ref{appendix_gap_err} we discuss our methods used to determine
+    that this particular source of systematic error is sufficinetly comparied to the gap
+    estimates for different types of excitatoins.
 
@@
 
-    In this paper we only investigate the high symetry points in the Brillouin zone.
-
+    In this paper we only investigate the gap at high symetry points in the Brillouin zone. 
     In Table~\ref{tab:gap_table} we show the estimates of the dimer gap, the double $Z_2$ vison gap
@@
         \centering
-        \caption{$\Delta \tau = 250$}
+        %\caption{$\Delta \tau = ??$}
         \label{tab:gap_table}
@@
             \hline
-            frac 1.0    &  &  & \\
+            $\gamma=1.0$ $(\Delta \tau =250)$    &  &  & \\
             $8\times8$  & $3.24(5)\times10^{-2}$ &                       &                            \\
             $12\times12$& $1.47(5)\times10^{-2}$ &                       &                            \\
-            $16\times16$&                       &                       &                            \\
-            $18\times18$&                       &                       &                            \\
+            $16\times16$& $0.66(3)\times10^{-2}$ &                       &                            \\
+            $18\times18$& $0.64(2)\times10^{-2}$ &                       &                            \\
             \hline
-            frac 0.9    &  &  & \\
+            $\gamma=0.9$ $(\Delta \tau =500)$    &  &  & \\
             $8\times8$  & $0.3549(9)\times10^{-2}$&$0.0993(3)\times10^{-2}$& $0.3069(3)\times10^{-2}$     \\
@@
             \hline
-            frac 0.5    &  &  & \\
+            $\gamma=0.5$    & & & \\
             $8\times8$  & $1.0(6)\times10^{-2}$ &$0.05(5)\times10^{-2}$ & $1.7(1)\times10^{-2}$     \\
@@
     \end{table*}
-
-    \subsection{Imaginary time vison correlations}
+    This table shows that the QDPM gap is relativly constant as the system size is increased and
+    that the vison gap is lower than the dimer gap. In Fig.~\ref{fig:qdm_qdpm_gap} we show the
+    finite size scaling of the dimer gap for both the QDM and the QDPM.
     \begin{figure}[htpb]
         \centering
-        \includegraphics[width=0.8\linewidth]{z2_origin_vison_time_cor.pdf}
-        \caption{Imaginary time $z_2$ \textit{single} vison correlations at the origin in the QDM model (red) and QDPM
-        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$.}
-        \label{fig:name}
+        \includegraphics[width=0.8\linewidth]{qdm_vs_qdpm_dmr_gap.pdf}
+        \caption{Here we show the finite size scaling of the dimer gap for both the QDM and the
+        QDPM.}
+        \label{fig:qdm_qdpm_gap}
     \end{figure}
 
-    \subsection{Imaginary time dimer correlations}
-    \begin{figure}[htpb]
-        \centering
-        \includegraphics[width=0.8\linewidth]{dimer_origin_time_cor.pdf}
-        \caption{Imaginary time dimer correlations of a single dimer in the QDM model (red) and QDPM
-        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$. }
-        \label{fig:}
-
-    \end{figure}
+%    \subsection{Imaginary time vison correlations}
+%    \begin{figure}[htpb]
+%        \centering
+%        \includegraphics[width=0.8\linewidth]{z2_origin_vison_time_cor.pdf}
+%        \caption{Imaginary time $z_2$ \textit{single} vison correlations at the origin in the QDM model (red) and QDPM
+%        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$.}
+%        \label{fig:name}
+%    \end{figure}
+%
+%    \subsection{Imaginary time dimer correlations}
+%    \begin{figure}[htpb]
+%        \centering
+%        \includegraphics[width=0.8\linewidth]{dimer_origin_time_cor.pdf}
+%        \caption{Imaginary time dimer correlations of a single dimer in the QDM model (red) and QDPM
+%        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$. }
+%        \label{fig:}
+%
+%    \end{figure}
 

### 2015-10-14 qdpm_paper.tex
small fix

@@
         \includegraphics[width=0.8\linewidth]{dimer_gry_scale_qdpm.pdf}
-        \caption{Gray scale (actualy data) of the dimer corelation between the dimer in the upper
-        left corner (colored red) and other dimers on a $16\times16$ lattice.}
+        \caption{Gray scale (actual data) of the dimer corelation between the dimer in the upper
+        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
+        dimers in the upperleft corner are colored red because they are off the scale shown at the
+        botom of the figure.}
         \label{fig:dimer_gry_scale_qdpm}

### 2016-04-13 qdpm_paper.tex
first commit in a while. Started refining the text and equations.

@@
 
-    Now we will introduce the toric code on the square lattice in some detail to sever as a point of reference and
-    comparison for the following discussion of the $Z_3$ case. The toric code Hamiltonian is given by
+    Now we will introduce the toric code on the square lattice which will sever as a reference and
+    point of comparison to the discussion of the $Z_3$ case. The toric code Hamiltonian is given by
     %
@@
     %
-    where the operator $A_v$ acts on the vertex $v$ and the sum over $v$ is the sum over all vertices. 
-    The operator $B_p$ acts on a plaquette $p$ and the sum over $p$ is the sum over all
-    plaquettes. In the $Z_2$ toric code, Ising degrees of freedom live on the links of the
-    lattice. Explicitly the operators $A_v$ and $B_p$ can be expressed as
+    where the operator $A_v$ ($B_p$) acts on the vertex $v$ (plaquette $p$), and the sum over $v$ ($p$) 
+    is the sum over all vertices (plaquettes). 
+    In the toric code, Ising degrees of freedom live on the links of the
+    lattice and the operators $A_v$ and $B_p$ can be expressed as
     %
@@
     %
-    The products are over the links adjacent to vertex $v$ and on the edges of plaquette $p$ for
-    $A_v$ and $B_p$ respectively. Since all $A_v$ operators commute with each other, all
-    $B_p$ operators commute with each other and $A_v$ commutes with $B_p$ even if they share
-    links (commute because they
-    can only share an even number of links) then the Hamiltonian can be solved term by term.
+    The products are over the links touching vertex $v$ and the edges of plaquette $p$ for
+    $A_v$ and $B_p$ respectively. It is not difficult to show that 
+    $[A_v,A_{v'}]=0$ for all $v$ and $v'$, 
+    $[B_p,B_{p'}]=0$ for all $p$ and $p'$, and $[A_v,B_p]=0$. The comutation relation between $A$
+    and $B$ holds even if they share links because they
+    can only share an even number of links. Given the commutation relations,
+    the toric Hamiltonian can be solved term by term.
 
-    Without a rigorous solution it is possible to guess at the form of the Toric code
-    ground state wave function. The first term in \ref{eqn:toric_code_ham} is maximized ($H_t$
-    minimized) when an even number of links touching a vertex are spin up or down in the
+    Even without a rigorous solution it is possible to guess at the form of the Toric code
+    ground state wave function. The first term in \ref{eqn:toric_code_ham} is maximized 
+    when an even number of links touching each vertex are spin up or down in the
     $\sigma^z$ basis. By coloring the links of all down spins the groundstate will
@@
 
-    NEED HERE Some stuff about plaquette flux ?? -> $B_p | \Psi \rangle = | \Psi \rangle$ -> only true if
-    grnd state as no vortices
-
-    NEED HERE String operators. The electric and magnetic string operators are respectively
+    The electric and magnetic string operators are
     \begin{equation}
@@
     \end{equation}
-    where the path is denoted by $\Gamma$. The path of the electric string operator is along the
-    links of the lattice and if this path is not closed then the operator
-    creates a pair of excitations. These excitations are defects in the system 
-    that can be thought of as electric charges that live at the
-    end of the unclosed string. Each of these electric defects has an energy costs of $2J_e$. 
-    The path of the magnetic string operator runs perpendicular to the links
-    and starts and ends on the dual lattice. An unclosed magnetic path results in two magnetic
-    excitations on the at the ends of the magnetic string each costing $2J_m$ each.
+    where the path is denoted by $\Gamma$. The electric string operator acts along the
+    links whereas the magnetic string operator acts along a path that perpendicularly
+    intersects the links. 
+    Electric and magnetic excitations are created when the string operator acts on an unclosed path. 
+    The electric excitations create monomer defects in the lattice at the end of the string, 
+    each of defects costing energy of $2J_e$. 
+    The magnetic excitations, which are 
+    are variational excited states  orthogonal
+    to the groundstate, create excitations at the ends in the ceter of two plaquettes.
+    Each end of the magnetic
+    string, a vison, costs energy of $2J_m$.
 
-    Using a nontrivial path (genus of system $>0$) one can move between topological sectors using $S_e$ and determine
-    the topological sector the system is in using $S_m$. On a torus, acting with $S_e$ along a
-    path that encloses either the major or minor axis of the torus changes the topological sector.
-    In general there are $4^g$ topological sectors where $g$ is the
-    genus of the system. For a torus then there are four topological sectors. If These can be
-    measuerd using the $S_m$ operator on a ...
+    operating on a nontrivial path (genus of system $>0$) with $S_e$ changes the topological sector.
+    The current topological sector can be determined
+    by acting around the congugate path with $S_m$, e.g. on a torus, acting with $S_e$ along a
+    path that encloses the major or minor axis changes the topological sector and acting on a path
+    that encloses the minor axis with $S_m$ measures the topological sector.
+    As defined the magnetic string can only produce two different values called winding number.
+    Therefore, there are $4^g$ topological sectors on the torus where $g$ is the
+    genus of the system.
 
-    \subsection{$Z_3$ Toric Code}
+    \subsection{$Z_3$ Toric Code on the Square Lattice}
+        In the $Z_3$ toric three degrees of freedom live on each link.
         We can represent the $Z_3$ algebra through the following expressions
@@
         %
-        where the operators $E_l$ and $A_l$ act on a given link $l$ and are analogous to the electric field and vector potential
-        respectively. 
-        By assigning orientations to the links between two vertices we can define 3 unique
-        link ``values'' pictorially. 
+        where the operators $E_l$ and $A_l$ act on a given link $l$ and are analogous to the 
+        electric field and vector potential respectively. 
+        By assigning orientations to the links between two vertices we can define the three degrees of
+        freedom pictorially. 
         %
@@
         % 
-        In this way we can define $e^{iA_l}$ as the operator $Q$ which acts on the links in the
+        To simplify notation, we define $e^{iA_l}$ as the operator $Q$ which acts on the links in the
         following way
@@
                 & Q^\dagger_{vv'}  | \leftarrowlink \rangle = | \emptylink \rangle
-                ,
+                .
             \end{split}
@@
         \end{equation}
-        where the link is specified by the two vertices it connects and the operator
-        $Q^\dagger_{vv'}$ acts in a direction from vertex $v$ to vertex $v'$. By changing the
-        direction in which $Q$ operates we can express it in terms of its hermitian conjugate. 
+        The link is specified by the two vertices it connects. The operator
+        $Q^\dagger_{vv'}$ acts in the direction from the first subscript to the second subscript, in
+        this case denoted as $v$ and $v'$. 
+        Changing the direction in which $Q$ operates is equivalent to taking the hermitian conjugate
+        of the operator withougt changing the direction.  
         %
@@
 
-        The operator $E$ The operator $E_{vv'}$ can be defined in a similar way as
+        We now define an operator $E_{vv'}$ in a similar way, 
         %
@@
         \end{equation}
-        and with it we can define.
+        and with it define the last important operator that acts on the links. 
         %
@@
         %
-        Now how $P_{vv'}^\dagger$ acts on the links: 
+        $P_{vv'}^\dagger$ acts on the links in the following way: 
         %
@@
 
-        The $Z_3$ toric code Hamiltonian can now be written in terms of the $P$ and $Q$ operators. The
-        usual string net Hamiltonian is written as 
+        With the above definitions the $Z_3$ toric code Hamiltonian can be written in terms of the $P$ and $Q$ operators.
+        In general a string net Hamiltonian might be written as 
         \begin{equation}
@@
         \end{equation}
-        where the sum over $v$ and the sum over $p$ are the sums over all vertices and plaquettes on
-        the lattice respectively and 
+        where 
         \begin{equation}
-            A_v = \prod_{i\in v} P^\dagger_{vv_i}~,~ B_p \prod_{i\in p} Q^\dagger_{v_iv_{i+1}}
+            A_v = \prod_{i\in v} P^\dagger_{vv_i}~,~ B_p = \prod_{i\in p} Q^\dagger_{v_iv_{i+1}}
             .
@@
         %
-        For the ground state of this Hamiltonian there is a local symmetry corresponding to the
-        minimization of the first term. The model has an exactly local gauge symmetry that can be
-        expressed as
+        For the ground state of this Hamiltonian there is aa local symmetry corresponding to the
+        minimization of the first term. This local symmetry is a gauge symmetry that can be
+        expressed in terms of the gauge operator.
         \begin{equation}
@@
 
-        \subsubsection{Hamiltonian Gauge symmetry }
-
-        \subsubsection{String operators}
-            With the above notation we can write down the string operators. The electric string operator along
-            the path $\Gamma_{v_b v_e}$ between the two vertices $v_0$ (beginning) and $v_N$ (end) is written
+        \subsubsection{$Z_3$ String operators}
+            With the above notation we can now write down the $Z_3$ string operators. The electric string operator along
+            the path $\Gamma$ is written
             %
@@
             where $v_l \in \Gamma$ and $N$ is the number of vertices in $\Gamma$. We show an example of an
-            electric string operator operation on an example configuration in Fig.~\ref{fig:example_elec_string}.
+            electric string operator operatiing on an example configuration in Fig.~\ref{fig:example_elec_string}.
             %
@@
             \begin{equation}
-                S^m_{\Gamma} = \prod_{l=0}^{N-1} Q_{v_{2l}v_{2l+1}}^\dagger
+                S^m_{\Gamma} = \prod_{l=0}^{N-1} P_{v_{2l}v_{2l+1}}^\dagger
                 %\label{eqn:}
@@
             The magnetic string operator acting on path $\Gamma$ in Fig.~\ref{fig:example_mag_string} is
-            explicitly
             %
@@
 
-            An interesting property of the electric string string operators in the $Z_3$ toric code is
-            that they produce two defects, one having positive charge and the other having negative
-            charge. This is most easily see by looking at Fig.~\ref{fig:example_elec_string}. The
-            configuration in Fig.~\ref{fig:example_elec_string}(a) obeys the local gauge symmetry and
-            when the electric string operator acts on path $\Gamma$ it results in two defects at the
-            end points of $\Gamma$. At the first $v_0$ (red) the local constraint is broken and
-            $G_{v_0} = e^{i2\pi /3}$ as shown in Fig.~\ref{fig:example_elec_string}(b), whereas
-            $G_{v_3} = e^{-i2\pi /3}$ which can be thought of as negative and positive gauge charges
-            at $v_0$ and $v_3$ respectively.
+            An interesting property of the electric string operator in the $Z_3$ toric code is
+            that an unclosed string produces two different defects. 
+            An example of an open string and the defects is shown in Fig.~\ref{fig:example_elec_string}. The
+            configuration in Fig.~\ref{fig:example_elec_string}(a) obeys the local gauge symmetry
+            aside from the endpoints of the path that it acts on ($\Gamma$). The two defects at the
+            end points produce two different values when the vertecies are operated on by $G_v$, being
+            $G_{\mathrm{red}} = e^{i2\pi /3}$, and $G_{\mathrm{blue}} = e^{-i2\pi /3}$.
 
-            The magnetic excitations, or $Z_3$ visons live at the endpoints of a path created with the magnetic
-            string operator. These visons can take three different values which can be changed by
-            operating with the electric operator on a path that encircles one endpoint of the
-            magnetic string path.
+            The magnetic excitations, or $Z_3$ visons live at the endpoints of the magnetic
+            strings.  These visons can change the phase of a configuration by different values.
 
-        \subsubsection{properties of $Z_3$ string operators}
+%        \subsubsection{properties of $Z_3$ string operators}
 
@@
 
-            The ground state of the $Z_3$ toric code on the torus is nine-fold degenerate because of
-            the nine different topological sectors in this topology. One can move between the
-            topological sectors with a nontrivial closed electric string wraps around either
-            the major axis or the minor axis of the torus. We will call the electric winding
+            The ground state of the $Z_3$ toric code has nine-fold topological degeneracy because of
+            the $3\times3$ different topological sectors. As the case of the toric code the $Z_3$
+            electric string changes the topological sector when acting on on a nontrivial closed
+            path. We call the electric winding
             operator that acts around the major axis $W^e_y$ and around the minor axis $W^e_x$.
-            A given topological sector can be distinguish 
-            by acting around the minor and major axes with the magnetic string operator $W^m_y$ and
-            $W^m_x$. All of the aforementioned winding operators commute with the Hamiltonian and
+            The topological sector can be determined 
+            by acting around the axes with the magnetic string operator, called $W^m_y$ and
+            $W^m_x$. All of the winding commute with the Hamiltonian and
             therefore share the same eigenvalues. The operator $W^m_{x}$ ($W^m_{y}$) can 
             have three different values depending on how many electric strings enclose the minor
-            (major) axis. Since there are three different
-            possible values for each winding number around each axis there are nine distinct
+            (major) axis. The three different
+            possible values for each winding number around each axis gives the model nine distinct
             topological sectors.
@@
         known exactly at the Rokhsar and Kivelson (RK) point, the point where $t/v =1$. At the RK
-        point the wave function is the equal weighted superposition over all dimer configurations.
-        HERE
+        point the wave function is the equal weighted superposition over all dimer configurations
+        and known to be in a critical liquid state with powerlaw decaying dimer correlations. This
+        model has an exact local $U(1)$ gauge symetry and is known to be described by a $U(1)$ gauge
+        thoery.
 
@@
     dimer liquid phase. It is likely that the QDPM in a liquid phase at the RK point because there 
-    we find no evedence of broken symmetries in the system sizes up to $32x32$. As an example of the
+    we find no evedence of broken symmetries for system sizes up to $32\times32$. As an example of the
     absence of broken symmetries we show
@@
 
-    We also find exponetialy decaying dimer correlations 
-    In Fig.~\ref{fig:fig:spacial_dmr_cor} we show the dimer correlations between horizontal dimers
+    The dimer correlations decay exponetialy in the distance between the dimers. 
+    In Fig.~\ref{fig:spacial_dmr_cor} we show the dimer correlations between horizontal dimers
     in a vertical column. We find the correlation length to be $HERE$.
@@
 
-    \subsection{Comparison to other models}
+    \subsection{Comparison to other models???}
 
@@
     The exponetial decay of the spacial correlations shown in the previous sections 
-    suggest a gap in the spectrum though it is important to determine if the lowest lying
-    excitations are in the vison-like
+    implieds a gap in the spectrum though it is important to determine if the lowest lying
+    excitations are vison-like
     or the dimer-like.  The energy gap of the dimer-like and vison-like excitations can be estimated 

### 2016-04-18 qdpm_paper.tex
Worked on intro text

@@
 
+\usepackage{color}
 \usepackage{bm}%bold math
@@
 
-Among the simplest class of models displaying topological quantum liquid phases are those with local geometric constraints; the frustration inherent in these constraints inhibits the formation of symmetry breaking local order and given sufficient dynamics, such models may have symmetric liquid ground states.
+Among the simplest class of models displaying topological quantum liquid phases are those with local geometric constraints; such constraints inhibit the formation of symmetry breaking local order and given sufficient dynamics, such models may have symmetric liquid ground states.
 The simplest such geometrically constrained model is the quantum dimer model (QDM) describing dimer degrees of freedom living on the links of a lattice~\cite{Rokhsar1988,Moessner2008}; the hard-core, fully-packed QDM has a local constraint that requires exactly one dimer touching each vertex.
@@
 
-Given that these models with dimer degrees of freedom and local constraints posses the simplest non-trivial local (Ising) Hilbert space at each link, they provide a (possibly) simpler route to engineering exotic phases; the local constraints constraint can often be enforced by a local potential energy penalty and the required dynamics are generally expected to arise at the lowest order non-trivial order in perturbation theory.
-Previous work as demonstrated that GQDM on the square lattice support gapped $Z_2$ topologically ordered phases as well as gapless quantum critical points.
-On non-bipartite lattices GQDM supported $Z_2$ topological order~\cite{Moessner2001a,Misguich2002} as well as doubled-semion phases~\cite{Qi2014,Buerschaper2014a}.
+Given that these models with dimer degrees of freedom and local constraints posses the simplest non-trivial local (Ising) Hilbert space at each link, they provide a potentially simpler route to engineering exotic phases; the local constraints can often be enforced by a local potential energy penalty and the required dynamics are generally expected to arise at the lowest order non-trivial order in perturbation theory.
+We will refer to such models with dimer degrees of freedom on links and local constraints at vertices as \emph{generalized quantum dimer modes} (GQDMs).
+Previous work as demonstrated that GQDMs on the square lattice support gapped $Z_2$ topologically ordered phases as well as gapless quantum critical points.
+On non-bipartite lattices, GQDMs support $Z_2$ topological order~\cite{Moessner2001a,Misguich2002} as well as doubled-semion phases~\cite{Qi2014,Buerschaper2014a}.
 A full characterization of all exotic phases that can exist within this framework is thus desirable.
 
-In this work we extend this paradigm to a new GQDM on the square lattice, what we term the quantum dimer-pentamer model (QDPM).
-In the QDPM, the local constraint is relaxed from that of the QDM to require that either $1$ or $4$ dimers to touching each vertex, as shown in figure \figref{fig:QDPMex}.
-Correspondingly, the QDPM extends the Hilbert space of the QDM to include both fully-packed hard-core dimer configurations, as well as those pentamers, four dimers touch a vertex.
-To give the system dynamics, the Hamiltonian includes terms that incorporate the simplest non-trivial dynamics that don't violate the local constraint.
+In this work we extend this paradigm to a new GQDM on the square lattice, what we term the \emph{quantum dimer-pentamer model} (QDPM).
+In the QDPM, the local constraint is relaxed from that of the QDM to allow either $1$ or $4$ dimers to touch each vertex, as shown in figure \figref{fig:QDPMex}.
+Correspondingly, the QDPM extends the Hilbert space of the QDM to include both fully-packed hard-core dimer configurations, as well as those with pentamers--four dimers touching a vertex.
+To give the system dynamics, the Hamiltonian includes terms that incorporate the simplest non-trivial dynamics that preserve the local constraint.
 
-We present a numerical study of the ground state of the QDPM at an exactly soluble point and demonstrate the the soluble point represents a gapped, disordered quantum liquid phase.
-Using Monte Carlo calculations, we explicitly demonstrate the absence of symmetry breaking order and the exponential decay of correlation functions; by computing imaginary-time correlation functions, we find that the RK point is gapped in the thermodynamic limit.
+We present a numerical study of the ground state of the QDPM at an exactly soluble point and demonstrate the the soluble point represents a \textcolor{red}{gapped}, disordered quantum liquid phase.
+Using Monte Carlo calculations, we explicitly demonstrate the absence of symmetry breaking order and the exponential decay of correlation functions; \textcolor{red}{by computing imaginary-time correlation functions, we find that the RK point is gapped in the thermodynamic limit}.
 By construction the QDPM has an exact local $Z_3$ symmetry and conserves a $Z_3$ topological winding number.
@@
 We write this constraint as $n_v = 1$, where $n_v$ is the number of dimers that touch a vertex.
-We can distinguish between number constraints of the form $n_v = n_0$ and parity constraints of the form $n_v \mod 2 = 0,1$.
-The unique, non-trivial constraints of this form are the number constraints $n_v=1,2$ and the parity constraints $n_v\mod2 =0,1$ and  $n_v\mod2 =1$ (see \figref{fig:GQDMexamples}).
-
-The presence of such local constraints implies all physical states in the Hilbert space are invariant under local gauge transformations at each vertex, $G_v$.
+We can distinguish between number constraints of the form $n_v = n_0$ and parity constraints of the form $n_v\mod 2 = 0,1$.
+The unique, non-trivial constraints of this form are the number constraints $n_v=1,2$ and the parity constraints $n_v\mod2 =0,1$ and  $n_v\mod2 =1$ (see \figref{fig:example_local_constraints}).
 
@@
 \end{equation}
-where $\hat{T}$ is an off-diagonal kinetic term that preserves the constraint, $\hat{V}$ is a local potential energy term, and $v$ and $t$ parametrize the strength of each term.
-We will take the kinetic term $\hat{T}$ to be the dynamics which preserved the constraint; for example in the QDM $\hat{T}$ is the sum of all possible ``plaquette" flip terms acting on plaquettes with parallel dimers.
+where $\hat{T}$ is an off-diagonal kinetic term that preserves the constraint, $\hat{V}$ is a diagonal potential energy term, and $v$ and $t$ parametrize the strength of each term.
+In the simplest case, $\hat{T}$ involves the minimum non-trivial dynamics that preserve the constraint.
+For example in the QDM $\hat{T}$ is the sum of all possible ``plaquette flip" terms acting on plaquettes with parallel dimers:
 \begin{equation}
     \label{}
-    \hat{T} = \sum_{\bplqt} 
+    \hat{T}_{\rm{QDM}} = \sum_{\bplqt} 
             \left|
@@
             +
-            \mathrm{h.c.}
+            h.c..
+\end{equation}
+
+Because of the local constraints, all states in the Hilbert space of a GQDM are invariant under local gauge transformations a the vertices, $G_v$~\cite{Moessner2001}.
+For GQDM with a number constraint, we write the gauge transformation as:
+\begin{equation}
+G_v = e^{i \alpha \left( n_v -n_0 \right)}; \notag
+\end{equation}
+as the states in the GQDM Hilbert space are invariant under $G_v$ for all $0 \leq \alpha \leq 2 \pi$, this represents a local $U(1)$ gauge symmetry.
+When the number constraint is relaxed to a parity constraint, there is a correspondingly reduced gauge symmetry which can be written as
+\begin{equation}
+G_v^e = e^{\pm i \pi n_v}, \quad G_v^o = e^{\pm i \pi \left(n_v-1\right)}, \notag
+\end{equation}
+where $G^{e\left(o\right)}_v$ is the transformation for the even (odd) parity constraint; the gauge symmetry is now reduced to to $Z_2$.
+By construction, the Hamiltonian is gauge invariant and thus commutes with $G_v$
+\begin{equation}
+\left[ H_{\rm{GQDM}}, G_v \right] = 0. \notag
 \end{equation}

### 2016-04-19 qdpm_paper.tex
Worked on Background section

@@
 }
-
+\newcommand{\ket}[1]{| #1 \rangle}
+\newcommand{\eket}[1]{\left | #1 \right \rangle}
+\newcommand{\ebra}[1]{\left \langle #1 \right |}
+\newcommand{\Eqref}[1]{Eq. \eqref{#1}}
+\newcommand{\RK}{\mathrm{RK}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{figure}[b!]
+\begin{figure}[t!]
     \centering
@@
     \caption{Clockwise from the upper left panel we show an example of a QDM with constraints: one
-    dimer, two dimers, an even number of dimers, and and odd number of dimers touching each vertex.}
+    dimer ($n_0 = 1$), two dimers ($n_0 = 2$), and an even ($n_P = 0$) or odd ($n_P = 1$) number of dimers touching each vertex.}
     \label{fig:example_local_constraints}
@@
 We consider systems with Ising-like dimer degrees of freedom on each link, such that each link has either $0$ or $1$ dimers.
-The Hilbert space consists of configurations of dimers on the square lattice that satisfy a local constraint at each vertex; the simplest constraint is that of the hard-core fully-packed QDM where a single dimer must touch each vertex.
-We write this constraint as $n_v = 1$, where $n_v$ is the number of dimers that touch a vertex.
-We can distinguish between number constraints of the form $n_v = n_0$ and parity constraints of the form $n_v\mod 2 = 0,1$.
-The unique, non-trivial constraints of this form are the number constraints $n_v=1,2$ and the parity constraints $n_v\mod2 =0,1$ and  $n_v\mod2 =1$ (see \figref{fig:example_local_constraints}).
+The Hilbert space consists of configurations of dimers on the square lattice that satisfy a local constraint at each vertex.
+Defining $n_v$ as the number of dimers that touch a vertex, we can distinguish between fixed number constraints of the form $n_v = n_0$ and fixed parity constraints of the form $n_v\mod 2 = n_P$.
+The unique, non-trivial constraints of this form for the square lattice are the number constraints $n_0=1,2$ and the parity constraints $n_P =0,1$ (see \figref{fig:example_local_constraints}).
 
@@
 \begin{equation}
-H_{\rm{GQDM}} = -t \hat{T} + v \hat{V}
-\end{equation}
-where $\hat{T}$ is an off-diagonal kinetic term that preserves the constraint, $\hat{V}$ is a diagonal potential energy term, and $v$ and $t$ parametrize the strength of each term.
-In the simplest case, $\hat{T}$ involves the minimum non-trivial dynamics that preserve the constraint.
+H_{\rm{GQDM}} = -\sum_\nu t_\nu \hat{T}_{\nu} + \sum_\nu v_\nu \hat{V}_{\nu} \label{eq:HGQDM}
+\end{equation}
+where $\hat{T}_\nu$ are off-diagonal kinetic energy operators, $\hat{V}_\nu$ are diagonal the potential energy operators, $t_\nu$ and $v_\nu$ parametrize the strength of these terms, and each $\nu$ and represents a set of $n_\nu$ neighboring links.
+$\hat{T}_\nu$ is constructed to favor a resonance between two distinct allowed dimerazations of $\nu$, $c_\nu$ and its compliment $\bar{c}_\nu$, and is written as:
+\begin{equation}
+\hat{T}_{\nu} = \eket{c_\nu}\ebra{\bar{c}_\nu} + h.c.;
+\end{equation}
+in the simplest case, $\hat{T_\nu}$ involves the minimum non-trivial dimer dynamics that preserve the constraint.
+Similarly, the potential energy term provides an energy cost for states with these local configurations:
+\begin{equation}
+\hat{V}_{\nu} = \eket{c_\nu}\ebra{c_\nu} +  \eket{\bar{c}_\nu}\ebra{\bar{c}_\nu}.
+\end{equation}
+In general the $T_\nu$'s don't commute with each other or with the $V_\nu$'s, and thus the ground state of $H_{\rm{GQDM}}$ is not explicitly known.
+
+However, at the special point where $t_\nu = v_\nu~\forall \nu$, $H_{\rm{GQDM}}$, known as the Rokhsar-Kivelson (RK) point, the exact ground state is known.
+This can be shown by writing \Eqref{eq:HGQDM} at the RK point as the sum of projection operators
+\begin{equation}
+H_{\rm{RK}} = 2 \sum_\nu \hat{h}_\nu \label{eq:HRK},
+\end{equation}
+where $\hat{h}_\nu \equiv \hat{P}^\dagger_{\nu} \hat{P}_{\nu}$ and $\hat{P}^\dagger_\nu$ is a vector orthogonal to the equal superposition of $c_\nu$ and $\bar{c}_\nu$
+\begin{equation}
+\hat{P}^\dagger_\nu \equiv \frac{1}{\sqrt{2}} \biggl( \eket{ c_\nu} - \eket{\bar{c}_\nu} \biggr).
+\end{equation} 
+Since all $h_\nu$ are projectors with eigenvalues $\{0,1\}$, a zero energy ground state of \Eqref{eq:HRK} is simultaneously annihilated by all $\hat{h}_\nu$.
+Such a zero energy state, known as the RK state, may be formed from an equal superposition of all dimerizations that are connected by $\{T_\nu\}$:
+\begin{equation}
+\eket{\Phi_{\RK}^{\Omega}} = \sum_{C \in \Omega} \eket{C}
+\end{equation} 
+where $\Omega$ is a subset of the Hilbert space connected by $\{T_\nu\}$.
+Thus $\{ \ket{\Phi_{\RK}^\Omega} \}$ are the exact, degenerate ground states of $H_{\rm{GQDM}}$ with a degeneracy labelled by $\Omega$ at the RK point.
+
+Because of the local constraints, all states in the Hilbert space of a GQDM are invariant under local gauge transformations a the vertices, $G_v$~\cite{Moessner2001}.
+For GQDM with a number constraint, we write the gauge transformation as:
+\begin{equation}
+G_v = e^{i \alpha \left( n_v -n_0 \right)}; \notag
+\end{equation}
+as the states in the GQDM Hilbert space are invariant under $G_v$ for all $0 \leq \alpha \leq 2 \pi$, this represents a local $U(1)$ gauge symmetry.
+When the number constraint is relaxed to a parity constraint, there is a correspondingly reduced gauge symmetry which can be written as
+\begin{equation}
+G_v^P = e^{\pm i \pi \left(n_v-n_P\right)}, \notag
+\end{equation}
+and the gauge symmetry is now reduced to to $Z_2$.
+By construction, the Hamiltonian is gauge invariant and thus commutes with $G_v$
+\begin{equation}
+\left[ H_{\rm{GQDM}}, G_v \right] = 0. \notag
+\end{equation}
+
+Given the gauge symmetry, one may construct a gauge invariant string operator along an oriented path $\Gamma$ path on the dual lattice
+\begin{equation}
+S_\Gamma \equiv \prod_{\ell \in \Gamma} e^{i \alpha_\ell n_\ell}
+\end{equation}
+where $\alpha_\ell$ is a phase that is associated with each link on the lattice, as well as the direction the link is crossed in $\Gamma$.
+
+\subsection{Square lattice QDM}
+
+the simplest constraint is that of the hard-core fully-packed QDM where a single dimer must touch each vertex. We write this constraint as $n_v = 1$,
+
 For example in the QDM $\hat{T}$ is the sum of all possible ``plaquette flip" terms acting on plaquettes with parallel dimers:
@@
             h.c..
-\end{equation}
-
-Because of the local constraints, all states in the Hilbert space of a GQDM are invariant under local gauge transformations a the vertices, $G_v$~\cite{Moessner2001}.
-For GQDM with a number constraint, we write the gauge transformation as:
-\begin{equation}
-G_v = e^{i \alpha \left( n_v -n_0 \right)}; \notag
-\end{equation}
-as the states in the GQDM Hilbert space are invariant under $G_v$ for all $0 \leq \alpha \leq 2 \pi$, this represents a local $U(1)$ gauge symmetry.
-When the number constraint is relaxed to a parity constraint, there is a correspondingly reduced gauge symmetry which can be written as
-\begin{equation}
-G_v^e = e^{\pm i \pi n_v}, \quad G_v^o = e^{\pm i \pi \left(n_v-1\right)}, \notag
-\end{equation}
-where $G^{e\left(o\right)}_v$ is the transformation for the even (odd) parity constraint; the gauge symmetry is now reduced to to $Z_2$.
-By construction, the Hamiltonian is gauge invariant and thus commutes with $G_v$
-\begin{equation}
-\left[ H_{\rm{GQDM}}, G_v \right] = 0. \notag
 \end{equation}

### 2016-04-20 qdpm_paper.tex
Worked on background section

@@
 \newcommand{\RK}{\mathrm{RK}}
+\newcommand{\HGQDM}{H_\mathrm{GQDM}}
+\newcommand{\HQDM}{H_\mathrm{QDM}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t!]
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Background}
 \label{sec:Background}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Generalized quantum dimer models}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[htpb]
@@
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Here we will provide background about generalized quantum dimer models on the square lattice.
@@
 The Hilbert space consists of configurations of dimers on the square lattice that satisfy a local constraint at each vertex.
-Defining $n_v$ as the number of dimers that touch a vertex, we can distinguish between fixed number constraints of the form $n_v = n_0$ and fixed parity constraints of the form $n_v\mod 2 = n_P$.
-The unique, non-trivial constraints of this form for the square lattice are the number constraints $n_0=1,2$ and the parity constraints $n_P =0,1$ (see \figref{fig:example_local_constraints}).
+Defining $n_v$ as the number of dimers that touch a vertex, we can distinguish between fixed number constraints of the form $n_v = n_0$ and fixed parity constraints of the form $n_v\mod 2 = n_P$ (see \figref{fig:example_local_constraints}).
 
@@
 
-Because of the local constraints, all states in the Hilbert space of a GQDM are invariant under local gauge transformations a the vertices, $G_v$~\cite{Moessner2001}.
-For GQDM with a number constraint, we write the gauge transformation as:
+Because of the local constraints, all states in the Hilbert space of a GQDM are invariant under local gauge transformations a the vertices, $G_v$~\cite{Moessner2001} of the general form
+\begin{equation}
+G_v = e^{i \alpha \left( n_v -c_0 \right)}; \notag
+\end{equation}
+where the $c_0$ and $\alpha$ depend on the constraint.  
+By construction, the Hamiltonian is gauge invariant and thus commutes with $G_v$
+\begin{equation}
+\left[ H_{\rm{GQDM}}, G_v \right] = 0. \notag
+\end{equation}
+
+The gauge symmetry allows one to construct a gauge invariant string operator $S_\gamma$ along an oriented path $\gamma$ path on the dual lattice.
+We first orient all the links of the square lattice such that they point from the $A$ sublattice to the $B$ sublattice (see \figref{fig:orientedSL}) and define an oriented dimer flux $\Phi_\gamma$ through the path:
+\begin{equation}
+\Phi_\gamma \equiv \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) n_\ell
+\end{equation}
+where $\mathrm{sgn}(\ell,\gamma)$ is positive (negative) if $\ell$ is oriented to the right with respect to the orientation of $\gamma$. The string operator is defined as
+\begin{equation}
+S_\gamma \equiv e^{i \alpha \Phi_\gamma}
+\end{equation}
+where $\alpha$ such that $S_\gamma$ commutes with $\HGQDM$ everywhere except at the ends of $\gamma$. Therefore, for closed loops $\Gamma$, $[ S_\Gamma,\HGQDM]=0$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htpb]
+    \centering
+    \includegraphics[width=0.8\linewidth]{QDPM_ex_config.pdf}
+    \caption{\textcolor{red}{Replace with a figure showing the orientations of the lattice links, with an open oriented string on the dual lattice as well as a closed oriented loop and topologically non-trivial loops.}The link orientations of the square lattice.}
+    \label{fig:orientedSL}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Fixed number constraints}
+
+The two unique fixed-number constraints on the square lattice $n_0 = 1$ and $n_0=2$ lead to the QDM and the quantum full-packed loop model (QFPLM), respectively.
+For such GQDMs with a number constraint, we write the gauge transformation as:
 \begin{equation}
@@
 as the states in the GQDM Hilbert space are invariant under $G_v$ for all $0 \leq \alpha \leq 2 \pi$, this represents a local $U(1)$ gauge symmetry.
+The Hamiltonian for these models gives dynamics to parallel dimers on the plaquettes of the lattice:
+\begin{align}
+    \label{}
+   \HQDM = &-t\sum_{\bplqt} \biggl( \eket{\vrtplqt} \ebra{\hrzplqt} +h.c. \biggr) \notag\\
+    					&+v\sum_{\bplqt} \biggl( \eket{\vrtplqt} \ebra{\vrtplqt} +\eket{\hrzplqt} \ebra{\hrzplqt} \biggr).
+\end{align}
+In this case of a fixed number constraint, the Hamiltonian conserves the dimer flux through a closed loop:
+\begin{equation}
+\left[ \Phi_\Gamma, \HQDM \right] = 0
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Fixed parity constraints}
+
 When the number constraint is relaxed to a parity constraint, there is a correspondingly reduced gauge symmetry which can be written as
@@
 and the gauge symmetry is now reduced to to $Z_2$.
-By construction, the Hamiltonian is gauge invariant and thus commutes with $G_v$
-\begin{equation}
-\left[ H_{\rm{GQDM}}, G_v \right] = 0. \notag
-\end{equation}
-
-Given the gauge symmetry, one may construct a gauge invariant string operator along an oriented path $\Gamma$ path on the dual lattice
-\begin{equation}
-S_\Gamma \equiv \prod_{\ell \in \Gamma} e^{i \alpha_\ell n_\ell}
-\end{equation}
-where $\alpha_\ell$ is a phase that is associated with each link on the lattice, as well as the direction the link is crossed in $\Gamma$.
-
-\subsection{Square lattice QDM}
-
-the simplest constraint is that of the hard-core fully-packed QDM where a single dimer must touch each vertex. We write this constraint as $n_v = 1$,
-
-For example in the QDM $\hat{T}$ is the sum of all possible ``plaquette flip" terms acting on plaquettes with parallel dimers:
-\begin{equation}
-    \label{}
-    \hat{T}_{\rm{QDM}} = \sum_{\bplqt} 
-            \left|
-                \vrtplqt
-            \right\rangle
-            \left\langle
-                \hrzplqt
-            \right|
-            +
-            h.c..
-\end{equation}
 

### 2016-04-21 qdpm_paper.tex
Worked on Background section

@@
 \newcommand{\HQDM}{H_\mathrm{QDM}}
+\newcommand{\HTC}{H_\mathrm{TC}}
 
@@
 If the hard-core constraint of the QDM is relaxed to a parity constraint such that each vertex much have an even (odd) number of dimers touching each vertex, the simplest non-trivial dynamics lead to the (odd) toric code which has a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
-
 The existence of topologically ordered ground states in dimer-based models is intimately related to the local constraint which imposes a local gauge symmetry in the low energy Hilbert space; the topological order that arises is directly related to a discrete gauge theory with the appropriate local gauge constraint~\cite{Moessner2001}.
@@
 where $\hat{T}_\nu$ are off-diagonal kinetic energy operators, $\hat{V}_\nu$ are diagonal the potential energy operators, $t_\nu$ and $v_\nu$ parametrize the strength of these terms, and each $\nu$ and represents a set of $n_\nu$ neighboring links.
+We will limit our discussion to $t_\nu >0$.
 $\hat{T}_\nu$ is constructed to favor a resonance between two distinct allowed dimerazations of $\nu$, $c_\nu$ and its compliment $\bar{c}_\nu$, and is written as:
@@
 \end{equation}
+Therefore we may define a Hamiltonian for a GQDM using \Eqref{eq:HGQDM} and defining a set of dimer resonances $\{(c_\nu,\bar{c}_\nu)\}$ and corresponding potential and kinetic energy strenghts $\{(t_\nu,v_\nu)\}$:
+\begin{equation}
+\HGQDM \biggl( \bigl\{\left(c_\nu,\bar{c}_\nu\right)\},\{\left(t_\nu,v_\nu\right)\bigr\}\biggr).
+\end{equation}
  In general the $T_\nu$'s don't commute with each other or with the $V_\nu$'s, and thus the ground state of $H_{\rm{GQDM}}$ is not explicitly known.
@@
 \end{equation}
+If a defect is introduced which violates the local constraint at a vertex, this can be viewed as an ``electric charge'' living on the vertex, within the context of the original GQDM.
 
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{QDPM_ex_config.pdf}
+    \includegraphics[width=0.5\columnwidth]{QDPM_ex_config.pdf}
     \caption{\textcolor{red}{Replace with a figure showing the orientations of the lattice links, with an open oriented string on the dual lattice as well as a closed oriented loop and topologically non-trivial loops.}The link orientations of the square lattice.}
@@
 as the states in the GQDM Hilbert space are invariant under $G_v$ for all $0 \leq \alpha \leq 2 \pi$, this represents a local $U(1)$ gauge symmetry.
-The Hamiltonian for these models gives dynamics to parallel dimers on the plaquettes of the lattice:
-\begin{align}
-    \label{}
-   \HQDM = &-t\sum_{\bplqt} \biggl( \eket{\vrtplqt} \ebra{\hrzplqt} +h.c. \biggr) \notag\\
-    					&+v\sum_{\bplqt} \biggl( \eket{\vrtplqt} \ebra{\vrtplqt} +\eket{\hrzplqt} \ebra{\hrzplqt} \biggr).
-\end{align}
+The Hamiltonian for these models gives dynamics to parallel dimers on the plaquettes $\bplqt$ of the lattice:
+\begin{equation}
+\HQDM\left(t,v\right) \equiv \HGQDM \biggl( \bigl\{ \left(\vrtplqt,\hrzplqt\right) \bigr\},\bigl\{ \left(t,v\right) \bigr\} \biggr)
+\end{equation}
+where we have taken $t_\bplqt = t$ \& $v_\bplqt =v$ $\forall \bplqt$.
+%\begin{align}
+%    \label{}
+%   \HQDM = &-t\sum_{\bplqt} \biggl( \eket{\vrtplqt} \ebra{\hrzplqt} +h.c. \biggr) \notag\\
+%    					&+v\sum_{\bplqt} \biggl( \eket{\vrtplqt} \ebra{\vrtplqt} +\eket{\hrzplqt} \ebra{\hrzplqt} \biggr). \label{eq:HQDM}
+%\end{align}
 In this case of a fixed number constraint, the Hamiltonian conserves the dimer flux through a closed loop:
@@
 \end{equation}
+and therefore we can define two conserved topological winding numbers $\Phi_{x}$ \& $\Phi_{y}$ which are the dimer flux through topologically non-trival loops that wind around each axis of the lattice when the system has periodic conditions (see \figref{fig:orientedSL}).
+On an lattice of dimensions $L_x\times L_y$, the the eigenvalues of $\Phi_{x/y}$ integers in range
+\begin{equation}
+-L_{x/y}/2 \leq  \Phi_{x/y} \leq L_{x/y}/2,
+\end{equation}
+thus there are $\mathcal{O} (L_x L_y)$ distinct topological sectors.
+Since the plaquette flip term in \Eqref{eq:HQDM} is ergodic in each of these topological sectors on the square lattice~\cite{????}, each of these topological sectors corresponds to a unique RK ground state where $\Omega$ is labeled by $(\Phi_x,\Phi_y)$.
+
+To understand defects in these models, we define background flux $\tilde{\Phi}_\ell$
+\begin{equation}
+\tilde{\Phi}_\gamma \equiv -\frac{n_0}{4} \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) 
+\end{equation}
+and the total charge $Q_\Gamma$ enclosed in a closed loop $\Gamma$ as
+\begin{equation}
+Q_\Gamma \equiv \Phi_\Gamma+ \tilde{\Phi}_\Gamma.
+\end{equation}
+(Alternately can think of the source of $\Phi_\Gamma$ to be static charges of charge $+n_0$ ($-n_0$) sitting at the verticies of the $A$($B$) sub-lattice.) In this language, the gauge constraint requires each vertex to have $Q_v = 0$; thus defects which violate the constraint have $Q_v \neq 0$.
+A table of the charges associated with defects in the QDM and QFPLM is listed in Table \ref{tab:defects}.
+
+The QDM and QFPLM on the square lattice have isolated liquid ground states at the RK point surrounded by symmetry broken phases~\cite{Rokhsar1988,Leung1996,Syljuasen2005,Syljuasen2006,Syljuasen2004,Moessner2008}.
+The RK point of these models have been shown to have power-law decaying dimer-dimer and monomer-monomer correlation functions and gapless excitations~\cite{Fisher1961,Kasteleyn1961,Fisher1966a,Fisher1963,Kasteleyn1963a,Sutherland1988b,Sutherland1988a,Kohmoto1988a,Liang1988,Sutherland1988,Kohmoto1988,Levitov1990,Leung1996,Henley1997,Henley1997,Henley2004a,Pollmann2006}.
+Thus, such fixed number constrained models on bipartite lattices are expected to have an isolated unstable gapless critical quantum liquid points with logarithmically confined defect and an extensive topological degeneracy.
+These features of fixed number constrained models are consistent with the effective U(1) gauge theory description of the RK point~\cite{Fradkin2004,Fradkin1990,Moessner2001}; in 2+1D pure U(1) gauge theories are always confining and thus the lack of an extended deconfined topologically ordered phase near the RK point~\cite{PolyakovBook}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+  \begin{tabular}{| l | c | c | c |}
+  	\hline
+      	type & $n_v$ & $Q_{\rm{QDM}}$ & $Q_{\rm{FPLM}}$  \\
+	\hline
+	monomer & $0$ & -1 & -2 \\
+	\hline
+	dimer & $1$ & 0 & -1 \\
+	\hline
+	trimer & $2$ & 1 & 0 \\
+	\hline
+	tetramer & $3$ & 2 & 1 \\
+	\hline
+	pentamer & $4$ & 3 & 2 \\
+	\hline
+  \end{tabular}
+  \caption{Defects and their associated charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
+  \label{tab:defects}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-When the number constraint is relaxed to a parity constraint, there is a correspondingly reduced gauge symmetry which can be written as
+We now consider relaxing the local constraint to a parity constraint such that $n_v \mod 2 = n_P$ for $n_P = 0,1$; the resulting GQDM are the even \& odd parity Toric Code (or Ising gauge theory).
+These models have a correspondingly reduced gauge symmetry which can be written as
 \begin{equation}
@@
 \end{equation}
-and the gauge symmetry is now reduced to to $Z_2$.
+and the gauge symmetry is now reduced from $U(1)$ to $Z_2$.
+The set of allowed dimer resonances $\mathcal{C}_{\rm{TC}}$ is expanded accordingly \textcolor{red}{Owen: Add symbols for 4-0 resonance, and 1-3 resonances and 2-2 resonsnce}:
+\begin{equation}
+\mathcal{C}_{\rm{TC}} \equiv \bigl\{ \left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right) \bigr\}
+\end{equation}
+where we implicitly include rotational symmetry related resonances. We will limit or discussion to $v_\bplqt=0$ such that the corresponding Hamiltonian is
+\begin{equation}
+\HTC\left(t\right) \equiv \HGQDM \biggl( \mathcal{C}_{\rm{TC}},\bigl\{ \left(t,0\right) \bigr\} \biggr).
+\end{equation}
+In this case the equal superposition RK wavefunction is the exact ground state occurs in the absence of a potential energy term.
 

### 2016-04-25 qdpm_paper.tex
Worked on Background section

@@
 \usepackage{amssymb}
+\usepackage{bbold}
 \usepackage{setspace}
@@
 
-However, at the special point where $t_\nu = v_\nu~\forall \nu$, $H_{\rm{GQDM}}$, known as the Rokhsar-Kivelson (RK) point, the exact ground state is known.
-This can be shown by writing \Eqref{eq:HGQDM} at the RK point as the sum of projection operators
-\begin{equation}
-H_{\rm{RK}} = 2 \sum_\nu \hat{h}_\nu \label{eq:HRK},
-\end{equation}
-where $\hat{h}_\nu \equiv \hat{P}^\dagger_{\nu} \hat{P}_{\nu}$ and $\hat{P}^\dagger_\nu$ is a vector orthogonal to the equal superposition of $c_\nu$ and $\bar{c}_\nu$
-\begin{equation}
-\hat{P}^\dagger_\nu \equiv \frac{1}{\sqrt{2}} \biggl( \eket{ c_\nu} - \eket{\bar{c}_\nu} \biggr).
-\end{equation} 
-Since all $h_\nu$ are projectors with eigenvalues $\{0,1\}$, a zero energy ground state of \Eqref{eq:HRK} is simultaneously annihilated by all $\hat{h}_\nu$.
+However, at the special points in the $\{(t_\nu,v_\nu)\}$ parameter space, the exact ground state is known when \Eqref{eq:HGQDM} can be written as the sum of projection operators
+\begin{equation}
+H_{\rm{RK}} = \sum_\nu \hat{h}_\nu \label{eq:HRK},
+\end{equation}
+where all $h_\nu$ are projectors with eigenvalues $\{0,1\}$; a zero energy ground state of \Eqref{eq:HRK} is simultaneously annihilated by all $\hat{h}_\nu$.
 Such a zero energy state, known as the RK state, may be formed from an equal superposition of all dimerizations that are connected by $\{T_\nu\}$:
@@
 
-Because of the local constraints, all states in the Hilbert space of a GQDM are invariant under local gauge transformations a the vertices, $G_v$~\cite{Moessner2001} of the general form
+Because of the local constraints, all states in the Hilbert space of a GQDM are invariant under local gauge transformations a the vertices, $G_v$ of the general form~\cite{Moessner2001}
 \begin{equation}
@@
 If a defect is introduced which violates the local constraint at a vertex, this can be viewed as an ``electric charge'' living on the vertex, within the context of the original GQDM.
+One may determine if such electric charges are confined by introducing a pair of such defects and computing their spatial correlation function, thus determining the confined or deconfined nature of the GQDM ground state.
 
@@
 \end{equation}
-where $\mathrm{sgn}(\ell,\gamma)$ is positive (negative) if $\ell$ is oriented to the right with respect to the orientation of $\gamma$. The string operator is defined as
-\begin{equation}
-S_\gamma \equiv e^{i \alpha \Phi_\gamma}
-\end{equation}
-where $\alpha$ such that $S_\gamma$ commutes with $\HGQDM$ everywhere except at the ends of $\gamma$. Therefore, for closed loops $\Gamma$, $[ S_\Gamma,\HGQDM]=0$.
+where $\mathrm{sgn}(\ell,\gamma)$ is positive (negative) if $\ell$ is oriented to the right with respect to the orientation of $\gamma$. Additionally, we define background flux $\tilde{\Phi}_\ell$
+\begin{equation}
+\tilde{\Phi}_\gamma \equiv -\frac{c_0}{4} \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) 
+\end{equation}
+and the total charge $Q_\Gamma$ enclosed in a closed loop $\Gamma$ as
+\begin{equation}
+Q_\Gamma \equiv \Phi_\Gamma+ \tilde{\Phi}_\Gamma.
+\end{equation}
+(Alternately can think of the source of $\Phi_\Gamma$ to be static charges of charge $+c_0$ ($-c_0$) sitting at the verticies of the $A$($B$) sub-lattice.).
+
+We define the string operator is defined as
+\begin{equation}
+S_\gamma \equiv e^{i \alpha \left( \Phi_\gamma - \tilde{\Phi}_\gamma \right)}
+\end{equation}
+where $\alpha$ such that $S_\gamma$ commutes with $\HGQDM$ everywhere except at the ends of $\gamma$.
+Therefore, for closed loops $\Gamma$, $[ S_\Gamma,\HGQDM]=0$.
+For open strings, $S_\gamma$ does not commute with the Hamiltonian and can be viewed as creating a pair of ``magnetic charges'' at the ends of the string: correspondingly $S_\gamma \ket{\Phi_{\RK}}$ can used as a trial wavefunction for an excited state with a pair of magnetic charges.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htpb]
+\begin{figure}[tpb]
     \centering
@@
 \begin{equation}
-\HQDM\left(t,v\right) \equiv \HGQDM \biggl( \bigl\{ \left(\vrtplqt,\hrzplqt\right) \bigr\},\bigl\{ \left(t,v\right) \bigr\} \biggr)
+\HQDM\left(t,v\right) \equiv \HGQDM \biggl( \bigl\{ \left(\vrtplqt,\hrzplqt\right) \bigr\},\bigl\{ \left(t,v\right) \bigr\} \biggr)  \label{eq:HQDM}
 \end{equation}
@@
 %\end{align}
+
 In this case of a fixed number constraint, the Hamiltonian conserves the dimer flux through a closed loop:
@@
 thus there are $\mathcal{O} (L_x L_y)$ distinct topological sectors.
-Since the plaquette flip term in \Eqref{eq:HQDM} is ergodic in each of these topological sectors on the square lattice~\cite{????}, each of these topological sectors corresponds to a unique RK ground state where $\Omega$ is labeled by $(\Phi_x,\Phi_y)$.
-
-To understand defects in these models, we define background flux $\tilde{\Phi}_\ell$
-\begin{equation}
-\tilde{\Phi}_\gamma \equiv -\frac{n_0}{4} \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) 
-\end{equation}
-and the total charge $Q_\Gamma$ enclosed in a closed loop $\Gamma$ as
-\begin{equation}
-Q_\Gamma \equiv \Phi_\Gamma+ \tilde{\Phi}_\Gamma.
-\end{equation}
-(Alternately can think of the source of $\Phi_\Gamma$ to be static charges of charge $+n_0$ ($-n_0$) sitting at the verticies of the $A$($B$) sub-lattice.) In this language, the gauge constraint requires each vertex to have $Q_v = 0$; thus defects which violate the constraint have $Q_v \neq 0$.
+
+At the Rokhsar-Kivelson point $t=v$, we may write $\HQDM$ in the form of \Eqref{eq:HRK} by defining projection operators  $\hat{h}_\nu \equiv \hat{P}^\dagger_{\nu} \hat{P}_{\nu}$, with
+\begin{equation}
+\hat{P}^\dagger_\nu \equiv \biggl( \eket{ c_\nu} - \eket{\bar{c}_\nu} \biggr).
+\end{equation} 
+Since the plaquette flip term in \Eqref{eq:HQDM} is ergodic in each of topological sector $(\Phi_x,\Phi_y)$ on the square lattice (\textcolor{red}{is this known for the FPLM???})~\cite{????}, each topological sector corresponds to a unique RK ground state where $\Omega$ is labeled by $(\Phi_x,\Phi_y)$.
+Thus the equal superposition RK points of the QDM and QFPLM have an \emph{extensively} degenerate ground states.
+
+The gauge constraint requires each vertex to have $Q_v = 0$; thus defects which violate the constraint have $Q_v \neq 0$.
 A table of the charges associated with defects in the QDM and QFPLM is listed in Table \ref{tab:defects}.
@@
 and the gauge symmetry is now reduced from $U(1)$ to $Z_2$.
-The set of allowed dimer resonances $\mathcal{C}_{\rm{TC}}$ is expanded accordingly \textcolor{red}{Owen: Add symbols for 4-0 resonance, and 1-3 resonances and 2-2 resonsnce}:
-\begin{equation}
-\mathcal{C}_{\rm{TC}} \equiv \bigl\{ \left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right) \bigr\}
-\end{equation}
+The set of allowed dimer resonances $\mathcal{C}_{\rm{TC}}$ is expanded accordingly \textcolor{red}{Owen: Add symbols for 4-0 resonance, and 1-3 resonances and 2-2 resonance}:
+\begin{align}
+\mathcal{C}_{\rm{TC}} &\equiv \bigl\{ \left(c_{\Box,i},\bar{c}_{\Box,i}\right) \bigr\} \\
+&=\bigl\{ \left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right) \bigr\}
+\end{align}
 where we implicitly include rotational symmetry related resonances. We will limit or discussion to $v_\bplqt=0$ such that the corresponding Hamiltonian is
@@
 \end{equation}
-In this case the equal superposition RK wavefunction is the exact ground state occurs in the absence of a potential energy term.
-
-    Now we will introduce the toric code on the square lattice which will sever as a reference and
-    point of comparison to the discussion of the $Z_3$ case. The toric code Hamiltonian is given by
-    %
-    \begin{equation}
-        H_t = -J_e\sum_v A_v - J_m\sum_p B_p
-        \label{eqn:toric_code_ham}
-    \end{equation}
-    %
-    where the operator $A_v$ ($B_p$) acts on the vertex $v$ (plaquette $p$), and the sum over $v$ ($p$) 
-    is the sum over all vertices (plaquettes). 
-    In the toric code, Ising degrees of freedom live on the links of the
-    lattice and the operators $A_v$ and $B_p$ can be expressed as
-    %
-    \begin{equation}
-        A_v = \prod_{i\in v} \sigma^x_i
-        ,
-    \end{equation}
-    %
-    and
-    \begin{equation}
-        B_p = \prod_{i\in p} \sigma^z_i
-        .
-    \end{equation}
-    %
-    The products are over the links touching vertex $v$ and the edges of plaquette $p$ for
-    $A_v$ and $B_p$ respectively. It is not difficult to show that 
-    $[A_v,A_{v'}]=0$ for all $v$ and $v'$, 
-    $[B_p,B_{p'}]=0$ for all $p$ and $p'$, and $[A_v,B_p]=0$. The comutation relation between $A$
-    and $B$ holds even if they share links because they
-    can only share an even number of links. Given the commutation relations,
-    the toric Hamiltonian can be solved term by term.
-
-    Even without a rigorous solution it is possible to guess at the form of the Toric code
-    ground state wave function. The first term in \ref{eqn:toric_code_ham} is maximized 
-    when an even number of links touching each vertex are spin up or down in the
-    $\sigma^z$ basis. By coloring the links of all down spins the groundstate will
-    contain closed loops. The second term in \ref{eqn:toric_code_ham} is maximized for a
-    superposition of loops since $B_p$ flips the spins around a plaquette $p$. The ground state
-    wave function is then a superposition of all possible closed loop configurations. 
-    %Since $B_p$ is a local operator
-    %though the alowed loop configurations are determined by how the sytem in initilized.
-
-    The electric and magnetic string operators are
-    \begin{equation}
-        S^e_{\Gamma} = \prod_{i\in\Gamma_e} \sigma^x_i
-        ,
-    \end{equation}
-    \begin{equation}
-        S^m_{\Gamma} = \prod_{i\in\Gamma_m} \sigma^z_i
-        ,
-    \end{equation}
-    where the path is denoted by $\Gamma$. The electric string operator acts along the
-    links whereas the magnetic string operator acts along a path that perpendicularly
-    intersects the links. 
-    Electric and magnetic excitations are created when the string operator acts on an unclosed path. 
-    The electric excitations create monomer defects in the lattice at the end of the string, 
-    each of defects costing energy of $2J_e$. 
-    The magnetic excitations, which are 
-    are variational excited states  orthogonal
-    to the groundstate, create excitations at the ends in the ceter of two plaquettes.
-    Each end of the magnetic
-    string, a vison, costs energy of $2J_m$.
-
-    operating on a nontrivial path (genus of system $>0$) with $S_e$ changes the topological sector.
-    The current topological sector can be determined
-    by acting around the congugate path with $S_m$, e.g. on a torus, acting with $S_e$ along a
-    path that encloses the major or minor axis changes the topological sector and acting on a path
-    that encloses the minor axis with $S_m$ measures the topological sector.
-    As defined the magnetic string can only produce two different values called winding number.
-    Therefore, there are $4^g$ topological sectors on the torus where $g$ is the
-    genus of the system.
+In this case the equal superposition RK wavefunction is the exact ground state occurs in the absence of a potential energy term, as we can define a projection operator on each plaquette
+\begin{equation}
+h_\Box \equiv \frac{1}{2} \left( \mathbb{1} - \sum_i \eket{c_{\Box,i}}\ebra{\bar{c}_{\Box,i}} + h.c. \right)
+\end{equation}
+such that $\HTC$ takes the form of \Eqref{eq:HRK} (up to a constant), and the RK state is the ground state for all values of $t$.
+
+The increased dynamics of $\HTC$ vs.
+$\HQDM$ no longer conserve the dimer flux $\Phi_\Gamma$ through a closed curve; only $\Phi_\Gamma \mod 2$ is preserved by $\HTC$.
+Consequently, the string operator which commutes with $\HTC$ (for closed strings) is
+\begin{equation}
+S_\gamma^{\rm{TC}} \equiv e^{i\pi \Phi_\gamma}.
+\end{equation}
+Thus for each topologically non-trival loop, $S_\Gamma$ has two eigenvalues $\pm 1$, and the topological sectors on the torus can be labeled as $\Omega: (\pm 1,\pm1)$.
+Thus the extensive degeneracy of the fixed number constrained models has been reduced to a finite ground state degeneracy in the fixed parity models.
+
+Defects at a vertex in the Toric Code models carry a $Z_2$ electric charge of $-1$, consistent with the $Z_2$ gauge theory description of the models.
 

### 2016-04-29 qdpm_paper.tex
Added some structure factor figures

@@
     \end{equation}
-    where $d_i$ is the ising degrees of freedom on link i.
+    where $d_i$ represents the presence of a dimer on link i, $1/2$ or $-1/2$ for the presence or
+    absence of a dimer respectively.
     In order for the QDPM to exhibit topological order there we must find that it is in a gaped
     dimer liquid phase. It is likely that the QDPM in a liquid phase at the RK point because there 
-    we find no evedence of broken symmetries for system sizes up to $32\times32$. As an example of the
+    we find no evidence of broken symmetries for system sizes up to $32\times32$. As an example of the
     absence of broken symmetries we show
-    the dimer correlation function measuered between a single dimer and all other dimers on the
+    the dimer correlation function measured between a single dimer and all other dimers on the
     lattice in Fig.~\ref{fig:fig:dimer_gry_scale_qdpm} for a $16x16$ lattice.
@@
         \includegraphics[width=0.8\linewidth]{dimer_gry_scale_qdpm.pdf}
-        \caption{Gray scale (actual data) of the dimer corelation between the dimer in the upper
+        \caption{Gray scale (actual data) of the dimer correlation between the dimer in the upper
         left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
@@
 
-    The dimer correlations decay exponetialy in the distance between the dimers. 
+    The dimer correlations decay exponentially in the distance between the dimers. 
     In Fig.~\ref{fig:spacial_dmr_cor} we show the dimer correlations between horizontal dimers
@@
         \label{fig:spacial_dmr_cor}
+    \end{figure}
+
+    %\begin{figure}[htpb]
+    %    \centering
+    %    \includegraphics[width=0.8\linewidth]{spacial_z3vis_cor.pdf}
+    %    \caption{The $Z_3$ vison correlation function for $\gamma=0.5$.}
+    %    \label{fig:spacial_z3vis_cor}
+    %\end{figure}
+
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=1.0\linewidth]{qdpm_dmr_HM_16x16.pdf}
+        \caption{QDPM dimer structure factor $\gamma=0.5$.}
+        \label{fig:spacial_z3vis_cor}
+    \end{figure}
+
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=1.0\linewidth]{qdpm_vis_HM_16x16.pdf}
+        \caption{QDPM $Z_3$ vison structure factor $\gamma=0.5$.}
+        \label{fig:spacial_z3vis_cor}
+    \end{figure}
+
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=1.0\linewidth]{vis_dmr_qdpm_struc_fac_16x16.pdf}
+        \caption{The QDPM dimer structure factor $S_d(k)$ and $Z_3$ vison structure factor $S_v(k)$
+        shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
+        points for $\gamma=0.5$.}
+        \label{fig:vis_dmr_cut}
     \end{figure}

### 2016-04-30 qdpm_paper.tex
Reorganized results sections

--- 2016-04-25 qdpm_paper.tex
@@
 \newcommand{\secref}[1]{Sec. \ref{#1}}
+\newcommand{\tabref}[1]{Tab. \ref{#1}}
 
@@
 \newcommand{\HQDM}{H_\mathrm{QDM}}
-\newcommand{\HTC}{H_\mathrm{TC}}
+\newcommand{\HIGT}{H_\mathrm{IGT}}
+\newcommand{\HQDPM}{H_\mathrm{QDPM}}
 
@@
 
-\title{Topological order in the quantum dimer-pentamer model}
+\title{$Z_3$ topological order in the quantum dimer-pentamer model}
 
@@
 Although not detectable by local operators, topological order arises due to a non-local entanglement structure that leaves a signatures in the bipartite entanglement entropy~\cite{Levin2006a,Kitaev2006b}.
-Such topological phases provide the basis for a proposal for fault-tolerant quantum information processing~\cite{Freedman2001,Kitaev2003}.
+Such topological phases may provide the basis for fault-tolerant quantum information processing~\cite{Freedman2001,Kitaev2003}.
 
@@
 Such models offer the possibility of furthering the understanding of these phases as well as providing possibly candidate experimental systems in which to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Martinis2015}.
-A variety of exactly soluble lattice models are known to support ground states with topological order that ranges from the simplest variety, so-called $Z_2$ topological order~\cite{Kitaev2003,Wen2003}, to those with non-Abelian anyonic excitations~\cite{Levin2005a,Kitaev2006a}.
-These exactly soluble models generally involve complex many-body interactions, and thus it is desirable to find simpler models supporting topological order that are closer to what is accessible experimentally.
-
-Among the simplest class of models displaying topological quantum liquid phases are those with local geometric constraints; such constraints inhibit the formation of symmetry breaking local order and given sufficient dynamics, such models may have symmetric liquid ground states.
-The simplest such geometrically constrained model is the quantum dimer model (QDM) describing dimer degrees of freedom living on the links of a lattice~\cite{Rokhsar1988,Moessner2008}; the hard-core, fully-packed QDM has a local constraint that requires exactly one dimer touching each vertex.
+A variety of exactly soluble lattice models are known to support ground states with topological order that ranges from the simplest variety, $Z_2$ topological order~\cite{Kitaev2003,Wen2003}, to those with non-Abelian anyonic excitations~\cite{Levin2005a,Kitaev2006a}; such models generally involve complex many-body interactions, and thus it is desirable to find simpler models supporting topological order that are closer to what is accessible experimentally.
+
+Among the simplest class of models displaying topological quantum liquid phases are those with local geometric constraints; the constraints inhibit the formation of symmetry breaking local order and given sufficient dynamics, may lead to a symmetric liquid ground state.
+One of the most basic of these is the quantum dimer model (QDM) describing dimer degrees of freedom living on the links of a lattice~\cite{Rokhsar1988,Moessner2008}; the hard-core, fully-packed QDM has a local constraint that requires exactly one dimer touching each vertex.
 
@@
 While on non-bipartite lattices, the QDM posses a topologically ordered ground state~\cite{Moessner2001a,Fendley2002}, on the square lattice there is only a liquid ground state at an isolated critical quantum point~\cite{Leung1996,Syljuasen2006}.
-If the hard-core constraint of the QDM is relaxed to a parity constraint such that each vertex much have an even (odd) number of dimers touching each vertex, the simplest non-trivial dynamics lead to the (odd) toric code which has a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
-The existence of topologically ordered ground states in dimer-based models is intimately related to the local constraint which imposes a local gauge symmetry in the low energy Hilbert space; the topological order that arises is directly related to a discrete gauge theory with the appropriate local gauge constraint~\cite{Moessner2001}.
-
-Given that these models with dimer degrees of freedom and local constraints posses the simplest non-trivial local (Ising) Hilbert space at each link, they provide a potentially simpler route to engineering exotic phases; the local constraints can often be enforced by a local potential energy penalty and the required dynamics are generally expected to arise at the lowest order non-trivial order in perturbation theory.
+If the hard-core constraint of the QDM is relaxed to a parity constraint such that each vertex much have an odd (or even) number of dimers touching each vertex, the simplest non-trivial dynamics leads to a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
+The existence of topologically ordered ground states in dimer-based models is intimately related to the local constraint which imposes a local gauge symmetry in the Hilbert space; the topological order that arises is directly related to a discrete gauge theory with the appropriate local gauge constraint~\cite{Moessner2001}.
+
+Given that these models with dimer degrees of freedom and local constraints posses the simplest non-trivial local (Ising) Hilbert space at each link, they provide a potentially simpler route to engineering exotic phases.
+The local constraints can often be enforced by a local potential energy penalty and the required dynamics are generally expected to arise at the lowest order non-trivial order in perturbation theory.
 We will refer to such models with dimer degrees of freedom on links and local constraints at vertices as \emph{generalized quantum dimer modes} (GQDMs).
@@
 We consider systems with Ising-like dimer degrees of freedom on each link, such that each link has either $0$ or $1$ dimers.
+Given an Ising spin $\sigma_\ell$ on each link $\ell$ we define the number of dimers on the link $n_\ell \equiv 1/2+\sigma_\ell^z$, where $\sigma_\ell^i$ are the associated Pauli matrices.
 The Hilbert space consists of configurations of dimers on the square lattice that satisfy a local constraint at each vertex.
-Defining $n_v$ as the number of dimers that touch a vertex, we can distinguish between fixed number constraints of the form $n_v = n_0$ and fixed parity constraints of the form $n_v\mod 2 = n_P$ (see \figref{fig:example_local_constraints}).
+We define a $U(1)$ charge $Q_v$ at each vertex $v$ of the lattice in terms of the number of dimers touching $v$, $n_v\equiv \sum_{\ell \in v}n_\ell$:
+\begin{equation}
+Q_v \equiv \pm \left( n_v - c_P \right)
+\end{equation}
+where $c_P = 2$, ($c_P=1$) for models in the even (odd) sector of the constraint, and the $+$($-$) sign corresponds to vertices on the $A$($B$) sublattice.
+A local dimer number constraint requires $Q_v$ to vanish for all vertices; a dimer parity constraint requires only $Q_v \mod 2$ to vanish $\forall v$.
 
@@
 
-Because of the local constraints, all states in the Hilbert space of a GQDM are invariant under local gauge transformations a the vertices, $G_v$ of the general form~\cite{Moessner2001}
-\begin{equation}
-G_v = e^{i \alpha \left( n_v -c_0 \right)}; \notag
-\end{equation}
-where the $c_0$ and $\alpha$ depend on the constraint.  
+Because of the local constraints, all states $\ket{\psi}$ in the Hilbert space of a GQDM are invariant under local gauge transformations $G_v \ket{\psi} = \ket{\psi}$ a the vertices, $G_v$ of the general form~\cite{Moessner2001}
+\begin{equation}
+G_v = e^{i \alpha_v Q_v}, \label{eq:Gv}
+\end{equation}
+where the allowed values of $\alpha_v$ depend on the constraint.  
 By construction, the Hamiltonian is gauge invariant and thus commutes with $G_v$
@@
 \end{equation}
+
 If a defect is introduced which violates the local constraint at a vertex, this can be viewed as an ``electric charge'' living on the vertex, within the context of the original GQDM. 
+%Defects may be created in a GQDM by defining an ``electric string'' operator that creates pairs of defects and thus generating ``charged'' states that are outside the gauge invariant Hilbert space:
+%\begin{equation}
+%S_{vv'}^e \equiv \prod_{\ell \in \tilde{\gamma}_{vv'}} \sigma_\ell^x
+%\end{equation}
+%where $\tilde{\gamma}_{vv'}$ is an open string on the lattice from $v$ to $v'$.
+When acting on a gauge invariant state, $S_{\tilde{\gamma}}^e$ creates a neutral pair of charges $Q_v = \pm 1$ at the ends of $\tilde{\gamma}$ where the signs depend on the lattice and the initial configuration of vertices.
 One may determine if such electric charges are confined by introducing a pair of such defects and computing their spatial correlation function, thus determining the confined or deconfined nature of the GQDM ground state.
@@
 \begin{equation}
-\tilde{\Phi}_\gamma \equiv -\frac{c_0}{4} \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) 
-\end{equation}
-and the total charge $Q_\Gamma$ enclosed in a closed loop $\Gamma$ as
-\begin{equation}
-Q_\Gamma \equiv \Phi_\Gamma+ \tilde{\Phi}_\Gamma.
-\end{equation}
+\tilde{\Phi}_\gamma \equiv -\frac{c_P}{4} \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) 
+\end{equation}
+and the total charge enclosed in a closed loop $\Gamma$ is $Q_\Gamma = \Phi_\Gamma+ \tilde{\Phi}_\Gamma$.
 (Alternately can think of the source of $\Phi_\Gamma$ to be static charges of charge $+c_0$ ($-c_0$) sitting at the verticies of the $A$($B$) sub-lattice.).
@@
 \begin{equation}
-S_\gamma \equiv e^{i \alpha \left( \Phi_\gamma - \tilde{\Phi}_\gamma \right)}
+S_\gamma \left( \alpha \right) \equiv e^{i \alpha \left( \Phi_\gamma - \tilde{\Phi}_\gamma \right)} \label{eq:Sgamma}
 \end{equation}
@@
 For open strings, $S_\gamma$ does not commute with the Hamiltonian and can be viewed as creating a pair of ``magnetic charges'' at the ends of the string: correspondingly $S_\gamma \ket{\Phi_{\RK}}$ can used as a trial wavefunction for an excited state with a pair of magnetic charges.
+
+On surfaces with non-trivial topology, we may define the topological loop operators
+\begin{equation}
+W_{X,Y} \left( \alpha \right) \equiv S_{\Gamma_{X,Y}} \left( \alpha \right)
+\end{equation}
+where $\Gamma_{X,Y}$ are topologically non-trivial closed loops that wind once about the $X$ and $Y$ directions of the torus, respectively.
+Since $W_{X,Y} (\alpha)$ commute with the Hamiltonian, we may use their eigenvalues to label the ground states.
 
@@
 
-The two unique fixed-number constraints on the square lattice $n_0 = 1$ and $n_0=2$ lead to the QDM and the quantum full-packed loop model (QFPLM), respectively.
-For such GQDMs with a number constraint, we write the gauge transformation as:
-\begin{equation}
-G_v = e^{i \alpha \left( n_v -n_0 \right)}; \notag
-\end{equation}
-as the states in the GQDM Hilbert space are invariant under $G_v$ for all $0 \leq \alpha \leq 2 \pi$, this represents a local $U(1)$ gauge symmetry.
+The two unique fixed-number constraints on the square lattice are lead to QDM in the odd sector and the quantum full-packed loop model (QFPLM) in the even sector.
+For configurations that satisfy these a number constraints, $Q_v$ strictly vanishes, and thus all states in the Hilbert space are invariant under $G_v$ for $0 \leq \alpha_v \leq 2 \pi$ in \Eqref{eq:Gv}; this represents a local $U(1)$ gauge symmetry.
+
 The Hamiltonian for these models gives dynamics to parallel dimers on the plaquettes $\bplqt$ of the lattice:
@@
 %\end{align}
-
-In this case of a fixed number constraint, the Hamiltonian conserves the dimer flux through a closed loop:
+In this case of a fixed number constraint, the Hamiltonian conserves $Q_v$ and therefore the dimer flux through any closed loop such that:
 \begin{equation}
@@
 
-The gauge constraint requires each vertex to have $Q_v = 0$; thus defects which violate the constraint have $Q_v \neq 0$.
-A table of the charges associated with defects in the QDM and QFPLM is listed in Table \ref{tab:defects}.
+Defects in these models correspond to states with $Q_v \neq 0$; a table of the charges associated with defects in the QDM and QFPLM is listed in \tabref{tab:defects}.
 
@@
   	\hline
-      	type & $n_v$ & $Q_{\rm{QDM}}$ & $Q_{\rm{FPLM}}$  \\
+      	type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  \\
 	\hline
@@
   \end{tabular}
-  \caption{Defects and their associated charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
+  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
   \label{tab:defects}
@@
 
-We now consider relaxing the local constraint to a parity constraint such that $n_v \mod 2 = n_P$ for $n_P = 0,1$; the resulting GQDM are the even \& odd parity Toric Code (or Ising gauge theory).
-These models have a correspondingly reduced gauge symmetry which can be written as
-\begin{equation}
-G_v^P = e^{\pm i \pi \left(n_v-n_P\right)}, \notag
-\end{equation}
-and the gauge symmetry is now reduced from $U(1)$ to $Z_2$.
+We now consider relaxing the local constraint to a parity constraint such that only $Q_v^{Z_2} \equiv (Q_v \mod 2)$ is required to vanish; the resulting GQDM are the even and odd sectors are the  even \& odd Ising gauge theories (IGT) (and the closely related even and odd sector Toric Codes).
+In these cases, the local constraint requires $\alpha_v \in \{ 0, \pi\}$ in \Eqref{eq:Gv} and therefore the gauge symmetry is reduced from $U(1)$ to $Z_2$.
 The set of allowed dimer resonances $\mathcal{C}_{\rm{TC}}$ is expanded accordingly \textcolor{red}{Owen: Add symbols for 4-0 resonance, and 1-3 resonances and 2-2 resonance}:
@@
 \begin{equation}
-\HTC\left(t\right) \equiv \HGQDM \biggl( \mathcal{C}_{\rm{TC}},\bigl\{ \left(t,0\right) \bigr\} \biggr).
+\HIGT\left(t\right) \equiv \HGQDM \biggl( \mathcal{C}_{\rm{IGT}},\bigl\{ \left(t,0\right) \bigr\} \biggr).
 \end{equation}
@@
 \end{equation}
-such that $\HTC$ takes the form of \Eqref{eq:HRK} (up to a constant), and the RK state is the ground state for all values of $t$.
-
-The increased dynamics of $\HTC$ vs.
-$\HQDM$ no longer conserve the dimer flux $\Phi_\Gamma$ through a closed curve; only $\Phi_\Gamma \mod 2$ is preserved by $\HTC$.
-Consequently, the string operator which commutes with $\HTC$ (for closed strings) is
-\begin{equation}
-S_\gamma^{\rm{TC}} \equiv e^{i\pi \Phi_\gamma}.
-\end{equation}
-Thus for each topologically non-trival loop, $S_\Gamma$ has two eigenvalues $\pm 1$, and the topological sectors on the torus can be labeled as $\Omega: (\pm 1,\pm1)$.
-Thus the extensive degeneracy of the fixed number constrained models has been reduced to a finite ground state degeneracy in the fixed parity models.
-
-Defects at a vertex in the Toric Code models carry a $Z_2$ electric charge of $-1$, consistent with the $Z_2$ gauge theory description of the models.
-
-    \subsection{$Z_3$ Toric Code on the Square Lattice}
+such that $\HIGT$ takes the form of \Eqref{eq:HRK} (up to a constant), and the RK state is the ground state for all values of $t$.
+
+The increased dynamics of $\HIGT$ vs.
+$\HQDM$ no longer conserve the dimer flux $\Phi_\Gamma$ through a closed curve; only $\Phi_\Gamma \mod 2$ is preserved by $\HIGT$.
+Consequently, to define the string and loop operators which commutes with $\HIGT$ (for closed strings) we fix $\alpha = \pi$ in \Eqref{eq:Sgamma}:
+\begin{equation}
+S_\gamma^{\rm{IGT}} \equiv S_\gamma \left( \pi \right), \quad W_{X,Y}^{\rm{IGT}} \equiv W_{X,Y} \left( \pi \right).
+\end{equation}
+Thus the $W_{X,Y}^{\rm{IGT}}$ have two eigenvalues $\pm 1$, and the topological sectors on the torus can be labeled as $\Omega: (\pm 1,\pm1)$; consequently the extensive degeneracy of the fixed number constrained models has been reduced to a finite ground state degeneracy in the fixed parity models.
+
+Defects in the Ising Gauge theories have $Q_v^{Z_2} = 1$ and we identify these defects as $Z_2$ electric charges on the corresponding vertices.
+
+The ground states of $\HIGT$ are fourfold degenerate on the torus and have exponentially decaying dimer-dimer and monomer-monomer correlations (\textcolor{red}{Is this known for both sectors}) and a finite energy gap; such features demonstrated the deconfined topologically ordered nature of the ground state of the IGTs.
+
+We may understand the emergence of the $Z_2$ topologically ordered phase of IGTs from the QDM and QFPLM from the following picture.
+The additional vertex configurations that are allowed in the IGTs (monomers and pentamers in the even sector and tetramers in the odd sector) relative to the number constrained models have $Q_v = \pm 2$.
+It is known that coupling a $U(1)$ gauge field to a charge $q$ matter field can result in an $Z_q$ gauge theory~\cite{Fradkin1979}; thus in the IGTs we have addded dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result.
+We note that pentamers are charge $\pm3$ objects in the QDM (see \tabref{tab:defects}); thus below we investigate whether introducing pentamers into the QDM leads to an effective $Z_3$ gauge theory.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Quantum Dimer Pentamer Model}
+
+We define the Hilbert space of the QDPM to be an odd sector GQDM where vertices are constrained to be touched by a single dimer or the center of a pentamer, such that $n_v = 1,4$.
+For defect-free configurations in the QDPM, $Q_v$ only vanishes modulo $3$;  thus we may define a $Z_3$ charge,
+\begin{equation}
+Q_v^{Z_3} \equiv \left(Q_v~\rm{mod}~3\right)
+\end{equation}
+ which strictly vanishes at each vertex, representing the local constraint.
+All states in the QDPM are invariant under an exact local $Z_3$ gauge symmetry given by \Eqref{eq:Gv} with $\alpha_v \in \{0,\pm 2\pi/3\}$.
+Thus introducing pentamers in the QDM reduces the gauge symmetry from $U(1)$ to $Z_3$.
+
+The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice (see \figref{fig:pentamer_moves}).
+Thus we may write $\HQDPM$ as the following:
+\begin{equation}
+\HQDPM \equiv \HQDM + H_{\rm{pent}}
+\end{equation}
+where $H_{\rm{pent}}$ only involves the resonances in \figref{fig:pentamter_moves} involving pentamers.
+
+ %%%%%%%%%%%%%%%%%
+\begin{figure}[tpb]
+\centering
+\includegraphics[width=0.8\linewidth]{pentamer_moves.pdf}
+\caption{a) Horizontal creation an annihilation, b) horizontal move \textcolor{red}{Owen:fix this move}, c) diagonal moves \textcolor{red}{Owen: Remove (d) as it is related to (c) by rotational symmetry}}
+\label{fig:pentamer_moves}
+\end{figure}
+%%%%%%%%%%%%%%%%%
+
+Because of the terms involving pentamers, $\HQDPM$ conserves $Q_v^{Z_3}$ rather than $Q_v$, and thus $\Phi_\Gamma$ does not commute with the Hamiltonian for closed loops $\Gamma$.
+The appropriate string and loop operator corresponds to \Eqref{eq:Sgamma} with $\alpha = 2\pi/3$:
+\begin{equation}
+S_\gamma^{\rm{QDPM}} \equiv S_\gamma \left( 2\pi/3\right), \quad W_{X,Y}^{\rm{QDPM}} \equiv W_{X,Y} \left( 2\pi/3\right).
+\end{equation}
+Thus we have 
+\begin{equation}
+\left[ W_{X,Y}^{\rm{QDPM}}, \HQDPM \right] = 0.
+\end{equation}
+and for closed curves $\Gamma$
+\begin{equation}
+\left[ S_\Gamma^{\rm{QDPM}}, \HQDPM \right] = 0.
+\end{equation}
+
+Our numerical simulations (discussed below in \ref{sec:???}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector.
+The exact zero energy ground state at the RK point, where $t_i=v_i, i \in \{ 0,1,2,3\}$, is the RK state, where the superposition is taken to be over all states in the topological sector $\Omega$ which are labeled by the topological loop operators
+\begin{equation}
+\Omega = \left(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}} \right)
+\end{equation}
+Since the $W_{X,Y}^{\rm{QDPM}}$ operators have eigenvalues $\{1,e^{i 2\pi/3},e^{-i 2\pi/3},\}$...
+
+Defects in the QDPM (monomers, trimers, and tetramers) carry a $Z_3$ electric charge $Q_v^{Z_3} = \pm 1$, where the sign depends on the sub-lattice and type of defect (see \ref{tab:QDPMdefects}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+  \begin{tabular}{| l | c | c | }
+  	\hline
+      	type & $n_v$ & $Q_v^{Z_3}$  \\
+	\hline
+	monomer & $0$ & -1  \\
+	\hline
+	dimer & $1$ & 0 \\
+	\hline
+	trimer & $2$ & 1 \\
+	\hline
+	tetramer & $3$ & -1  \\
+	\hline
+	pentamer & $4$ & 0 \\
+	\hline
+  \end{tabular}
+  \caption{Defects where $n_v$ dimers touch a vertex and their associated $Z_3$ electric charges on the A sub-lattice in the QDPM. Defects on the B sub-lattice have opposite charge.}
+  \label{tab:QDPMdefects}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Thus we have demonstrated that ground state at the RK point of the QDPM has an exact $Z_3$ gauge symmetry and a corresponding $9$-fold topological degeneracy on the torus.
+It remains to address whether this RK state is in the deconfined $Z_3$ topologically ordered phase of a $Z_3$ gauge theory, or in an confining symmetry broken phase.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Numerical Study of the RK ground state of the QDPM}
+
+To determine the nature of the ground state at the RK point of the QDPM, we have performed Monte Carlo calculations of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \figref{fig:pentamer_moves}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Topological winding sectors}
+
+We explicitly demonstrate how the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the $U(1)$ topological winding number $\Phi_X$ histogram.
+This is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors.
+We confirm that $\Phi_{X,Y}$ are conserved modulo $3$, leading to $9$-fold topological degeneracy.
+Notice that $\Phi_X = \pm L/2$ correspond to ordered configurations, and therefore the probability of $\Phi_{XY}$ reaching these extrema vanishes in the RK state.
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[]
+    \centering
+    \includegraphics[width=0.8\linewidth]{u1_wind_qdpm.pdf}
+    \caption{The histogram of the $U(1)$ winding number $\Phi_X$ as measured in the QDPM on a $16\times16$ lattice.
+Different colors correspond to calculations initialized to different winding sectors.
+Note that $\Phi_X$ is conserved modulo $3$, resulting in a $9$-fold topological degeneracy.}
+    \label{fig:u1_wind_qdpm}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Dimer correlations}
+
+To investigate the possibility of symmetry breaking order in the RK ground state of the QDPM, we have computed the dimer-dimer correlation function:
+\begin{equation}
+    C_{\mathrm{d}} = \langle n_0 n_r \rangle - \langle n_0 \rangle   \langle n_r \rangle   
+    .
+\end{equation}
+\figref{fig:dimer_gry_scale_qdpm} shows $C_d$ in real space for and $L=16$ lattice; we see no evidence of symmetry breaking in systems up to $L=64$.
+In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel dimers is plotted as a function of separation, and displays an exponential decay with correlation length $\chi \approx ?????$.
+Thus we find that the RK ground state of the QDPM is a symmetric dimer-pentamer liquid with exponentially decaying correlations.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.8\linewidth]{dimer_gry_scale_qdpm.pdf}
+        \caption{Gray scale of the dimer correlation function between the dimer in the upper
+        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
+         red dimers indicate correlations that are off the scale shown at the
+        bottom of the figure. \textcolor{red}{Owen: make the origin dimer a different color that the off-scale dimers}.}
+        \label{fig:dimer_gry_scale_qdpm}
+    \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{spacial_dmr_cor.pdf}
+    \caption{Correlation function between parallel dimers one the same (blue) and different (red) 
+    sub-lattice on an $L=32$ lattice. The lines represent least-squares fits to exponential decay. }
+    \label{fig:spatial_dmr_cor}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Estimating the Gap}
+    The exponetial decay of the spacial correlations shown in the previous sections 
+    implieds a gap in the spectrum though it is important to determine if the lowest lying
+    excitations are vison-like
+    or the dimer-like.  The energy gap of the dimer-like and vison-like excitations can be estimated 
+    by investigating the dimer and
+    vison imaginary time correlations respectivly as outlined by Henley \cite{Henley2004a}. 
+    One changlenge in this type of gap estimate is in resloving the correlation functions far enough out
+    in imaginary time. In appendix \ref{appendix_gap_err} we discuss our methods used to determine
+    that this particular source of systematic error is sufficinetly comparied to the gap
+    estimates for different types of excitatoins.
+
+    %At the RK point the Hamiltonian is proportional to the matrix of transitions rates the eigen modes of wich describe the time evolution of the
+    %system. Since the Hamiltonian and the rate matrix share eigenvalues the lowest energy can be
+    %found by looking at the fit of the imaginary time correlations far out in imaginary time where
+    %the smalles exponetial dominates.
+
+    In this paper we only investigate the gap at high symetry points in the Brillouin zone. 
+    In Table~\ref{tab:gap_table} we show the estimates of the dimer gap, the double $Z_2$ vison gap
+    at $L/2$ and the $Z_3$ vison gap.
+    \begin{table*}[htpb]
+    \setlength\tabcolsep{0.3cm}
+        \centering
+        %\caption{$\Delta \tau = ??$}
+        \label{tab:gap_table}
+        \begin{tabular}{l l l l}
+            \hline\hline
+                        & Dimer                 & $Z_2$ double ($L/2$)  &  $Z_3$ single (origin)     \\   
+            \hline
+            $\gamma=1.0$ $(\Delta \tau =250)$    &  &  & \\
+            $8\times8$  & $3.24(5)\times10^{-2}$ &                       &                            \\
+            $12\times12$& $1.47(5)\times10^{-2}$ &                       &                            \\
+            $16\times16$& $0.66(3)\times10^{-2}$ &                       &                            \\
+            $18\times18$& $0.64(2)\times10^{-2}$ &                       &                            \\
+            \hline
+            $\gamma=0.9$ $(\Delta \tau =500)$    &  &  & \\
+            $8\times8$  & $0.3549(9)\times10^{-2}$&$0.0993(3)\times10^{-2}$& $0.3069(3)\times10^{-2}$     \\
+            $12\times12$& $0.357(2)\times10^{-2} $&$0.256(2)\times10^{-2} $ & $0.3164(7)\times10^{-2}$    \\
+            $16\times16$& $0.357(3)\times10^{-2} $&$0.363(5)\times10^{-2} $ & $0.3170(9)\times10^{-2}$    \\
+            $18\times18$& $0.352(2)\times10^{-2} $&$0.419(3)\times10^{-2} $ & $0.3167(7)\times10^{-2}$    \\
+            \hline
+            $\gamma=0.5$    & & & \\
+            $8\times8$  & $1.0(6)\times10^{-2}$ &$0.05(5)\times10^{-2}$ & $1.7(1)\times10^{-2}$     \\
+            $12\times12$& $1.5(7)\times10^{-2}$ &                       & $1.9(7)\times10^{-2}$      \\
+            $16\times16$&                       &                       &                            \\
+            $18\times18$&                       &                       &                            \\
+        \end{tabular}
+    \end{table*}
+    This table shows that the QDPM gap is relativly constant as the system size is increased and
+    that the vison gap is lower than the dimer gap. In Fig.~\ref{fig:qdm_qdpm_gap} we show the
+    finite size scaling of the dimer gap for both the QDM and the QDPM.
+    \begin{figure}[htpb]
+        \centering
+        \includegraphics[width=0.8\linewidth]{qdm_vs_qdpm_dmr_gap.pdf}
+        \caption{Here we show the finite size scaling of the dimer gap for both the QDM and the
+        QDPM.}
+        \label{fig:qdm_qdpm_gap}
+    \end{figure}
+
+%    \subsection{Imaginary time vison correlations}
+%    \begin{figure}[htpb]
+%        \centering
+%        \includegraphics[width=0.8\linewidth]{z2_origin_vison_time_cor.pdf}
+%        \caption{Imaginary time $z_2$ \textit{single} vison correlations at the origin in the QDM model (red) and QDPM
+%        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$.}
+%        \label{fig:name}
+%    \end{figure}
+%
+%    \subsection{Imaginary time dimer correlations}
+%    \begin{figure}[htpb]
+%        \centering
+%        \includegraphics[width=0.8\linewidth]{dimer_origin_time_cor.pdf}
+%        \caption{Imaginary time dimer correlations of a single dimer in the QDM model (red) and QDPM
+%        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$. }
+%        \label{fig:}
+%
+%    \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+
+    \section{$Z_3$ Toric Code on the Square Lattice}
         In the $Z_3$ toric three degrees of freedom live on each link.
@@
 
-            \begin{figure}[htpb]
-                \centering
-                \includegraphics[width=0.8\linewidth]{u1_wind_qdpm.pdf}
-                \caption{The $U(1)$ winding number as measured in the QDPM on a $16\times16$ lattice
-                with a dimer to pentamer move fraction (need a name for this fraction HERE) of 0.5.}
-                \label{fig:u1_wind_qdpm}
-            \end{figure}
-
-    \subsection{QDM on Square lattice}
-        Here we will review the relevant
-        properties and attributes of the QDM on the square lattice for which the Hamiltonian is.
-        \begin{equation}
-            \label{}
-            H_{\mathrm{QDM}} = -t\sum_{\bplqt} 
-                \left(
-                    \left|
-                        \vrtplqt
-                    \right\rangle
-                    \left\langle
-                        \hrzplqt
-                    \right|
-                    +
-                    \mathrm{h.c.}
-                \right)
-            - v\sum_{\bplqt}
-                \left(
-                    \left|
-                        \vrtplqt
-                    \right\rangle
-                    \left\langle
-                        \vrtplqt
-                    \right|
-                    +
-                    \left|
-                        \hrzplqt{}
-                    \right\rangle
-                    \left\langle
-                        \hrzplqt
-                    \right|
-                \right)
-                .
-        \end{equation}
-        This model can be defined in terms of a single parameter $t/v$ for which the wave function is
-        known exactly at the Rokhsar and Kivelson (RK) point, the point where $t/v =1$. At the RK
-        point the wave function is the equal weighted superposition over all dimer configurations
-        and known to be in a critical liquid state with powerlaw decaying dimer correlations. This
-        model has an exact local $U(1)$ gauge symetry and is known to be described by a $U(1)$ gauge
-        thoery.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Quantum Dimer Pentamer Model}
-
-    \subsection{Local $Z_3$ Gauge Symmetry}
-
-        In the QDPM Ising degrees of freedom live on the links of the lattice.
-        The operator $\hat{\sigma}^x_l$ acts on these links with 
-        eigenvalues $\sigma_l = \pm 1$, where $\sigma_l$ is the
-        Ising variables of the $l^{\mathrm{th}}$ link on the lattice. The number operator for a give link is
-        defined as $\hat{n}_l \equiv (1+\hat{\sigma}_x)/2$ and counts the number of dimers on link $l$.
-        An exactly local gauge symmetry exists on the lattice due to the constraint that either one or
-        four dimers touch any give vertex. In terms of $n_l$ we can define an operator that counts the
-        number of dimers touching a given vertex $v$ as $n_v = \sum_{l\in v} n_l$.
-
-        the local gauge transformation $G_v$ acting on a give vertex $v$ for the quantum dimer model
-        can be expressed as
-        %
-        \begin{equation}
-            \label{}
-            G_v=e^{i \alpha (n_v - n_0)}
-        \end{equation}
-        %
-        where $n_0$ is the constrained number of dimers touching a vertex, $n_0=1$ in the QDM model,
-        The operator $G_v$ then acts in such a
-        way that only the physical states, states satisfying the local constraint 
-        are invariant. For the QDM $G_v =
-        e^{i\alpha (0)}$ and therefore $G_v$ leaves a physical state unchanged for any
-        $\alpha$ making the local gauge symmetry $U(1)$. The local gauge transformation that leaves
-        only configurations containing dimers and pentamers invariant is
-        %
-        \begin{equation}
-            \label{eqn:gauge_trans}
-            G_v = e^{i (\hat{n}_v -1) 2\pi/3}    
-        \end{equation}
-        %
-        For the QDPM $\alpha$ is must be $2\pi/3$ due to the relaxed constraint of the QDM
-        model that allows for pentamers. Relaxing the constraint of the QDM brings the local gauge
-        symmetry from $U(1)$ to $Z(3)$.
-
-    \subsection{QDPM Hamiltonian}
-
-        We work specifically at the RK point where the ground state wave function
-        is an equal weighted superposition of fully packed dimer pentamer configurations
-        %
-        \begin{equation}
-            \label{}
-            \left| \Psi \right\rangle = \frac{1}{\sqrt{N}}\sum_{\{C\}} \left| C \right\rangle
-            ,
-        \end{equation}
-        %
-        where $\{C\}$ is the set of fully packed configurations. The Hilbert space can be defined
-        using the gauge transformation in Eq.~\ref{eqn:gauge_trans} as all $\left| C \right\rangle$
-        satisfying $G \left| C \right\rangle = \left| C \right\rangle$.
-
-        The QDPM Hamiltonian comprises the QDM Hamiltonian pluss additional terms coresponding to
-        the pentamer dynamics.
-        \begin{equation}
-            H_{\mathrm{QDPM}} = H_{\mathrm{QDM}} + (1-\gamma)\mathrm{pentamer\ terms}
-            ,
-        \end{equation}
-        where $\gamma$ is a single parameter that tunes the relative energy scale of the petamer
-        terms to the QDM terms in the Hamiltonian.
-
-        The penatamers pentamer terms are constructed with the dynamics shown in
-        Fig.~\ref{fig:pentamer_moves}.  
-        \begin{figure}[htpb]
-            \centering
-            \includegraphics[width=0.8\linewidth]{pentamer_moves.pdf}
-            \caption{a) Horizontal creation an annihilation, b) horizontal move, c) and d) are two
-            different possible diagonal moves in the same direction.}
-            \label{fig:pentamer_moves}
-        \end{figure}
-        Each of the  moves shown in Fig.~\ref{fig:pentamer_moves} can be
-        rotated to produce the symmetry related counterpart (eg. vertical creation and annihilation). 
-        As an example the creation and annihilation term in the Hamiltonian is
-        \begin{multline}
-        H_{\mathrm{pentamer\ creation}} = t_{\mathrm{create}}
-            \sum_{\bstr}
-            \left(
-                \left|
-                    \hprs
-                \right\rangle
-                \left\langle
-                    \hspr
-                \right|
-                +
-                \mathrm{h.c.}
-            \right)
-            \\
-            - v_{\mathrm{create}}
-            \sum_{\bstr}
-                \left(
-                    \left|
-                        \hprs
-                    \right\rangle
-                    \left\langle
-                        \hprs
-                    \right|
-                    +
-                    \left|
-                        \hspr
-                    \right\rangle
-                    \left\langle
-                        \hspr
-                    \right|
-                \right)
-        \end{multline}
-        where the factors $t_{\mathrm{create}}$ and $v_{\mathrm{create}}$ are the coefficients of
-        the pentamer pair creation and annihilation respectively. At the RK point
-        $t/v=1$ for each all the pentamer terms. 
-        Writing the kinetic and potential energy terms as done above for all the dynamics shown in
-        Fig.~\ref{fig:pentamer_moves} and all of their symmetry related counterparts comprise the
-        the pentamer terms of the Hamiltonian.
-
-    \subsection{Winding operators}
-
-        In the QDPM there is a conserved winding operator in a given topological sector
-        \begin{equation}
-            W_{x,y} = (N_A - N_B)\mod{3} = n
-            .
-        \end{equation}
-        For $W_y$ ($W_x$), $N_A$ is the number of dimers crossed on a vertical (horizontal) cut and
-        $n=0$, $1$, or $2$ depending on the topological sector. The winding operator commutes with
-        the Hamiltonian and therefore share the same eigenvalues. Since there are three winding numbers in
-        each direction then the ground state is ninefold degenerate.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Spacial Dimer Correlation Results}
-
-    In this section we discuss the dimer dimer correlation function
-    \begin{equation}
-        C_{\mathrm{dimer}} = \langle d_0 d_r \rangle - \langle d_0 \rangle   \langle d_r \rangle   
-        ,
-    \end{equation}
-    where $d_i$ is the ising degrees of freedom on link i.
-    In order for the QDPM to exhibit topological order there we must find that it is in a gaped
-    dimer liquid phase. It is likely that the QDPM in a liquid phase at the RK point because there 
-    we find no evedence of broken symmetries for system sizes up to $32\times32$. As an example of the
-    absence of broken symmetries we show
-    the dimer correlation function measuered between a single dimer and all other dimers on the
-    lattice in Fig.~\ref{fig:fig:dimer_gry_scale_qdpm} for a $16x16$ lattice.
-    \subsection{Liquid}
-    \begin{figure}[htpb]
-        \centering
-        \includegraphics[width=0.8\linewidth]{dimer_gry_scale_qdpm.pdf}
-        \caption{Gray scale (actual data) of the dimer corelation between the dimer in the upper
-        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
-        dimers in the upperleft corner are colored red because they are off the scale shown at the
-        botom of the figure.}
-        \label{fig:dimer_gry_scale_qdpm}
-    \end{figure}
-
-    The dimer correlations decay exponetialy in the distance between the dimers. 
-    In Fig.~\ref{fig:spacial_dmr_cor} we show the dimer correlations between horizontal dimers
-    in a vertical column. We find the correlation length to be $HERE$.
-    \begin{figure}[htpb]
-        \centering
-        \includegraphics[width=0.8\linewidth]{spacial_dmr_cor.pdf}
-        \caption{(Note: This figure was made using equal probabilities of plaquette flips and
-        pentamer moves) Spacial correlation function of parallel dimers for the two different
-        sublattices distinguished by their color (red, green).}
-        \label{fig:spacial_dmr_cor}
-    \end{figure}
-
-    \subsection{Comparison to other models???}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Estimating the Gap}
-    The exponetial decay of the spacial correlations shown in the previous sections 
-    implieds a gap in the spectrum though it is important to determine if the lowest lying
-    excitations are vison-like
-    or the dimer-like.  The energy gap of the dimer-like and vison-like excitations can be estimated 
-    by investigating the dimer and
-    vison imaginary time correlations respectivly as outlined by Henley \cite{Henley2004a}. 
-    One changlenge in this type of gap estimate is in resloving the correlation functions far enough out
-    in imaginary time. In appendix \ref{appendix_gap_err} we discuss our methods used to determine
-    that this particular source of systematic error is sufficinetly comparied to the gap
-    estimates for different types of excitatoins.
-
-    %At the RK point the Hamiltonian is proportional to the matrix of transitions rates the eigen modes of wich describe the time evolution of the
-    %system. Since the Hamiltonian and the rate matrix share eigenvalues the lowest energy can be
-    %found by looking at the fit of the imaginary time correlations far out in imaginary time where
-    %the smalles exponetial dominates.
-
-    In this paper we only investigate the gap at high symetry points in the Brillouin zone. 
-    In Table~\ref{tab:gap_table} we show the estimates of the dimer gap, the double $Z_2$ vison gap
-    at $L/2$ and the $Z_3$ vison gap.
-    \begin{table*}[htpb]
-    \setlength\tabcolsep{0.3cm}
-        \centering
-        %\caption{$\Delta \tau = ??$}
-        \label{tab:gap_table}
-        \begin{tabular}{l l l l}
-            \hline\hline
-                        & Dimer                 & $Z_2$ double ($L/2$)  &  $Z_3$ single (origin)     \\   
-            \hline
-            $\gamma=1.0$ $(\Delta \tau =250)$    &  &  & \\
-            $8\times8$  & $3.24(5)\times10^{-2}$ &                       &                            \\
-            $12\times12$& $1.47(5)\times10^{-2}$ &                       &                            \\
-            $16\times16$& $0.66(3)\times10^{-2}$ &                       &                            \\
-            $18\times18$& $0.64(2)\times10^{-2}$ &                       &                            \\
-            \hline
-            $\gamma=0.9$ $(\Delta \tau =500)$    &  &  & \\
-            $8\times8$  & $0.3549(9)\times10^{-2}$&$0.0993(3)\times10^{-2}$& $0.3069(3)\times10^{-2}$     \\
-            $12\times12$& $0.357(2)\times10^{-2} $&$0.256(2)\times10^{-2} $ & $0.3164(7)\times10^{-2}$    \\
-            $16\times16$& $0.357(3)\times10^{-2} $&$0.363(5)\times10^{-2} $ & $0.3170(9)\times10^{-2}$    \\
-            $18\times18$& $0.352(2)\times10^{-2} $&$0.419(3)\times10^{-2} $ & $0.3167(7)\times10^{-2}$    \\
-            \hline
-            $\gamma=0.5$    & & & \\
-            $8\times8$  & $1.0(6)\times10^{-2}$ &$0.05(5)\times10^{-2}$ & $1.7(1)\times10^{-2}$     \\
-            $12\times12$& $1.5(7)\times10^{-2}$ &                       & $1.9(7)\times10^{-2}$      \\
-            $16\times16$&                       &                       &                            \\
-            $18\times18$&                       &                       &                            \\
-        \end{tabular}
-    \end{table*}
-    This table shows that the QDPM gap is relativly constant as the system size is increased and
-    that the vison gap is lower than the dimer gap. In Fig.~\ref{fig:qdm_qdpm_gap} we show the
-    finite size scaling of the dimer gap for both the QDM and the QDPM.
-    \begin{figure}[htpb]
-        \centering
-        \includegraphics[width=0.8\linewidth]{qdm_vs_qdpm_dmr_gap.pdf}
-        \caption{Here we show the finite size scaling of the dimer gap for both the QDM and the
-        QDPM.}
-        \label{fig:qdm_qdpm_gap}
-    \end{figure}
-
-%    \subsection{Imaginary time vison correlations}
-%    \begin{figure}[htpb]
-%        \centering
-%        \includegraphics[width=0.8\linewidth]{z2_origin_vison_time_cor.pdf}
-%        \caption{Imaginary time $z_2$ \textit{single} vison correlations at the origin in the QDM model (red) and QDPM
-%        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$.}
-%        \label{fig:name}
-%    \end{figure}
-%
-%    \subsection{Imaginary time dimer correlations}
-%    \begin{figure}[htpb]
-%        \centering
-%        \includegraphics[width=0.8\linewidth]{dimer_origin_time_cor.pdf}
-%        \caption{Imaginary time dimer correlations of a single dimer in the QDM model (red) and QDPM
-%        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$. }
-%        \label{fig:}
-%
-%    \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
 \section{Error in the Gap Estimations}

### 2016-04-30 qdpm_paper.tex

@@
         \centering
-        \includegraphics[width=0.8\linewidth]{dimer_gry_scale_qdpm.pdf}
+        \includegraphics[width=0.75\columnwidth]{dimer_gry_scale_qdpm.pdf}
         \caption{Gray scale of the dimer correlation function between the dimer in the upper
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{spacial_dmr_cor.pdf}
+    \includegraphics[width=1.0\columnwidth]{spacial_dmr_cor.pdf}
     \caption{Correlation function between parallel dimers one the same (blue) and different (red) 
@@
     \label{fig:spatial_dmr_cor}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+   \begin{figure}[]
+        \centering
+        \includegraphics[width=0.75\columnwidth]{qdpm_dmr_HM_16x16.pdf}
+        \caption{QDPM dimer structure factor $\gamma=0.5$.}
+        \label{fig:spacial_z3vis_cor}
+    \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%
+    \begin{figure}[]
+        \centering
+        \includegraphics[width=0.75\columnwidth]{qdpm_vis_HM_16x16.pdf}
+        \caption{QDPM $Z_3$ vison structure factor $\gamma=0.5$.}
+        \label{fig:spacial_z3vis_cor}
+    \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%
+    \begin{figure}[]
+        \centering
+        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_16x16.pdf}
+        \caption{The QDPM dimer structure factor $S_d(k)$ and $Z_3$ vison structure factor $S_v(k)$
+        shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
+        points for $\gamma=0.5$.}
+        \label{fig:vis_dmr_cut}
     \end{figure}
@@
 
-\section{Error in the Gap Estimations}
 \label{appendix_gap_err}

### 2016-05-07 qdpm_paper.tex
updated and added some figures
Worked on text
symbols in table

@@
 }
+\newcommand*{\fplqt}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.2ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/full_plqt} }
+}
 \newcommand*{\bhrzmv}{%
@@
     ]{Symbols/vrtplqt.pdf} }
+}
+\newcommand*{\threedownplqt}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/threedownplqt.pdf} }
+}
+\newcommand*{\threeupplqt}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/threeupplqt.pdf} }
+}
+\newcommand*{\threerightplqt}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/threerightplqt.pdf} }
+}
+\newcommand*{\threeleftplqt}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/threeleftplqt.pdf} }
+}
+\newcommand*{\onedownplqt}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/onedownplqt.pdf} }
+}
+\newcommand*{\oneupplqt}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/oneupplqt.pdf} }
+}
+\newcommand*{\onerightplqt}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/onerightplqt.pdf} }
+}
+\newcommand*{\oneleftplqt}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/oneleftplqt.pdf} }
+}
+\newcommand*{\twoupplqt}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/twoupplqt.pdf} }
+}
+\newcommand*{\twodownplqt}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=1.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/twodownplqt.pdf} }
+}
+\newcommand*{\svrtmon}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=3.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/sing_vrt_monomer.pdf} }
+}
+\newcommand*{\svrtdmr}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=3.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/sing_vrt_dimer.pdf} }
+}
+\newcommand*{\svrttrmr}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=3.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/sing_vrt_trimer.pdf} }
+}
+\newcommand*{\svrtquat}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=3.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/sing_vrt_quatramer.pdf} }
+}
+\newcommand*{\svrtpent}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=3.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/sing_vrt_pentamer.pdf} }
 }
@@
 
-Over the last several decades, experimental and theoretical work has demonstrated that strongly interacting quantum many-body systems support exotic quantum phases phases of matter not described by the Landau symmetry breaking paradigm.
+Over the last several decades, experimental and theoretical work has demonstrated that strongly interacting quantum many-body systems support exotic quantum phases of matter not described by the Landau symmetry breaking paradigm.
 One class of such quantum phases of matter are topologically ordered quantum liquids~\cite{Wen1990}, first realized experimentally via the fractional quantum Hall effect~\cite{FQHE????}.
@@
 \begin{table}
-  \begin{tabular}{| l | c | c | c |}
-  	\hline
-      	type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  \\
-	\hline
-	monomer & $0$ & -1 & -2 \\
-	\hline
-	dimer & $1$ & 0 & -1 \\
-	\hline
-	trimer & $2$ & 1 & 0 \\
-	\hline
-	tetramer & $3$ & 2 & 1 \\
-	\hline
-	pentamer & $4$ & 3 & 2 \\
+  \begin{tabular}{| l | c | c | c | c |}
+  	\hline
+    type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  &  \\
+	\hline
+    monomer & $0$ & -1 & -2 & $\svrtmon$ \\
+	\hline
+    dimer & $1$ & 0 & -1 &  $\svrtdmr$ \\
+	\hline
+    trimer & $2$ & 1 & 0 &  $\svrttrmr $ \\
+	\hline
+    tetramer & $3$ & 2 & 1 &  $\svrtquat$ \\
+	\hline
+    pentamer & $4$ & 3 & 2 &  $\svrtpent$ \\
 	\hline
@@
 \mathcal{C}_{\rm{TC}} &\equiv \bigl\{ \left(c_{\Box,i},\bar{c}_{\Box,i}\right) \bigr\} \\
-&=\bigl\{ \left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right),\left(\vrtplqt,\hrzplqt\right) \bigr\}
+&=\bigl\{
+\left(\vrtplqt,\hrzplqt\right),\left(\threeleftplqt,\oneleftplqt\right),\left(\twodownplqt,\twoupplqt\right),\left(\bplqt,\fplqt\right) \bigr\}
 \end{align}
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{u1_wind_qdpm.pdf}
+    \includegraphics[width=1.0\linewidth]{u1_wind_qdpm.pdf}
     \caption{The histogram of the $U(1)$ winding number $\Phi_X$ as measured in the QDPM on a $16\times16$ lattice.
@@
         \centering
-        \includegraphics[width=0.75\columnwidth]{qdpm_dmr_HM_16x16.pdf}
+        \includegraphics[width=0.75\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
         \caption{QDPM dimer structure factor $\gamma=0.5$.}
-        \label{fig:spacial_z3vis_cor}
-    \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%
-    \begin{figure}[]
-        \centering
-        \includegraphics[width=0.75\columnwidth]{qdpm_vis_HM_16x16.pdf}
-        \caption{QDPM $Z_3$ vison structure factor $\gamma=0.5$.}
-        \label{fig:spacial_z3vis_cor}
+        \label{fig:spacial_dmr_z3vis_cor}
     \end{figure}

### 2016-05-07 qdpm_paper.tex
changed figure sizes

@@
 \usepackage{epstopdf}
-\usepackage{scalerel}
+%\usepackage{scalerel}
 \epstopdfsetup{update} % only regenerate pdf files when eps file is newer
@@
     ]{Symbols/twodownplqt.pdf} }
-}
-\newcommand*{\svrtmon}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=3.5ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/sing_vrt_monomer.pdf} }
-}
-\newcommand*{\svrtdmr}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=3.5ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/sing_vrt_dimer.pdf} }
-}
-\newcommand*{\svrttrmr}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=3.5ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/sing_vrt_trimer.pdf} }
-}
-\newcommand*{\svrtquat}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=3.5ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/sing_vrt_quatramer.pdf} }
-}
-\newcommand*{\svrtpent}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=3.5ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/sing_vrt_pentamer.pdf} }
 }
@@
 
-Over the last several decades, experimental and theoretical work has demonstrated that strongly interacting quantum many-body systems support exotic quantum phases of matter not described by the Landau symmetry breaking paradigm.
+Over the last several decades, experimental and theoretical work has demonstrated that strongly interacting quantum many-body systems support exotic quantum phases phases of matter not described by the Landau symmetry breaking paradigm.
 One class of such quantum phases of matter are topologically ordered quantum liquids~\cite{Wen1990}, first realized experimentally via the fractional quantum Hall effect~\cite{FQHE????}.
@@
 \begin{table}
-  \begin{tabular}{| l | c | c | c | c |}
-  	\hline
-    type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  &  \\
-	\hline
-    monomer & $0$ & -1 & -2 & $\svrtmon$ \\
-	\hline
-    dimer & $1$ & 0 & -1 &  $\svrtdmr$ \\
-	\hline
-    trimer & $2$ & 1 & 0 &  $\svrttrmr $ \\
-	\hline
-    tetramer & $3$ & 2 & 1 &  $\svrtquat$ \\
-	\hline
-    pentamer & $4$ & 3 & 2 &  $\svrtpent$ \\
+  \begin{tabular}{| l | c | c | c |}
+  	\hline
+      	type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  \\
+	\hline
+	monomer & $0$ & -1 & -2 \\
+	\hline
+	dimer & $1$ & 0 & -1 \\
+	\hline
+	trimer & $2$ & 1 & 0 \\
+	\hline
+	tetramer & $3$ & 2 & 1 \\
+	\hline
+	pentamer & $4$ & 3 & 2 \\
 	\hline
@@
         \centering
-        \includegraphics[width=0.75\columnwidth]{dimer_gry_scale_qdpm.pdf}
+        \includegraphics[width=0.5\columnwidth]{dimer_gry_scale_qdpm.pdf}
         \caption{Gray scale of the dimer correlation function between the dimer in the upper
@@
         \centering
-        \includegraphics[width=0.75\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
+        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
         \caption{QDPM dimer structure factor $\gamma=0.5$.}

### 2016-05-08 qdpm_paper.tex
New figure of magnetic strings.

--- 2016-05-07 qdpm_paper.tex
@@
 }
+\newcommand*{\svrttrmrtwo}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=3.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/sing_vrt_trimer2.pdf} }
+}
 \newcommand*{\svrtquat}{%
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{QDPM_ex_config.pdf}
-    \caption{\textcolor{red}{Replace with a figure showing the orientations of the lattice links, with an open oriented string on the dual lattice as well as a closed oriented loop and topologically non-trivial loops.}The link orientations of the square lattice.}
+    \includegraphics[width=1.0\columnwidth]{mag_loops_on_orntd_lat.pdf}
+    \caption{Three oriented magnetic strings on the square lattice. From left to right we show: i) a
+    nontrivial string winding around the system in one of the two possible directions, ii) an open
+    magnetic string with two different charged (colored) visons at the end points, iii) a trivial closed
+    string. The colors red and blue distinguish the two different sublattices that orient the links.}
     \label{fig:orientedSL}
@@
 	\hline
-    trimer & $2$ & 1 & 0 &  $\svrttrmr $ \\
+    trimer & $2$ & 1 & 0 &  $\svrttrmr$ $\svrttrmrtwo$\\
 	\hline

### 2016-05-14 qdpm_paper.tex
Figures

@@
     ]{Symbols/sing_vrt_pentamer.pdf} }
+}
+\newcommand*{\pentmvcreate}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=3.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/pentmvcreate1.pdf} }
+}
+\newcommand*{\pentmvanal}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=3.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/pentmvcreate2.pdf} }
 }
@@
  %%%%%%%%%%%%%%%%%
-\begin{figure}[tpb]
-\centering
-\includegraphics[width=0.8\linewidth]{pentamer_moves.pdf}
-\caption{a) Horizontal creation an annihilation, b) horizontal move \textcolor{red}{Owen:fix this move}, c) diagonal moves \textcolor{red}{Owen: Remove (d) as it is related to (c) by rotational symmetry}}
-\label{fig:pentamer_moves}
-\end{figure}
+%\begin{figure}[tpb]
+%\centering
+%\includegraphics[width=0.8\linewidth]{pentamer_moves.pdf}
+%\caption{a) Horizontal creation an annihilation, b) horizontal move \textcolor{red}{Owen:fix this move}, c) diagonal moves \textcolor{red}{Owen: Remove (d) as it is related to (c) by rotational symmetry}}
+%\label{fig:pentamer_moves}
+%\end{figure}
 %%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+  \begin{tabular}{| l | c | }
+  	\hline
+    $c1$, $\bar{c}1$ & $\pentmvcreate$, $\pentmvanal$ \\
+	\hline
+  \end{tabular}
+  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
+  \label{tab:defects}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%
@@
     \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+    \begin{figure}[]
+        \centering
+        \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
+        \caption{Monomer correlations in the QDPM.}
+        \label{fig:vis_dmr_cut}
+    \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%

### 2016-05-26 qdpm_paper.tex
more figure stuff

@@
 \usepackage{epstopdf}
-%\usepackage{scalerel}
+\usepackage{scalerel}
 \epstopdfsetup{update} % only regenerate pdf files when eps file is newer
@@
 
-\newcommand*{\hprs}{%
+%\newcommand*{\hprs}{%
+%  \text{% change size in subscripts or superscripts
+%    \includegraphics[
+%      height=1.2ex,% adjust to suit
+%      valign=M,% center vertically
+%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+%    ]{Symbols/hrzprestar} }
+%}
+%\newcommand*{\hspr}{%
+%  \text{% change size in subscripts or superscripts
+%    \includegraphics[
+%      height=1.2ex,% adjust to suit
+%      valign=M,% center vertically
+%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+%    ]{Symbols/hrzstarpair} }
+%}
+
+\newcommand*{\bplqt}{%
   \text{% change size in subscripts or superscripts
@@
       raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/hrzprestar} }
-}
-\newcommand*{\hspr}{%
+    ]{Symbols/blank_plqt} }
+}
+\newcommand*{\fplqt}{%
   \text{% change size in subscripts or superscripts
@@
       raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/hrzstarpair} }
-}
-
-\newcommand*{\bplqt}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=1.2ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/blank_plqt} }
-}
-\newcommand*{\fplqt}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=1.2ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
     ]{Symbols/full_plqt} }
 }
-\newcommand*{\bhrzmv}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=1.2ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/blank_hrzmv} }
-}
-\newcommand*{\bdiag}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=1.2ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/blank_diag} }
-}
-\newcommand*{\bstr}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=1.2ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/blank_str} }
-}
+%\newcommand*{\bhrzmv}{%
+%  \text{% change size in subscripts or superscripts
+%    \includegraphics[
+%      height=1.2ex,% adjust to suit
+%      valign=M,% center vertically
+%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+%    ]{Symbols/blank_hrzmv} }
+%}
+%\newcommand*{\bdiag}{%
+%  \text{% change size in subscripts or superscripts
+%    \includegraphics[
+%      height=1.2ex,% adjust to suit
+%      valign=M,% center vertically
+%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+%    ]{Symbols/blank_diag} }
+%}
+%\newcommand*{\bstr}{%
+%  \text{% change size in subscripts or superscripts
+%    \includegraphics[
+%      height=1.2ex,% adjust to suit
+%      valign=M,% center vertically
+%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+%    ]{Symbols/blank_str} }
+%}
 \newcommand*{\vvemptylink}{%
@@
 }
-\newcommand*{\threedownplqt}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=1.5ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/threedownplqt.pdf} }
-}
-\newcommand*{\threeupplqt}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=1.5ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/threeupplqt.pdf} }
-}
-\newcommand*{\threerightplqt}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=1.5ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/threerightplqt.pdf} }
-}
+%\newcommand*{\threedownplqt}{%
+%  \text{% change size in subscripts or superscripts
+%    \includegraphics[
+%      height=1.5ex,% adjust to suit
+%      valign=M,% center vertically
+%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+%    ]{Symbols/threedownplqt.pdf} }
+%}
+%\newcommand*{\threeupplqt}{%
+%  \text{% change size in subscripts or superscripts
+%    \includegraphics[
+%      height=1.5ex,% adjust to suit
+%      valign=M,% center vertically
+%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+%    ]{Symbols/threeupplqt.pdf} }
+%}
+%\newcommand*{\threerightplqt}{%
+%  \text{% change size in subscripts or superscripts
+%    \includegraphics[
+%      height=1.5ex,% adjust to suit
+%      valign=M,% center vertically
+%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+%    ]{Symbols/threerightplqt.pdf} }
+%}
 \newcommand*{\threeleftplqt}{%
@@
 }
-\newcommand*{\onedownplqt}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=1.5ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/onedownplqt.pdf} }
-}
-\newcommand*{\oneupplqt}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=1.5ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/oneupplqt.pdf} }
-}
-\newcommand*{\onerightplqt}{%
-  \text{% change size in subscripts or superscripts
-    \includegraphics[
-      height=1.5ex,% adjust to suit
-      valign=M,% center vertically
-      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-    ]{Symbols/onerightplqt.pdf} }
-}
+%\newcommand*{\onedownplqt}{%
+%  \text{% change size in subscripts or superscripts
+%    \includegraphics[
+%      height=1.5ex,% adjust to suit
+%      valign=M,% center vertically
+%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+%    ]{Symbols/onedownplqt.pdf} }
+%}
+%\newcommand*{\oneupplqt}{%
+%  \text{% change size in subscripts or superscripts
+%    \includegraphics[
+%      height=1.5ex,% adjust to suit
+%      valign=M,% center vertically
+%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+%    ]{Symbols/oneupplqt.pdf} }
+%}
+%\newcommand*{\onerightplqt}{%
+%  \text{% change size in subscripts or superscripts
+%    \includegraphics[
+%      height=1.5ex,% adjust to suit
+%      valign=M,% center vertically
+%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+%    ]{Symbols/onerightplqt.pdf} }
+%}
 \newcommand*{\oneleftplqt}{%
@@
     ]{Symbols/pentmvcreate2.pdf} }
+}
+\newcommand*{\penmvhrzleft}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=3.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/pentmvhorzleft.pdf} }
+}
+\newcommand*{\penmvhrzright}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=3.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/pentmvhorzright.pdf} }
+}
+\newcommand*{\penmvdiagup}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=5.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/pentmvdiagup.pdf} }
+}
+\newcommand*{\penmvdiagdown}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=5.5ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/pentmvdiagdown.pdf} }
 }
@@
 \begin{table}
-  \begin{tabular}{| l | c | c | c | c |}
+  \begin{tabular}{| l | c | c | c | c | c |}
   	\hline
-    type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  &  \\
+    %type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  & $Q_v^{Z_3}$ & \\
+    type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  & $Q_v^{QDPM}$ & \\
 	\hline
-    monomer & $0$ & -1 & -2 & $\svrtmon$ \\
+    monomer & $0$ & -1 & -2 &  -1 & $\svrtmon$  \\
 	\hline
-    dimer & $1$ & 0 & -1 &  $\svrtdmr$ \\
+    dimer & $1$ & 0 & -1 &   0 & $\svrtdmr$ \\
 	\hline
-    trimer & $2$ & 1 & 0 &  $\svrttrmr$ $\svrttrmrtwo$\\
+    trimer & $2$ & 1 & 0 &   1 & $\svrttrmr$ $\svrttrmrtwo$ \\
 	\hline
-    tetramer & $3$ & 2 & 1 &  $\svrtquat$ \\
+    tetramer & $3$ & 2 & 1 &   -1 & $\svrtquat$ \\
 	\hline
-    pentamer & $4$ & 3 & 2 &  $\svrtpent$ \\
+    pentamer & $4$ & 3 & 2 &  0 & $\svrtpent$  \\
 	\hline
   \end{tabular}
-  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
+  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM, QFPLM, and QDPM. Defects on the B sub-lattice have opposite charge.}
   \label{tab:defects}
@@
 \begin{table}
-  \begin{tabular}{| l | c | }
+    \begin{tabular}{| c | c | c | c | c | c |}
   	\hline
-    $c1$, $\bar{c}1$ & $\pentmvcreate$, $\pentmvanal$ \\
+    $c_1$& $\bar{c}_1$ & $c_2$& $\bar{c}_2$ & $c_2$& $\bar{c}_2$ \\
+	\hline
+    $\pentmvcreate$& $\pentmvanal$ & $\penmvhrzleft$& $\penmvhrzright$ & $\penmvdiagup$& $\penmvdiagdown$ \\
 	\hline
@@
 \end{equation}
-Since the $W_{X,Y}^{\rm{QDPM}}$ operators have eigenvalues $\{1,e^{i 2\pi/3},e^{-i 2\pi/3},\}$...
-
-Defects in the QDPM (monomers, trimers, and tetramers) carry a $Z_3$ electric charge $Q_v^{Z_3} = \pm 1$, where the sign depends on the sub-lattice and type of defect (see \ref{tab:QDPMdefects}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}
-  \begin{tabular}{| l | c | c | }
-  	\hline
-      	type & $n_v$ & $Q_v^{Z_3}$  \\
-	\hline
-	monomer & $0$ & -1  \\
-	\hline
-	dimer & $1$ & 0 \\
-	\hline
-	trimer & $2$ & 1 \\
-	\hline
-	tetramer & $3$ & -1  \\
-	\hline
-	pentamer & $4$ & 0 \\
-	\hline
-  \end{tabular}
-  \caption{Defects where $n_v$ dimers touch a vertex and their associated $Z_3$ electric charges on the A sub-lattice in the QDPM. Defects on the B sub-lattice have opposite charge.}
-  \label{tab:QDPMdefects}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Since the $W_{X,Y}^{\rm{QDPM}}$ operators have eigenvalues $\{0,1,-1\}$...
+
+Defects in the QDPM (monomers, trimers, and tetramers) carry a $Z_3$ electric charge $Q_v^{Z_3} = \pm 1$, where the sign depends on the sub-lattice and type of defect (see \ref{tab:defects}).
 
@@
         \centering
-        \includegraphics[width=0.5\columnwidth]{dimer_gry_scale_qdpm.pdf}
+        \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
         \caption{Gray scale of the dimer correlation function between the dimer in the upper
@@
     \centering
-    \includegraphics[width=1.0\columnwidth]{spacial_dmr_cor.pdf}
+    \includegraphics[width=1.0\columnwidth]{spacial_cors.pdf}
     \caption{Correlation function between parallel dimers one the same (blue) and different (red) 
@@
         \centering
-        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
+        \includegraphics[width=0.75\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
         \caption{QDPM dimer structure factor $\gamma=0.5$.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Estimating the Gap}
-    The exponetial decay of the spacial correlations shown in the previous sections 
-    implieds a gap in the spectrum though it is important to determine if the lowest lying
-    excitations are vison-like
-    or the dimer-like.  The energy gap of the dimer-like and vison-like excitations can be estimated 
-    by investigating the dimer and
-    vison imaginary time correlations respectivly as outlined by Henley \cite{Henley2004a}. 
-    One changlenge in this type of gap estimate is in resloving the correlation functions far enough out
-    in imaginary time. In appendix \ref{appendix_gap_err} we discuss our methods used to determine
-    that this particular source of systematic error is sufficinetly comparied to the gap
-    estimates for different types of excitatoins.
-
-    %At the RK point the Hamiltonian is proportional to the matrix of transitions rates the eigen modes of wich describe the time evolution of the
-    %system. Since the Hamiltonian and the rate matrix share eigenvalues the lowest energy can be
-    %found by looking at the fit of the imaginary time correlations far out in imaginary time where
-    %the smalles exponetial dominates.
-
-    In this paper we only investigate the gap at high symetry points in the Brillouin zone. 
-    In Table~\ref{tab:gap_table} we show the estimates of the dimer gap, the double $Z_2$ vison gap
-    at $L/2$ and the $Z_3$ vison gap.
-    \begin{table*}[htpb]
-    \setlength\tabcolsep{0.3cm}
-        \centering
-        %\caption{$\Delta \tau = ??$}
-        \label{tab:gap_table}
-        \begin{tabular}{l l l l}
-            \hline\hline
-                        & Dimer                 & $Z_2$ double ($L/2$)  &  $Z_3$ single (origin)     \\   
-            \hline
-            $\gamma=1.0$ $(\Delta \tau =250)$    &  &  & \\
-            $8\times8$  & $3.24(5)\times10^{-2}$ &                       &                            \\
-            $12\times12$& $1.47(5)\times10^{-2}$ &                       &                            \\
-            $16\times16$& $0.66(3)\times10^{-2}$ &                       &                            \\
-            $18\times18$& $0.64(2)\times10^{-2}$ &                       &                            \\
-            \hline
-            $\gamma=0.9$ $(\Delta \tau =500)$    &  &  & \\
-            $8\times8$  & $0.3549(9)\times10^{-2}$&$0.0993(3)\times10^{-2}$& $0.3069(3)\times10^{-2}$     \\
-            $12\times12$& $0.357(2)\times10^{-2} $&$0.256(2)\times10^{-2} $ & $0.3164(7)\times10^{-2}$    \\
-            $16\times16$& $0.357(3)\times10^{-2} $&$0.363(5)\times10^{-2} $ & $0.3170(9)\times10^{-2}$    \\
-            $18\times18$& $0.352(2)\times10^{-2} $&$0.419(3)\times10^{-2} $ & $0.3167(7)\times10^{-2}$    \\
-            \hline
-            $\gamma=0.5$    & & & \\
-            $8\times8$  & $1.0(6)\times10^{-2}$ &$0.05(5)\times10^{-2}$ & $1.7(1)\times10^{-2}$     \\
-            $12\times12$& $1.5(7)\times10^{-2}$ &                       & $1.9(7)\times10^{-2}$      \\
-            $16\times16$&                       &                       &                            \\
-            $18\times18$&                       &                       &                            \\
-        \end{tabular}
-    \end{table*}
-    This table shows that the QDPM gap is relativly constant as the system size is increased and
-    that the vison gap is lower than the dimer gap. In Fig.~\ref{fig:qdm_qdpm_gap} we show the
-    finite size scaling of the dimer gap for both the QDM and the QDPM.
-    \begin{figure}[htpb]
-        \centering
-        \includegraphics[width=0.8\linewidth]{qdm_vs_qdpm_dmr_gap.pdf}
-        \caption{Here we show the finite size scaling of the dimer gap for both the QDM and the
-        QDPM.}
-        \label{fig:qdm_qdpm_gap}
-    \end{figure}
-
-%    \subsection{Imaginary time vison correlations}
-%    \begin{figure}[htpb]
-%        \centering
-%        \includegraphics[width=0.8\linewidth]{z2_origin_vison_time_cor.pdf}
-%        \caption{Imaginary time $z_2$ \textit{single} vison correlations at the origin in the QDM model (red) and QDPM
-%        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$.}
-%        \label{fig:name}
-%    \end{figure}
-%
-%    \subsection{Imaginary time dimer correlations}
-%    \begin{figure}[htpb]
-%        \centering
-%        \includegraphics[width=0.8\linewidth]{dimer_origin_time_cor.pdf}
-%        \caption{Imaginary time dimer correlations of a single dimer in the QDM model (red) and QDPM
-%        model (green) on an $8\times8$ lattice. For the QDPM the dimer/pentamer move fraction is $0.9$. }
-%        \label{fig:}
-%
-%    \end{figure}
 
@@
 
-\label{appendix_gap_err}
-
-When estimating the gap by calculating correlations in imaginary time one has to be sure
-that the range of imaginary time is appropriate otherwise it is not meaningful to compare the relative 
-sizes of the vison and dimer gaps. In
-%Fig.~\ref{fig:HERE} 
-we show the finite size scaling of the different gaps. For each gap estimation we wanted to reduce
-if not eliminate the systematic error due to and inadiquate range of imaginary time. This was
-accived by investegating the gap as a fuction of the lower cutoff in the exponential fit of. We
-extended the range of $\tau$ until the gap plataued and had little dependence on the cutoff. We show an
-example of the estimate of the $Z_3$ vison gap dependence on the lower cutoff of the fit for the
-$HERE\times HERE$ lattice with a fraction (HERE) of $0.9$ in 
-%Fig.~\ref{fig:}
-%\begin{figure}[htpb]
-%    \centering
-%    \includegraphics[width=0.8\linewidth]{name.ext}
-%    \caption{Name}
-%    \label{fig:name}
-%\end{figure}
-
-NOTE: There is also some systematic error in the discritization of time. This error falls off in the QDM
-as the number of flippable plaquestts. We assume this error it is small compared to the
-statistical error.
-
-\section{Imaginary time Vison Correlations}
-\label{appendix_tau_corr}
-
-    \subsection{$Z_2$ Single and Double Visons}
-
-        \subsubsection{Single Vison}
-            First we distiguish between the single and double vison correlation fuctions. We start with the
-            the described by Ivanov \cite{Ivanov2004} for rewriting the single vison correlation function in a
-            convieient form to implement numericaly. 
-            The correlation function between two point visons $V(\bm{x}_1,\tau_1)$, and $V(\bm{x}_2,\tau_2)$ at 
-            points in space $\bm{x}_1$, $\bm{x}_2$ and in imaginary time $\tau_1$ and $\tau_2$ can be writen as
-            \begin{equation}
-                C_{\mathrm{single}}(\bm{x}_2-\bm{x}_1,\tau_2 - \tau_1) = \langle V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_2) \rangle
-            \end{equation}
-            For the $Z_2$ vison $V(\bm{x}_i,\tau_j)^2=1$ and inserting this for $i=2$ and $j=1$ between the two vison
-            operators in the above equation we get 
-            \begin{equation}
-                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_2) = \big(V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_1)\big)
-                \big( V(\bm{x}_2,\tau_1) V(\bm{x}_2,\tau_2) \big),
-                \label{eqn:expanded_z2_v_tau_cor}
-            \end{equation}
-
-            The first product in Eq.~\ref{eqn:expanded_z2_v_tau_cor} on the RHS is a 
-            string operator between two points on the lattice at a given imaginary time $\tau_2$ 
-            \begin{equation}
-                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_1) = (-1)^{n},
-                \label{eqn:simp_z2_vison_phase}
-            \end{equation}
-            $n$ being the number of dimers intersecting the path between $\bm{x}_1$ and $\bm{x}_1$. This number
-            can not depend on the path so one must choose a meathod of ``gauge fixing''. This can be done
-            by choosing an imutable bacround configureation which also changes the phase of the
-            operator $V_{12}(\tau)$ in the same way as the dynamic dimers. 
-            Including the gauge fixing Eqn.~\ref{eqn:simp_z2_vison_phase} becomes
-            \begin{equation}
-                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_1) = (-1)^{n+n_{\mathrm{backround}}}.
-            \end{equation}
-
-            The second product in Eq.~\ref{eqn:expanded_z2_v_tau_cor} on the RHS is a string operator 
-            between two points at the location but at different imaginary time $\tau_2$. 
-            In order for the full path in space and
-            imaginary time to maintain its path independece it can be shown that the phase 
-            changes with every plaquet flip at $\bm{x}_2$. So
-            \begin{equation}
-                V(\bm{x}_2,\tau_1) V(\bm{x}_2,\tau_2) = (-1)^{n_{\mathrm{flipped}}},
-            \end{equation}
-            where $n_{\mathrm{flipped}}$ is the number of times the plaquette at $\bm{x}_2$ is flipped.
-            Finaly Eq.~\ref{eqn:expanded_z2_v_tau_cor} can be expresed as 
-            \begin{equation}
-                V(\bm{x}_1,\tau_1) V(\bm{x}_2,\tau_2) =
-                (-1)^{n+n_{\mathrm{backround}+n_{\mathrm{flipped}}}}.
-            \end{equation}
-            The gap that is being estimated by looking at the single vison correlatoin function is
-            the energy gap of a single vison exciation, only physical when the system has
-            boundries but measureable in any system topology.
-
-        \subsubsection{Double Vison}
-            Calculating the doublue vison imaginary time correlation funciton
-            \begin{equation}
-                C_{\mathrm{double}}(\bm{x}_{12},\tau_2 - \tau_1) = \langle V(\bm{x}_1,\tau_1)V(\bm{x}_2,\tau_1) V(\bm{x}_1,\tau_2)V(\bm{x}_2,\tau_2) \rangle
-            \end{equation}
-            where the first product on the RHS is the string operator acting along path between points
-            $\bm{x}_1$ and $\bm{x}_1$ at imaginary time $\tau_1$ and the second product is the
-            string operator along a path between the same points but at $\tau_2$.
-
-            by looking at the double vison correlation function in imaginary time the gap of a pair
-            of visons is extracted.
-
-    \subsection{$Z_3$ Single and Double Visons}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-06-04 qdpm_paper.tex
fis

@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{QDPM_ex_config.pdf}
+    \includegraphics[width=1.0\columnwidth]{QDPM_ex_config.pdf}
     \caption{Example of an allowed configuration in the quantum dimer-pentamer model.}
@@
     \includegraphics[width=1.0\columnwidth]{mag_loops_on_orntd_lat.pdf}
-    \caption{Three oriented magnetic strings on the square lattice. From left to right we show: i) a
-    nontrivial string winding around the system in one of the two possible directions, ii) an open
-    magnetic string with two different charged (colored) visons at the end points, iii) a trivial closed
+    \caption{$\Phi_i$: a nontrivial string winding around the system in one of the two possible
+        directions. $\Phi_2$: an open
+    magnetic string with two different charged (colored) visons at the end points. $\Phi_3$ a trivial closed
     string. The colors red and blue distinguish the two different sublattices that orient the links.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{table}
+%    \begin{tabular}{| c | c | c | c | c | c |}
+%  	\hline
+%    $c_1$& $\bar{c}_1$ & $c_2$& $\bar{c}_2$ & $c_2$& $\bar{c}_2$ \\
+%	\hline
+%    $\pentmvcreate$& $\pentmvanal$ & $\penmvhrzleft$& $\penmvhrzright$ & $\penmvdiagup$& $\penmvdiagdown$ \\
+%	\hline
+%  \end{tabular}
+%  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
+%  \label{tab:defects}
+%\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}
-    \begin{tabular}{| c | c | c | c | c | c |}
-  	\hline
-    $c_1$& $\bar{c}_1$ & $c_2$& $\bar{c}_2$ & $c_2$& $\bar{c}_2$ \\
-	\hline
-    $\pentmvcreate$& $\pentmvanal$ & $\penmvhrzleft$& $\penmvhrzright$ & $\penmvdiagup$& $\penmvdiagdown$ \\
+    \begin{tabular}{| l | c | c |}
+  	\hline
+     & $c$ & $\bar{c}$ \\
+	\hline
+    1 & $\pentmvcreate$ &  $\pentmvanal$  \\
+	\hline
+    2 &$\penmvhrzleft$&$\penmvhrzright$ \\
+	\hline
+    3 &$\penmvdiagup$& $\penmvdiagdown$\\
 	\hline
@@
 \end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
     \includegraphics[width=1.0\linewidth]{u1_wind_qdpm.pdf}
-    \caption{The histogram of the $U(1)$ winding number $\Phi_X$ as measured in the QDPM on a $16\times16$ lattice.
+    \caption{The histogram of the $U(1)$ winding number $\Phi_X$ as measured in the QDPM on a
+    $32\times 32$ lattice.
 Different colors correspond to calculations initialized to different winding sectors.
@@
         \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
-        \caption{Gray scale of the dimer correlation function between the dimer in the upper
-        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
-         red dimers indicate correlations that are off the scale shown at the
-        bottom of the figure. \textcolor{red}{Owen: make the origin dimer a different color that the off-scale dimers}.}
+        \caption{Gray scale of the dimer (left) and $Z_3$ vison (right) correlation functions
+            The color blue indicates the dimer (plaquete) from which the correlation is measured. The 
+            color red indicate correlations that are off the gray scale used here .}
         \label{fig:dimer_gry_scale_qdpm}

### 2016-06-28 qdpm_paper.tex
more fig updates

@@
     \centering
-    \includegraphics[width=1.0\columnwidth]{spacial_cors.pdf}
-    \caption{Correlation function between parallel dimers one the same (blue) and different (red) 
-    sub-lattice on an $L=32$ lattice. The lines represent least-squares fits to exponential decay. }
+    \includegraphics[width=1.0\columnwidth]{spacial_cors_parallel.pdf}
+    \caption{Correlation function between parallel dimers on the same (blue) and different (red) 
+    sub-lattice for a $L=64$ lattice. }
     \label{fig:spatial_dmr_cor}
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
+%    The lines represent least-squares fits to exponential decay. }
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=1.0\columnwidth]{spacial_cors_perp.pdf}
+    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
+    sub-lattice for a $L=64$ lattice.}
+    \label{fig:spatial_dmr_cor}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=1.0\columnwidth]{spacial_cors_z3_vis.pdf}
+    \caption{ $Z_3$ vison correlation function for $L=64$ lattice.}
+    \label{fig:spatial_dmr_cor}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
    \begin{figure}[]

### 2016-07-28 qdpm_paper.tex
new struc factor cut plot
Worked on text

@@
 \newcommand{\tabref}[1]{Tab. \ref{#1}}
+\newcommand{\note}[1]{\textcolor{red}{#1}}
 
@@
     \centering
-    \includegraphics[width=1.0\columnwidth]{QDPM_ex_config.pdf}
+    \includegraphics[width=0.75\columnwidth]{QDPM_ex_config.pdf}
     \caption{Example of an allowed configuration in the quantum dimer-pentamer model.}
@@
 \begin{equation}
-\tilde{\Phi}_\gamma \equiv -\frac{c_P}{4} \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) 
-\end{equation}
-and the total charge enclosed in a closed loop $\Gamma$ is $Q_\Gamma = \Phi_\Gamma+ \tilde{\Phi}_\Gamma$.
+\tilde{\Phi}_\gamma \equiv - \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) \tilde{n}_\ell
+\end{equation}
+where $n_\ell$ is the number operator for a static background dimer configuration which is chosen to fix the gauge, and the total charge enclosed in a closed loop $\Gamma$ is $Q_\Gamma = \Phi_\Gamma+ \tilde{\Phi}_\Gamma$.
 (Alternately can think of the source of $\Phi_\Gamma$ to be static charges of charge $+c_0$ ($-c_0$) sitting at the verticies of the $A$($B$) sub-lattice.).
@@
 
- %%%%%%%%%%%%%%%%%
-%\begin{figure}[tpb]
-%\centering
-%\includegraphics[width=0.8\linewidth]{pentamer_moves.pdf}
-%\caption{a) Horizontal creation an annihilation, b) horizontal move \textcolor{red}{Owen:fix this move}, c) diagonal moves \textcolor{red}{Owen: Remove (d) as it is related to (c) by rotational symmetry}}
-%\label{fig:pentamer_moves}
-%\end{figure}
-%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{table}
-%    \begin{tabular}{| c | c | c | c | c | c |}
-%  	\hline
-%    $c_1$& $\bar{c}_1$ & $c_2$& $\bar{c}_2$ & $c_2$& $\bar{c}_2$ \\
-%	\hline
-%    $\pentmvcreate$& $\pentmvanal$ & $\penmvhrzleft$& $\penmvhrzright$ & $\penmvdiagup$& $\penmvdiagdown$ \\
-%	\hline
-%  \end{tabular}
-%  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
-%  \label{tab:defects}
-%\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}
@@
 	\hline
-    1 & $\pentmvcreate$ &  $\pentmvanal$  \\
-	\hline
-    2 &$\penmvhrzleft$&$\penmvhrzright$ \\
-	\hline
-    3 &$\penmvdiagup$& $\penmvdiagdown$\\
+    $i$ & $\pentmvcreate$ &  $\pentmvanal$  \\
+	\hline
+    $ii$ &$\penmvhrzleft$&$\penmvhrzright$ \\
+	\hline
+    $iii$ &$\penmvdiagup$& $\penmvdiagdown$\\
 	\hline
   \end{tabular}
-  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
-  \label{tab:defects}
+  \caption{The pairs of local dimer \& pentamer configurations $c\leftrightarrow\bar{c}$ generate minimal local dynamics that create/annihilate pairs ($i$) of pentamers and translate single pentamers ($ii$ \& $iii$).
+Note that pentamers always stay on the same sublattice which is associates with their $U(1)$ charge.
+}
+  \label{tab:pentamerMoves}
 \end{table}
@@
 
-To determine the nature of the ground state at the RK point of the QDPM, we have performed Monte Carlo calculations of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \figref{fig:pentamer_moves}.
+To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamerMoves} to compute ground state expectation values.
+We studied $L\times L$ lattices with periodic boundary conditions on systems up to $L=64$.
 
@@
 
-We explicitly demonstrate how the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the $U(1)$ topological winding number $\Phi_X$ histogram.
-This is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors.
-We confirm that $\Phi_{X,Y}$ are conserved modulo $3$, leading to $9$-fold topological degeneracy.
-Notice that $\Phi_X = \pm L/2$ correspond to ordered configurations, and therefore the probability of $\Phi_{XY}$ reaching these extrema vanishes in the RK state.
+We explicitly demonstrate how the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the histogram of $U(1)$ topological winding number $\Phi_X$ .
+This is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors; we confirm that $\Phi_{X/Y}$ is only conserved modulo $3$, rather than strictly conserved as it is in the QDM.
+We find that $P(\Phi_{X/Y})$ has a roughly gaussian envelope with a width that scales with system size--this is expected as $\Phi_{X/Y} = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
+Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled by $\Phi_{X/Y} \mod 3$, or equivalently $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$, in contrast with the extensive degeneracy of the QDM.
+For the remainder of the paper we present results in the $(0,0)$, topological sector, but we see no dependence the topological sector for any of the results presented here~\note{Owen: which calculations/system sizes have you checked different topological sectors?}.
 %%%%%%%%%%%%%%%%%%%%%%%
@@
     \caption{The histogram of the $U(1)$ winding number $\Phi_X$ as measured in the QDPM on a
-    $32\times 32$ lattice.
+    $L=32$ lattice.
 Different colors correspond to calculations initialized to different winding sectors.
-Note that $\Phi_X$ is conserved modulo $3$, resulting in a $9$-fold topological degeneracy.}
+Note that $\Phi_X$ is conserved modulo $3$, resulting in a $9$-fold topological degeneracy on a torus.
+    \note{Owen: change the y-axis label to $P(\Phi_x)$ and the x-axis to $\Phi_x$. Is this still an $L=32$ lattice? Do you have $L=64$? Perhaps put both on the same plot? (with no vertical bars)}}
     \label{fig:u1_wind_qdpm}
@@
 
-To investigate the possibility of symmetry breaking order in the RK ground state of the QDPM, we have computed the dimer-dimer correlation function:
+Here we discuss the dimer density correlations in the RK ground state of the QDPM.
+In \figref{fig:dimer_gry_scale_qdpm} we plot the bare dimer-dimer correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice; here the origin $\bm{0}$ represents the blue link, and $\bm{r}$ varies over all other links of the lattice.
+We see no evidence of symmetry breaking in the dimer correlations on lattices up $L=64$.
+
   \begin{equation}
@@
 \end{equation}
-\figref{fig:dimer_gry_scale_qdpm} shows $C_d$ in real space for and $L=16$ lattice; we see no evidence of symmetry breaking in systems up to $L=64$.
  In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel dimers is plotted as a function of separation, and displays an exponential decay with correlation length $\chi \approx ?????$.
@@
         \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
-        \caption{Gray scale of the dimer (left) and $Z_3$ vison (right) correlation functions
-            The color blue indicates the dimer (plaquete) from which the correlation is measured. The 
-            color red indicate correlations that are off the gray scale used here .}
+        \caption{({\it left}) Gray scale of the dimer-dimer correlation function $\langle n_0 n_{\bm{r}}\rangle$ on an $L=16$ lattice.
+The origin corresponds to the blue link, and $\bm{r}$ varies over all other links of the lattice.
+Red links have correlations that are off the given scale.~\note{Owen: Is this the bare or connected correlation function?
+What do these plots look like on a log scale?} ({\it right}) $Z_3$ magnetic string correlation function.
+}
         \label{fig:dimer_gry_scale_qdpm}
@@
     \caption{Correlation function between parallel dimers on the same (blue) and different (red) 
-    sub-lattice for a $L=64$ lattice. }
+    sub-lattice for a $L=64$ lattice. \note{Owen: Which direction is this? Do you have data for the perpendicular direction?}}
     \label{fig:spatial_dmr_cor}
@@
         \centering
-        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_16x16.pdf}
+        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
         \caption{The QDPM dimer structure factor $S_d(k)$ and $Z_3$ vison structure factor $S_v(k)$

### 2016-07-30 qdpm_paper.tex
monomer move added
Worked on text

@@
 where $n_\ell$ is the number operator for a static background dimer configuration which is chosen to fix the gauge, and the total charge enclosed in a closed loop $\Gamma$ is $Q_\Gamma = \Phi_\Gamma+ \tilde{\Phi}_\Gamma$.
-(Alternately can think of the source of $\Phi_\Gamma$ to be static charges of charge $+c_0$ ($-c_0$) sitting at the verticies of the $A$($B$) sub-lattice.).
+(Alternately can think of the source of $\tilde{\Phi}_\Gamma$ to be static charges of charge $+c_0$ ($-c_0$) sitting at the verticies of the $A$($B$) sub-lattice.).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fixed number constraints}
+\subsection{Fixed dimer number constraints}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fixed parity constraints}
+\subsection{Fixed dimer parity constraints}
 
@@
 In these cases, the local constraint requires $\alpha_v \in \{ 0, \pi\}$ in \Eqref{eq:Gv} and therefore the gauge symmetry is reduced from $U(1)$ to $Z_2$.
-The set of allowed dimer resonances $\mathcal{C}_{\rm{TC}}$ is expanded accordingly \textcolor{red}{Owen: Add symbols for 4-0 resonance, and 1-3 resonances and 2-2 resonance}:
+The set of allowed dimer resonances $\mathcal{C}_{\rm{TC}}$ is expanded accordingly:
 \begin{align}
@@
 
-The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice (see \figref{fig:pentamer_moves}).
+The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice (see \tabref{tab:pentamer_moves}).
 Thus we may write $\HQDPM$ as the following:
@@
 \end{equation}
-where $H_{\rm{pent}}$ only involves the resonances in \figref{fig:pentamter_moves} involving pentamers.
+where $H_{\rm{pent}}$ only involves the resonances in \tabref{tab:pentamer_moves} involving pentamers.
 
@@
   \caption{The pairs of local dimer \& pentamer configurations $c\leftrightarrow\bar{c}$ generate minimal local dynamics that create/annihilate pairs ($i$) of pentamers and translate single pentamers ($ii$ \& $iii$).
-Note that pentamers always stay on the same sublattice which is associates with their $U(1)$ charge.
-}
-  \label{tab:pentamerMoves}
+Note that pentamers always stay on the same sublattice which is associated with their $U(1)$ charge.
+}
+  \label{tab:pentamer_moves}
 \end{table}
@@
 
-Our numerical simulations (discussed below in \ref{sec:???}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector.
+Our numerical simulations (discussed below in \secref{sec:numerics}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector.
 The exact zero energy ground state at the RK point, where $t_i=v_i, i \in \{ 0,1,2,3\}$, is the RK state, where the superposition is taken to be over all states in the topological sector $\Omega$ which are labeled by the topological loop operators
@@
 \section{Numerical Study of the RK ground state of the QDPM}
-
-To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamerMoves} to compute ground state expectation values.
-We studied $L\times L$ lattices with periodic boundary conditions on systems up to $L=64$.
+\label{sec:numerics}
+
+To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamer_moves} to compute ground state expectation values.
+Below we present the results of calculations on $L\times L$ lattices with periodic boundary conditions on systems up to $L=64$.
 
@@
 Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled by $\Phi_{X/Y} \mod 3$, or equivalently $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$, in contrast with the extensive degeneracy of the QDM.
+Additionally, we find no evidence of a lack of ergodicity within each of the 9 topological sectors.
 For the remainder of the paper we present results in the $(0,0)$, topological sector, but we see no dependence the topological sector for any of the results presented here~\note{Owen: which calculations/system sizes have you checked different topological sectors?}.
@@
 We see no evidence of symmetry breaking in the dimer correlations on lattices up $L=64$.
-
-  \begin{equation}
-    C_{\mathrm{d}} = \langle n_0 n_r \rangle - \langle n_0 \rangle   \langle n_r \rangle   
-    .
-\end{equation}
- In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel dimers is plotted as a function of separation, and displays an exponential decay with correlation length $\chi \approx ?????$.
-Thus we find that the RK ground state of the QDPM is a symmetric dimer-pentamer liquid with exponentially decaying correlations.
+We will restrict the rest of our disucssion to correlations between horizontal of dimers, as we find no rotational symmetry breaking, or qualitative difference between the the correlations between parallel dimers and perpendicular dimers.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-    \centering
-    \includegraphics[width=1.0\columnwidth]{spacial_cors_parallel.pdf}
-    \caption{Correlation function between parallel dimers on the same (blue) and different (red) 
-    sub-lattice for a $L=64$ lattice. \note{Owen: Which direction is this? Do you have data for the perpendicular direction?}}
-    \label{fig:spatial_dmr_cor}
-\end{figure}
-%    The lines represent least-squares fits to exponential decay. }
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-    \centering
-    \includegraphics[width=1.0\columnwidth]{spacial_cors_perp.pdf}
-    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
-    sub-lattice for a $L=64$ lattice.}
-    \label{fig:spatial_dmr_cor}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-    \centering
-    \includegraphics[width=1.0\columnwidth]{spacial_cors_z3_vis.pdf}
-    \caption{ $Z_3$ vison correlation function for $L=64$ lattice.}
-    \label{fig:spatial_dmr_cor}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
+
+The left panel of \figref{fig:structure_factor} shows the equal-time dimer-dimer structure factor, 
+\begin{equation}
+S\left( \bm{q} \right) \equiv \frac{1}{ L^2} \sum_{i,j} e^{-i \bm{q} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_i n_j \right \rangle
+\end{equation}
+where we restrict the sum to horizontal links.
+
+%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[]
@@
         \caption{QDPM dimer structure factor $\gamma=0.5$.}
-        \label{fig:spacial_dmr_z3vis_cor}
+        \label{fig:structure_factor}
     \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+  \begin{equation}
+    C_{\mathrm{d}} = \langle n_0 n_r \rangle - \langle n_0 \rangle   \langle n_r \rangle   
+    .
+\end{equation}
+ In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel dimers is plotted as a function of separation, and displays an exponential decay with correlation length $\chi \approx ?????$.
+Thus we find that the RK ground state of the QDPM is a symmetric dimer-pentamer liquid with exponentially decaying correlations.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=1.0\columnwidth]{spatial_cors_parallel.pdf}
+    \caption{Correlation function between parallel dimers on the same (blue) and different (red) 
+    sub-lattice for a $L=64$ lattice. \note{Owen: Which direction is this? Do you have data for the perpendicular direction?}}
+    \label{fig:spatial_dmr_cor}
+\end{figure}
+%    The lines represent least-squares fits to exponential decay. }
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
+    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
+    sub-lattice for a $L=64$ lattice.}
+    \label{fig:spatial_dmr_cor}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=1.0\columnwidth]{spatial_cors_z3_vis.pdf}
+    \caption{ $Z_3$ vison correlation function for $L=64$ lattice.}
+    \label{fig:spatial_dmr_cor}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
     \begin{figure}[]

### 2016-08-01 qdpm_paper.tex
Worked on text of paper

@@
 }
+\newcommand*{\monomermvA}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=5.0ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/monomer_mv_1} }
+}
+\newcommand*{\monomermvB}{%
+  \text{% change size in subscripts or superscripts
+    \includegraphics[
+      height=5.0ex,% adjust to suit
+      valign=M,% center vertically
+      raise=\fontdimen22\textfont2,% but raise it to the formula axis
+    ]{Symbols/monomer_mv_2} }
+}
 \newcommand{\ket}[1]{| #1 \rangle}
@@
     \includegraphics[width=0.75\columnwidth]{QDPM_ex_config.pdf}
-    \caption{Example of an allowed configuration in the quantum dimer-pentamer model.}
+    \caption{An example of an allowed configuration in the quantum dimer-pentamer model, in which pentamers (four dimers touching at a vertex) are allowed.}
     \label{fig:QDPMex}
@@
 \begin{equation}
-\Phi_\gamma \equiv \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) n_\ell
+\Phi_\gamma \equiv \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) n_\ell \label{eq:phi}
 \end{equation}
@@
 \begin{equation}
-\tilde{\Phi}_\gamma \equiv - \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) \tilde{n}_\ell
+\tilde{\Phi}_\gamma \equiv - \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) \tilde{n}_\ell \label{eq:phiBackground}
 \end{equation}
@@
 
+\begin{table}
+    \begin{tabular}{| l | c | c |}
+  	\hline
+     & $c$ & $\bar{c}$ \\
+	\hline
+    $i$ & $\monomermvA$ &  $\monomermvB$  \\
+    \hline
+  \end{tabular}
+  \caption{The pair of local dimer \& monomer configurations $c\leftrightarrow\bar{c}$ generate
+  minimal local monomer dynamics. Monomers always remain on their origonal sublattice. }
+  \label{tab:pentamerMoves}
+\end{table}
+
 Because of the terms involving pentamers, $\HQDPM$ conserves $Q_v^{Z_3}$ rather than $Q_v$, and thus $\Phi_\Gamma$ does not commute with the Hamiltonian for closed loops $\Gamma$.
@@
 \begin{equation}
-S_\gamma^{\rm{QDPM}} \equiv S_\gamma \left( 2\pi/3\right), \quad W_{X,Y}^{\rm{QDPM}} \equiv W_{X,Y} \left( 2\pi/3\right).
+S_\gamma^{\rm{QDPM}} \equiv S_\gamma \left( 2\pi/3\right), \quad W_{X,Y}^{\rm{QDPM}} \equiv W_{X,Y} \left( 2\pi/3\right). \label{eq:SQDPM}
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Topological winding sectors}
+\subsection{Topological sectors}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Dimer correlations}
+\subsection{Dimer density correlations}
 
 Here we discuss the dimer density correlations in the RK ground state of the QDPM.
-In \figref{fig:dimer_gry_scale_qdpm} we plot the bare dimer-dimer correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice; here the origin $\bm{0}$ represents the blue link, and $\bm{r}$ varies over all other links of the lattice.
+In \figref{fig:dimer_gry_scale_qdpm} we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice; here the origin $\bm{0}$ represents the blue link, and $\bm{r}$ varies over all other links of the lattice.
 We see no evidence of symmetry breaking in the dimer correlations on lattices up $L=64$.
@@
 \begin{equation}
-S\left( \bm{q} \right) \equiv \frac{1}{ L^2} \sum_{i,j} e^{-i \bm{q} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_i n_j \right \rangle
-\end{equation}
-where we restrict the sum to horizontal links.
+S_d\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{i,j} e^{-i \bm{k} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_i n_j \right \rangle
+\end{equation}
+where we restrict the sum to horizontal links, for an $L=32$ lattice.
+$S_d(\bm{k})$ displays maxima at $\bm{k} = (0, \pm \pi)$ due to correlation between parallel links on a given plaquette but we see no evidence of translational symmetry breaking.
+The lack of rotational symmetry of $S_d(\bm{k})$ is due to the fact that we have isolated horizontal dimers--we see no evidence of rotational symmetry breaking between horizontal and vertical dimer correlations.
+\figref{fig:structure_factor_path} shows $S_d(\bm{k})$ for a particular path through the Brillouin zone.
 
@@
         \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
-        \caption{QDPM dimer structure factor $\gamma=0.5$.}
+        \caption{({\it left}) The horizontal dimer density structure factor $S_d(\bm{k})$ for the QDPM RK ground state on an $L=32$ lattice.
+The lack of $x\leftrightarrow y$ rotational symmetry is due to the fact that horizontal links have been isolated.
+({\it right}) \note{Owen: What does this vison structure factor look like w/o the factor for the background dimerization?}}
         \label{fig:structure_factor} 
@@
         \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
-        \caption{The QDPM dimer structure factor $S_d(k)$ and $Z_3$ vison structure factor $S_v(k)$
+        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the ({\it bottom})
         shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
-        points for $\gamma=0.5$.}
-        \label{fig:vis_dmr_cut}
-    \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-  \begin{equation}
-    C_{\mathrm{d}} = \langle n_0 n_r \rangle - \langle n_0 \rangle   \langle n_r \rangle   
-    .
-\end{equation}
- In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel dimers is plotted as a function of separation, and displays an exponential decay with correlation length $\chi \approx ?????$.
-Thus we find that the RK ground state of the QDPM is a symmetric dimer-pentamer liquid with exponentially decaying correlations.
+        points for $\gamma=0.5$. Statistical errors are smaller than the symbols. \note{Owen: Make the k's in the y-axis bold. What do there look like if you added $L=16$ data to these plots?}}
+        \label{fig:structure_factor_path}
+    \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
+Additionally we have studied the nature of the decay of the connected dimer-dimer correlation function,
+  \begin{equation}
+    C_{\mathrm{d}} \left(r\right) \equiv \langle n_{\bm{0}} n_{\bm{r}} \rangle - \langle n_{\bm{0}} \rangle   \langle n_{\bm{r}} \rangle   
+\end{equation}
+where $r$ is the distance between the links $\bm{0}$ and $\bm{r}$.
+In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel links is plotted as a function of separation, \textcolor{red}{for both $r$ parallel and perpendicular to the orientation of the dimers} \note{(Owen: can you add both directions to this plot?)} for an $L=64$ lattice.
+We find that $C_d$ decays exponentially with distance with a correlations length  $\chi\approx???$; additionally we find that correlations between perpendicular dimers also decay exponentially.
 
@@
     \includegraphics[width=1.0\columnwidth]{spatial_cors_parallel.pdf}
-    \caption{Correlation function between parallel dimers on the same (blue) and different (red) 
-    sub-lattice for a $L=64$ lattice. \note{Owen: Which direction is this? Do you have data for the perpendicular direction?}}
+    \caption{The dimer-dimer density correlation function $C_d$ between parallel links in the QDPM RK ground state on a $L=64$ lattice, in directions perpendicular (circles) and parallel (squares) to the dimer orientation.
+The lines represent the best fit to an exponential decay with correlation length $\chi\approx???$.
+\note{Owen: Can you add the other direction to this plot?
+The y-axis also needs a label.
+Can you add the correlation length estimate here as well?}}
     \label{fig:spatial_dmr_cor}
 \end{figure}
-%    The lines represent least-squares fits to exponential decay. }
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-    \centering
-    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
-    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
-    sub-lattice for a $L=64$ lattice.}
-    \label{fig:spatial_dmr_cor}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{$Z_3$ magnetic string correlations}
+
+To investigate the $Z_3$ gauge theory description of the QDPM RK ground state, we study the $Z_3$ magnetic string correlation function as defined in \eqref{eq:Sgamma} \& \eqref{eq:SQDPM}:
+\begin{equation}
+C_M \left( \bm{r}_{pp'} \right) \equiv \left \langle \exp \left[ \frac{2 \pi}{3} i \left( \Phi_{\gamma_{pp'}} -\tilde{\Phi}_{\gamma_{pp'}} \right) \right] \right \rangle
+\end{equation}
+where $p$ and $p'$ are two plaquettes, and $\gamma_{pp'}$ is any open string on the dual lattice connecting $p$ and $p'$.
+
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Monomer deconfinement}
+
+%%%%%%%%%%%%%%%%%%%%%%%
     \begin{figure}[]
@@
 \section{Discussion}
+
+We have presented the quantum dimer-pentamer model on the square lattice and studied the ground state at the RK point.
+Using numerical calculations, we have demonstrated that the RK state of the QDPM is a dimer liquid, without spontaneously broken symmetry.
+We find that the correlations decay exponentially with distance in contrast to the power-law decay of correlations in the QDM.
+Additionally the extensive topological degeneracy of the QDM has been reduced to a finite 9-fold degeneracy in the QDPM on a torus.
+We also have demonstrated that monomer defects are deconfined in the QDPM.
+These results are consistent with an effective $Z_3$ gauge theory description of the low energy physics of the QDPM and the RK ground state possessing $Z_3$ topological order.
+
+Future work could directly probe the existence of a finite gap above the RK point by studying the imaginary time dynamics of correlations functions using Monte Carlo~\cite{Henley}.
+Additionally, one could conclusively demonstrate the existence of $Z_3$ topological order by computing the topological entanglement entropy in the QDPM ground state~\cite{Levin2005,Kitaev2005,Hastings2010}.
+
+A finite gap above the RK point suggests that a stable topologically ordered phase should exist surrounding the RK point; the neighboring phase diagram could be studied using quantum Monte Carlo methods.
+
+Finally, given the stability of the topologically ordered phase, it may be possible to realize the QDPM in a more microscopically realistic spin model with two body interactions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Acknowledgements}
+
+Our calculations were performed on the VACC....
 
@@
 
+\section{Additional numerical results on the QDPM RK ground state}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
+    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
+    sub-lattice for a $L=64$ lattice.}
+    \label{fig:spatial_dmr_cor}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-08-02 qdpm_paper.tex
Worked on text, updated bib

@@
     \includegraphics[
-      height=5.0ex,% adjust to suit
+      height=3.5ex,% adjust to suit
       valign=M,% center vertically
@@
 where $c_P = 2$, ($c_P=1$) for models in the even (odd) sector of the constraint, and the $+$($-$) sign corresponds to vertices on the $A$($B$) sublattice.
-A local dimer number constraint requires $Q_v$ to vanish for all vertices; a dimer parity constraint requires only $Q_v \mod 2$ to vanish $\forall v$.
+A local dimer number constraint requires $Q_v$ to vanish for all vertices; a dimer parity constraint requires only $(Q_v\mod 2)$ to vanish.
 
@@
 Therefore, for closed loops $\Gamma$, $[ S_\Gamma,\HGQDM]=0$.
-For open strings, $S_\gamma$ does not commute with the Hamiltonian and can be viewed as creating a pair of ``magnetic charges'' at the ends of the string: correspondingly $S_\gamma \ket{\Phi_{\RK}}$ can used as a trial wavefunction for an excited state with a pair of magnetic charges.
+For open strings, $S_\gamma$ does not commute with the Hamiltonian and can be viewed as creating a pair of ``magnetic charges'' at the ends of the string: correspondingly $S_\gamma \ket{\Phi_{\RK}}$ can used as a trial wavefunction for an excited state with a pair of magnetic vortices.
+If a state has topological order with deconfined electric charges, these magnetic vortices should be gapped excitations, and correspondingly the magnetic string operator should decay exponentially~\cite{Read1989a,Senthil2000,Senthil2001e}.
+The condensation of magnetic vortices can drive a phase transition from a topologically ordered phase to a conventionally order phase~\cite{Jalabert1991,Ralko2007}.
+Thus, the magnetic string correlation can be used as test for deconfinement of electric charges.
 
@@
 
-\begin{table}
-    \begin{tabular}{| l | c | c |}
-  	\hline
-     & $c$ & $\bar{c}$ \\
-	\hline
-    $i$ & $\monomermvA$ &  $\monomermvB$  \\
-    \hline
-  \end{tabular}
-  \caption{The pair of local dimer \& monomer configurations $c\leftrightarrow\bar{c}$ generate
-  minimal local monomer dynamics. Monomers always remain on their origonal sublattice. }
-  \label{tab:pentamerMoves}
-\end{table}
-
 Because of the terms involving pentamers, $\HQDPM$ conserves $Q_v^{Z_3}$ rather than $Q_v$, and thus $\Phi_\Gamma$ does not commute with the Hamiltonian for closed loops $\Gamma$.
@@
 Here we discuss the dimer density correlations in the RK ground state of the QDPM.
-In \figref{fig:dimer_gry_scale_qdpm} we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice; here the origin $\bm{0}$ represents the blue link, and $\bm{r}$ varies over all other links of the lattice.
+In \figref{fig:dimer_vison_heatmap} we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice; here the origin $\bm{0}$ represents the blue link, and $\bm{r}$ varies over all other links of the lattice.
 We see no evidence of symmetry breaking in the dimer correlations on lattices up $L=64$.
@@
         \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
-        \caption{({\it left}) Gray scale of the dimer-dimer correlation function $\langle n_0 n_{\bm{r}}\rangle$ on an $L=16$ lattice.
+        \caption{({\it left}) Gray scale of the dimer-dimer correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice.
 The origin corresponds to the blue link, and $\bm{r}$ varies over all other links of the lattice.
 Red links have correlations that are off the given scale.~\note{Owen: Is this the bare or connected correlation function?
-What do these plots look like on a log scale?} ({\it right}) $Z_3$ magnetic string correlation function.
-}
-        \label{fig:dimer_gry_scale_qdpm}
+What do these plots look like on a log scale?} ({\it right}) The $Z_3$ magnetic string correlation function $C_m(\bm{r}_{\bm{0}p})$, where the the correlations is with respect to the blue plaquette.
+\note{Are we using the real part?
+What does $\sqrt{C_M^*C_m}$ look like?
+Regardless we should make this a positive quantity so the lefthand side of the grayscale is zero.}}
+        \label{fig:dimer_vison_heatmap}
     \end{figure}
@@
 The lack of $x\leftrightarrow y$ rotational symmetry is due to the fact that horizontal links have been isolated.
-({\it right}) \note{Owen: What does this vison structure factor look like w/o the factor for the background dimerization?}}
+({\it right}) \note{Owen: Is this the real part or $\sqrt{S_M^* S_M}$}}
         \label{fig:structure_factor} 
@@
 where $p$ and $p'$ are two plaquettes, and $\gamma_{pp'}$ is any open string on the dual lattice connecting $p$ and $p'$.
+\note{Something about the background dimerization and gauge fixing here.
+Are we using the real parts or $\sqrt{C_M^*C_M}$?}
+
+In \figref{fig:dimer_vison_heatmap}, we have ploted $C_M$ for an $L=16$ lattice, which displays short distance correlations that quickly decay.
+\note{Comment here about gauge fixing breaking symmetry, if still present...}.
+We find no evidence of magnetic vortex condensation on lattices up to $L=64$.
 
@@
 \subsection{Monomer deconfinement}
+
+To study the confinement of electrically charged defects in the QDPM, we have Monte Carlo sampled the RK ground state with a single pair of monomers.
+We initialize the system with a monomer on each sub-lattice and supplement the local Monte Carlo updates with updates of the form:
+\begin{equation}
+\monomermvA  \Longleftrightarrow \monomermvB
+\end{equation}
+which appear to provide ergodic dynamics in the monomer-dimer-pentamer configuration space.
+Notice that monomers remain on the same sub-lattice, which is consistent with their assignment of a $Z_3$ electric charge of $\pm1$, depending on the sub-lattice.
 

### 2016-08-02 qdpm_paper.tex
pulling

--- 2016-07-30 qdpm_paper.tex
@@
 where $n_\ell$ is the number operator for a static background dimer configuration which is chosen to fix the gauge, and the total charge enclosed in a closed loop $\Gamma$ is $Q_\Gamma = \Phi_\Gamma+ \tilde{\Phi}_\Gamma$.
-(Alternately can think of the source of $\tilde{\Phi}_\Gamma$ to be static charges of charge $+c_0$ ($-c_0$) sitting at the verticies of the $A$($B$) sub-lattice.).
+(Alternately can think of the source of $\Phi_\Gamma$ to be static charges of charge $+c_0$ ($-c_0$) sitting at the verticies of the $A$($B$) sub-lattice.).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fixed dimer number constraints}
+\subsection{Fixed number constraints}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fixed dimer parity constraints}
+\subsection{Fixed parity constraints}
 
@@
 In these cases, the local constraint requires $\alpha_v \in \{ 0, \pi\}$ in \Eqref{eq:Gv} and therefore the gauge symmetry is reduced from $U(1)$ to $Z_2$.
-The set of allowed dimer resonances $\mathcal{C}_{\rm{TC}}$ is expanded accordingly:
+The set of allowed dimer resonances $\mathcal{C}_{\rm{TC}}$ is expanded accordingly \textcolor{red}{Owen: Add symbols for 4-0 resonance, and 1-3 resonances and 2-2 resonance}:
 \begin{align}
@@
 
-The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice (see \tabref{tab:pentamer_moves}).
+The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice (see \figref{fig:pentamer_moves}).
 Thus we may write $\HQDPM$ as the following:
@@
 \end{equation}
-where $H_{\rm{pent}}$ only involves the resonances in \tabref{tab:pentamer_moves} involving pentamers.
+where $H_{\rm{pent}}$ only involves the resonances in \figref{fig:pentamter_moves} involving pentamers.
 
@@
   \caption{The pairs of local dimer \& pentamer configurations $c\leftrightarrow\bar{c}$ generate minimal local dynamics that create/annihilate pairs ($i$) of pentamers and translate single pentamers ($ii$ \& $iii$).
-Note that pentamers always stay on the same sublattice which is associated with their $U(1)$ charge.
-}
-  \label{tab:pentamer_moves}
+Note that pentamers always stay on the same sublattice which is associates with their $U(1)$ charge.
+}
+  \label{tab:pentamerMoves}
 \end{table}
@@
 
-Our numerical simulations (discussed below in \secref{sec:numerics}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector.
+Our numerical simulations (discussed below in \ref{sec:???}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector.
 The exact zero energy ground state at the RK point, where $t_i=v_i, i \in \{ 0,1,2,3\}$, is the RK state, where the superposition is taken to be over all states in the topological sector $\Omega$ which are labeled by the topological loop operators
@@
 \section{Numerical Study of the RK ground state of the QDPM}
-\label{sec:numerics}
-
-To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamer_moves} to compute ground state expectation values.
-Below we present the results of calculations on $L\times L$ lattices with periodic boundary conditions on systems up to $L=64$.
+
+To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamerMoves} to compute ground state expectation values.
+We studied $L\times L$ lattices with periodic boundary conditions on systems up to $L=64$.
 
@@
 Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled by $\Phi_{X/Y} \mod 3$, or equivalently $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$, in contrast with the extensive degeneracy of the QDM.
-Additionally, we find no evidence of a lack of ergodicity within each of the 9 topological sectors.
 For the remainder of the paper we present results in the $(0,0)$, topological sector, but we see no dependence the topological sector for any of the results presented here~\note{Owen: which calculations/system sizes have you checked different topological sectors?}.
@@
 We see no evidence of symmetry breaking in the dimer correlations on lattices up $L=64$.
-We will restrict the rest of our disucssion to correlations between horizontal of dimers, as we find no rotational symmetry breaking, or qualitative difference between the the correlations between parallel dimers and perpendicular dimers.
+
+  \begin{equation}
+    C_{\mathrm{d}} = \langle n_0 n_r \rangle - \langle n_0 \rangle   \langle n_r \rangle   
+    .
+\end{equation}
+ In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel dimers is plotted as a function of separation, and displays an exponential decay with correlation length $\chi \approx ?????$.
+Thus we find that the RK ground state of the QDPM is a symmetric dimer-pentamer liquid with exponentially decaying correlations.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-
-The left panel of \figref{fig:structure_factor} shows the equal-time dimer-dimer structure factor, 
-\begin{equation}
-S\left( \bm{q} \right) \equiv \frac{1}{ L^2} \sum_{i,j} e^{-i \bm{q} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_i n_j \right \rangle
-\end{equation}
-where we restrict the sum to horizontal links.
-
-%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=1.0\columnwidth]{spacial_cors_parallel.pdf}
+    \caption{Correlation function between parallel dimers on the same (blue) and different (red) 
+    sub-lattice for a $L=64$ lattice. \note{Owen: Which direction is this? Do you have data for the perpendicular direction?}}
+    \label{fig:spatial_dmr_cor}
+\end{figure}
+%    The lines represent least-squares fits to exponential decay. }
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=1.0\columnwidth]{spacial_cors_perp.pdf}
+    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
+    sub-lattice for a $L=64$ lattice.}
+    \label{fig:spatial_dmr_cor}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=1.0\columnwidth]{spacial_cors_z3_vis.pdf}
+    \caption{ $Z_3$ vison correlation function for $L=64$ lattice.}
+    \label{fig:spatial_dmr_cor}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
    \begin{figure}[]
@@
         \caption{QDPM dimer structure factor $\gamma=0.5$.}
-        \label{fig:structure_factor}
+        \label{fig:spacial_dmr_z3vis_cor}
     \end{figure}
@@
 
-  \begin{equation}
-    C_{\mathrm{d}} = \langle n_0 n_r \rangle - \langle n_0 \rangle   \langle n_r \rangle   
-    .
-\end{equation}
- In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel dimers is plotted as a function of separation, and displays an exponential decay with correlation length $\chi \approx ?????$.
-Thus we find that the RK ground state of the QDPM is a symmetric dimer-pentamer liquid with exponentially decaying correlations.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-    \centering
-    \includegraphics[width=1.0\columnwidth]{spatial_cors_parallel.pdf}
-    \caption{Correlation function between parallel dimers on the same (blue) and different (red) 
-    sub-lattice for a $L=64$ lattice. \note{Owen: Which direction is this? Do you have data for the perpendicular direction?}}
-    \label{fig:spatial_dmr_cor}
-\end{figure}
-%    The lines represent least-squares fits to exponential decay. }
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-    \centering
-    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
-    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
-    sub-lattice for a $L=64$ lattice.}
-    \label{fig:spatial_dmr_cor}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-    \centering
-    \includegraphics[width=1.0\columnwidth]{spatial_cors_z3_vis.pdf}
-    \caption{ $Z_3$ vison correlation function for $L=64$ lattice.}
-    \label{fig:spatial_dmr_cor}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Monomer correlations}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
     \begin{figure}[]
@@
     \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+    \begin{tabular}{| l | c | c |}
+  	\hline
+     & $c$ & $\bar{c}$ \\
+	\hline
+    $i$ & $\monomermvA$ &  $\monomermvB$  \\
+    \hline
+  \end{tabular}
+  \caption{The pair of local dimer \& monomer configurations $c\leftrightarrow\bar{c}$ generate
+  minimal local monomer dynamics. Monomers always remain on their origonal sublattice. }
+  \label{tab:pentamerMoves}
+\end{table}
 %%%%%%%%%%%%%%%%%%%%%%%

### 2016-08-04 qdpm_paper.tex
Worked on section IV and V

--- 2016-08-02 qdpm_paper.tex
@@
 Thus we have demonstrated that ground state at the RK point of the QDPM has an exact $Z_3$ gauge symmetry and a corresponding $9$-fold topological degeneracy on the torus.
-It remains to address whether this RK state is in the deconfined $Z_3$ topologically ordered phase of a $Z_3$ gauge theory, or in an confining symmetry broken phase.
+We emphasize that despite the exact $Z_3$ local gauge symmetry of the QDPM, there is not an exact mapping to a $Z_3$ gauge theory on the square lattice, as the QDPM has Ising degrees of freedom on the links, rather than the 3 dimensional local Hilbert space of a $Z_3$ gauge theory.
+It remains to address whether this RK state is in the deconfined $Z_3$ topologically ordered phase of a $Z_3$ gauge theory, or a critically correlated or confining symmetry broken phase, which we do below.
 
@@
         \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
-        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the ({\it bottom})
+        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the $Z_3$ magnetic string structure factor $S_M$ ({\it bottom})
         shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
-        points for $\gamma=0.5$. Statistical errors are smaller than the symbols. \note{Owen: Make the k's in the y-axis bold. What do there look like if you added $L=16$ data to these plots?}}
+        points for $\gamma=0.5$.
+Statistical errors are smaller than the symbols.
+\note{Owen: Make the k's in the y-axis bold.
+What do there look like if you added $L=16$ data to these plots?
+Switch the y-axis from $S_v\rightarrow S_M$.}}
         \label{fig:structure_factor_path}
@@
 We find that $C_d$ decays exponentially with distance with a correlations length  $\chi\approx???$; additionally we find that correlations between perpendicular dimers also decay exponentially.
+
+Thus we find that the RK point of the QDPM is a symmetric dimer liquid with exponentially decaying dimer correlations, in contrast with the power-law decaying correlations of the
 
@@
 The y-axis also needs a label.
-Can you add the correlation length estimate here as well?}}
+Can you add the correlation length estimate here as well?
+Can you add the $r=0$ data point to this plot?}}
     \label{fig:spatial_dmr_cor}
@@
 \note{Comment here about gauge fixing breaking symmetry, if still present...}.
-We find no evidence of magnetic vortex condensation on lattices up to $L=64$.
+Additionally, we have plotted the magnetic string structure factor
+\begin{equation}
+S_M\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{p,p'} e^{-i \bm{k} \cdot r_{pp'}} C_M\left( \bm{r}_{pp'}\right)
+\end{equation}
+in \figref{fig:structure_factor}. \note{Discuss any effect of gauge fixing here, if relevant}.
+
+\figref{fig:vison_cor} show the decay of $C_M$ along one of the axes of the dual lattice; \note{we find this decays exponentially with distance, with a correlation length $\chi\approx???$}
+
+Thus we find no evidence of magnetic vortex condensation on lattices up to $L=64$.
 
@@
     \includegraphics[width=1.0\columnwidth]{spatial_cors_z3_vis.pdf}
-    \caption{ $Z_3$ vison correlation function for $L=64$ lattice.}
-    \label{fig:spatial_dmr_cor}
+    \caption{ $Z_3$ magnetic string correlation $C_M$ along along one axis of an $L=64$ lattice. The line corresponds to an exponential fit with correlations length \note{$\chi\approx???$}.}
+    \label{fig:vison_cor}
 \end{figure}
@@
 
-To study the confinement of electrically charged defects in the QDPM, we have Monte Carlo sampled the RK ground state with a single pair of monomers.
+To study the confinement of electrically charged defects in the QDPM, we have Monte Carlo sampled the RK ground state doped with a single pair of monomers.
 We initialize the system with a monomer on each sub-lattice and supplement the local Monte Carlo updates with updates of the form:
@@
 which appear to provide ergodic dynamics in the monomer-dimer-pentamer configuration space.
-Notice that monomers remain on the same sub-lattice, which is consistent with their assignment of a $Z_3$ electric charge of $\pm1$, depending on the sub-lattice.
+Notice that monomers remain on the same sub-lattice, which is consistent with their assignment of a $Z_3$ electric charge of $\pm1$, where the positive and negative monomers live on different sub-lattices.
+
+We then can test for the confinement of monomers by studying the monomer-monomer density correlation function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$, which is plotted in \figref{fig:monomer_correlation}.
+If the monomers are confined, we expect $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ to decay to zero at large distances; conversely if monomers are deconfined, we expect the monomers to be randomly distributed on the lattice, such that $\langle m_{\bm{0}} m_{\bm{r}} \rangle \sim L^{-4}$ at large separations.
+In \figref{fig:monomer_correlations}, the horizontal lines correspond to $L^{-4}$ for each system size; we find that the monomer correlations quickly decay to $L^{-4}$ indicating a deconfinement of monomers.
 
@@
         \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
-        \caption{Monomer correlations in the QDPM.}
-        \label{fig:vis_dmr_cut}
+        \caption{Monomer-monomer correlations function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ along the  in the QDPM RK ground state doped with a single pair of monomers on lattices up to \note{$L=48$}.
+The horizontal lines correspond to $L^{-4}$ with the color corresponding to the system size.
+\note{Owen: Do you have data for $L=64$?
+Can you make the subscripts in the y-axis label bold math?
+Maybe we should renomalize this plot by a factor of $L^2$.}}
+        \label{fig:monomer_correlation}
     \end{figure}
@@
 Using numerical calculations, we have demonstrated that the RK state of the QDPM is a dimer liquid, without spontaneously broken symmetry.
-We find that the correlations decay exponentially with distance in contrast to the power-law decay of correlations in the QDM.
-Additionally the extensive topological degeneracy of the QDM has been reduced to a finite 9-fold degeneracy in the QDPM on a torus.
-We also have demonstrated that monomer defects are deconfined in the QDPM.
-These results are consistent with an effective $Z_3$ gauge theory description of the low energy physics of the QDPM and the RK ground state possessing $Z_3$ topological order.
+The extensive topological degeneracy of the QDM has been reduced to a finite 9-fold degeneracy in the QDPM on a torus.
+We find that the dimer correlations decay exponentially with distance in contrast to the power-law decay of dimer correlations in the QDM.
+Additionally we also have demonstrated that monomer defects are deconfined in the QDPM, in contrast with the critical confinement of monomers in the QDM.
+Finally, we find that the $Z_3$ magnetic string correlations decay exponentially and display no evidence of $Z_3$ vortex condensation; this is consistent with $Z_3$ vortices being gapped quasiparticles excitations about the QDPM ground state.
+
+The above results suggest a $Z_3$ gauge theory description of the low energy physics of the QDPM and the RK ground state possessing $Z_3$ topological order.
 

### 2016-08-05 qdpm_paper.tex
Worked on discussion and references

@@
 Over the last several decades, experimental and theoretical work has demonstrated that strongly interacting quantum many-body systems support exotic quantum phases of matter not described by the Landau symmetry breaking paradigm.
-One class of such quantum phases of matter are topologically ordered quantum liquids~\cite{Wen1990}, first realized experimentally via the fractional quantum Hall effect~\cite{FQHE????}.
+One class of such quantum phases of matter are topologically ordered quantum liquids~\cite{Wen1990}, first realized experimentally via the fractional quantum Hall effect~\cite{Tsui1982,Laughlin1983,Wen1990a,Wen1995}.
 Despite the absence of conventional symmetry breaking and a local order parameter, topological quantum liquids possess a non-trivial quantum order that distinguishes them from trivial liquid phases~\cite{Nayak2008}.
@@
 Because of the exotic nature of topological phases and their potential use for quantum information processing, there is great interest in the development of theoretical models which display these phases.
-Such models offer the possibility of furthering the understanding of these phases as well as providing possibly candidate experimental systems in which to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Martinis2015}.
+Such models offer the possibility of furthering the understanding of these phases as well as providing candidate experimental systems in which to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Fowler2012a}.
 A variety of exactly soluble lattice models are known to support ground states with topological order that ranges from the simplest variety, $Z_2$ topological order~\cite{Kitaev2003,Wen2003}, to those with non-Abelian anyonic excitations~\cite{Levin2005a,Kitaev2006a}; such models generally involve complex many-body interactions, and thus it is desirable to find simpler models supporting topological order that are closer to what is accessible experimentally.
@@
     \includegraphics[width=0.75\columnwidth]{QDPM_ex_config.pdf}
-    \caption{An example of an allowed configuration in the quantum dimer-pentamer model, in which pentamers (four dimers touching at a vertex) are allowed.}
+    \caption{An example of an allowed configuration in the quantum dimer-pentamer model, in which pentamers (four dimers touching at a vertex) are allowed.
+\note{Owen: maybe we should stick with black and white for these cartoons}}
     \label{fig:QDPMex}
@@
     \caption{Clockwise from the upper left panel we show an example of a QDM with constraints: one
-    dimer ($n_0 = 1$), two dimers ($n_0 = 2$), and an even ($n_P = 0$) or odd ($n_P = 1$) number of dimers touching each vertex.}
+    dimer ($n_0 = 1$), two dimers ($n_0 = 2$), and an even ($n_P = 0$) or odd ($n_P = 1$) number of dimers touching each vertex.
+\note{Owen: Maybe for consistency we should make all the dimers loos like the dimers in the upper-left.}}
     \label{fig:example_local_constraints}
@@
 If a state has topological order with deconfined electric charges, these magnetic vortices should be gapped excitations, and correspondingly the magnetic string operator should decay exponentially~\cite{Read1989a,Senthil2000,Senthil2001e}.
-The condensation of magnetic vortices can drive a phase transition from a topologically ordered phase to a conventionally order phase~\cite{Jalabert1991,Ralko2007}.
+The condensation of magnetic vortices can drive a phase transition from a topologically ordered phase to a conventionally order phase~\cite{Jalabert1991,Ralko2007,Huh2011}.
 Thus, the magnetic string correlation can be used as test for deconfinement of electric charges.
@@
         \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
-        \caption{Monomer-monomer correlations function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ along the  in the QDPM RK ground state doped with a single pair of monomers on lattices up to \note{$L=48$}.
-The horizontal lines correspond to $L^{-4}$ with the color corresponding to the system size.
+        \caption{ The monomer-monomer correlations function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ along a coordinate axis in the QDPM RK ground state doped with a single pair of monomers on lattices up to \note{$L=48$}.
+The horizontal lines correspond to $L^{-4}$ for the system size corresponding to the color.
 \note{Owen: Do you have data for $L=64$?
 Can you make the subscripts in the y-axis label bold math?
-Maybe we should renomalize this plot by a factor of $L^2$.}}
-        \label{fig:monomer_correlation}
+Maybe we should renomalize this plot by a factor of $L^2$.
+This is only one sub-lattice--what about the other sublattice?}}
+        \label{fig:monomer_correlations}
     \end{figure}
@@
 
-We have presented the quantum dimer-pentamer model on the square lattice and studied the ground state at the RK point.
+We have introduced the quantum dimer-pentamer model on the square lattice and studied the ground state at the RK point.
 Using numerical calculations, we have demonstrated that the RK state of the QDPM is a dimer liquid, without spontaneously broken symmetry.
-The extensive topological degeneracy of the QDM has been reduced to a finite 9-fold degeneracy in the QDPM on a torus.
+The extensive topological degeneracy of the square lattice QDM has been reduced to a finite 9-fold degeneracy in the QDPM on a torus.
 We find that the dimer correlations decay exponentially with distance in contrast to the power-law decay of dimer correlations in the QDM.
 Additionally we also have demonstrated that monomer defects are deconfined in the QDPM, in contrast with the critical confinement of monomers in the QDM.
-Finally, we find that the $Z_3$ magnetic string correlations decay exponentially and display no evidence of $Z_3$ vortex condensation; this is consistent with $Z_3$ vortices being gapped quasiparticles excitations about the QDPM ground state.
-
-The above results suggest a $Z_3$ gauge theory description of the low energy physics of the QDPM and the RK ground state possessing $Z_3$ topological order.
-
-Future work could directly probe the existence of a finite gap above the RK point by studying the imaginary time dynamics of correlations functions using Monte Carlo~\cite{Henley}.
-Additionally, one could conclusively demonstrate the existence of $Z_3$ topological order by computing the topological entanglement entropy in the QDPM ground state~\cite{Levin2005,Kitaev2005,Hastings2010}.
-
-A finite gap above the RK point suggests that a stable topologically ordered phase should exist surrounding the RK point; the neighboring phase diagram could be studied using quantum Monte Carlo methods.
+Finally, we find that the $Z_3$ magnetic string correlations decay exponentially and display no evidence of $Z_3$ vortex condensation; this is consistent with $Z_3$ vortices being gapped quasiparticles excitations above the QDPM ground state.
+
+The above results suggest a the low energy physics of the QDPM is described by a $Z_3$ gauge theory with a $Z_3$ topological ordered ground state.
+Thus we have demonstrated that systems with Ising degrees of freedom and local constraints can lead to $Z_N$ topological order for $N>2$, providing the a new stable phase of matter beyond the commonly seen $Z_2$ topological spin liqud.
+
+Future work could directly probe the existence of a finite gap above the RK point by studying the imaginary time dynamics of correlations functions using Monte Carlo methods similar to those used in here~\cite{Henley1997,Henley2004a}; such an approach could be used to explore if the low energy excitations are best described by $Z_3$ magnetic vorticies~\cite{Ivanov2004,Ralko2007,Misguich2008d}.
+Additionally, one could conclusively demonstrate the existence of $Z_3$ topological order by computing the topological entanglement entropy in the QDPM ground state Monte Carlo methods~\cite{Levin2005a,Kitaev2006b,Hastings2010}.
+
+A finite gap above the RK point suggests that a stable topologically ordered phase should exist surrounding the RK point.
+While the Monte Carlo techniques used in this manuscript are limited to the RK point, the phase diagram near the RK point can be explored in future work using quantum Monte Carlo methods, as the QDPM has no sign problem.
+Away from RK, the condensation of $Z_3$ magnetic vortices could drive a continuous phase transition out of the topologically order phase, analogous to vison condensation in $Z_2$ spin liquids~\cite{Jalabert1991,Ralko2007,Huh2011,Hao2014,Slagle2014}; if such a continuous transition exists in the QDPM it may provide access to a new universality of class of quantum transitions~\cite{XU2012}.
 
 Finally, given the stability of the topologically ordered phase, it may be possible to realize the QDPM in a more microscopically realistic spin model with two body interactions.
+The local constraints of the QDM can be realized in two-body spin-$1/2$ and Bose-Hubbard models, and the QDM Hamiltonian can arise perturbatively in the constrained low energy Hilbert space~\cite{Balents2002a,Zhitomirsky2005,Isakov2006c,Albuquerque2008}.
+Thus future work, it may be possible to engineer the QDPM in the low energy subspace of an experimentally realizable two-body model.
 

### 2016-08-06 qdpm_paper.tex

--- 2016-08-04 qdpm_paper.tex
@@
 Thus we have demonstrated that ground state at the RK point of the QDPM has an exact $Z_3$ gauge symmetry and a corresponding $9$-fold topological degeneracy on the torus.
-We emphasize that despite the exact $Z_3$ local gauge symmetry of the QDPM, there is not an exact mapping to a $Z_3$ gauge theory on the square lattice, as the QDPM has Ising degrees of freedom on the links, rather than the 3 dimensional local Hilbert space of a $Z_3$ gauge theory.
-It remains to address whether this RK state is in the deconfined $Z_3$ topologically ordered phase of a $Z_3$ gauge theory, or a critically correlated or confining symmetry broken phase, which we do below.
+It remains to address whether this RK state is in the deconfined $Z_3$ topologically ordered phase of a $Z_3$ gauge theory, or in an confining symmetry broken phase.
 
@@
         \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
-        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the $Z_3$ magnetic string structure factor $S_M$ ({\it bottom})
+        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the ({\it bottom})
         shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
-        points for $\gamma=0.5$.
-Statistical errors are smaller than the symbols.
-\note{Owen: Make the k's in the y-axis bold.
-What do there look like if you added $L=16$ data to these plots?
-Switch the y-axis from $S_v\rightarrow S_M$.}}
+        points for $\gamma=0.5$. Statistical errors are smaller than the symbols. \note{Owen: Make the k's in the y-axis bold. What do there look like if you added $L=16$ data to these plots?}}
         \label{fig:structure_factor_path}
@@
 We find that $C_d$ decays exponentially with distance with a correlations length  $\chi\approx???$; additionally we find that correlations between perpendicular dimers also decay exponentially.
-
-Thus we find that the RK point of the QDPM is a symmetric dimer liquid with exponentially decaying dimer correlations, in contrast with the power-law decaying correlations of the
 
@@
 The y-axis also needs a label.
-Can you add the correlation length estimate here as well?
-Can you add the $r=0$ data point to this plot?}}
+Can you add the correlation length estimate here as well?}}
     \label{fig:spatial_dmr_cor}
@@
 \note{Comment here about gauge fixing breaking symmetry, if still present...}.
-Additionally, we have plotted the magnetic string structure factor
-\begin{equation}
-S_M\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{p,p'} e^{-i \bm{k} \cdot r_{pp'}} C_M\left( \bm{r}_{pp'}\right)
-\end{equation}
-in \figref{fig:structure_factor}. \note{Discuss any effect of gauge fixing here, if relevant}.
-
-\figref{fig:vison_cor} show the decay of $C_M$ along one of the axes of the dual lattice; \note{we find this decays exponentially with distance, with a correlation length $\chi\approx???$}
-
-Thus we find no evidence of magnetic vortex condensation on lattices up to $L=64$.
+We find no evidence of magnetic vortex condensation on lattices up to $L=64$.
 
@@
     \includegraphics[width=1.0\columnwidth]{spatial_cors_z3_vis.pdf}
-    \caption{ $Z_3$ magnetic string correlation $C_M$ along along one axis of an $L=64$ lattice. The line corresponds to an exponential fit with correlations length \note{$\chi\approx???$}.}
-    \label{fig:vison_cor}
+    \caption{ $Z_3$ vison correlation function for $L=64$ lattice.}
+    \label{fig:spatial_dmr_cor}
 \end{figure}
@@
 
-To study the confinement of electrically charged defects in the QDPM, we have Monte Carlo sampled the RK ground state doped with a single pair of monomers.
+To study the confinement of electrically charged defects in the QDPM, we have Monte Carlo sampled the RK ground state with a single pair of monomers.
 We initialize the system with a monomer on each sub-lattice and supplement the local Monte Carlo updates with updates of the form:
@@
 which appear to provide ergodic dynamics in the monomer-dimer-pentamer configuration space.
-Notice that monomers remain on the same sub-lattice, which is consistent with their assignment of a $Z_3$ electric charge of $\pm1$, where the positive and negative monomers live on different sub-lattices.
-
-We then can test for the confinement of monomers by studying the monomer-monomer density correlation function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$, which is plotted in \figref{fig:monomer_correlation}.
-If the monomers are confined, we expect $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ to decay to zero at large distances; conversely if monomers are deconfined, we expect the monomers to be randomly distributed on the lattice, such that $\langle m_{\bm{0}} m_{\bm{r}} \rangle \sim L^{-4}$ at large separations.
-In \figref{fig:monomer_correlations}, the horizontal lines correspond to $L^{-4}$ for each system size; we find that the monomer correlations quickly decay to $L^{-4}$ indicating a deconfinement of monomers.
-
+Notice that monomers remain on the same sub-lattice, which is consistent with their assignment of a $Z_3$ electric charge of $\pm1$, depending on the sub-lattice.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Monomer correlations}
+
+%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%
@@
         \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
-        \caption{Monomer-monomer correlations function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ along the  in the QDPM RK ground state doped with a single pair of monomers on lattices up to \note{$L=48$}.
-The horizontal lines correspond to $L^{-4}$ with the color corresponding to the system size.
-\note{Owen: Do you have data for $L=64$?
-Can you make the subscripts in the y-axis label bold math?
-Maybe we should renomalize this plot by a factor of $L^2$.}}
-        \label{fig:monomer_correlation}
-    \end{figure}
+        \caption{Monomer correlations in the QDPM.}
+        \label{fig:vis_dmr_cut}
+    \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+    \begin{tabular}{| l | c | c |}
+  	\hline
+     & $c$ & $\bar{c}$ \\
+	\hline
+    $i$ & $\monomermvA$ &  $\monomermvB$  \\
+    \hline
+  \end{tabular}
+  \caption{The pair of local dimer \& monomer configurations $c\leftrightarrow\bar{c}$ generate
+  minimal local monomer dynamics. Monomers always remain on their origonal sublattice. }
+  \label{tab:pentamerMoves}
+\end{table}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 Using numerical calculations, we have demonstrated that the RK state of the QDPM is a dimer liquid, without spontaneously broken symmetry.
-The extensive topological degeneracy of the QDM has been reduced to a finite 9-fold degeneracy in the QDPM on a torus.
-We find that the dimer correlations decay exponentially with distance in contrast to the power-law decay of dimer correlations in the QDM.
-Additionally we also have demonstrated that monomer defects are deconfined in the QDPM, in contrast with the critical confinement of monomers in the QDM.
-Finally, we find that the $Z_3$ magnetic string correlations decay exponentially and display no evidence of $Z_3$ vortex condensation; this is consistent with $Z_3$ vortices being gapped quasiparticles excitations about the QDPM ground state.
-
-The above results suggest a $Z_3$ gauge theory description of the low energy physics of the QDPM and the RK ground state possessing $Z_3$ topological order.
+We find that the correlations decay exponentially with distance in contrast to the power-law decay of correlations in the QDM.
+Additionally the extensive topological degeneracy of the QDM has been reduced to a finite 9-fold degeneracy in the QDPM on a torus.
+We also have demonstrated that monomer defects are deconfined in the QDPM.
+These results are consistent with an effective $Z_3$ gauge theory description of the low energy physics of the QDPM and the RK ground state possessing $Z_3$ topological order.
 

### 2016-08-06 qdpm_paper.tex
fig updates

--- 2016-08-05 qdpm_paper.tex
@@
 While on non-bipartite lattices, the QDM posses a topologically ordered ground state~\cite{Moessner2001a,Fendley2002}, on the square lattice there is only a liquid ground state at an isolated critical quantum point~\cite{Leung1996,Syljuasen2006}.
-If the hard-core constraint of the QDM is relaxed to a parity constraint such that each vertex much have an odd (or even) number of dimers touching each vertex, the simplest non-trivial dynamics leads to a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
+If the hard-core constraint of the QDM is relaxed to a parity constraint such that each vertex must have an odd (or even) number of dimers touching each vertex, the simplest non-trivial dynamics leads to a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
 The existence of topologically ordered ground states in dimer-based models is intimately related to the local constraint which imposes a local gauge symmetry in the Hilbert space; the topological order that arises is directly related to a discrete gauge theory with the appropriate local gauge constraint~\cite{Moessner2001}.
@@
 We will refer to such models with dimer degrees of freedom on links and local constraints at vertices as \emph{generalized quantum dimer modes} (GQDMs).
-Previous work as demonstrated that GQDMs on the square lattice support gapped $Z_2$ topologically ordered phases as well as gapless quantum critical points.
+Previous work has demonstrated that GQDMs on the square lattice support gapped $Z_2$ topologically ordered phases as well as gapless quantum critical points.
 On non-bipartite lattices, GQDMs support $Z_2$ topological order~\cite{Moessner2001a,Misguich2002} as well as doubled-semion phases~\cite{Qi2014,Buerschaper2014a}.
@@
 
-This this paper is organized as follows.
+This paper is organized as follows.
 In \secref{sec:Background} we provide relevant background for the QDM and related models.
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Monomer correlations}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
     \begin{figure}[]
@@
     \centering
-    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
-    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
+    \includegraphics[width=1.0\columnwidth]{spatial_cors_end_to_end_parallel.pdf}
+    \caption{Correlation function between parallel dimers (end-to-end) on the same (blue) and different (red) 
     sub-lattice for a $L=64$ lattice.}

### 2016-08-06 qdpm_paper.tex
Worked on Appendix

--- 2016-08-05 qdpm_paper.tex
@@
 
-    \section{$Z_3$ Toric Code on the Square Lattice}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{$Z_3$ Gauge theory on the Square Lattice}
+
+Here we will review the string-net implementation of $Z_3$ gauge theory on the square lattice.
+We define a three -dimensional Hilbert space on each link, corresponding to the presence or absence of an oriented string segment that carries $Z_3$ electric flux which we represent graphically as
+\begin{equation}
+     \vvemptylink  \rightarrowlink \leftarrowlink
+\end{equation}
+
         In the $Z_3$ toric three degrees of freedom live on each link.
@@
         %
-        \begin{itemize}
-            \item $\vvemptylink$ 
-            \item $\rightarrowlink$ 
-            \item $\leftarrowlink$ 
-        \end{itemize}
         % 

### 2016-08-08 qdpm_paper.tex
Worked on the appendix

--- 2016-08-06 qdpm_paper.tex
@@
     magnetic string with two different charged (colored) visons at the end points. $\Phi_3$ a trivial closed
-    string. The colors red and blue distinguish the two different sublattices that orient the links.}
+    string.
+The colors red and blue distinguish the two different sublattices that orient the links.
+\note{Owen: Add a dimer/pentamer-ization to the figure.
+Also, add a monomer defect in the magnetic loop, to demonstrate the fractional statistics of defects.}}
     \label{fig:orientedSL}
@@
 
-    \section{$Z_3$ Toric Code on the Square Lattice}
-        In the $Z_3$ toric three degrees of freedom live on each link.
-        We can represent the $Z_3$ algebra through the following expressions
-        %
-        %Z_N
-        %\begin{equation}
-        %    E |n\rangle = n |n\rangle, ~ n=0,1,2,...,N-1
-        %    \\
-        %    e^{iA} |n\rangle = |n+1 \rangle, ~ n=0,1,2,...,N-2
-        %    \\
-        %    e^{iA} |N-1\rangle = |0\rangle
-        %    %\label{eqn:}
-        %\end{equation}
-        %Z_3
-        %
-        \begin{equation}
-            \begin{split}
-            & E_l |n_l\rangle = n_l |n_l\rangle, ~ n_l=0,1,2
-            \\
-            & e^{iA_l} |n_l \rangle = |n_l+1 \rangle, ~ n_l =0,1
-            \\ 
-            & e^{iA_l} |2 \rangle = |0\rangle
-            \end{split}
-            ,
-            %\label{eqn:}
-        \end{equation}
-        %
-        where the operators $E_l$ and $A_l$ act on a given link $l$ and are analogous to the 
-        electric field and vector potential respectively. 
-        By assigning orientations to the links between two vertices we can define the three degrees of
-        freedom pictorially. 
-        %
-        \begin{itemize}
-            \item $\vvemptylink$ 
-            \item $\rightarrowlink$ 
-            \item $\leftarrowlink$ 
-        \end{itemize}
-        % 
-        To simplify notation, we define $e^{iA_l}$ as the operator $Q$ which acts on the links in the
-        following way
-        \begin{equation}
-            \begin{split}
-                & Q^\dagger_{vv'}  | \vvemptylink \rangle = | \rightarrowlink \rangle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{$Z_3$ Gauge theory on the square lattice}
+
+Here we will review a string-net implementation of $Z_3$ gauge theory on the square lattice~\cite{Horn1979}.
+We define a three -dimensional Hilbert space on each link, corresponding to the presence or absence of an oriented string segment that carries $Z_3$ electric flux which are eigenstates of the Hermitian $Z_3$ electric flux operator $E_{vv'}$
+\begin{align}
+        & E_{vv'}  \eket{\vvemptylink} = 0
         ,
         \\
-                & Q^\dagger_{vv'}  | \rightarrowlink \rangle = | \leftarrowlink \rangle
+        & E_{vv'}  \eket{\rightarrowlink} = + \eket{\rightarrowlink}
         ,
         \\
-                & Q^\dagger_{vv'}  | \leftarrowlink \rangle = | \emptylink \rangle
+        & E_{vv'} \eket{\leftarrowlink} = - \eket{\leftarrowlink}
         .
-            \end{split}
-            %\label{eqn:}
-        \end{equation}
-        The link is specified by the two vertices it connects. The operator
-        $Q^\dagger_{vv'}$ acts in the direction from the first subscript to the second subscript, in
-        this case denoted as $v$ and $v'$. 
-        Changing the direction in which $Q$ operates is equivalent to taking the hermitian conjugate
-        of the operator withougt changing the direction.  
-        %
-        \begin{equation}
-            (Q^\dagger_{vv'})^\dagger = Q_{vv'}^\dagger
-            .
-            %\label{eqn:}
-        \end{equation}
-
-        We now define an operator $E_{vv'}$ in a similar way, 
-        %
-        \begin{equation}
-            \begin{split}
-                & E^\dagger_{vv'}  | \vvemptylink \rangle = 0
+\end{align}
+\note{Owen:can you add symbols with $v$ and $v'$ at both end points for all types of links?}.
+
+At each vertex we define a local unitary gauge transformation $G_v$,
+\begin{equation}
+G_v \equiv \prod_{v'} P^\dagger_{vv'}
+\end{equation}
+where the product is over all nearest neighbor vertices $v'$, and we have defined the unitary operator
+\begin{equation}
+P_{vv'}^\dagger \equiv e^{i 2\pi/3 E_{vv'}}.
+\end{equation}
+We consider eigenstates of $G_v$ to have a definite $Z_3$ electric charge at vertex $v$. The charge-free sector is the gauge invariant subspace where
+\begin{equation}
+G_v \eket{\psi} = \eket{\psi} \quad \forall v.
+\end{equation}
+This gauge invariant subspace corresponds to states where the ``string flux" vanishes modulo 3 at each vertex, thus including vertices where three inward or three outward strings meet at a vertex.
+For eigenstates of $G_v$ with  nonzero electric charge
+\begin{equation}
+G_v \ket{\psi} = e^{\pm 2\pi/3 i} \ket{\psi}
+\end{equation}
+which corresponds to the presence of a $Z_3$ charge of $\pm1$ at vertex $v$.
+A vertex with a positive (negative) charge has a net outward (inward) string flux of 1 modulo 3, or net inward (outward) flux of 2.
+\figref{fig:example_elec_string} shows examples of charged and charge free string configurations.
+
+To provide dynamics, we define a unitary operator electric flux ladder operator $Q^\dagger_{vv'}$ that increments the electric flux:
+\begin{align}
+        & Q^\dagger_{vv'}  \eket{\vvemptylink} = \eket{\rightarrowlink}
         ,
         \\
-                & E^\dagger_{vv'}  | \rightarrowlink \rangle = | \rightarrowlink \rangle
+        & Q^\dagger_{vv'}  \eket{\rightarrowlink} = \eket{\leftarrowlink}
         ,
         \\
-                & E^\dagger_{vv'}  | \leftarrowlink \rangle = 2| \leftarrowlink \rangle
-                ,
-            \end{split}
-            %\label{eqn:}
-        \end{equation}
-        and with it define the last important operator that acts on the links. 
+        & Q^\dagger_{vv'}  \eket{\leftarrowlink} = \eket{\emptylink}
+\end{align}
+The simplest gauge invariant Hamiltonian is then
+\begin{equation}
+H_{Z_3} = - J  \sum_p  \left( Q^\dagger_{v_1^pv_2^p} Q^\dagger_{v_2^pv_3^p} Q^\dagger_{v_3^pv_4^p} Q^\dagger_{v_4^pv_1^p} + h.c. \right)
+\end{equation}
+where $v_i^p$ represent the four vertices in the plaquette $p$, ordered cyclically by nearest neighbors.
+
+We can define two oriented open string operators which commute with $H_{Z_3}$ everywhere except at the endpoints.
+The electric string operator $S_e$, which acts on an open, oriented string on the lattice $\gamma_{vv'}$ with endpoints $v,v'$, and creates a $+1$ ($-1$) charge at vertex $v$ ($v')$, is defined as
+\begin{equation}
+    S_e \left( \gamma_{vv'} \right) \equiv \prod_{l \in \gamma_{vv'}} Q_{v_l v_l'}^\dagger
+\end{equation}
+where the product is over all links $l$ in $\gamma_{vv'}$, $v_l$ and $v_l'$ are the two vertices in $l$, ordered according to the orientation of $\gamma_{vv'}$ (see \figref{fig:example_elec_string}).
+The magnetic string operator $S_m$ is defined by an open, oriented string on the dual lattice and creates a magnetic vortex-antivortex pair on plaquettes at the endpoints of $\tilde{\gamma}_{pp'}$
+\begin{equation}
+    S_m \left( \tilde{\gamma}_{vv'} \right) \equiv \prod_{l \perp \tilde{\gamma}_{pp'}} P_{v_l v_l'}^\dagger
+\end{equation}
+where the product is over all links $l$ that cross $\tilde{\gamma}$ and $v_l$ ($v_l'$) is the vertex to the left (right) of the string as $\tilde{\gamma}$ is traversed from $p$ to $p'$. 
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.8\linewidth]{example_elec_string.pdf}
+    \caption{ ({\it left}) An example of a charge free $Z_3$ electric string configuration.
+The electric string operator $S_\gamma^e$ represented by the thick gray line, oriented from the red to blue vertex.
+({\it right}) An example of a $Z_3$ electric string configuration with a $+1$ ($-1$) electric charge at the red (blue) vertex; this string configuration results form the action of $S_\gamma^e$ on the left panel.
+\note{Owen: Can you remove the a) and b) labels on the figure?
+Also switch the $\Gamma$ to $\gamma$, and remove the $v_0-v_3$ labels.
+Add a gray arrow on the string operator from red to blue.
+Can you add a non-trivial magnetic loop around the blue charge on the right?} }
+    \label{fig:example_elec_string}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[]
+    \centering
+    \includegraphics[width=0.5\columnwidth]{example_mag_string.pdf}
+    \caption{The magnetic string operator $S_m$ is defined by the open, oriented string $\tilde{\gamma}_{pp'}$, and creates a vortex (anti-vortex) a the red (blue) plaquette.
+\note{Owen: can you add a gray arrow orienting the string from red to blue.
+Change the label to $\tilde{\gamma}$.
+Maybe we should distinguish between the electric and magnetic charges in these two figures (maybe add a small e/m in the circles?}}
+    \label{fig:example_mag_string}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%
+
+Note that  $S_e$ and $S_m$ do not commute if their corresponding strings intersect--this underlies the non-trivial statics of electric charges and magnetic vortices.
+Consider the magnetic string operator $S_m(\tilde{\Gamma})$ defined by an oriented \emph{closed} loop $\tilde{\Gamma}$ on the dual lattice.
+This operator corresponds to the creation of a vortex-antivortex pair, winding of the vortex around $\Gamma$, and annihilation of the vortex pair.
+A state with definite electric charge inside $\Gamma$ will be an eigenstate of $S_m(\tilde{\Gamma})$, with eigenvalue $e^{ i 2 \pi/3 q}$, where $q=0,\pm1$ is the net $Z_3$ electric charge (modulo 3) inside $\tilde{\Gamma}$.
+For $\Gamma$ winding around an isolated electric charge, we see that electric charges and magnetic vortices are anyons with relative braiding statics with a statistical phase of $e^{\pm i 2\pi/3}$.
+
+Additionally, topologically non-trivial string operators give rise to a topological degeneracy...
+
+%\section{Additional numerical results on the QDPM RK ground state}
 %
-        \begin{equation}
-            P_{vv'}^\dagger \equiv e^{i2\pi E_{vv'}/3}
-            .
-            %\label{eqn:}
-        \end{equation}
-        %
-        $P_{vv'}^\dagger$ acts on the links in the following way: 
-        %
-        \begin{equation}
-            \begin{split}
-                & P^\dagger_{vv'}  | \vvemptylink \rangle = | \vvemptylink \rangle
-                ,
-                \\
-                & P^\dagger_{vv'}  | \rightarrowlink \rangle = e^{i2\pi/3} | \rightarrowlink \rangle
-                ,
-                \\
-                & P^\dagger_{vv'}  | \leftarrowlink \rangle = e^{-i2\pi/3} | \leftarrowlink \rangle
-                .
-            \end{split}
-            %\label{eqn:}
-        \end{equation}
-        %
-
-        With the above definitions the $Z_3$ toric code Hamiltonian can be written in terms of the $P$ and $Q$ operators.
-        In general a string net Hamiltonian might be written as 
-        \begin{equation}
-            H = - J_e \sum_v A_v - J_m \sum_p B_p
-            %\label{eqn:}
-        \end{equation}
-        where 
-        \begin{equation}
-            A_v = \prod_{i\in v} P^\dagger_{vv_i}~,~ B_p = \prod_{i\in p} Q^\dagger_{v_iv_{i+1}}
-            .
-            %\label{eqn:}
-        \end{equation}
-        The specific vertex and plaquette labeling scheme is shown in Fig.~\ref{fig:vertex_link_labels}.
-        %
-        \begin{figure}[htpb]
-            \centering
-            \includegraphics[width=0.8\linewidth]{vertex_link_gauge_def}
-            \caption{Notation of vertex and plaquette labels}
-            \label{fig:vertex_link_labels}
-        \end{figure}
-        %
-        For the ground state of this Hamiltonian there is aa local symmetry corresponding to the
-        minimization of the first term. This local symmetry is a gauge symmetry that can be
-        expressed in terms of the gauge operator.
-        \begin{equation}
-            G_v | \psi \rangle= | \psi \rangle
-            %\label{eqn:}
-        \end{equation}
-        where $G_v$ = $A_v$.
-
-        \subsubsection{$Z_3$ String operators}
-            With the above notation we can now write down the $Z_3$ string operators. The electric string operator along
-            the path $\Gamma$ is written
-            %
-            \begin{equation}
-                S^e_{\Gamma} = \prod_{l=0}^{N-2} Q_{v_lv_{l+1}}^\dagger
-                %\label{eqn:}
-                ,
-            \end{equation}
-            %
-            where $v_l \in \Gamma$ and $N$ is the number of vertices in $\Gamma$. We show an example of an
-            electric string operator operatiing on an example configuration in Fig.~\ref{fig:example_elec_string}.
-            %
-            %
-            \begin{figure}[htpb]
-                \centering
-                \includegraphics[width=0.8\linewidth]{example_elec_string.pdf}
-                \caption{The grey line is the path $\Gamma$ on which the string operator acts. The operator acts
-            in the direction from the vertex labeled in red to the one labeled in blue.}
-                \label{fig:example_elec_string}
-            \end{figure}
-            %
-            %
-            The magnetic string operator can be written as
-            \begin{equation}
-                S^m_{\Gamma} = \prod_{l=0}^{N-1} P_{v_{2l}v_{2l+1}}^\dagger
-                %\label{eqn:}
-            \end{equation}
-            %
-            where $v_l$ are the vertices adjacent to the links in $\Gamma$ and $N$ is the number of
-            vertices
-            on the \textit{left} side of the path when looking along the path from red to blue. 
-            An example of this operator acting
-            on a configuration is shown in Fig.~\ref{fig:example_mag_string} along with the vertex labeling
-            scheme.
-            %
-            %
-            \begin{figure}[htpb]
-                \centering
-                \includegraphics[width=0.8\linewidth]{example_mag_string.pdf}
-                \caption{The grey line is the path $\Gamma$ on which the string operator acts. The magnetic
-                    string operator acts in the 
-                    direction from the plaquette labeled in red to the one labeled in blue.}
-                \label{fig:example_mag_string}
-            \end{figure}
-            %
-            The magnetic string operator acting on path $\Gamma$ in Fig.~\ref{fig:example_mag_string} is
-            %
-            \begin{multline}
-                S^m_{\Gamma} (\mathrm{~Fig.~\ref{fig:example_mag_string}~config})
-                = P_{v_0v_1}^\dagger P_{v_2v_3}^\dagger P_{v_4v_5}^\dagger
-                \\
-                = \exp{[0 - \frac{i2\pi}{3} + \frac{i2\pi}{3} ]} 
-                = 1 (\mathrm{~Fig.~\ref{fig:example_mag_string}~config})
-                .
-            \end{multline}
-            %
-
-            An interesting property of the electric string operator in the $Z_3$ toric code is
-            that an unclosed string produces two different defects. 
-            An example of an open string and the defects is shown in Fig.~\ref{fig:example_elec_string}. The
-            configuration in Fig.~\ref{fig:example_elec_string}(a) obeys the local gauge symmetry
-            aside from the endpoints of the path that it acts on ($\Gamma$). The two defects at the
-            end points produce two different values when the vertecies are operated on by $G_v$, being
-            $G_{\mathrm{red}} = e^{i2\pi /3}$, and $G_{\mathrm{blue}} = e^{-i2\pi /3}$.
-
-            The magnetic excitations, or $Z_3$ visons live at the endpoints of the magnetic
-            strings.  These visons can change the phase of a configuration by different values.
-
-%        \subsubsection{properties of $Z_3$ string operators}
-
-        \subsubsection{Winding Numbers}
-
-            The ground state of the $Z_3$ toric code has nine-fold topological degeneracy because of
-            the $3\times3$ different topological sectors. As the case of the toric code the $Z_3$
-            electric string changes the topological sector when acting on on a nontrivial closed
-            path. We call the electric winding
-            operator that acts around the major axis $W^e_y$ and around the minor axis $W^e_x$.
-            The topological sector can be determined 
-            by acting around the axes with the magnetic string operator, called $W^m_y$ and
-            $W^m_x$. All of the winding commute with the Hamiltonian and
-            therefore share the same eigenvalues. The operator $W^m_{x}$ ($W^m_{y}$) can 
-            have three different values depending on how many electric strings enclose the minor
-            (major) axis. The three different
-            possible values for each winding number around each axis gives the model nine distinct
-            topological sectors.
-
-\section{Additional numerical results on the QDPM RK ground state}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-    \centering
-    \includegraphics[width=1.0\columnwidth]{spatial_cors_end_to_end_parallel.pdf}
-    \caption{Correlation function between parallel dimers (end-to-end) on the same (blue) and different (red) 
-    sub-lattice for a $L=64$ lattice.}
-    \label{fig:spatial_dmr_cor}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=1.0\columnwidth]{spatial_cors_end_to_end_parallel.pdf}
+%    \caption{Correlation function between parallel dimers (end-to-end) on the same (blue) and different (red) 
+%    sub-lattice for a $L=64$ lattice.}
+%    \label{fig:spatial_dmr_cor}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2016-08-09 qdpm_paper.tex
Finished draft of appendix

@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[]
+\begin{figure}
     \centering
@@
 
-Additionally, topologically non-trivial string operators give rise to a topological degeneracy...
+Additionally, these string operators give rise to a topological degeneracy in systems of non-trivial topology.
+For example, consider the charge free sector on a torus.
+We can consider two topologically non-trivial closed loops $\tilde{\Gamma}_{X/Y}$ which have single winding around the $x/y$ directions of the torus.
+Since $S_m(\Gamma_{X/Y})$ commutes with $H_{Z_3}$, we can label the energy eigenstates by the eigenvalues of $S_m(\Gamma_{X/Y})$: $\{1,e^{\pm i 2\pi/3}\}$.
+Thus $H_{Z_3}$ has a 9-fold ground state degeneracy on the torus, and the ground states subspace can be labeled by the $Z_3$ electric flux winding about each axis of the torus.
 

### 2016-09-10 qdpm_paper.tex
minor paper changes

--- 2016-08-06 qdpm_paper.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{$Z_3$ Gauge theory on the Square Lattice}
-
-Here we will review the string-net implementation of $Z_3$ gauge theory on the square lattice.
-We define a three -dimensional Hilbert space on each link, corresponding to the presence or absence of an oriented string segment that carries $Z_3$ electric flux which we represent graphically as
-\begin{equation}
-     \vvemptylink  \rightarrowlink \leftarrowlink
-\end{equation}
-
+    \section{$Z_3$ Toric Code on the Square Lattice}
         In the $Z_3$ toric three degrees of freedom live on each link.
@@
         %
+        \begin{itemize}
+            \item $\vvemptylink$ 
+            \item $\rightarrowlink$ 
+            \item $\leftarrowlink$ 
+        \end{itemize}
         % 
@@
     \centering
-    \includegraphics[width=1.0\columnwidth]{spatial_cors_end_to_end_parallel.pdf}
-    \caption{Correlation function between parallel dimers (end-to-end) on the same (blue) and different (red) 
+    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
+    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
     sub-lattice for a $L=64$ lattice.}

### 2016-09-10 qdpm_paper.tex

--- 2016-08-09 qdpm_paper.tex
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{example_mag_string.pdf}
-    \caption{The magnetic string operator $S_m$ is defined by the open, oriented string $\tilde{\gamma}_{pp'}$, and creates a vortex (anti-vortex) a the red (blue) plaquette.
-\note{Owen: can you add a gray arrow orienting the string from red to blue.
-Change the label to $\tilde{\gamma}$.
-Maybe we should distinguish between the electric and magnetic charges in these two figures (maybe add a small e/m in the circles?}}
-    \label{fig:example_mag_string}
+    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
+    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
+    sub-lattice for a $L=64$ lattice.}
+    \label{fig:spatial_dmr_cor}
 \end{figure}

### 2016-10-13 qdpm_paper.tex
new figs
updated figs

@@
 
+\subsection{Order Parameters}
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[]
+    \centering
+    \includegraphics[width=1.0\linewidth]{order_params_plot.pdf}
+    \caption{}
+    \label{fig:order_params}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         \centering
-        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM_16x16.pdf}
-        \caption{({\it left}) The horizontal dimer density structure factor $S_d(\bm{k})$ for the QDPM RK ground state on an $L=32$ lattice.
+        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM.pdf}
+        \caption{({\it left}) The horizontal dimer density structure factor $S_d(\bm{k})$ for the QDPM RK ground state on an $L=64$ lattice.
 The lack of $x\leftrightarrow y$ rotational symmetry is due to the fact that horizontal links have been isolated.

### 2016-10-21 qdpm_paper.tex

@@
 \newcommand{\ebra}[1]{\left \langle #1 \right |}
+\newcommand{\exval}[1]{\langle #1 \rangle}
 \newcommand{\Eqref}[1]{Eq. \eqref{#1}}
@@
 \newcommand{\HQDPM}{H_\mathrm{QDPM}}
+\newcommand{\Mrot}{M_{\rm{rot}}}
+\newcommand{\Mperp}{M_\perp}
+\newcommand{\Mpar}{M_{\vert\vert}}
+\newcommand{\MstagSq}{M_{\rm{stag}}^2}
+\newcommand{\McolSq}{M_{\rm{col}}^2}
 
@@
 
-To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamer_moves} to compute ground state expectation values.
+To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamer_moves}.
 Below we present the results of calculations on $L\times L$ lattices with periodic boundary conditions on systems up to $L=64$.
@@
 
-We explicitly demonstrate how the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the histogram of $U(1)$ topological winding number $\Phi_X$ .
-This is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors; we confirm that $\Phi_{X/Y}$ is only conserved modulo $3$, rather than strictly conserved as it is in the QDM.
-We find that $P(\Phi_{X/Y})$ has a roughly gaussian envelope with a width that scales with system size--this is expected as $\Phi_{X/Y} = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
+We explicitly demonstrate how the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the histogram of $U(1)$ topological winding number $\Phi_{X/Y}$ .
+$\Phi_X$ is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors (the behavior of $\Phi_Y$ is identical to that of $\Phi_X$~\note{(Owen: can you confirm this?)}).
+We confirm that $\Phi_{X/Y}$ is only conserved modulo $3$, rather than strictly conserved as it is in the QDM.
+We find that $P(\Phi_{X/Y})$ has a roughly Gaussian envelope with a width that increases with system size--this is expected as $\Phi_{X/Y} = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
+We find no evidence of a lack of ergodicity within each of the 9 topological sectors.
+For the remainder of the paper we present results in the $(0,0)$, topological sector, but we see no qualitative, dependence the topological sector for any of the results presented here.
 Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled by $\Phi_{X/Y} \mod 3$, or equivalently $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$, in contrast with the extensive degeneracy of the QDM.
-Additionally, we find no evidence of a lack of ergodicity within each of the 9 topological sectors.
-For the remainder of the paper we present results in the $(0,0)$, topological sector, but we see no dependence the topological sector for any of the results presented here~\note{Owen: which calculations/system sizes have you checked different topological sectors?}.
 %%%%%%%%%%%%%%%%%%%%%%%
@@
     $L=32$ lattice.
-Different colors correspond to calculations initialized to different winding sectors.
-Note that $\Phi_X$ is conserved modulo $3$, resulting in a $9$-fold topological degeneracy on a torus.
-    \note{Owen: change the y-axis label to $P(\Phi_x)$ and the x-axis to $\Phi_x$. Is this still an $L=32$ lattice? Do you have $L=64$? Perhaps put both on the same plot? (with no vertical bars)}}
+Different colors correspond to calculations initialized to different winding sectors, and the lines are fits to a Gaussian.
+Note that $\Phi_X$ is conserved modulo $3$, resulting in a $9$-fold topological degeneracy on a torus, that is labeled by $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$.
+\note{Owen: Can you plot $P\left(\Phi_Y\right)$ on this plot also?
+Maybe with open symbols?}}
     \label{fig:u1_wind_qdpm}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Order Parameters}
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[]
-    \centering
-    \includegraphics[width=1.0\linewidth]{order_params_plot.pdf}
-    \caption{}
-    \label{fig:order_params}
 \end{figure}
@@
 In \figref{fig:dimer_vison_heatmap} we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice; here the origin $\bm{0}$ represents the blue link, and $\bm{r}$ varies over all other links of the lattice.
-We see no evidence of symmetry breaking in the dimer correlations on lattices up $L=64$.
-We will restrict the rest of our disucssion to correlations between horizontal of dimers, as we find no rotational symmetry breaking, or qualitative difference between the the correlations between parallel dimers and perpendicular dimers.
+The left panel of \figref{fig:structure_factor} shows the equal-time dimer-dimer structure factor,
+\begin{equation}
+S_d\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{i,j} e^{-i \bm{k} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_{\bm{r}_i} n_{\bm{r}_j} \right \rangle
+\end{equation}
+where we restrict the sum to horizontal links, for an $L=32$ lattice.
+\figref{fig:structure_factor_path} shows $S_d(\bm{k})$ for a particular path through the Brillouin zone.
+The dimer structure factor displays broad maxima at $\bm{k} = (0, \pm \pi)$ and $\bm{k} = (\pm \pi, \pm \pi)$.
+The lack of rotational symmetry of $S_d(\bm{k})$ is due to the fact that we have isolated horizontal dimers--the correlations between vertical dimers display the same behavior, rotated by $\pi/2$.
 
@@
 The origin corresponds to the blue link, and $\bm{r}$ varies over all other links of the lattice.
-Red links have correlations that are off the given scale.~\note{Owen: Is this the bare or connected correlation function?
-What do these plots look like on a log scale?} ({\it right}) The $Z_3$ magnetic string correlation function $C_m(\bm{r}_{\bm{0}p})$, where the the correlations is with respect to the blue plaquette.
-\note{Are we using the real part?
-What does $\sqrt{C_M^*C_m}$ look like?
-Regardless we should make this a positive quantity so the lefthand side of the grayscale is zero.}}
+Red links have correlations that are off the given scale.
+({\it right}) The $Z_3$ magnetic string correlation function $C_M(\bm{r}_{\bm{0}p})$, where the the correlations is with respect to the blue plaquette.
+\note{Owen:What if we put the dimer structure factor on the right panel here, and move the vison correlation to the left pannel of figure 6, and put the top panel of figure 7 below these two?}}
         \label{fig:dimer_vison_heatmap}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-
-The left panel of \figref{fig:structure_factor} shows the equal-time dimer-dimer structure factor, 
-\begin{equation}
-S_d\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{i,j} e^{-i \bm{k} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_i n_j \right \rangle
-\end{equation}
-where we restrict the sum to horizontal links, for an $L=32$ lattice.
-$S_d(\bm{k})$ displays maxima at $\bm{k} = (0, \pm \pi)$ due to correlation between parallel links on a given plaquette but we see no evidence of translational symmetry breaking.
-The lack of rotational symmetry of $S_d(\bm{k})$ is due to the fact that we have isolated horizontal dimers--we see no evidence of rotational symmetry breaking between horizontal and vertical dimer correlations.
-\figref{fig:structure_factor_path} shows $S_d(\bm{k})$ for a particular path through the Brillouin zone.
 
@@
         shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
-        points for $\gamma=0.5$.
-Statistical errors are smaller than the symbols.
-\note{Owen: Make the k's in the y-axis bold.
-What do there look like if you added $L=16$ data to these plots?
-Switch the y-axis from $S_v\rightarrow S_M$.}}
+        points for $\gamma=0.5$. Statistical errors are smaller than the symbols. \note{Owen: Make the k's in the y-axis bold. Switch the y-axis from $S_v\rightarrow S_M$.}}
         \label{fig:structure_factor_path}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+To test for the possibility of translational and rotational symmetry breaking corresponding to the features in $S_d$ at the Brillouin zone edges, we define several order parameters which would capture such potential symmetry breaking.
+For rotational symmetry breaking we define
+\begin{equation}
+\Mrot \equiv  \frac{2}{L^2} \left(N_h - N_v\right) \label{eq:Mrot},
+\end{equation}
+where $N_v$ ($N_h$) is the total number of vertical (horizontal) dimers; note that $\exval{M_{\rm{rot}}^2 } \neq 0$ implies there is rotational symmetry breaking.
+to To capture translational symmetry breaking by one lattice site in a direction perpendicular to the majority of the dimers we define $\Mperp$
+\begin{align}
+\Mperp \equiv  \frac{8}{L^2} \sum_{\Box} \Bigl(  &(-1)^{r_x} \theta\left(\Mrot \right) \Pi_\Box^v \notag\\
++ &(-1)^{r_y}\theta\left(-\Mrot \right) \Pi_\Box^h\Bigr) \label{eq:Mperp},
+\end{align}
+where $\theta(x)$ is the Heaviside function, and $\Pi_\Box^h$ ($\Pi_\Box^v$) is one if the plaquette $\Box$ has two horizontal (vertical) dimers, and zero otherwise.
+Similarly, we define $\Mpar$ to be given by \Eqref{eq:Mperp} with $r_x$ and $r_y$ swapped between terms.
+Additionally, we define order parameters that indicate ``columnar" and ``staggered" dimer order~\cite{Syljuasen2005}:
+\begin{align}
+\MstagSq \equiv  \frac{1}{4L^2} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
++&\biggl( \sum_{\ell_v} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2\biggr]\label{eq:Mstag},
+\end{align}
+\begin{align}
+\McolSq \equiv  \frac{1}{4L^2} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
++ &\biggl( \sum_{\ell_v} (-1)^{r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2  \biggr]\label{eq:Mcol},
+\end{align}
+where the sums over $\ell_h$ ($\ell_v$) are taken over all horizontal (vertical) links.
+In \figref{fig:order_params} we have plotted the finite-size scaling of these order parameters; we find in all cases that while finite size systems display symmetry breaking due to finite-size effects, these order parameters all vanish in the thermodynamic limit, as demonstrated by the extrapolation in \figref{fig:order_params}.
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[]
+    \centering
+    \includegraphics[width=1.0\linewidth]{order_params_plot.pdf}
+    \caption{The symmetry breaking order parameters defined in \eqref{Mperp}.}
+    \label{fig:order_params}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 The lines represent the best fit to an exponential decay with correlation length $\chi\approx???$.
-\note{Owen: Can you add the other direction to this plot?
-The y-axis also needs a label.
-Can you add the correlation length estimate here as well?
-Can you add the $r=0$ data point to this plot?}}
+\note{Owen: Can you add the direction parallel to the dimers to this plot?
+Can you add the correlation length estimate here as well?}}
     \label{fig:spatial_dmr_cor}

### 2016-11-05 qdpm_paper.tex
Moved correlation function to appendix
Added Bragg peak scaling figure
z3
Worked on text

@@
 The lack of rotational symmetry of $S_d(\bm{k})$ is due to the fact that we have isolated horizontal dimers--the correlations between vertical dimers display the same behavior, rotated by $\pi/2$.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-    \begin{figure}
+We have plotted the finite size scaling of the intensity of these peaks in  \figref{fig:bragg_scaling}, which we find to vanish in the thermodynamic limit.
+These maxima at $(0,\pi)$ and $(\pi,\pi)$ are thus consistent with finite size effects due to short distance correlations.
+Thus we see no evidence of thermodynamic limit symmetry breaking.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+    \begin{figure}[t]
         \centering
@@
 Red links have correlations that are off the given scale.
-({\it right}) The $Z_3$ magnetic string correlation function $C_M(\bm{r}_{\bm{0}p})$, where the the correlations is with respect to the blue plaquette.
+({\it right}) The magnitude of the $Z_3$ magnetic string correlation function $|C_M(\bm{r}_{\bm{0}p})|$, where the the correlations is with respect to the blue plaquette.
 \note{Owen:What if we put the dimer structure factor on the right panel here, and move the vison correlation to the left pannel of figure 6, and put the top panel of figure 7 below these two?}}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%
-   \begin{figure}[]
+%%%%%%%%%%%%%%%%%%%%%%%
+   \begin{figure}[t]
         \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-    \begin{figure}[]
+    \begin{figure}[t]
         \centering
         \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
-        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the $Z_3$ magnetic string structure factor $S_M$ ({\it bottom})
-        shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
-        points for $\gamma=0.5$. Statistical errors are smaller than the symbols. \note{Owen: Make the k's in the y-axis bold. Switch the y-axis from $S_v\rightarrow S_M$.}}
+        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the magnitude of the $Z_3$ magnetic string structure factor $|S_M|$ ({\it bottom})
+        shown along a path in $k$ space for an $L=64$ lattice.
+Statistical errors are smaller than the symbols.
+\note{Owen: Make the k's in the y-axis bold.
+Switch the y-axis from $S_v\rightarrow S_M$.}}
         \label{fig:structure_factor_path}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-
-To test for the possibility of translational and rotational symmetry breaking corresponding to the features in $S_d$ at the Brillouin zone edges, we define several order parameters which would capture such potential symmetry breaking.
-For rotational symmetry breaking we define
-\begin{equation}
-\Mrot \equiv  \frac{2}{L^2} \left(N_h - N_v\right) \label{eq:Mrot},
-\end{equation}
-where $N_v$ ($N_h$) is the total number of vertical (horizontal) dimers; note that $\exval{M_{\rm{rot}}^2 } \neq 0$ implies there is rotational symmetry breaking.
-to To capture translational symmetry breaking by one lattice site in a direction perpendicular to the majority of the dimers we define $\Mperp$
-\begin{align}
-\Mperp \equiv  \frac{8}{L^2} \sum_{\Box} \Bigl(  &(-1)^{r_x} \theta\left(\Mrot \right) \Pi_\Box^v \notag\\
-+ &(-1)^{r_y}\theta\left(-\Mrot \right) \Pi_\Box^h\Bigr) \label{eq:Mperp},
-\end{align}
-where $\theta(x)$ is the Heaviside function, and $\Pi_\Box^h$ ($\Pi_\Box^v$) is one if the plaquette $\Box$ has two horizontal (vertical) dimers, and zero otherwise.
-Similarly, we define $\Mpar$ to be given by \Eqref{eq:Mperp} with $r_x$ and $r_y$ swapped between terms.
-Additionally, we define order parameters that indicate ``columnar" and ``staggered" dimer order~\cite{Syljuasen2005}:
-\begin{align}
-\MstagSq \equiv  \frac{1}{4L^2} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
-+&\biggl( \sum_{\ell_v} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2\biggr]\label{eq:Mstag},
-\end{align}
-\begin{align}
-\McolSq \equiv  \frac{1}{4L^2} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
-+ &\biggl( \sum_{\ell_v} (-1)^{r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2  \biggr]\label{eq:Mcol},
-\end{align}
-where the sums over $\ell_h$ ($\ell_v$) are taken over all horizontal (vertical) links.
-In \figref{fig:order_params} we have plotted the finite-size scaling of these order parameters; we find in all cases that while finite size systems display symmetry breaking due to finite-size effects, these order parameters all vanish in the thermodynamic limit, as demonstrated by the extrapolation in \figref{fig:order_params}.
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[]
-    \centering
-    \includegraphics[width=1.0\linewidth]{order_params_plot.pdf}
-    \caption{The symmetry breaking order parameters defined in \eqref{Mperp}.}
-    \label{fig:order_params}
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=1.0\columnwidth]{peak_scaling.pdf}
+    \caption{Finite-size scaling of the maxima in the dimer ($S_d$) and magnetic string ($|S_M|$) structure factors.
+All maximum vanish in the thermodynamic limit, indicating that the RK state of the QDPM is a symmetric dimer liquid.
+\note{Owen: We don't need the absolute value bars for $S_d$ since it's real.}}
+    \label{fig:bragg_scaling}
 \end{figure}
@@
 In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel links is plotted as a function of separation, \textcolor{red}{for both $r$ parallel and perpendicular to the orientation of the dimers} \note{(Owen: can you add both directions to this plot?)} for an $L=64$ lattice.
-We find that $C_d$ decays exponentially with distance with a correlations length  $\chi\approx???$; additionally we find that correlations between perpendicular dimers also decay exponentially.
-
-Thus we find that the RK point of the QDPM is a symmetric dimer liquid with exponentially decaying dimer correlations, in contrast with the power-law decaying correlations of the
+We find that $C_d$ decays exponentially with distance with a correlations length  $\chi\approx???$.
+Additionally, $C_d$ displays a sub-lattice oscillation that is consistent with the finite-size maximum in $S_d$ at $(0,\pi)$.
+Thus we find that the RK point of the QDPM is a symmetric dimer liquid with exponentially decaying dimer correlations, in contrast with the power-law decaying correlations of the QDM.
 
@@
 where $p$ and $p'$ are two plaquettes, and $\gamma_{pp'}$ is any open string on the dual lattice connecting $p$ and $p'$.
-\note{Something about the background dimerization and gauge fixing here.
-Are we using the real parts or $\sqrt{C_M^*C_M}$?}
-
-In \figref{fig:dimer_vison_heatmap}, we have ploted $C_M$ for an $L=16$ lattice, which displays short distance correlations that quickly decay.
-\note{Comment here about gauge fixing breaking symmetry, if still present...}.
-Additionally, we have plotted the magnetic string structure factor
+In \figref{fig:dimer_vison_heatmap}, we have plotted $|C_M|$ for an $L=16$ lattice.
+Note, that while $C_M$ depends on the choice of the background dimerization which fixes the gauge, $|C_M|$ is independent of the background dimerization.
+Additionally, we have computed the magnetic string structure factor
 \begin{equation}
@@
 \end{equation}
-in \figref{fig:structure_factor}. \note{Discuss any effect of gauge fixing here, if relevant}.
-
-\figref{fig:vison_cor} show the decay of $C_M$ along one of the axes of the dual lattice; \note{we find this decays exponentially with distance, with a correlation length $\chi\approx???$}
-
-Thus we find no evidence of magnetic vortex condensation on lattices up to $L=64$.
+and plot the magnitude $|S_M$ in \figref{fig:structure_factor}.
+We have chosen d a columnar background dimerization comprising horizontal background dimers stacked in columns along the $y$-axis, as shown in \figref{fig:BKGD_dimers}\note{Where should we show the background dimerization??}; this chose breaks the translational symmetry and thus requires doubling the unit cell the $x$-direction.
+\note{Owen: What are the effects of the background dimerization?}.
+While $|C_M|$ displays no obvious symmetry breaking, there are peaks in $|S_M|$ at $(0,0)$ \& $(0,\pi$) \note{(Owen: What about $(\pi,\pi)$??)}.
+We have plotted the finite-size scaling of these peaks in \figref{fig:bragg_scaling} which demonstrates that these peaks vanish in the thermodynamic limit.
+While the vanishing of the $(0,\pi)$ peak demonstrates the restoration of rotational and translational symmetries in the thermodynamic limit, the vanishing of the $(0,0)$ peak demonstrates the lack of magnetic vortex condensation, which is a mechanism for destroying topological order and breaking lattice symmetries~\cite{Jalabert1991,Ralko2007,Huh2011}.
+\figref{fig:vison_cor} shows the decay of $|C_M|$ along one of the axes of the dual lattice; \note{we find this decays exponentially with distance, with a correlation length $\chi\approx???$}.
+These exponentially decaying magnetic string correlations are therefore consistent with a symmetric dimer liquid with no magnetic vortex condensation.
 
@@
     \includegraphics[width=1.0\columnwidth]{spatial_cors_z3_vis.pdf}
-    \caption{ $Z_3$ magnetic string correlation $C_M$ along along one axis of an $L=64$ lattice. The line corresponds to an exponential fit with correlations length \note{$\chi\approx???$}.}
+    \caption{ The magnitude of the $Z_3$ magnetic string correlation $|C_M|$ along along one axis of the dual lattice of an $L=64$ lattice.
+The line corresponds to an exponential fit with correlations length \note{$\chi\approx???$}.}
     \label{fig:vison_cor}
@@
 
-To study the confinement of electrically charged defects in the QDPM, we have Monte Carlo sampled the RK ground state doped with a single pair of monomers.
+To study the confinement of $Z_3$ electrically charged defects in the QDPM, we have Monte Carlo sampled the RK ground state doped with a single pair of monomers.
 We initialize the system with a monomer on each sub-lattice and supplement the local Monte Carlo updates with updates of the form:
@@
 Notice that monomers remain on the same sub-lattice, which is consistent with their assignment of a $Z_3$ electric charge of $\pm1$, where the positive and negative monomers live on different sub-lattices.
-
-We then can test for the confinement of monomers by studying the monomer-monomer density correlation function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$, which is plotted in \figref{fig:monomer_correlation}.
+We then can test for the confinement of monomers by studying the monomer-monomer density correlation function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$, which is plotted in \figref{fig:monomer_correlations}.
 If the monomers are confined, we expect $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ to decay to zero at large distances; conversely if monomers are deconfined, we expect the monomers to be randomly distributed on the lattice, such that $\langle m_{\bm{0}} m_{\bm{r}} \rangle \sim L^{-4}$ at large separations.
-In \figref{fig:monomer_correlations}, the horizontal lines correspond to $L^{-4}$ for each system size; we find that the monomer correlations quickly decay to $L^{-4}$ indicating a deconfinement of monomers.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Monomer correlations}
-
+\figref{fig:monomer_correlations} demonstrates that $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ decays to $L^{-4}$ for each system size, indicating a deconfinement of monomers.
+%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{table}
+%    \begin{tabular}{| l | c | c |}
+%  	\hline
+%     & $c$ & $\bar{c}$ \\
+%	\hline
+%    $i$ & $\monomermvA$ &  $\monomermvB$  \\
+%    \hline
+%  \end{tabular}
+%  \caption{The pair of local dimer \& monomer configurations $c\leftrightarrow\bar{c}$ generate
+%  minimal local monomer dynamics. Monomers always remain on their origonal sublattice. }
+%  \label{tab:pentamerMoves}
+%\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%
@@
         \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
-        \caption{ The monomer-monomer correlations function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ along a coordinate axis in the QDPM RK ground state doped with a single pair of monomers on lattices up to \note{$L=48$}.
+        \caption{ The monomer-monomer correlations function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ along a coordinate axis in the QDPM RK ground state doped with a single pair of monomers on lattices up to $L=64$.
 The horizontal lines correspond to $L^{-4}$ for the system size corresponding to the color.
-\note{Owen: Do you have data for $L=64$?
-Can you make the subscripts in the y-axis label bold math?
-Maybe we should renomalize this plot by a factor of $L^2$.
-This is only one sub-lattice--what about the other sublattice?}}
+\note{Owen: Make the subscripts in the y-axis label bold math.
+Extend the horizontal lines all the way across the plot.
+Remove the legend bounding box and use one symbol for each legend entry.
+Remove the black boundaries of the symbols.}}
         \label{fig:monomer_correlations}
     \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}
-    \begin{tabular}{| l | c | c |}
-  	\hline
-     & $c$ & $\bar{c}$ \\
-	\hline
-    $i$ & $\monomermvA$ &  $\monomermvB$  \\
-    \hline
-  \end{tabular}
-  \caption{The pair of local dimer \& monomer configurations $c\leftrightarrow\bar{c}$ generate
-  minimal local monomer dynamics. Monomers always remain on their origonal sublattice. }
-  \label{tab:pentamerMoves}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-    \centering
-    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
-    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
-    sub-lattice for a $L=64$ lattice.}
-    \label{fig:spatial_dmr_cor}
-\end{figure}
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
+%    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
+%    sub-lattice for a $L=64$ lattice.}
+%    \label{fig:spatial_dmr_cor}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\section{Additional numerical results on the QDPM RK ground state}
+\section{Additional numerical results on the QDPM RK ground state}
 %
@@
 
+To test for the possibility of translational and rotational symmetry breaking corresponding to the features in $S_d$ at the Brillouin zone edges, we define several order parameters which would capture such potential symmetry breaking.
+For rotational symmetry breaking we define
+\begin{equation}
+\Mrot \equiv  \frac{2}{L^2} \left(N_h - N_v\right) \label{eq:Mrot},
+\end{equation}
+where $N_v$ ($N_h$) is the total number of vertical (horizontal) dimers; note that $\exval{M_{\rm{rot}}^2 } \neq 0$ implies there is rotational symmetry breaking.
+to To capture translational symmetry breaking by one lattice site in a direction perpendicular to the majority of the dimers we define $\Mperp$
+\begin{align}
+\Mperp \equiv  \frac{8}{L^2} \sum_{\Box} \Bigl(  &(-1)^{r_x} \theta\left(\Mrot \right) \Pi_\Box^v \notag\\
++ &(-1)^{r_y}\theta\left(-\Mrot \right) \Pi_\Box^h\Bigr) \label{eq:Mperp},
+\end{align}
+where $\theta(x)$ is the Heaviside function, and $\Pi_\Box^h$ ($\Pi_\Box^v$) is one if the plaquette $\Box$ has two horizontal (vertical) dimers, and zero otherwise.
+Similarly, we define $\Mpar$ to be given by \Eqref{eq:Mperp} with $r_x$ and $r_y$ swapped between terms.
+Additionally, we define order parameters that indicate ``columnar" and ``staggered" dimer order~\cite{Syljuasen2005}:
+\begin{align}
+\MstagSq \equiv  \frac{1}{L^2} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
++&\biggl( \sum_{\ell_v} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2\biggr]\label{eq:Mstag},
+\end{align}
+\begin{align}
+\McolSq \equiv  \frac{1}{L^2} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
++ &\biggl( \sum_{\ell_v} (-1)^{r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2  \biggr]\label{eq:Mcol},
+\end{align}
+where the sums over $\ell_h$ ($\ell_v$) are taken over all horizontal (vertical) links.
+In \figref{fig:order_params} we have plotted the finite-size scaling of these order parameters; we find in all cases that while finite size systems display symmetry breaking due to finite-size effects, these order parameters all vanish in the thermodynamic limit, as demonstrated by the extrapolation in \figref{fig:order_params}.
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[]
+    \centering
+    \includegraphics[width=1.0\linewidth]{order_params_plot.pdf}
+    \caption{The symmetry breaking order parameters defined in \eqref{Mperp}.}
+    \label{fig:order_params}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-11-26 qdpm_paper.tex
new figures with color scheme

@@
         \centering
-        \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
-        \caption{({\it left}) Gray scale of the dimer-dimer correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice.
-The origin corresponds to the blue link, and $\bm{r}$ varies over all other links of the lattice.
-Red links have correlations that are off the given scale.
-({\it right}) The magnitude of the $Z_3$ magnetic string correlation function $|C_M(\bm{r}_{\bm{0}p})|$, where the the correlations is with respect to the blue plaquette.
-\note{Owen:What if we put the dimer structure factor on the right panel here, and move the vison correlation to the left pannel of figure 6, and put the top panel of figure 7 below these two?}}
-        \label{fig:dimer_vison_heatmap}
-    \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-   \begin{figure}[t]
-        \centering
-        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM.pdf}
-        \caption{({\it left}) The horizontal dimer density structure factor $S_d(\bm{k})$ for the QDPM RK ground state on an $L=64$ lattice.
-The lack of $x\leftrightarrow y$ rotational symmetry is due to the fact that horizontal links have been isolated.
-({\it right}) \note{Owen: Is this the real part or $\sqrt{S_M^* S_M}$}}
-        \label{fig:structure_factor} 
-    \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-    \begin{figure}[t]
-        \centering
-        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
-        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the magnitude of the $Z_3$ magnetic string structure factor $|S_M|$ ({\it bottom})
-        shown along a path in $k$ space for an $L=64$ lattice.
-Statistical errors are smaller than the symbols.
-\note{Owen: Make the k's in the y-axis bold.
-Switch the y-axis from $S_v\rightarrow S_M$.}}
-        \label{fig:structure_factor_path}
+        \includegraphics[width=1.0\columnwidth]{dimer_3way.pdf}
+        \caption
+        {
+            (a) Gray scale of the dimer-dimer correlation function $\langle n_{\bm{0}}
+            n_{\bm{r}}\rangle$ on an $L=32$ lattice. The origin corresponds to the orange link, and
+            $\bm{r}$ varies over all other links of the lattice. Red links have correlations that are off
+            the given scale. 
+            (b) The horizontal dimer density structure factor $S_d(\bm{k})$ for the
+            QDPM RK ground state on an $L=64$ lattice. The lack of $x\leftrightarrow y$ rotational
+            symmetry is due to the fact that horizontal links have been isolated. 
+            (c) The horizontal dimer-dimer structure factor $S_d(\bm{k})$ shown along a
+            path in $k$ space for an $L=64$ lattice. Statistical errors are smaller than the symbols.
+        }
+        \label{fig:dimer_3way}
     \end{figure}
@@
 These exponentially decaying magnetic string correlations are therefore consistent with a symmetric dimer liquid with no magnetic vortex condensation.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+    \begin{figure}[t]
+        \centering
+        \includegraphics[width=1.0\columnwidth]{vison_3way.pdf}
+        \caption
+        {
+            (a) Color scale of the magnetic string correlation function 
+            on an $L=32$ lattice. The origin corresponds to the orange circle and it has been removed from
+            the color scale.
+            (b) The magnitude of the $Z_3$ magnetic string correlation function
+            $|C_M(\bm{r}_{\bm{0}p})|$, where the correlations is with respect to the orange plaquette.
+            (c) The magnitude of the $Z_3$ magnetic string structure factor $|S_M|$ shown along a
+            path in $k$ space for an $L=64$ lattice. Statistical errors are smaller than the symbols.
+        }
+        \label{fig:vison_3way}
+    \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
 

### 2016-11-27 qdpm_paper.tex
v primes in appendix fixed
included correlation lengths

@@
     \includegraphics[
-      height=1.5ex,% adjust to suit
+      height=1.8ex,% adjust to suit
       valign=M,% center vertically
@@
     \caption{The dimer-dimer density correlation function $C_d$ between parallel links in the QDPM RK ground state on a $L=64$ lattice, in directions perpendicular (circles) and parallel (squares) to the dimer orientation.
-The lines represent the best fit to an exponential decay with correlation length $\chi\approx???$.
-\note{Owen: Can you add the direction parallel to the dimers to this plot?
-Can you add the correlation length estimate here as well?}}
+The lines represent the best fit to an exponential decay with correlation length $\chi\approx 1.1$.}
     \label{fig:spatial_dmr_cor}
@@
 While the vanishing of the $(0,\pi)$ peak demonstrates the restoration of rotational and translational symmetries in the thermodynamic limit, the vanishing of the $(0,0)$ peak demonstrates the lack of magnetic vortex condensation, which is a mechanism for destroying topological order and breaking lattice symmetries~\cite{Jalabert1991,Ralko2007,Huh2011}.
-\figref{fig:vison_cor} shows the decay of $|C_M|$ along one of the axes of the dual lattice; \note{we find this decays exponentially with distance, with a correlation length $\chi\approx???$}.
+\figref{fig:vison_cor} shows the decay of $|C_M|$ along one of the axes of the dual lattice; \note{we find this decays exponentially with distance, with a correlation length $\chi\approx 2.90$}.
 These exponentially decaying magnetic string correlations are therefore consistent with a symmetric dimer liquid with no magnetic vortex condensation.
@@
 \end{align}
-\note{Owen:can you add symbols with $v$ and $v'$ at both end points for all types of links?}.
 

### 2016-11-27 qdpm_paper.tex
some changes to the text

@@
 \end{equation}
-and therefore we can define two conserved topological winding numbers $\Phi_{x}$ \& $\Phi_{y}$ which are the dimer flux through topologically non-trival loops that wind around each axis of the lattice when the system has periodic conditions (see \figref{fig:orientedSL}).
-On an lattice of dimensions $L_x\times L_y$, the the eigenvalues of $\Phi_{x/y}$ integers in range
+and therefore we can define two conserved topological winding numbers $\Phi_{x}$ \& $\Phi_{y}$ which are the dimer flux through topologically non-trivial loops that wind around each axis of the lattice when the system has periodic boundary conditions (see \figref{fig:orientedSL}).
+On an lattice of dimensions $L_x\times L_y$, the eigenvalues of $\Phi_{x/y}$ are integers in the range
 \begin{equation}
@@
 $\HQDM$ no longer conserve the dimer flux $\Phi_\Gamma$ through a closed curve; only $\Phi_\Gamma \mod 2$ is preserved by $\HIGT$.
-Consequently, to define the string and loop operators which commutes with $\HIGT$ (for closed strings) we fix $\alpha = \pi$ in \Eqref{eq:Sgamma}:
+Consequently, to define the string and loop operators which commute with $\HIGT$ (for closed strings) we fix $\alpha = \pi$ in \Eqref{eq:Sgamma}:
 \begin{equation}
@@
 \end{equation}
-where $H_{\rm{pent}}$ only involves the resonances in \tabref{tab:pentamer_moves} involving pentamers.
+where $H_{\rm{pent}}$ only involves the pentamer resonances in \tabref{tab:pentamer_moves} and their
+rotational symmetry related resonances.
 
@@
 We find no evidence of a lack of ergodicity within each of the 9 topological sectors.
-For the remainder of the paper we present results in the $(0,0)$, topological sector, but we see no qualitative, dependence the topological sector for any of the results presented here.
+For the remainder of the paper we present results in the $(0,0)$ topological sector, but we see no qualitative dependence between topological sectors for any of the results presented here.
 Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled by $\Phi_{X/Y} \mod 3$, or equivalently $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$, in contrast with the extensive degeneracy of the QDM.
@@
 Here we discuss the dimer density correlations in the RK ground state of the QDPM.
-In \figref{fig:dimer_vison_heatmap} we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice; here the origin $\bm{0}$ represents the blue link, and $\bm{r}$ varies over all other links of the lattice.
-The left panel of \figref{fig:structure_factor} shows the equal-time dimer-dimer structure factor,
+In \figref{fig:dimer_3way} (a) we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=32$ lattice; here the origin $\bm{0}$ represents the orange link, and $\bm{r}$ varies over all other links of the lattice.
+In \figref{fig:dimer_3way} (b) we show the equal-time dimer-dimer structure factor,
 \begin{equation}
@@
 \end{equation}
-where we restrict the sum to horizontal links, for an $L=32$ lattice.
-\figref{fig:structure_factor_path} shows $S_d(\bm{k})$ for a particular path through the Brillouin zone.
+where we restrict the sum to horizontal links, for an $L=64$ lattice. 
+\figref{fig:dimer_3way} (c) shows $S_d(\bm{k})$ for a particular path through the Brillouin zone.
 The dimer structure factor displays broad maxima at $\bm{k} = (0, \pm \pi)$ and $\bm{k} = (\pm \pi, \pm \pi)$.
@@
 where $r$ is the distance between the links $\bm{0}$ and $\bm{r}$.
-In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel links is plotted as a function of separation, \textcolor{red}{for both $r$ parallel and perpendicular to the orientation of the dimers} \note{(Owen: can you add both directions to this plot?)} for an $L=64$ lattice.
-We find that $C_d$ decays exponentially with distance with a correlations length  $\chi\approx???$.
+In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel links is plotted as a function of separation, for $r$ perpendicular to the orientation of the dimers for an $L=64$ lattice.
+We find that $C_d$ decays exponentially with distance having a correlations length  $\chi\approx 1.1$.
 Additionally, $C_d$ displays a sub-lattice oscillation that is consistent with the finite-size maximum in $S_d$ at $(0,\pi)$.
@@
 \end{equation}
-where $p$ and $p'$ are two plaquettes, and $\gamma_{pp'}$ is any open string on the dual lattice connecting $p$ and $p'$.
-In \figref{fig:dimer_vison_heatmap}, we have plotted $|C_M|$ for an $L=16$ lattice.
+where $p$ and $p'$ are two plaquettes, and $\gamma_{pp'}$ is any open string on the dual lattice
+connecting $p$ and $p'$.
+In \figref{fig:vison_3way} (a), we have plotted $|C_M|$ for an $L=32$ lattice.
 Note, that while $C_M$ depends on the choice of the background dimerization which fixes the gauge, $|C_M|$ is independent of the background dimerization.
@@
 \end{equation}
-and plot the magnitude $|S_M$ in \figref{fig:structure_factor}.
-We have chosen d a columnar background dimerization comprising horizontal background dimers stacked in columns along the $y$-axis, as shown in \figref{fig:BKGD_dimers}\note{Where should we show the background dimerization??}; this chose breaks the translational symmetry and thus requires doubling the unit cell the $x$-direction.
-\note{Owen: What are the effects of the background dimerization?}.
+and plot the magnitude $|S_M|$ in \figref{fig:vison_3way} (b). We have chosen a columnar background dimerization comprising horizontal background dimers stacked in columns along the $y$-axis
+%, as shown in \figref{fig:BKGD_dimers}
+\note{Where should we show the background dimerization??}; this chose breaks the translational symmetry and thus requires doubling the unit cell the $x$-direction.
 While $|C_M|$ displays no obvious symmetry breaking, there are peaks in $|S_M|$ at $(0,0)$ \& $(0,\pi$) \note{(Owen: What about $(\pi,\pi)$??)}.
@@
 While the vanishing of the $(0,\pi)$ peak demonstrates the restoration of rotational and translational symmetries in the thermodynamic limit, the vanishing of the $(0,0)$ peak demonstrates the lack of magnetic vortex condensation, which is a mechanism for destroying topological order and breaking lattice symmetries~\cite{Jalabert1991,Ralko2007,Huh2011}.
-\figref{fig:vison_cor} shows the decay of $|C_M|$ along one of the axes of the dual lattice; \note{we find this decays exponentially with distance, with a correlation length $\chi\approx 2.90$}.
+\figref{fig:vison_cor} shows the decay of $|C_M|$ along one of the axes of the dual lattice; we find this decays exponentially with distance, with a correlation length $\chi\approx 2.90$.
 These exponentially decaying magnetic string correlations are therefore consistent with a symmetric dimer liquid with no magnetic vortex condensation.
@@
     \caption{ The magnitude of the $Z_3$ magnetic string correlation $|C_M|$ along along one axis of the dual lattice of an $L=64$ lattice.
-The line corresponds to an exponential fit with correlations length \note{$\chi\approx???$}.}
+The line corresponds to an exponential fit with correlations length \note{$\chi\approx 2.90$}.}
     \label{fig:vison_cor}

### 2016-11-27 qdpm_paper.tex
small changes to paper

--- 2016-11-26 qdpm_paper.tex
@@
         \centering
-        \includegraphics[width=1.0\columnwidth]{dimer_3way.pdf}
-        \caption
-        {
-            (a) Gray scale of the dimer-dimer correlation function $\langle n_{\bm{0}}
-            n_{\bm{r}}\rangle$ on an $L=32$ lattice. The origin corresponds to the orange link, and
-            $\bm{r}$ varies over all other links of the lattice. Red links have correlations that are off
-            the given scale. 
-            (b) The horizontal dimer density structure factor $S_d(\bm{k})$ for the
-            QDPM RK ground state on an $L=64$ lattice. The lack of $x\leftrightarrow y$ rotational
-            symmetry is due to the fact that horizontal links have been isolated. 
-            (c) The horizontal dimer-dimer structure factor $S_d(\bm{k})$ shown along a
-            path in $k$ space for an $L=64$ lattice. Statistical errors are smaller than the symbols.
-        }
-        \label{fig:dimer_3way}
+        \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
+        \caption{({\it left}) Gray scale of the dimer-dimer correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice.
+The origin corresponds to the blue link, and $\bm{r}$ varies over all other links of the lattice.
+Red links have correlations that are off the given scale.
+({\it right}) The magnitude of the $Z_3$ magnetic string correlation function $|C_M(\bm{r}_{\bm{0}p})|$, where the the correlations is with respect to the blue plaquette.
+\note{Owen:What if we put the dimer structure factor on the right panel here, and move the vison correlation to the left pannel of figure 6, and put the top panel of figure 7 below these two?}}
+        \label{fig:dimer_vison_heatmap}
+    \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+   \begin{figure}[t]
+        \centering
+        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM.pdf}
+        \caption{({\it left}) The horizontal dimer density structure factor $S_d(\bm{k})$ for the QDPM RK ground state on an $L=64$ lattice.
+The lack of $x\leftrightarrow y$ rotational symmetry is due to the fact that horizontal links have been isolated.
+({\it right}) \note{Owen: Is this the real part or $\sqrt{S_M^* S_M}$}}
+        \label{fig:structure_factor} 
+    \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+    \begin{figure}[t]
+        \centering
+        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
+        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the magnitude of the $Z_3$ magnetic string structure factor $|S_M|$ ({\it bottom})
+        shown along a path in $k$ space for an $L=64$ lattice.
+Statistical errors are smaller than the symbols.
+\note{Owen: Make the k's in the y-axis bold.
+Switch the y-axis from $S_v\rightarrow S_M$.}}
+        \label{fig:structure_factor_path}
     \end{figure}
@@
 These exponentially decaying magnetic string correlations are therefore consistent with a symmetric dimer liquid with no magnetic vortex condensation.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-    \begin{figure}[t]
-        \centering
-        \includegraphics[width=1.0\columnwidth]{vison_3way.pdf}
-        \caption
-        {
-            (a) Color scale of the magnetic string correlation function 
-            on an $L=32$ lattice. The origin corresponds to the orange circle and it has been removed from
-            the color scale.
-            (b) The magnitude of the $Z_3$ magnetic string correlation function
-            $|C_M(\bm{r}_{\bm{0}p})|$, where the correlations is with respect to the orange plaquette.
-            (c) The magnitude of the $Z_3$ magnetic string structure factor $|S_M|$ shown along a
-            path in $k$ space for an $L=64$ lattice. Statistical errors are smaller than the symbols.
-        }
-        \label{fig:vison_3way}
-    \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Finally, we find that the $Z_3$ magnetic string correlations decay exponentially and display no evidence of $Z_3$ vortex condensation; this is consistent with $Z_3$ vortices being gapped quasiparticles excitations above the QDPM ground state.
-
-The above results suggest a the low energy physics of the QDPM is described by a $Z_3$ gauge theory with a $Z_3$ topological ordered ground state.
+These results suggest a the low energy physics of the QDPM is described by a $Z_3$ gauge theory with a $Z_3$ topological ordered ground state.
 Thus we have demonstrated that systems with Ising degrees of freedom and local constraints can lead to $Z_N$ topological order for $N>2$, providing the a new stable phase of matter beyond the commonly seen $Z_2$ topological spin liqud.
@@
 The local constraints of the QDM can be realized in two-body spin-$1/2$ and Bose-Hubbard models, and the QDM Hamiltonian can arise perturbatively in the constrained low energy Hilbert space~\cite{Balents2002a,Zhitomirsky2005,Isakov2006c,Albuquerque2008}.
-Thus future work, it may be possible to engineer the QDPM in the low energy subspace of an experimentally realizable two-body model.
+Thus future work, it may be possible to engineer the QDPM in the low energy subspace of an experimentally realizable two-body model, providing a route to the experimental realization of a $Z_3$ topologically ordered spin liquid.
 
@@
 
-Our calculations were performed on the VACC....
+Computations were performed on the Vermont Advanced Computing Core supported by NASA (NNX-08AO96G).
 

### 2016-11-27 qdpm_paper.tex
some fixes

--- 2016-11-27 qdpm_paper.tex
@@
 ({\it right}) An example of a $Z_3$ electric string configuration with a $+1$ ($-1$) electric charge at the red (blue) vertex; this string configuration results form the action of $S_\gamma^e$ on the left panel.
-\note{Owen: Can you remove the a) and b) labels on the figure?
-Also switch the $\Gamma$ to $\gamma$, and remove the $v_0-v_3$ labels.
-Add a gray arrow on the string operator from red to blue.
-Can you add a non-trivial magnetic loop around the blue charge on the right?} }
+}
     \label{fig:example_elec_string}
@@
     \includegraphics[width=1.0\linewidth]{order_params_plot.pdf}
-    \caption{The symmetry breaking order parameters defined in \eqref{Mperp}.}
+    \caption{The symmetry breaking order parameters.}
     \label{fig:order_params}

### 2016-12-03 qdpm_paper.tex
updates to figures
small changes to manuscript

@@
 In these cases, the local constraint requires $\alpha_v \in \{ 0, \pi\}$ in \Eqref{eq:Gv} and therefore the gauge symmetry is reduced from $U(1)$ to $Z_2$.
-The set of allowed dimer resonances $\mathcal{C}_{\rm{TC}}$ is expanded accordingly:
+The set of allowed dimer resonances $\mathcal{C}_{\rm{IGT}}$ is expanded accordingly:
 \begin{align}
-\mathcal{C}_{\rm{TC}} &\equiv \bigl\{ \left(c_{\Box,i},\bar{c}_{\Box,i}\right) \bigr\} \\
+\mathcal{C}_{\rm{IGT}} &\equiv \bigl\{ \left(c_{\Box,i},\bar{c}_{\Box,i}\right) \bigr\} \\
 &=\bigl\{
@@
 
-We define the Hilbert space of the QDPM to be an odd sector GQDM where vertices are constrained to be touched by a single dimer or the center of a pentamer, such that $n_v = 1,4$.
+We define the Hilbert space of the QDPM to be a GQDM where vertices are constrained to be touched by a single dimer or the center of a pentamer, such that $n_v = 1,4$.
 For defect-free configurations in the QDPM, $Q_v$ only vanishes modulo $3$;  thus we may define a $Z_3$ charge,
@@
 \begin{equation}
-\Mrot \equiv  \frac{2}{L^2} \left(N_h - N_v\right) \label{eq:Mrot},
+\Mrot \equiv  \frac{2}{L^2} \left(N_v - N_h\right) \label{eq:Mrot},
 \end{equation}
@@
 \begin{align}
-\MstagSq \equiv  \frac{1}{L^2} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
+\MstagSq \equiv  \frac{1}{L^4} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
 +&\biggl( \sum_{\ell_v} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2\biggr]\label{eq:Mstag},
@@
 \begin{align}
-\McolSq \equiv  \frac{1}{L^2} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
+\McolSq \equiv  \frac{1}{L^4} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
 + &\biggl( \sum_{\ell_v} (-1)^{r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2  \biggr]\label{eq:Mcol},

### 2016-12-05 qdpm_paper.tex
Worked on Intro and section II

@@
 \begin{abstract}
-We study the ground state of the quantum dimer-pentamer model (QDPM) on the square lattice.
-This model is a generalization of the square lattice quantum dimer model (QDM) as its configuration space comprises fully-packed hard-core dimer coverings as well as configurations containing pentamers, where four dimers touch a vertex.
+We introduce quantum dimer-pentamer model (QDPM) on the square lattice.
+This model is a generalization of the square lattice quantum dimer model (QDM) as its configuration space comprises fully-packed hard-core dimer coverings as well as dimer configurations containing pentamers, where four dimers touch a vertex.
 Thus in the QDPM, the fully-packed, hard-core constraint of the QDM is relaxed such that the local dimer number at each vertex is fixed modulo 3; correspondingly, the local $U(1)$ gauge symmetry of the QDM Hilbert space is reduced to a local $Z_3$ gauge symmetry in the QDPM.
-We construct a local Hamiltonian for which the Rokhsar-Kivelson (RK) state (the equal superposition of all configurations in a topological sector) is the exact ground state and has a 9-fold topological degeneracy on the torus.
+We construct a local Hamiltonian for which the Rokhsar-Kivelson (RK) equal superposition state is the exact ground state and has a 9-fold topological degeneracy on the torus.
 Using Monte Carlo calculations, we find no spontaneous symmetry breaking in the RK wavefunction and that its dimer-dimer correlation function decays exponentially.
-Additionally, we discuss the possibility of $Z_3$ topological order in the ground state of the QDPM.
+By doping the QDPM RK state with a pair of monomers, we demonstrate that $Z_3$ electric charges are deconfined.
+Additionally, we introduce a $Z_3$ magnetic string operator which shows no signatures of magnetic vortex condensation also decay exponentially.
+These numerical results suggest that the ground state of the QDPM is a dimer liquid with $Z_3$ topological order.
 \end{abstract}
@@
 
-Over the last several decades, experimental and theoretical work has demonstrated that strongly interacting quantum many-body systems support exotic quantum phases of matter not described by the Landau symmetry breaking paradigm.
-One class of such quantum phases of matter are topologically ordered quantum liquids~\cite{Wen1990}, first realized experimentally via the fractional quantum Hall effect~\cite{Tsui1982,Laughlin1983,Wen1990a,Wen1995}.
-Despite the absence of conventional symmetry breaking and a local order parameter, topological quantum liquids possess a non-trivial quantum order that distinguishes them from trivial liquid phases~\cite{Nayak2008}.
-Although not detectable by local operators, topological order arises due to a non-local entanglement structure that leaves a signatures in the bipartite entanglement entropy~\cite{Levin2006a,Kitaev2006b}.
-Such topological phases may provide the basis for fault-tolerant quantum information processing~\cite{Freedman2001,Kitaev2003}.
-
-Because of the exotic nature of topological phases and their potential use for quantum information processing, there is great interest in the development of theoretical models which display these phases.
-Such models offer the possibility of furthering the understanding of these phases as well as providing candidate experimental systems in which to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Fowler2012a}.
+Strongly interacting quantum many-body systems are known to support a variety of exotic quantum phases of matter with no classical analogue.
+One class of such quantum phases of matter are topologically ordered quantum liquids; their non-trivial topological order can not be identified by a local order parameter as these phases of matter don't break conventional symmetries~\cite{Wen1990,Nayak2008}.
+Both because of of the exotic nature of topological phases and their potential use for quantum information processing~\cite{Freedman2001,Kitaev2003}, there is great interest in the development of theoretical models which display these phases and potentially provide candidate experimental systems in which to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Fowler2012a}.
+
 A variety of exactly soluble lattice models are known to support ground states with topological order that ranges from the simplest variety, $Z_2$ topological order~\cite{Kitaev2003,Wen2003}, to those with non-Abelian anyonic excitations~\cite{Levin2005a,Kitaev2006a}; such models generally involve complex many-body interactions, and thus it is desirable to find simpler models supporting topological order that are closer to what is accessible experimentally.
-
 Among the simplest class of models displaying topological quantum liquid phases are those with local geometric constraints; the constraints inhibit the formation of symmetry breaking local order and given sufficient dynamics, may lead to a symmetric liquid ground state.
@@
     \centering
-    \includegraphics[width=0.75\columnwidth]{QDPM_ex_config.pdf}
-    \caption{An example of an allowed configuration in the quantum dimer-pentamer model, in which pentamers (four dimers touching at a vertex) are allowed.
-\note{Owen: maybe we should stick with black and white for these cartoons}}
+    \includegraphics[width=0.9\columnwidth]{QDPM_ex_config.pdf}
+    \caption{An example of an allowed configuration in the quantum dimer-pentamer model. The local constraint requires that each vertex is touched by either one dimer or a four dimers (a pentamer).}
     \label{fig:QDPMex}
@@
 
-While on non-bipartite lattices, the QDM posses a topologically ordered ground state~\cite{Moessner2001a,Fendley2002}, on the square lattice there is only a liquid ground state at an isolated critical quantum point~\cite{Leung1996,Syljuasen2006}.
-If the hard-core constraint of the QDM is relaxed to a parity constraint such that each vertex must have an odd (or even) number of dimers touching each vertex, the simplest non-trivial dynamics leads to a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
-The existence of topologically ordered ground states in dimer-based models is intimately related to the local constraint which imposes a local gauge symmetry in the Hilbert space; the topological order that arises is directly related to a discrete gauge theory with the appropriate local gauge constraint~\cite{Moessner2001}.
-
-Given that these models with dimer degrees of freedom and local constraints posses the simplest non-trivial local (Ising) Hilbert space at each link, they provide a potentially simpler route to engineering exotic phases.
-The local constraints can often be enforced by a local potential energy penalty and the required dynamics are generally expected to arise at the lowest order non-trivial order in perturbation theory.
-We will refer to such models with dimer degrees of freedom on links and local constraints at vertices as \emph{generalized quantum dimer modes} (GQDMs).
+While on non-bipartite lattices, the QDM has a topologically ordered ground state~\cite{Moessner2001a,Fendley2002}, on the square lattice there is only a symmetric liquid ground state at an isolated critical quantum point~\cite{Leung1996,Syljuasen2006}.
+If the hard-core constraint of the QDM is relaxed such that only the parity of the number of dimer touching each vertex is fixed, the simplest non-trivial dynamics leads to a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
+The existence of topologically ordered ground states in these models is intimately related to the local constraint which imposes a local gauge symmetry in the Hilbert space; the topological order that arises is directly related to a discrete gauge theory with the appropriate local gauge constraint~\cite{Moessner2001}.
+
+Given that these models with dimer degrees of freedom and local constraints posses the simplest non-trivial local Hilbert space at each link, they provide a potentially simpler route to engineering exotic phases.
+The local constraints can be enforced by a local potential energy penalty and the minimal dynamics are often arise at the lowest order non-trivial order in perturbation theory from a related spin model.
+We will refer to such models with dimer degrees of freedom on links and local constraints as \emph{generalized quantum dimer modes} (GQDMs).
 Previous work has demonstrated that GQDMs on the square lattice support gapped $Z_2$ topologically ordered phases as well as gapless quantum critical points.
@@
 Correspondingly, the QDPM extends the Hilbert space of the QDM to include both fully-packed hard-core dimer configurations, as well as those with pentamers--four dimers touching a vertex.
-To give the system dynamics, the Hamiltonian includes terms that incorporate the simplest non-trivial dynamics that preserve the local constraint.
-
-We present a numerical study of the ground state of the QDPM at an exactly soluble point and demonstrate the the soluble point represents a \textcolor{red}{gapped}, disordered quantum liquid phase.
-Using Monte Carlo calculations, we explicitly demonstrate the absence of symmetry breaking order and the exponential decay of correlation functions; \textcolor{red}{by computing imaginary-time correlation functions, we find that the RK point is gapped in the thermodynamic limit}.
-By construction the QDPM has an exact local $Z_3$ symmetry and conserves a $Z_3$ topological winding number.
-Thus the QDPM has a 9-fold topological degeneracy on the torus.
-Thus we argue that the ground state of the QDPM posses $Z_3$ topological order.
+We define a local Hamiltonian that provides the simplest non-trivial dynamics that preserve this local constraint.
+Consequently, the Hamiltonian has an exact local $Z_3$ symmetry and conserves a $Z_3$ topological winding number; thus the QDPM has a 9-fold topological ground state degeneracy on the torus.
+
+Additionally we present a numerical study of the ground state of the QDPM at an exactly soluble point.
+Using Monte Carlo calculations, we explicitly demonstrate the absence of symmetry breaking order and the exponential decay of correlation functions.
+Additionally, we define a $Z_3$ magnetic string operator, whose correlations display no evidence of magnetic vortex condensation.
+Finally, by a studying systems doped with a pair of  monomer defects, we demonstrate that monomers are deconfined in the QDPM.
+Thus we argue that the ground state of the QDPM is a $Z_3$ topologically ordered dimer liquid.
 
@@
 In \secref{sec:QDPM} we present the details of the QPDM.
-\secref{sec:MC} provides the results of a Monte Carlo study of the ground state of the QDPM at its exactly soluble point.
+\secref{sec:numerics} provides the results of a Monte Carlo study of the ground state of the QDPM at its exactly soluble point.
+Finally, \secref{sec:discussion} discusses potential future work.
 
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{example_local_constraints.pdf}
-    \caption{Clockwise from the upper left panel we show an example of a QDM with constraints: one
-    dimer ($n_0 = 1$), two dimers ($n_0 = 2$), and an even ($n_P = 0$) or odd ($n_P = 1$) number of dimers touching each vertex.
-\note{Owen: Maybe for consistency we should make all the dimers loos like the dimers in the upper-left.}}
+    \includegraphics[width=0.9\linewidth]{example_local_constraints.pdf}
+    \caption{Examples of GQDMs with different local constraints. Clockwise from the upper left panel; fixed dimer number: $n_d=1$, $n_d=2$;  fixed dimer parity: odd, even.}
     \label{fig:example_local_constraints}
@@
 \end{equation}
-where $\hat{T}_\nu$ are off-diagonal kinetic energy operators, $\hat{V}_\nu$ are diagonal the potential energy operators, $t_\nu$ and $v_\nu$ parametrize the strength of these terms, and each $\nu$ and represents a set of $n_\nu$ neighboring links.
+where $\hat{T}_\nu$ are off-diagonal kinetic energy operators, $\hat{V}_\nu$ are diagonal the potential energy operators, $t_\nu$ and $v_\nu$ parametrize the strength of these terms, and each $\nu$ and represents a set of  neighboring links.
 We will limit our discussion to $t_\nu >0$.
-$\hat{T}_\nu$ is constructed to favor a resonance between two distinct allowed dimerazations of $\nu$, $c_\nu$ and its compliment $\bar{c}_\nu$, and is written as:
+$\hat{T}_\nu$ is constructed to generate resonances between two distinct allowed dimerazations of $\nu$, $c_\nu$ and its compliment $\bar{c}_\nu$, and is written as:
 \begin{equation}
@@
 
-However, at the special points in the $\{(t_\nu,v_\nu)\}$ parameter space, the exact ground state is known when \Eqref{eq:HGQDM} can be written as the sum of projection operators
+However, at the special points in the $\{(t_\nu,v_\nu)\}$ parameter space, known as the Rokhsar-Kivelson (RK) points,the exact ground state is known when \Eqref{eq:HGQDM} can be written as the sum of projection operators
 \begin{equation}
@@
 If a defect is introduced which violates the local constraint at a vertex, this can be viewed as an ``electric charge'' living on the vertex, within the context of the original GQDM.
-%Defects may be created in a GQDM by defining an ``electric string'' operator that creates pairs of defects and thus generating ``charged'' states that are outside the gauge invariant Hilbert space:
-%\begin{equation}
-%S_{vv'}^e \equiv \prod_{\ell \in \tilde{\gamma}_{vv'}} \sigma_\ell^x
-%\end{equation}
-%where $\tilde{\gamma}_{vv'}$ is an open string on the lattice from $v$ to $v'$.
-When acting on a gauge invariant state, $S_{\tilde{\gamma}}^e$ creates a neutral pair of charges $Q_v = \pm 1$ at the ends of $\tilde{\gamma}$ where the signs depend on the lattice and the initial configuration of vertices.
-One may determine if such electric charges are confined by introducing a pair of such defects and computing their spatial correlation function, thus determining the confined or deconfined nature of the GQDM ground state.
-
-The gauge symmetry allows one to construct a gauge invariant string operator $S_\gamma$ along an oriented path $\gamma$ path on the dual lattice.
+One may determine if such electric charges are confined by introducing a pair of such defects and computing their spatial correlation function; if the free energy of defects a large distances remains finite, electric charges are deconfined in the GQDM ground state.
+
+The gauge symmetry allows for the construction of a gauge invariant magnetic string operator $S_\gamma$ along an oriented path $\gamma$ path on the dual lattice.
 We first orient all the links of the square lattice such that they point from the $A$ sublattice to the $B$ sublattice (see \figref{fig:orientedSL}) and define an oriented dimer flux $\Phi_\gamma$ through the path:
@@
 \section{The Quantum Dimer Pentamer Model}
+\label{sec:QDPM}
 
@@
 \section{Discussion}
+\label{sec:discussion}
 
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{example_elec_string.pdf}
+    \includegraphics[width=1.0\linewidth]{example_elec_string.pdf}
     \caption{ ({\it left}) An example of a charge free $Z_3$ electric string configuration.
@@
 \begin{align}
-\MstagSq \equiv  \frac{1}{L^4} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
+\MstagSq \equiv  \frac{2}{L^4} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
 +&\biggl( \sum_{\ell_v} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2\biggr]\label{eq:Mstag},
@@
 \begin{align}
-\McolSq \equiv  \frac{1}{L^4} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
+\McolSq \equiv  \frac{2}{L^4} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
 + &\biggl( \sum_{\ell_v} (-1)^{r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2  \biggr]\label{eq:Mcol},

### 2016-12-06 qdpm_paper.tex
going to pull

--- 2016-11-27 qdpm_paper.tex
@@
 Finally, we find that the $Z_3$ magnetic string correlations decay exponentially and display no evidence of $Z_3$ vortex condensation; this is consistent with $Z_3$ vortices being gapped quasiparticles excitations above the QDPM ground state.
-These results suggest a the low energy physics of the QDPM is described by a $Z_3$ gauge theory with a $Z_3$ topological ordered ground state.
+
+The above results suggest a the low energy physics of the QDPM is described by a $Z_3$ gauge theory with a $Z_3$ topological ordered ground state.
 Thus we have demonstrated that systems with Ising degrees of freedom and local constraints can lead to $Z_N$ topological order for $N>2$, providing the a new stable phase of matter beyond the commonly seen $Z_2$ topological spin liqud.
@@
 The local constraints of the QDM can be realized in two-body spin-$1/2$ and Bose-Hubbard models, and the QDM Hamiltonian can arise perturbatively in the constrained low energy Hilbert space~\cite{Balents2002a,Zhitomirsky2005,Isakov2006c,Albuquerque2008}.
-Thus future work, it may be possible to engineer the QDPM in the low energy subspace of an experimentally realizable two-body model, providing a route to the experimental realization of a $Z_3$ topologically ordered spin liquid.
+Thus future work, it may be possible to engineer the QDPM in the low energy subspace of an experimentally realizable two-body model.
 
@@
 
-Computations were performed on the Vermont Advanced Computing Core supported by NASA (NNX-08AO96G).
+Our calculations were performed on the VACC....
 
@@
 \begin{align}
-\MstagSq \equiv  \frac{1}{L^2} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
+\MstagSq \equiv  \frac{4}{L^4} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
 +&\biggl( \sum_{\ell_v} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2\biggr]\label{eq:Mstag},
@@
 \begin{align}
-\McolSq \equiv  \frac{1}{L^2} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
+\McolSq \equiv  \frac{4}{L^4} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
 + &\biggl( \sum_{\ell_v} (-1)^{r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2  \biggr]\label{eq:Mcol},

### 2016-12-25 qdpm_paper.tex
Worked on text

--- 2016-12-05 qdpm_paper.tex
@@
 \secref{sec:numerics} provides the results of a Monte Carlo study of the ground state of the QDPM at its exactly soluble point.
-Finally, \secref{sec:discussion} discusses potential future work.
+Finally, \secref{sec:discussion} discusses potential future studies of the QDPM.
 
@@
 Here we will provide background about generalized quantum dimer models on the square lattice.
-We consider systems with Ising-like dimer degrees of freedom on each link, such that each link has either $0$ or $1$ dimers.
+We consider systems with Ising-like dimer degrees of freedom on each link, such that each link is either unoccupied or occupied by a single dimer.
 Given an Ising spin $\sigma_\ell$ on each link $\ell$ we define the number of dimers on the link $n_\ell \equiv 1/2+\sigma_\ell^z$, where $\sigma_\ell^i$ are the associated Pauli matrices.
@@
 where $c_P = 2$, ($c_P=1$) for models in the even (odd) sector of the constraint, and the $+$($-$) sign corresponds to vertices on the $A$($B$) sublattice.
-A local dimer number constraint requires $Q_v$ to vanish for all vertices; a dimer parity constraint requires only $(Q_v\mod 2)$ to vanish.
+A local dimer number constraint requires $Q_v$ to vanish for all vertices; a dimer parity constraint requires $(Q_v\mod 2)$ to vanish.
 
@@
 \begin{equation}
-H_{\rm{GQDM}} = -\sum_\nu t_\nu \hat{T}_{\nu} + \sum_\nu v_\nu \hat{V}_{\nu} \label{eq:HGQDM}
-\end{equation}
-where $\hat{T}_\nu$ are off-diagonal kinetic energy operators, $\hat{V}_\nu$ are diagonal the potential energy operators, $t_\nu$ and $v_\nu$ parametrize the strength of these terms, and each $\nu$ and represents a set of  neighboring links.
+H_{\rm{GQDM}} = -\sum_\nu t_\nu  {T}_{\nu} + \sum_\nu v_\nu  {V}_{\nu} \label{eq:HGQDM}
+\end{equation}
+where ${T}_\nu$ are off-diagonal kinetic energy operators, ${V}_\nu$ are diagonal potential energy operators, $t_\nu$ and $v_\nu$ parametrize the strength of these terms, and each $\nu$ and represents a set of  neighboring links.
 We will limit our discussion to $t_\nu >0$.
-$\hat{T}_\nu$ is constructed to generate resonances between two distinct allowed dimerazations of $\nu$, $c_\nu$ and its compliment $\bar{c}_\nu$, and is written as:
-\begin{equation}
-\hat{T}_{\nu} = \eket{c_\nu}\ebra{\bar{c}_\nu} + h.c.;
-\end{equation}
-in the simplest case, $\hat{T_\nu}$ involves the minimum non-trivial dimer dynamics that preserve the constraint.
+$ t{T}_\nu$ is constructed to generate resonances between two distinct allowed dimerazations of $\nu$, $c_\nu$ and its compliment $\bar{c}_\nu$, and is written as:
+\begin{equation}
+ {T}_{\nu} = \eket{c_\nu}\ebra{\bar{c}_\nu} + h.c.;
+\end{equation}
+in the simplest case, $ t{T_\nu}$ involves the minimum non-trivial dimer dynamics that preserve the constraint.
 Similarly, the potential energy term provides an energy cost for states with these local configurations:
 \begin{equation}
-\hat{V}_{\nu} = \eket{c_\nu}\ebra{c_\nu} +  \eket{\bar{c}_\nu}\ebra{\bar{c}_\nu}.
-\end{equation}
-Therefore we may define a Hamiltonian for a GQDM using \Eqref{eq:HGQDM} and defining a set of dimer resonances $\{(c_\nu,\bar{c}_\nu)\}$ and corresponding potential and kinetic energy strenghts $\{(t_\nu,v_\nu)\}$:
+ {V}_{\nu} = \eket{c_\nu}\ebra{c_\nu} +  \eket{\bar{c}_\nu}\ebra{\bar{c}_\nu}.
+\end{equation}
+Therefore we may define a Hamiltonian for a GQDM using \Eqref{eq:HGQDM} and defining a set of dimer resonances $\{(c_\nu,\bar{c}_\nu)\}$ and their corresponding strengths $\{(t_\nu,v_\nu)\}$:
 \begin{equation}
@@
 \end{equation}
- In general the $T_\nu$'s don't commute with each other or with the $V_\nu$'s, and thus the ground state of $H_{\rm{GQDM}}$ is not explicitly known.
-
-However, at the special points in the $\{(t_\nu,v_\nu)\}$ parameter space, known as the Rokhsar-Kivelson (RK) points,the exact ground state is known when \Eqref{eq:HGQDM} can be written as the sum of projection operators
-\begin{equation}
-H_{\rm{RK}} = \sum_\nu \hat{h}_\nu \label{eq:HRK},
-\end{equation}
-where all $h_\nu$ are projectors with eigenvalues $\{0,1\}$; a zero energy ground state of \Eqref{eq:HRK} is simultaneously annihilated by all $\hat{h}_\nu$.
+ In general the $[T_\nu, T_{\nu'}] \neq 0 $ and $[T_\nu,V_{\nu'}]\neq0$ when $\nu$ and $\nu'$ share links, and thus the ground state of $H_{\rm{GQDM}}$ is not explicitly known.
+
+However, at the special points in the $\{(t_\nu,v_\nu)\}$ parameter space, known as the Rokhsar-Kivelson (RK) points, when \Eqref{eq:HGQDM} can be written as the sum of projection operators
+\begin{equation}
+H_{\rm{RK}} = \sum_\nu  {h}_\nu \label{eq:HRK},
+\end{equation}
+where all $h_\nu$ are projectors with eigenvalues $\{0,1\}$, the exact ground state is known to be the zero energy state of \Eqref{eq:HRK} that is simultaneously annihilated by all ${h}_\nu$.
 Such a zero energy state, known as the RK state, may be formed from an equal superposition of all dimerizations that are connected by $\{T_\nu\}$:
@@
 If a defect is introduced which violates the local constraint at a vertex, this can be viewed as an ``electric charge'' living on the vertex, within the context of the original GQDM.
-One may determine if such electric charges are confined by introducing a pair of such defects and computing their spatial correlation function; if the free energy of defects a large distances remains finite, electric charges are deconfined in the GQDM ground state.
+One may determine if such electric charges are confined by introducing a pair of such defects and computing their spatial correlation function; if the free energy of defects at large distances remains finite, electric charges are deconfined in the GQDM ground state.
 
@@
 \begin{equation}
-\tilde{\Phi}_\gamma \equiv - \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) \tilde{n}_\ell \label{eq:phiBackground}
-\end{equation}
-where $n_\ell$ is the number operator for a static background dimer configuration which is chosen to fix the gauge, and the total charge enclosed in a closed loop $\Gamma$ is $Q_\Gamma = \Phi_\Gamma+ \tilde{\Phi}_\Gamma$.
-(Alternately can think of the source of $\tilde{\Phi}_\Gamma$ to be static charges of charge $+c_0$ ($-c_0$) sitting at the verticies of the $A$($B$) sub-lattice.).
-
-We define the string operator is defined as
+\tilde{\Phi}_\gamma \equiv  \sum_{\ell \in \gamma} \rm{sgn}\left(\ell,\gamma\right) \tilde{n}_\ell \label{eq:phiBackground}
+\end{equation}
+where $n_\ell$ is the number operator for a static background dimer configuration which is chosen to fix the gauge.
+With this gauge fixing, the total charge enclosed in a closed loop $\Gamma$ is $Q_\Gamma = \Phi_\Gamma- \tilde{\Phi}_\Gamma$.
+An alternative physical picture is that there are static charges of charge $+c_0$ ($-c_0$) sitting at the vertices of the $A$($B$) sub-lattice, which are the source of the non-vanishing $\Phi_\Gamma$ flux through a closed loop.
+
+We now may define the string operator
 \begin{equation}
@@
     \includegraphics[width=1.0\columnwidth]{mag_loops_on_orntd_lat.pdf}
-    \caption{$\Phi_i$: a nontrivial string winding around the system in one of the two possible
-        directions. $\Phi_2$: an open
-    magnetic string with two different charged (colored) visons at the end points. $\Phi_3$ a trivial closed
-    string.
-The colors red and blue distinguish the two different sublattices that orient the links.
-\note{Owen: Add a dimer/pentamer-ization to the figure.
-Also, add a monomer defect in the magnetic loop, to demonstrate the fractional statistics of defects.}}
+    \caption{The A(B) sublattices of the square lattice are colored red (blue) and the link orientations are chosen to point from the A to the B sublattice.
+The narrow dark dimers are a static background dimerization used to fix the gauge, in this case chosen to be a columnar pattern; the wider light gray dimers are the physical degrees of freedom.
+$W_Y$ is a magnetic string operator with a non-trivial winding around one axis of the torus that measured the topological sector; $S_\gamma$ and $S_\Gamma$ are examples of open and closed string operators, respectively.
+Note the monomer defect which can be detected by $S_\Gamma$.
+\note{Owen: The sublattice coloring is inconsistent}}
     \label{fig:orientedSL}
@@
 
-The two unique fixed-number constraints on the square lattice are lead to QDM in the odd sector and the quantum full-packed loop model (QFPLM) in the even sector.
-For configurations that satisfy these a number constraints, $Q_v$ strictly vanishes, and thus all states in the Hilbert space are invariant under $G_v$ for $0 \leq \alpha_v \leq 2 \pi$ in \Eqref{eq:Gv}; this represents a local $U(1)$ gauge symmetry.
+The two unique fixed-number constraints on the square lattice are lead to QDM in the odd sector ($n_v = 1$) and the quantum full-packed loop model (QFPLM) in the even sector ($n_v = 2$).
+For configurations that satisfy these a number constraints, $Q_v$ strictly vanishes, and thus all states in the Hilbert space are invariant under $G_v$ for $0 \leq \alpha_v \leq 2 \pi$ in \Eqref{eq:Gv}; this represents a local $U(1)$ gauge symmetry~\cite{Moessner2001}.
 
@@
 \end{equation}
-where we have taken $t_\bplqt = t$ \& $v_\bplqt =v$ $\forall \bplqt$.
+where we have chosen $t_\bplqt = t$, $v_\bplqt =v, \forall \bplqt$.
 %\begin{align}
@@
 \end{equation}
-and therefore we can define two conserved topological winding numbers $\Phi_{x}$ \& $\Phi_{y}$ which are the dimer flux through topologically non-trivial loops that wind around each axis of the lattice when the system has periodic boundary conditions (see \figref{fig:orientedSL}).
-On an lattice of dimensions $L_x\times L_y$, the eigenvalues of $\Phi_{x/y}$ are integers in the range
-\begin{equation}
--L_{x/y}/2 \leq  \Phi_{x/y} \leq L_{x/y}/2,
-\end{equation}
-thus there are $\mathcal{O} (L_x L_y)$ distinct topological sectors.
-
-At the Rokhsar-Kivelson point $t=v$, we may write $\HQDM$ in the form of \Eqref{eq:HRK} by defining projection operators  $\hat{h}_\nu \equiv \hat{P}^\dagger_{\nu} \hat{P}_{\nu}$, with
-\begin{equation}
-\hat{P}^\dagger_\nu \equiv \biggl( \eket{ c_\nu} - \eket{\bar{c}_\nu} \biggr).
-\end{equation} 
-Since the plaquette flip term in \Eqref{eq:HQDM} is ergodic in each of topological sector $(\Phi_x,\Phi_y)$ on the square lattice (\textcolor{red}{is this known for the FPLM???})~\cite{????}, each topological sector corresponds to a unique RK ground state where $\Omega$ is labeled by $(\Phi_x,\Phi_y)$.
-Thus the equal superposition RK points of the QDM and QFPLM have an \emph{extensively} degenerate ground states.
-
-Defects in these models correspond to states with $Q_v \neq 0$; a table of the charges associated with defects in the QDM and QFPLM is listed in \tabref{tab:defects}.
+and therefore we can define two conserved topological winding numbers $\Phi_{X}$ \& $\Phi_{Y}$ which are the dimer flux through topologically non-trivial loops that wind around each axis of the lattice when the system has periodic boundary conditions (see \figref{fig:orientedSL}).
+On an lattice of dimensions $L_x\times L_y$, the eigenvalues of $\Phi_X$ and $\Phi_Y$ are integers in the range
+\begin{equation}
+-L_{x}/2 \leq  \Phi_{X} \leq L_{x}/2,
+\end{equation}
+and similarly for $\Phi_Y$, thus there are $\mathcal{O} (L_x L_y)$ distinct topological sectors.
+
+At the Rokhsar-Kivelson point $t=v$, we may write $\HQDM$ in the form of \Eqref{eq:HRK} by defining projection operators  $ {h}_\nu \equiv  {P}^\dagger_{\nu} {P}_{\nu}$, with
+\begin{equation}
+ {P}^\dagger_\nu \equiv \biggl( \eket{ c_\nu} - \eket{\bar{c}_\nu} \biggr).
+\end{equation} 
+Since the plaquette flip term in \Eqref{eq:HQDM} is ergodic in each of topological sector $(\Phi_x,\Phi_y)$ on the square lattice~\cite{????}, each topological sector corresponds to a unique RK ground state where $\Omega$ is labeled by $(\Phi_x,\Phi_y)$.
+Thus the  RK points of the QDM and QFPLM have an \emph{extensively} degenerate ground states.
+
+Defects in these models that violate the local dimer number constraint and thus carry non-zero U(1) electric charge.
+\tabref{tab:defects} lists all the possible defects and their associated U(1) charges in QDM and QFPLM.
+When a defect lives on sublattice A, it has the opposite charge that the same defect on sublattice B has.
+Note that in the QDM, the maximum charge is $\pm 3$, and there are six distinct possible non-trivial electric charges of defects.
 
@@
 The RK point of these models have been shown to have power-law decaying dimer-dimer and monomer-monomer correlation functions and gapless excitations~\cite{Fisher1961,Kasteleyn1961,Fisher1966a,Fisher1963,Kasteleyn1963a,Sutherland1988b,Sutherland1988a,Kohmoto1988a,Liang1988,Sutherland1988,Kohmoto1988,Levitov1990,Leung1996,Henley1997,Henley1997,Henley2004a,Pollmann2006}.
+The algebraic decay of monomer correlations is indicative of the logarithmic confinement of electric charges in these models.
 Thus, such fixed number constrained models on bipartite lattices are expected to have an isolated unstable gapless critical quantum liquid points with logarithmically confined defect and an extensive topological degeneracy.
@@
     %type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  & $Q_v^{Z_3}$ & \\
-    type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  & $Q_v^{QDPM}$ & \\
+    type & $n_v$& configuration & $Q_v$ & $Q_v^{Z_2}$  & $Q_v^{\rm{Z_3}}$  \\
 	\hline
-    monomer & $0$ & -1 & -2 &  -1 & $\svrtmon$  \\
+    monomer & $0$& $\svrtmon$ & -1 & 1 &  -1   \\
 	\hline
-    dimer & $1$ & 0 & -1 &   0 & $\svrtdmr$ \\
+    dimer  & $1$ & $\svrtdmr$& 0 & 0 &   0  \\
 	\hline
-    trimer & $2$ & 1 & 0 &   1 & $\svrttrmr$ $\svrttrmrtwo$ \\
+    trimer  & $2$ & $\svrttrmr$ $\svrttrmrtwo$& 1 & 1 &   1  \\
 	\hline
-    tetramer & $3$ & 2 & 1 &   -1 & $\svrtquat$ \\
+    tetramer & $3$& $\svrtquat$  & 2 & 0 &   -1  \\
 	\hline
-    pentamer & $4$ & 3 & 2 &  0 & $\svrtpent$  \\
+    pentamer & $4$& $\svrtpent$ & 3 & 1 &  0   \\
 	\hline
   \end{tabular}
-  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM, QFPLM, and QDPM. Defects on the B sub-lattice have opposite charge.}
+  \caption{Local dimer configurations where $n_v$ dimers touch a vertex; only one representative of symmetry related configurations is shown.
+$Q_v$, $Q_v^{Z_2}$, and the $Q_v^{Z_3}$ are the associated $U(1)$, $Z_2$ and $Z_3$ charges on the A sub-lattice in the odd sector theories (QDM, odd IGT, QDPM).
+Defects on the B sub-lattice have opposite charge, with the exception of $Q_v^{Z_2}$, as there is only one type of non-trivial $Z_2$ charge.}
   \label{tab:defects}
@@
 
-We now consider relaxing the local constraint to a parity constraint such that only $Q_v^{Z_2} \equiv (Q_v \mod 2)$ is required to vanish; the resulting GQDM are the even and odd sectors are the  even \& odd Ising gauge theories (IGT) (and the closely related even and odd sector Toric Codes).
+We now consider relaxing the local constraint to a parity constraint such that only $Q_v^{Z_2} \equiv (Q_v \mod 2)$ is required to vanish; the resulting GQDM are the even and odd sectors are the  even \& odd Ising gauge theories (IGT) with constraints $n_v \in \{0,2,4\}$ and $n_v \in \{1,3\}$, respectively.
 In these cases, the local constraint requires $\alpha_v \in \{ 0, \pi\}$ in \Eqref{eq:Gv} and therefore the gauge symmetry is reduced from $U(1)$ to $Z_2$.
@@
 \end{align}
-where we implicitly include rotational symmetry related resonances. We will limit or discussion to $v_\bplqt=0$ such that the corresponding Hamiltonian is
+where we implicitly include symmetry related resonances. We will limit or discussion to $v_\bplqt=0$ such that the corresponding Hamiltonian is
 \begin{equation}
@@
 $\HQDM$ no longer conserve the dimer flux $\Phi_\Gamma$ through a closed curve; only $\Phi_\Gamma \mod 2$ is preserved by $\HIGT$.
-Consequently, to define the string and loop operators which commute with $\HIGT$ (for closed strings) we fix $\alpha = \pi$ in \Eqref{eq:Sgamma}:
+Consequently, to define the string and loop operators that commute with $\HIGT$ (for closed strings) we fix $\alpha = \pi$ in \Eqref{eq:Sgamma}:
 \begin{equation}
@@
 \end{equation}
-Thus the $W_{X,Y}^{\rm{IGT}}$ have two eigenvalues $\pm 1$, and the topological sectors on the torus can be labeled as $\Omega: (\pm 1,\pm1)$; consequently the extensive degeneracy of the fixed number constrained models has been reduced to a finite ground state degeneracy in the fixed parity models.
-
-Defects in the Ising Gauge theories have $Q_v^{Z_2} = 1$ and we identify these defects as $Z_2$ electric charges on the corresponding vertices.
-
-The ground states of $\HIGT$ are fourfold degenerate on the torus and have exponentially decaying dimer-dimer and monomer-monomer correlations (\textcolor{red}{Is this known for both sectors}) and a finite energy gap; such features demonstrated the deconfined topologically ordered nature of the ground state of the IGTs.
+Thus the $W_{X,Y}^{\rm{IGT}}$ have two eigenvalues $\pm 1$, and the topological sectors on the torus can be labeled as~$\Omega: (\pm 1,\pm1)$; consequently the extensive degeneracy of the fixed number constrained models has been reduced to a finite ground state degeneracy in the fixed parity models.
+
+Defects violating the dimer parity constraint in the IGT's have $Q_v^{Z_2} = 1$, as listed in \tabref{tab:defects}; we identify these defects as $Z_2$ electric charges on the corresponding vertices.
+Note that there is only one non-trivial charge in $Z_2$ gauge theory, thus there is no distinction between the charges of defects living on the two sublattices.
+
+The ground states of $\HIGT$ are fourfold degenerate on the torus, and have exponentially decaying dimer-dimer and monomer-monomer correlations and a finite energy gap; such features demonstrate the deconfined topologically ordered nature of the ground state of the IGTs.
 
 We may understand the emergence of the $Z_2$ topologically ordered phase of IGTs from the QDM and QFPLM from the following picture.
-The additional vertex configurations that are allowed in the IGTs (monomers and pentamers in the even sector and tetramers in the odd sector) relative to the number constrained models have $Q_v = \pm 2$.
-It is known that coupling a $U(1)$ gauge field to a charge $q$ matter field can result in an $Z_q$ gauge theory~\cite{Fradkin1979}; thus in the IGTs we have addded dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result.
+The additional vertex configurations that are allowed in the IGTs relative to the models with a dimer number constraint (monomers and pentamers in the even sector and tetramers in the odd sector, see \tabref{tab:defects}) have charge U(1) charge $Q_v = \pm 2$.
+It is known that coupling a $U(1)$ gauge field to a dynamics charge $q$ matter field can result in an $Z_q$ gauge theory~\cite{Fradkin1979}; as in the IGT's we have added dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result.
 We note that pentamers are charge $\pm3$ objects in the QDM (see \tabref{tab:defects}); thus below we investigate whether introducing pentamers into the QDM leads to an effective $Z_3$ gauge theory.
@@
 
-We define the Hilbert space of the QDPM to be a GQDM where vertices are constrained to be touched by a single dimer or the center of a pentamer, such that $n_v = 1,4$.
+We define the Hilbert space of the QDPM to be a GQDM where vertices are constrained to be touched by a single dimer or the center of a pentamer, such that $n_v \in \{1,4\}$.
 For defect-free configurations in the QDPM, $Q_v$ only vanishes modulo $3$;  thus we may define a $Z_3$ charge,
@@
 
-The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice (see \tabref{tab:pentamer_moves}).
+The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice; these local dynamics involving pentamers are illustrated in  \tabref{tab:pentamer_moves}.
 Thus we may write $\HQDPM$ as the following:
 \begin{equation}
-\HQDPM \equiv \HQDM + H_{\rm{pent}}
-\end{equation}
-where $H_{\rm{pent}}$ only involves the pentamer resonances in \tabref{tab:pentamer_moves} and their
-rotational symmetry related resonances.
+\HQDPM \equiv \HQDM + H_{\rm{pen}}
+\end{equation}
+where $H_{\rm{pen}}$ only involves the pentamer resonances in \tabref{tab:pentamer_moves} and those related by symmetry:
+\begin{align}
+H_{\rm{pen}} \equiv \HGQDM \biggl( &\bigl\{ \left(c_a,\bar{c}_a\right),\left(c_b,\bar{c}_b\right),\left(c_c,\bar{c}_c\right) \bigr\},\biggr.\notag\\
+\biggl. &\bigl\{ \left(t_a,v_a\right),\left(t_b,v_b\right),\left(t_c,v_c\right) \bigr\} \biggr)  \label{eq:Hpen}
+\end{align}
 
@@
   	\hline
-     & $c$ & $\bar{c}$ \\
+    $\nu$ & $c_\nu$ & $\bar{c}_\nu$ \\
 	\hline
-    $i$ & $\pentmvcreate$ &  $\pentmvanal$  \\
+    $a$ & $\pentmvcreate$ &  $\pentmvanal$  \\
 	\hline
-    $ii$ &$\penmvhrzleft$&$\penmvhrzright$ \\
+    $b$ &$\penmvhrzleft$&$\penmvhrzright$ \\
 	\hline
-    $iii$ &$\penmvdiagup$& $\penmvdiagdown$\\
+    $c$ &$\penmvdiagup$& $\penmvdiagdown$\\
 	\hline
   \end{tabular}
-  \caption{The pairs of local dimer \& pentamer configurations $c\leftrightarrow\bar{c}$ generate minimal local dynamics that create/annihilate pairs ($i$) of pentamers and translate single pentamers ($ii$ \& $iii$).
+  \caption{The pairs of local dimer \& pentamer configurations $c_\nu\leftrightarrow\bar{c}_\nu$ generate minimal local dynamics that create/annihilate pairs ($a$) of pentamers and translate single pentamers ($b$ \& $c$).
 Note that pentamers always stay on the same sublattice which is associated with their $U(1)$ charge.
@@
 
-Our numerical simulations (discussed below in \secref{sec:numerics}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector.
-The exact zero energy ground state at the RK point, where $t_i=v_i, i \in \{ 0,1,2,3\}$, is the RK state, where the superposition is taken to be over all states in the topological sector $\Omega$ which are labeled by the topological loop operators
-\begin{equation}
-\Omega = \left(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}} \right)
-\end{equation}
-Since the $W_{X,Y}^{\rm{QDPM}}$ operators have eigenvalues $\{0,1,-1\}$...
-
-Defects in the QDPM (monomers, trimers, and tetramers) carry a $Z_3$ electric charge $Q_v^{Z_3} = \pm 1$, where the sign depends on the sub-lattice and type of defect (see \ref{tab:defects}).
-
-Thus we have demonstrated that ground state at the RK point of the QDPM has an exact $Z_3$ gauge symmetry and a corresponding $9$-fold topological degeneracy on the torus.
-We emphasize that despite the exact $Z_3$ local gauge symmetry of the QDPM, there is not an exact mapping to a $Z_3$ gauge theory on the square lattice, as the QDPM has Ising degrees of freedom on the links, rather than the 3 dimensional local Hilbert space of a $Z_3$ gauge theory.
-It remains to address whether this RK state is in the deconfined $Z_3$ topologically ordered phase of a $Z_3$ gauge theory, or a critically correlated or confining symmetry broken phase, which we do below.
+Our numerical simulations (discussed below in \secref{sec:numerics}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector $\Omega$ that are labeled by the topological loop operators:
+\begin{equation}
+\Omega = \left(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}} \right).
+\end{equation}
+The exact zero energy ground state at the RK point, where $t_i=v_i, i \in \{ 0,1,2,3\}$, is the RK state, where the superposition is taken to be over all states in the topological sector.
+Since the $W_{X,Y}^{\rm{QDPM}}$ operators have eigenvalues $\{1,e^{i2\pi/3},e^{-i2\pi/3}\}$, the RK point of the QDPM is therefore 9-fold degenerate on the torus.
+
+Defects in the QDPM include monomers, trimers, and tetramers.
+As these dimer configurations violate the local constraint at the vertex, these defects carry a non-vanishing $Z_3$ electric charge $Q_v^{Z_3} = \pm 1$, where the sign depends on the sub-lattice and type of defect.
+\tabref{tab:defects} lists the $Z_3$ charge for these defects on one sublattice; defects of the same type carry opposite charge when living on opposite sublattices.
+
+We have demonstrated that ground state at the RK point of the QDPM has an exact $Z_3$ gauge symmetry and a corresponding $9$-fold topological degeneracy on the torus.
+We emphasize that despite the exact $Z_3$ local gauge symmetry of the QDPM, there is not an exact mapping to a $Z_3$ gauge theory on the square lattice, as the QDPM has Ising degrees of freedom on the links, rather than the 3 dimensional local Hilbert space of a $Z_3$ gauge theory (see \ref{sec:Z3GT} for details of $Z_3$ gauge theory).
+It remains to address whether this RK state is in the deconfined $Z_3$ topologically ordered phase of a $Z_3$ gauge theory, or a critically correlated or confining symmetry broken phase, which we discuss below.
 
@@
 To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamer_moves}.
-Below we present the results of calculations on $L\times L$ lattices with periodic boundary conditions on systems up to $L=64$.
+Below we present the results of calculations on $L\times L$ square lattices with periodic boundary conditions on systems up to $L=128$.
 
@@
 
-We explicitly demonstrate how the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the histogram of $U(1)$ topological winding number $\Phi_{X/Y}$ .
-$\Phi_X$ is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors (the behavior of $\Phi_Y$ is identical to that of $\Phi_X$~\note{(Owen: can you confirm this?)}).
+We explicitly demonstrate how the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the histogram of $U(1)$ topological winding numbers $\Phi_{X}$ and $\Phi_{Y}$.
+The histograms of these U(1) winding numbers is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors (the behavior of $\Phi_Y$ is identical to that of $\Phi_X$~\note{(Owen: can you confirm this?)}).
 We confirm that $\Phi_{X/Y}$ is only conserved modulo $3$, rather than strictly conserved as it is in the QDM.
@@
     \includegraphics[width=1.0\linewidth]{u1_wind_qdpm.pdf}
-    \caption{The histogram of the $U(1)$ winding number $\Phi_X$ as measured in the QDPM on a
-    $L=32$ lattice.
+    \caption{The histogram of the $U(1)$ winding number $\Phi_X$ as measured in for the ground state of the RK point of the QDPM for three different lattice sizes.
 Different colors correspond to calculations initialized to different winding sectors, and the lines are fits to a Gaussian.
-Note that $\Phi_X$ is conserved modulo $3$, resulting in a $9$-fold topological degeneracy on a torus, that is labeled by $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$.
-\note{Owen: Can you plot $P\left(\Phi_Y\right)$ on this plot also?
-Maybe with open symbols?}}
+Note that $\Phi_X$ is conserved modulo $3$, resulting in a $9$-fold topological degeneracy on a torus.}
     \label{fig:u1_wind_qdpm}
@@
 \section{$Z_3$ Gauge theory on the square lattice}
-
+\label{sec:Z3GT}
 Here we will review a string-net implementation of $Z_3$ gauge theory on the square lattice~\cite{Horn1979}.
@@
 \begin{align}
-\MstagSq \equiv  \frac{2}{L^4} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
+\MstagSq \equiv  \frac{4}{L^4} \biggl[ &\biggl( \sum_{\ell_h} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2  \notag\\
 +&\biggl( \sum_{\ell_v} (-1)^{r_x+r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2\biggr]\label{eq:Mstag},
@@
 \begin{align}
-\McolSq \equiv  \frac{2}{L^4} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
+\McolSq \equiv  \frac{4}{L^4} \biggl[  &\biggl( \sum_{\ell_h} (-1)^{r_x} n_d \left(\vec{r}_{\ell_h}\right) \biggr)^2 \notag \\
 + &\biggl( \sum_{\ell_v} (-1)^{r_y} n_d \left(\vec{r}_{\ell_v}\right) \biggr)^2  \biggr]\label{eq:Mcol},

### 2016-12-25 qdpm_paper.tex
Worked on sec IV

@@
 $W_Y$ is a magnetic string operator with a non-trivial winding around one axis of the torus that measured the topological sector; $S_\gamma$ and $S_\Gamma$ are examples of open and closed string operators, respectively.
-Note the monomer defect which can be detected by $S_\Gamma$.
-\note{Owen: The sublattice coloring is inconsistent}}
+Note the monomer defect which can be detected by $S_\Gamma$.}
     \label{fig:orientedSL}
@@
 
-To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamer_moves}.
-Below we present the results of calculations on $L\times L$ square lattices with periodic boundary conditions on systems up to $L=128$.
+To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamer_moves} and single plaquette flips, as defined in \Eqref{eq:HQDM}.
+Below we present the results of calculations on $L\times L$ square lattices with periodic boundary conditions on systems of linear dimension up to $L=128$.
 
@@
 We explicitly demonstrate how the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the histogram of $U(1)$ topological winding numbers $\Phi_{X}$ and $\Phi_{Y}$.
-The histograms of these U(1) winding numbers is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors (the behavior of $\Phi_Y$ is identical to that of $\Phi_X$~\note{(Owen: can you confirm this?)}).
-We confirm that $\Phi_{X/Y}$ is only conserved modulo $3$, rather than strictly conserved as it is in the QDM.
-We find that $P(\Phi_{X/Y})$ has a roughly Gaussian envelope with a width that increases with system size--this is expected as $\Phi_{X/Y} = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
+The histograms of these U(1) winding numbers is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors $(\Phi_X,\Phi_Y)$.
+This confirms that $\Phi_X$ and $\Phi_Y$ are only conserved modulo $3$, rather than strictly conserved as they are in the QDM.
+We find that the histogram $P(\Phi)$ has a roughly Gaussian envelope with a width that increases with system size; this is expected as $\Phi = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
 We find no evidence of a lack of ergodicity within each of the 9 topological sectors.
 For the remainder of the paper we present results in the $(0,0)$ topological sector, but we see no qualitative dependence between topological sectors for any of the results presented here.
-Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled by $\Phi_{X/Y} \mod 3$, or equivalently $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$, in contrast with the extensive degeneracy of the QDM.
+Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$, in contrast with the extensive degeneracy of the QDM.
 %%%%%%%%%%%%%%%%%%%%%%%
@@
     \includegraphics[width=1.0\linewidth]{u1_wind_qdpm.pdf}
-    \caption{The histogram of the $U(1)$ winding number $\Phi_X$ as measured in for the ground state of the RK point of the QDPM for three different lattice sizes.
-Different colors correspond to calculations initialized to different winding sectors, and the lines are fits to a Gaussian.
-Note that $\Phi_X$ is conserved modulo $3$, resulting in a $9$-fold topological degeneracy on a torus.}
+    \caption{The histogram of the $U(1)$ topological winding numbers $\Phi_X$ and $\Phi_Y$ as measured in for the ground state of the RK point of the QDPM for three different lattice sizes.
+The colors correspond to calculations initialized to different topological sectors $(\Phi_X,\Phi_Y)$: blue $(0,0)$, red $(1,1)$, and purple $(-1,-1)$.
+The lines are fits to a Gaussian for each system size.
+Note that $\Phi$ is conserved modulo $3$, resulting in a $9$-fold topological degeneracy on a torus.}
     \label{fig:u1_wind_qdpm}
@@
 
-Here we discuss the dimer density correlations in the RK ground state of the QDPM.
+We will now present a numerical study of the dimer density correlations in the RK ground state of the QDPM.
 In \figref{fig:dimer_3way} (a) we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=32$ lattice; here the origin $\bm{0}$ represents the orange link, and $\bm{r}$ varies over all other links of the lattice.
+These bare dimer correlations display only short range correlations no obvious symmetry breaking.
 In \figref{fig:dimer_3way} (b) we show the equal-time dimer-dimer structure factor,
@@
 The dimer structure factor displays broad maxima at $\bm{k} = (0, \pm \pi)$ and $\bm{k} = (\pm \pi, \pm \pi)$.
-The lack of rotational symmetry of $S_d(\bm{k})$ is due to the fact that we have isolated horizontal dimers--the correlations between vertical dimers display the same behavior, rotated by $\pi/2$.
-We have plotted the finite size scaling of the intensity of these peaks in  \figref{fig:bragg_scaling}, which we find to vanish in the thermodynamic limit.
-These maxima at $(0,\pi)$ and $(\pi,\pi)$ are thus consistent with finite size effects due to short distance correlations.
-Thus we see no evidence of thermodynamic limit symmetry breaking.
+The lack of rotational symmetry of $S_d(\bm{k})$ is due to the fact that we have isolated horizontal dimers; the correlations between vertical dimers display the same behavior, rotated by $\pi/2$.
+We have plotted the finite size scaling of the intensity of the broad maximum of $S_d$ in  \figref{fig:bragg_scaling}, which we find to vanish in the thermodynamic limit; these maxima are therefore consistent with finite size effects due to short distance correlations.
+Thus we see no evidence of symmetry breaking in the thermodynamic limit.
 
@@
     \includegraphics[width=1.0\columnwidth]{peak_scaling.pdf}
-    \caption{Finite-size scaling of the maxima in the dimer ($S_d$) and magnetic string ($|S_M|$) structure factors.
+    \caption{Finite-size scaling of the maxima in the dimer ($S_d$) and magnetic string ($S_M$) structure factors.
 All maximum vanish in the thermodynamic limit, indicating that the RK state of the QDPM is a symmetric dimer liquid.
-\note{Owen: We don't need the absolute value bars for $S_d$ since it's real.}}
+}
     \label{fig:bragg_scaling}
@@
 where $r$ is the distance between the links $\bm{0}$ and $\bm{r}$.
-In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel links is plotted as a function of separation, for $r$ perpendicular to the orientation of the dimers for an $L=64$ lattice.
-We find that $C_d$ decays exponentially with distance having a correlations length  $\chi\approx 1.1$.
+In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel links is plotted as a function of separation, for $\bm{r}$ perpendicular to the orientation of the dimers for an $L=64$ lattice.
+We find that $C_d$ decays exponentially with distance having a correlations length  $\chi\approx 1$.
 Additionally, $C_d$ displays a sub-lattice oscillation that is consistent with the finite-size maximum in $S_d$ at $(0,\pi)$.
@@
     \includegraphics[width=1.0\columnwidth]{spatial_cors_parallel.pdf}
-    \caption{The dimer-dimer density correlation function $C_d$ between parallel links in the QDPM RK ground state on a $L=64$ lattice, in directions perpendicular (circles) and parallel (squares) to the dimer orientation.
-The lines represent the best fit to an exponential decay with correlation length $\chi\approx 1.1$.}
+    \caption{The dimer-dimer density correlation function $C_d$ between parallel links in the QDPM RK ground state on a $L=64$ lattice, in the direction perpendicular to the dimer orientation.
+The lines represent the best fit to an exponential decay with correlation length $\chi\approx 1$.}
     \label{fig:spatial_dmr_cor}
@@
 Note, that while $C_M$ depends on the choice of the background dimerization which fixes the gauge, $|C_M|$ is independent of the background dimerization.
+We find that$C_M$ only displays short range correlations, and no obvious symmetry breaking.
+
 Additionally, we have computed the magnetic string structure factor
 \begin{equation}
-S_M\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{p,p'} e^{-i \bm{k} \cdot r_{pp'}} C_M\left( \bm{r}_{pp'}\right)
-\end{equation}
-and plot the magnitude $|S_M|$ in \figref{fig:vison_3way} (b). We have chosen a columnar background dimerization comprising horizontal background dimers stacked in columns along the $y$-axis
-%, as shown in \figref{fig:BKGD_dimers}
-\note{Where should we show the background dimerization??}; this chose breaks the translational symmetry and thus requires doubling the unit cell the $x$-direction.
+S_M\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{p,p'} e^{-i \bm{k} \cdot \bm{r}_{pp'}} C_M\left( \bm{r}_{pp'}\right)
+\end{equation}
+and plot the magnitude $|S_M|$ in \figref{fig:vison_3way} (b).
+We have chosen a columnar background dimerization comprising horizontal background dimers stacked in columns along the $y$-axis, as shown in \figref{mag_loops_on_orntd_lat.pdf}; this chose breaks the translational symmetry and thus requires doubling the unit cell the $x$-direction.
 While $|C_M|$ displays no obvious symmetry breaking, there are peaks in $|S_M|$ at $(0,0)$ \& $(0,\pi$) \note{(Owen: What about $(\pi,\pi)$??)}.

### 2017-01-06 qdpm_paper.tex
Worked on text

@@
 
-If a defect is introduced which violates the local constraint at a vertex, this can be viewed as an ``electric charge'' living on the vertex, within the context of the original GQDM.
-One may determine if such electric charges are confined by introducing a pair of such defects and computing their spatial correlation function; if the free energy of defects at large distances remains finite, electric charges are deconfined in the GQDM ground state.
+If a defect is introduced which violates the local constraint at a vertex, this can be viewed as an ``electric charge'' living on the vertex.
+One may determine if such electric charges are confined by introducing a pair of such defects and computing their spatial correlation function; if the free energy cost of defects at large distances remains finite, electric charges are deconfined in the GQDM ground state.
 
@@
 
-We now consider relaxing the local constraint to a parity constraint such that only $Q_v^{Z_2} \equiv (Q_v \mod 2)$ is required to vanish; the resulting GQDM are the even and odd sectors are the  even \& odd Ising gauge theories (IGT) with constraints $n_v \in \{0,2,4\}$ and $n_v \in \{1,3\}$, respectively.
+We now relax the local constraint to a parity constraint such that only $Q_v^{Z_2} \equiv (Q_v \mod 2)$ is required to vanish; the resulting GQDM are the even and odd sectors are the  even \& odd Ising gauge theories (IGT) with constraints $n_v \in \{0,2,4\}$ and $n_v \in \{1,3\}$, respectively.
 In these cases, the local constraint requires $\alpha_v \in \{ 0, \pi\}$ in \Eqref{eq:Gv} and therefore the gauge symmetry is reduced from $U(1)$ to $Z_2$.
@@
 \begin{equation}
-S_\gamma^{\rm{IGT}} \equiv S_\gamma \left( \pi \right), \quad W_{X,Y}^{\rm{IGT}} \equiv W_{X,Y} \left( \pi \right).
-\end{equation}
-Thus the $W_{X,Y}^{\rm{IGT}}$ have two eigenvalues $\pm 1$, and the topological sectors on the torus can be labeled as~$\Omega: (\pm 1,\pm1)$; consequently the extensive degeneracy of the fixed number constrained models has been reduced to a finite ground state degeneracy in the fixed parity models.
+S_\gamma^{Z_2} \equiv S_\gamma \left( \pi \right), \quad W_{X,Y}^{Z_2} \equiv W_{X,Y} \left( \pi \right).
+\end{equation}
+Thus the $W_{X,Y}^{Z_2}$ have two eigenvalues $\pm 1$, and the topological sectors on the torus can be labeled as~$\Omega= (\pm 1,\pm1)$; consequently the extensive degeneracy of the fixed number constrained models has been reduced to a finite ground state degeneracy in the fixed parity models.
 
@@
 We may understand the emergence of the $Z_2$ topologically ordered phase of IGTs from the QDM and QFPLM from the following picture.
-The additional vertex configurations that are allowed in the IGTs relative to the models with a dimer number constraint (monomers and pentamers in the even sector and tetramers in the odd sector, see \tabref{tab:defects}) have charge U(1) charge $Q_v = \pm 2$.
+The additional vertex configurations that are allowed in the IGTs relative to the models with a dimer number constraint  have charge U(1) charge $Q_v = \pm 2$ (see \tabref{tab:defects}).
 It is known that coupling a $U(1)$ gauge field to a dynamics charge $q$ matter field can result in an $Z_q$ gauge theory~\cite{Fradkin1979}; as in the IGT's we have added dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result.
@@
 The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice; these local dynamics involving pentamers are illustrated in  \tabref{tab:pentamer_moves}.
-Thus we may write $\HQDPM$ as the following:
+Note that pentamers give dynamics to ``staggered" regions with no flippable plaquettes; thus we expect the QDPM to have weaker correlations that the QDM, where the dynamics are more constrained.
+We may write $\HQDPM$ as the following:
 \begin{equation}
@@
 \begin{align}
-H_{\rm{pen}} \equiv \HGQDM \biggl( &\bigl\{ \left(c_a,\bar{c}_a\right),\left(c_b,\bar{c}_b\right),\left(c_c,\bar{c}_c\right) \bigr\},\biggr.\notag\\
-\biggl. &\bigl\{ \left(t_a,v_a\right),\left(t_b,v_b\right),\left(t_c,v_c\right) \bigr\} \biggr)  \label{eq:Hpen}
+H_{\rm{pen}} \equiv \HGQDM \biggl( &\bigl\{ \left(c_{\nu_1},\bar{c}_{\nu_1}\right),\left(c_{\nu_2},\bar{c}_{\nu_2}\right),\left(c_{\nu_3},\bar{c}_{\nu_3}\right) \bigr\},\biggr.\notag\\
+\biggl. &\bigl\{ \left(t_1,v_1\right),\left(t_2,v_2\right),\left(t_3,v_3\right) \bigr\} \biggr)  \label{eq:Hpen}
 \end{align}
@@
 	\hline
-    $a$ & $\pentmvcreate$ &  $\pentmvanal$  \\
+    $\nu_1$ & $\pentmvcreate$ &  $\pentmvanal$  \\
 	\hline
-    $b$ &$\penmvhrzleft$&$\penmvhrzright$ \\
+    $\nu_2$ &$\penmvhrzleft$&$\penmvhrzright$ \\
 	\hline
-    $c$ &$\penmvdiagup$& $\penmvdiagdown$\\
+    $\nu_3$ &$\penmvdiagup$& $\penmvdiagdown$\\
 	\hline
   \end{tabular}
-  \caption{The pairs of local dimer \& pentamer configurations $c_\nu\leftrightarrow\bar{c}_\nu$ generate minimal local dynamics that create/annihilate pairs ($a$) of pentamers and translate single pentamers ($b$ \& $c$).
+  \caption{The pairs of local dimer \& pentamer configurations $c_\nu\leftrightarrow\bar{c}_\nu$ generate minimal local dynamics that create/annihilate pairs ($\nu_1$) of pentamers and translate single pentamers ($\nu_2$ \& $\nu_3$).
 Note that pentamers always stay on the same sublattice which is associated with their $U(1)$ charge.
@@
 \begin{equation}
-S_\gamma^{\rm{QDPM}} \equiv S_\gamma \left( 2\pi/3\right), \quad W_{X,Y}^{\rm{QDPM}} \equiv W_{X,Y} \left( 2\pi/3\right). \label{eq:SQDPM}
-\end{equation}
-Thus we have 
-\begin{equation}
-\left[ W_{X,Y}^{\rm{QDPM}}, \HQDPM \right] = 0.
-\end{equation}
-and for closed curves $\Gamma$
-\begin{equation}
-\left[ S_\Gamma^{\rm{QDPM}}, \HQDPM \right] = 0.
-\end{equation}
+S_\gamma^{Z_3} \equiv S_\gamma \left( 2\pi/3\right), \quad W_{X}^{Z_3} \equiv W_{X} \left( 2\pi/3\right) \label{eq:SQDPM}
+\end{equation}
+and similarly for $W_Y^{Z_3}$. With these definitions, closed string operators $S_\Gamma^{Z_3}$ and the topological loop operators $W_{X}^{Z_3}$ and $W_{Y}^{Z_3}$ commute with $\HQDPM$.
 
@@
 \begin{equation}
-\Omega = \left(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}} \right).
-\end{equation}
-The exact zero energy ground state at the RK point, where $t_i=v_i, i \in \{ 0,1,2,3\}$, is the RK state, where the superposition is taken to be over all states in the topological sector.
-Since the $W_{X,Y}^{\rm{QDPM}}$ operators have eigenvalues $\{1,e^{i2\pi/3},e^{-i2\pi/3}\}$, the RK point of the QDPM is therefore 9-fold degenerate on the torus.
+\Omega = \left(W_X^{Z_3},W_Y^{Z_3} \right).
+\end{equation}
+The exact zero energy ground state at the RK point, where $t_i=v_i, i \in \{ 1,2,3\}$, is the RK state, where the superposition is taken to be over all states in the topological sector.
+Since the $W_{X}^{Z_3}$ and  $W_{Y}^{Z_3}$ have eigenvalues $\{1,e^{i2\pi/3},e^{-i2\pi/3}\}$, the RK point of the QDPM is therefore 9-fold degenerate on the torus.
 
@@
 We emphasize that despite the exact $Z_3$ local gauge symmetry of the QDPM, there is not an exact mapping to a $Z_3$ gauge theory on the square lattice, as the QDPM has Ising degrees of freedom on the links, rather than the 3 dimensional local Hilbert space of a $Z_3$ gauge theory (see \ref{sec:Z3GT} for details of $Z_3$ gauge theory).
-It remains to address whether this RK state is in the deconfined $Z_3$ topologically ordered phase of a $Z_3$ gauge theory, or a critically correlated or confining symmetry broken phase, which we discuss below.
+It remains to address whether this RK state is in the deconfined $Z_3$ topologically ordered phase of a $Z_3$ gauge theory, or a confined symmetry broken or critical state, which we discuss below.
 
@@
 This confirms that $\Phi_X$ and $\Phi_Y$ are only conserved modulo $3$, rather than strictly conserved as they are in the QDM.
-We find that the histogram $P(\Phi)$ has a roughly Gaussian envelope with a width that increases with system size; this is expected as $\Phi = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
+We find that the histogram $P(\Phi)$ has a Gaussian shape with a width that increases with system size; this is expected as $\Phi = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
 We find no evidence of a lack of ergodicity within each of the 9 topological sectors.
 For the remainder of the paper we present results in the $(0,0)$ topological sector, but we see no qualitative dependence between topological sectors for any of the results presented here.
-Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled $(W_X^{\rm{QDPM}},W_Y^{\rm{QDPM}})$, in contrast with the extensive degeneracy of the QDM.
+Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled $(W_X^{Z_3},W_Y^{Z_3})$, in contrast with the extensive degeneracy of the QDM.
 %%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-23 qdpm_paper.tex
Revised sections IV & V

@@
 Thus, such fixed number constrained models on bipartite lattices are expected to have an isolated unstable gapless critical quantum liquid points with logarithmically confined defect and an extensive topological degeneracy.
-These features of fixed number constrained models are consistent with the effective U(1) gauge theory description of the RK point~\cite{Fradkin2004,Fradkin1990,Moessner2001}; in 2+1D pure U(1) gauge theories are always confining and thus the lack of an extended deconfined topologically ordered phase near the RK point~\cite{PolyakovBook}.
+These features of fixed number constrained models are consistent with the effective U(1) gauge theory description of the RK point~\cite{Fradkin2004,Fradkin1990,Moessner2001}; in 2+1D pure U(1) gauge theories are confining and thus the lack of an extended deconfined topologically ordered phase near the RK point~\cite{PolyakovBook}.
 
@@
 
-To determine the nature of the ground state at the RK point of the QDPM, we have used Monte Carlo sampling of $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamer_moves} and single plaquette flips, as defined in \Eqref{eq:HQDM}.
+To determine the nature of the ground state at the RK point of the QDPM, we have Monte Carlo sampled $\ket{\Psi_{\rm{RK}}}$, using local updates corresponding to the dimer resonances shown in \tabref{tab:pentamer_moves} and single plaquette flips, as defined in \Eqref{eq:HQDM}.
 Below we present the results of calculations on $L\times L$ square lattices with periodic boundary conditions on systems of linear dimension up to $L=128$.
@@
 
-We explicitly demonstrate how the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the histogram of $U(1)$ topological winding numbers $\Phi_{X}$ and $\Phi_{Y}$.
-The histograms of these U(1) winding numbers is shown in \figref{fig:u1_wind_qdpm}, where the different colors represent calculations that were initialized to different winding sectors $(\Phi_X,\Phi_Y)$.
-This confirms that $\Phi_X$ and $\Phi_Y$ are only conserved modulo $3$, rather than strictly conserved as they are in the QDM.
-We find that the histogram $P(\Phi)$ has a Gaussian shape with a width that increases with system size; this is expected as $\Phi = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
+We explicitly demonstrate that the extensive topological degeneracy of the QDM is reduced to a finite degeneracy in the QDPM by computing the histogram of $U(1)$ topological winding numbers $\Phi_{X}$ and $\Phi_{Y}$, which is shown in \figref{fig:u1_wind_qdpm}.
+The different colors represent calculations that were initialized to different winding sectors $(\Phi_X,\Phi_Y)$, and we find that $\Phi_X$ and $\Phi_Y$ are not  strictly conserved (as they are in the QDM), but are only conserved modulo $3$.
+The histogram $P(\Phi)$ has a Gaussian shape with a width that increases with system size; this is expected as $\Phi = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
 We find no evidence of a lack of ergodicity within each of the 9 topological sectors.
@@
 We will now present a numerical study of the dimer density correlations in the RK ground state of the QDPM.
-In \figref{fig:dimer_3way} (a) we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=32$ lattice; here the origin $\bm{0}$ represents the orange link, and $\bm{r}$ varies over all other links of the lattice.
+In \figref{fig:dimer_3way} (a) we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on a $L=32$ lattice; here the origin $\bm{0}$ represents the orange link, and $\bm{r}$ varies over all other links of the lattice.
 These bare dimer correlations display only short range correlations no obvious symmetry breaking.
@@
 \begin{equation}
-S_d\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{i,j} e^{-i \bm{k} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_{\bm{r}_i} n_{\bm{r}_j} \right \rangle
-\end{equation}
-where we restrict the sum to horizontal links, for an $L=64$ lattice. 
-\figref{fig:dimer_3way} (c) shows $S_d(\bm{k})$ for a particular path through the Brillouin zone.
+S_d\left( \bm{k} \right) \equiv \frac{1}{ L^4} \sum_{i,j} e^{-i \bm{k} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_{\bm{r}_i} n_{\bm{r}_j} \right \rangle
+\end{equation}
+where we restrict the sum to horizontal links, for a $L=64$ lattice. 
+\figref{fig:dimer_3way} (c) shows the magnitude \note{(Owen: Is $S_d$ real \& positive?)} of $S_d(\bm{k})$ for a particular path through the Brillouin zone.
 The dimer structure factor displays broad maxima at $\bm{k} = (0, \pm \pi)$ and $\bm{k} = (\pm \pi, \pm \pi)$.
@@
     \caption{Finite-size scaling of the maxima in the dimer ($S_d$) and magnetic string ($S_M$) structure factors.
-All maximum vanish in the thermodynamic limit, indicating that the RK state of the QDPM is a symmetric dimer liquid.
+All maxima vanish in the thermodynamic limit, indicating that the RK state of the QDPM is a symmetric dimer liquid.
 }
@@
 where $r$ is the distance between the links $\bm{0}$ and $\bm{r}$.
-In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel links is plotted as a function of separation, for $\bm{r}$ perpendicular to the orientation of the dimers for an $L=64$ lattice.
+In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel links is plotted as a function of separation, for $\bm{r}$ perpendicular to the orientation of the dimers for a $L=64$ lattice.
 We find that $C_d$ decays exponentially with distance having a correlations length  $\chi\approx 1$.
@@
     \includegraphics[width=1.0\columnwidth]{spatial_cors_parallel.pdf}
-    \caption{The dimer-dimer density correlation function $C_d$ between parallel links in the QDPM RK ground state on a $L=64$ lattice, in the direction perpendicular to the dimer orientation.
+    \caption{The dimer-dimer density correlation function $C_d$ between parallel links in the QDPM RK ground state on a $L=64$ lattice, along the direction perpendicular to the link orientation.
 The lines represent the best fit to an exponential decay with correlation length $\chi\approx 1$.}
@@
 \end{equation}
-where $p$ and $p'$ are two plaquettes, and $\gamma_{pp'}$ is any open string on the dual lattice
+where $p$ and $p'$ are two plaquettes, $\bm{r}_{pp'}$ is the displacement between $p$ and $p'$,  and $\gamma_{pp'}$ is any open string on the dual lattice
 connecting $p$ and $p'$.
-In \figref{fig:vison_3way} (a), we have plotted $|C_M|$ for an $L=32$ lattice.
-Note, that while $C_M$ depends on the choice of the background dimerization which fixes the gauge, $|C_M|$ is independent of the background dimerization.
-We find that$C_M$ only displays short range correlations, and no obvious symmetry breaking.
+In \figref{fig:vison_3way} (a), we have plotted $|C_M|$ for a $L=32$ lattice.
+Note that while $C_M$ depends on the choice of the background dimerization which fixes the gauge, $|C_M|$ is independent of the background dimerization.
+We find only short range magnetic string correlations correlations that display no obvious symmetry breaking.
 
@@
 \begin{equation}
-S_M\left( \bm{k} \right) \equiv \frac{1}{ L^2} \sum_{p,p'} e^{-i \bm{k} \cdot \bm{r}_{pp'}} C_M\left( \bm{r}_{pp'}\right)
+S_M\left( \bm{k} \right) \equiv \frac{1}{ L^4} \sum_{p,p'} e^{-i \bm{k} \cdot \bm{r}_{pp'}} C_M\left( \bm{r}_{pp'}\right)
 \end{equation}
 and plot the magnitude $|S_M|$ in \figref{fig:vison_3way} (b).
-We have chosen a columnar background dimerization comprising horizontal background dimers stacked in columns along the $y$-axis, as shown in \figref{mag_loops_on_orntd_lat.pdf}; this chose breaks the translational symmetry and thus requires doubling the unit cell the $x$-direction.
-While $|C_M|$ displays no obvious symmetry breaking, there are peaks in $|S_M|$ at $(0,0)$ \& $(0,\pi$) \note{(Owen: What about $(\pi,\pi)$??)}.
+We have chosen a columnar background dimerization comprising horizontal background dimers stacked in columns along the $y$-axis, as shown in \figref{fig:orientedSL}; this choice breaks the translational symmetry of the lattice and thus requires doubling the unit cell the $x$-direction.
+While $|C_M|$ displays no obvious symmetry breaking, there are peaks in $|S_M|$ at $(0,0)$ \& $(0,\pi$).
 We have plotted the finite-size scaling of these peaks in \figref{fig:bragg_scaling} which demonstrates that these peaks vanish in the thermodynamic limit.
-While the vanishing of the $(0,\pi)$ peak demonstrates the restoration of rotational and translational symmetries in the thermodynamic limit, the vanishing of the $(0,0)$ peak demonstrates the lack of magnetic vortex condensation, which is a mechanism for destroying topological order and breaking lattice symmetries~\cite{Jalabert1991,Ralko2007,Huh2011}.
-\figref{fig:vison_cor} shows the decay of $|C_M|$ along one of the axes of the dual lattice; we find this decays exponentially with distance, with a correlation length $\chi\approx 2.90$.
+We have additionally studied $S_M$ using different background dimerization and find that the location of the finite-size peaks depend on the gauge choice; however in cases we find that these peaks vanish in the thermodynamic limit.
+The vanishing of the $(0,\pi)$ peak demonstrates the restoration of rotational and translational symmetries in the thermodynamic limit, and the additional vanishing of the $(0,0)$ peak demonstrates the lack of magnetic vortex condensation, which is a mechanism for destroying topological order and breaking lattice symmetries~\cite{Jalabert1991,Ralko2007,Huh2011}.
+\figref{fig:vison_cor} shows the decay of $|C_M|$ along one of the axes of the dual lattice which we find decays exponentially with distance, with a correlation length $\chi\approx 3$.
 These exponentially decaying magnetic string correlations are therefore consistent with a symmetric dimer liquid with no magnetic vortex condensation.
@@
         {
-            (a) Color scale of the magnetic string correlation function 
-            on an $L=32$ lattice. The origin corresponds to the orange circle and it has been removed from
-            the color scale.
-            (b) The magnitude of the $Z_3$ magnetic string correlation function
-            $|C_M(\bm{r}_{\bm{0}p})|$, where the correlations is with respect to the orange plaquette.
-            (c) The magnitude of the $Z_3$ magnetic string structure factor $|S_M|$ shown along a
-            path in $k$ space for an $L=64$ lattice. Statistical errors are smaller than the symbols.
+            (a) Color scale of the $Z_3$ magnetic string correlation function $|C_M(\bm{r}_{\bm{0}p})|$,
+            on a $L=32$ lattice where $\bm{0}$ corresponds to plaquette represented by the orange circle.
+            (b) The magnitude of the $Z_3$ magnetic string structure factor $S_M$ for a $L=64$ lattice, using a columnar background dimerization as shown in \figref{fig:orientedSL}.             
+            (c) $|S_M|$ shown along a path in $k$ space. Statistical errors are smaller than the symbols.
         }
@@
     \includegraphics[width=1.0\columnwidth]{spatial_cors_z3_vis.pdf}
-    \caption{ The magnitude of the $Z_3$ magnetic string correlation $|C_M|$ along along one axis of the dual lattice of an $L=64$ lattice.
-The line corresponds to an exponential fit with correlations length \note{$\chi\approx 2.90$}.}
+    \caption{ The magnitude of the $Z_3$ magnetic string correlation $|C_M|$ along along one axis of the dual lattice of a $L=64$ lattice.
+The line corresponds to an exponential fit with correlations length $\chi\approx 3$.}
     \label{fig:vison_cor}
@@
 which appear to provide ergodic dynamics in the monomer-dimer-pentamer configuration space.
-Notice that monomers remain on the same sub-lattice, which is consistent with their assignment of a $Z_3$ electric charge of $\pm1$, where the positive and negative monomers live on different sub-lattices.
+Notice that monomers remain on the same sub-lattice, which is consistent with their assignment of a $Z_3$ electric charge of $\pm1$ (see \tabref{tab:defects}) and the positive and negative monomers live on different sub-lattices.
 We then can test for the confinement of monomers by studying the monomer-monomer density correlation function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$, which is plotted in \figref{fig:monomer_correlations}.
@@
 \figref{fig:monomer_correlations} demonstrates that $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ decays to $L^{-4}$ for each system size, indicating a deconfinement of monomers.
+This is in contrast with the QDM where monomer correlations decay as a power-law.
+Thus we find that $Z_3$ electric charges are deconfined in the QDPM.
+
 %%%%%%%%%%%%%%%%%%%%%%%
@@
         \caption{ The monomer-monomer correlations function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ along a coordinate axis in the QDPM RK ground state doped with a single pair of monomers on lattices up to $L=64$.
-The horizontal lines correspond to $L^{-4}$ for the system size corresponding to the color.
-\note{Owen: Make the subscripts in the y-axis label bold math.
-Extend the horizontal lines all the way across the plot.
-Remove the legend bounding box and use one symbol for each legend entry.
-Remove the black boundaries of the symbols.}}
+The horizontal lines correspond to $L^{-4}$ for the system size corresponding to the color.}
         \label{fig:monomer_correlations}
@@
 Using numerical calculations, we have demonstrated that the RK state of the QDPM is a dimer liquid, without spontaneously broken symmetry.
-The extensive topological degeneracy of the square lattice QDM has been reduced to a finite 9-fold degeneracy in the QDPM on a torus.
+Our numerical calculations explicitly show how the extensive topological degeneracy of the square lattice QDM has been reduced to a finite 9-fold degeneracy in the QDPM on a torus.
 We find that the dimer correlations decay exponentially with distance in contrast to the power-law decay of dimer correlations in the QDM.
@@
 While the Monte Carlo techniques used in this manuscript are limited to the RK point, the phase diagram near the RK point can be explored in future work using quantum Monte Carlo methods, as the QDPM has no sign problem.
-Away from RK, the condensation of $Z_3$ magnetic vortices could drive a continuous phase transition out of the topologically order phase, analogous to vison condensation in $Z_2$ spin liquids~\cite{Jalabert1991,Ralko2007,Huh2011,Hao2014,Slagle2014}; if such a continuous transition exists in the QDPM it may provide access to a new universality of class of quantum transitions~\cite{XU2012}.
+Away from the RK point, the condensation of $Z_3$ magnetic vortices could drive a continuous phase transition out of the topologically order phase, analogous to vison condensation in $Z_2$ spin liquids~\cite{Jalabert1991,Ralko2007,Huh2011,Hao2014,Slagle2014}; if such a continuous transition exists in the QDPM it may provide access to a new universality of class of quantum transitions~\cite{XU2012}.
 

### 2017-02-23 qdpm_paper.tex
Worked on the appendices

@@
 \usepackage{epstopdf}
+\usepackage{placeins}
 %\usepackage{scalerel}
@@
 \newcommand{\tabref}[1]{Tab. \ref{#1}}
+\newcommand{\appref}[1]{Appendix \ref{#1}}
 \newcommand{\note}[1]{\textcolor{red}{#1}}
@@
 It is known that coupling a $U(1)$ gauge field to a dynamics charge $q$ matter field can result in an $Z_q$ gauge theory~\cite{Fradkin1979}; as in the IGT's we have added dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result.
-We note that pentamers are charge $\pm3$ objects in the QDM (see \tabref{tab:defects}); thus below we investigate whether introducing pentamers into the QDM leads to an effective $Z_3$ gauge theory.
+We note that pentamers are charge $\pm3$ objects in the QDM (see \tabref{tab:defects}); thus below we investigate whether introducing pentamers into the QDM leads to an effective $Z_3$ gauge theory (see \appref{sec:Z3GT} for a review of $Z_3$ gauge theory).
 
@@
 We have plotted the finite size scaling of the intensity of the broad maximum of $S_d$ in  \figref{fig:bragg_scaling}, which we find to vanish in the thermodynamic limit; these maxima are therefore consistent with finite size effects due to short distance correlations.
+In \appref{sec:dimer_order_parameters} we additionally have plotted order parameters that specifically test for rotational and translational symmetry breaking; in all cases we find no symmetry breaking in the thermodynamic limit.
 Thus we see no evidence of symmetry breaking in the thermodynamic limit.
@@
 
-To provide dynamics, we define a unitary operator electric flux ladder operator $Q^\dagger_{vv'}$ that increments the electric flux:
+To provide dynamics, we define a unitary operator electric flux ladder operator $Q^\dagger_{vv'}$ that cyclically increments the electric flux:
 \begin{align}
@@
     \caption{ ({\it left}) An example of a charge free $Z_3$ electric string configuration.
-The electric string operator $S_\gamma^e$ represented by the thick gray line, oriented from the red to blue vertex.
+The electric string operator $S_\gamma^e$ represented by the thick gray line, oriented from the white to black vertex.
 ({\it right}) An example of a $Z_3$ electric string configuration with a $+1$ ($-1$) electric charge at the red (blue) vertex; this string configuration results form the action of $S_\gamma^e$ on the left panel.
@@
 Consider the magnetic string operator $S_m(\tilde{\Gamma})$ defined by an oriented \emph{closed} loop $\tilde{\Gamma}$ on the dual lattice.
-This operator corresponds to the creation of a vortex-antivortex pair, winding of the vortex around $\Gamma$, and annihilation of the vortex pair.
-A state with definite electric charge inside $\Gamma$ will be an eigenstate of $S_m(\tilde{\Gamma})$, with eigenvalue $e^{ i 2 \pi/3 q}$, where $q=0,\pm1$ is the net $Z_3$ electric charge (modulo 3) inside $\tilde{\Gamma}$.
-For $\Gamma$ winding around an isolated electric charge, we see that electric charges and magnetic vortices are anyons with relative braiding statics with a statistical phase of $e^{\pm i 2\pi/3}$.
+This operator corresponds to the creation of a vortex-antivortex pair, winding of the vortex around $\tilde{\Gamma}$, and annihilation of the vortex pair.
+A state with definite electric charge inside $\tilde{\Gamma}$ will be an eigenstate of $S_m(\tilde{\Gamma})$, with eigenvalue $e^{ i 2 \pi/3 q}$, where $q=0,\pm1$ is the net $Z_3$ electric charge (modulo 3) inside $\tilde{\Gamma}$.
+Thus for $\tilde{\Gamma}$ winding around an isolated electric charge, we see that electric charges and magnetic vortices are anyons with relative braiding statics with a statistical phase of $e^{\pm i 2\pi/3}$.
 
@@
 For example, consider the charge free sector on a torus.
-We can consider two topologically non-trivial closed loops $\tilde{\Gamma}_{X/Y}$ which have single winding around the $x/y$ directions of the torus.
-Since $S_m(\Gamma_{X/Y})$ commutes with $H_{Z_3}$, we can label the energy eigenstates by the eigenvalues of $S_m(\Gamma_{X/Y})$: $\{1,e^{\pm i 2\pi/3}\}$.
+We can consider two topologically non-trivial closed loops $\tilde{\Gamma}_{x}$ \& $\tilde{\Gamma}_{Y}$ which have a single winding around the $x$ or $y$ directions of the torus.
+Since $S_m(\tilde{\Gamma}_{X})$ commutes with $H_{Z_3}$, we can label the energy eigenstates by the eigenvalues of $S_m(\tilde{\Gamma}_{X})$, and similarly for $\tilde{\Gamma}_Y$: $\{1,e^{ i 2\pi/3},e^{- i 2\pi/3}\}$.
 Thus $H_{Z_3}$ has a 9-fold ground state degeneracy on the torus, and the ground states subspace can be labeled by the $Z_3$ electric flux winding about each axis of the torus.
 
-\section{Additional numerical results on the QDPM RK ground state}
+\section{Dimer order parameters QDPM RK ground state}
+\label{sec:dimer_order_parameters}
 %
@@
 
-To test for the possibility of translational and rotational symmetry breaking corresponding to the features in $S_d$ at the Brillouin zone edges, we define several order parameters which would capture such potential symmetry breaking.
-For rotational symmetry breaking we define
+To explicitly test for the possibility of translational and rotational symmetry breaking corresponding to the features in $S_d$ at the Brillouin zone edges, we define several order parameters which would capture such potential symmetry breaking.
+For rotational symmetry breaking we define~\cite{Syljuasen2005}
 \begin{equation}
@@
 where $N_v$ ($N_h$) is the total number of vertical (horizontal) dimers; note that $\exval{M_{\rm{rot}}^2 } \neq 0$ implies there is rotational symmetry breaking.
-to To capture translational symmetry breaking by one lattice site in a direction perpendicular to the majority of the dimers we define $\Mperp$
+To capture translational symmetry breaking by one lattice site in a direction perpendicular to the majority of the dimers we define~\cite{Syljuasen2005}
 \begin{align}
@@
 where the sums over $\ell_h$ ($\ell_v$) are taken over all horizontal (vertical) links.
-In \figref{fig:order_params} we have plotted the finite-size scaling of these order parameters; we find in all cases that while finite size systems display symmetry breaking due to finite-size effects, these order parameters all vanish in the thermodynamic limit, as demonstrated by the extrapolation in \figref{fig:order_params}.
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[]
+In \figref{fig:order_params} we have plotted the finite-size scaling of these order parameters; we find in all cases that while finite size systems display symmetry breaking due to finite-size effects, these order parameters all vanish in the thermodynamic limit, as demonstrated by the extrapolation shown in \figref{fig:order_params}.
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t!]
     \centering
     \includegraphics[width=1.0\linewidth]{order_params_plot.pdf}
-    \caption{The symmetry breaking order parameters.}
+    \caption{Symmetry breaking order parameters defined in the text computed for the RK point of the QDPM.
+In all cases we find they vanish in the thermodynamic limit, demonstrating the lack of symmetry breaking.}
     \label{fig:order_params}
@@
 
+\FloatBarrier
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-23 qdpm_paper.tex
Worked on the abstract/intro

@@
 \begin{abstract}
-We introduce quantum dimer-pentamer model (QDPM) on the square lattice.
+We introduce the quantum dimer-pentamer model (QDPM) on the square lattice.
 This model is a generalization of the square lattice quantum dimer model (QDM) as its configuration space comprises fully-packed hard-core dimer coverings as well as dimer configurations containing pentamers, where four dimers touch a vertex.
@@
 One class of such quantum phases of matter are topologically ordered quantum liquids; their non-trivial topological order can not be identified by a local order parameter as these phases of matter don't break conventional symmetries~\cite{Wen1990,Nayak2008}.
-Both because of of the exotic nature of topological phases and their potential use for quantum information processing~\cite{Freedman2001,Kitaev2003}, there is great interest in the development of theoretical models which display these phases and potentially provide candidate experimental systems in which to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Fowler2012a}.
+Both because of of the exotic nature of topological phases and their potential use for quantum information processing~\cite{Freedman2001,Kitaev2003}, there is great interest in the development of theoretical models which display these phases and potentially could provide candidate experimental systems in which to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Fowler2012a}.
 
@@
 
-While on non-bipartite lattices, the QDM has a topologically ordered ground state~\cite{Moessner2001a,Fendley2002}, on the square lattice there is only a symmetric liquid ground state at an isolated critical quantum point~\cite{Leung1996,Syljuasen2006}.
+While on non-bipartite two-dimensionsal lattices, the QDM has a topologically ordered ground state~\cite{Moessner2001a,Fendley2002}, on the square lattice there is only a symmetric liquid ground state at an isolated critical quantum point~\cite{Leung1996,Syljuasen2006}.
 If the hard-core constraint of the QDM is relaxed such that only the parity of the number of dimer touching each vertex is fixed, the simplest non-trivial dynamics leads to a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
@@
 We will limit our discussion to $t_\nu >0$.
-$ t{T}_\nu$ is constructed to generate resonances between two distinct allowed dimerazations of $\nu$, $c_\nu$ and its compliment $\bar{c}_\nu$, and is written as:
+${T}_\nu$ is constructed to generate resonances between two distinct allowed dimerazations of $\nu$, $c_\nu$ and its compliment $\bar{c}_\nu$, and is written as:
 \begin{equation}
@@
 \end{equation}
-in the simplest case, $ t{T_\nu}$ involves the minimum non-trivial dimer dynamics that preserve the constraint.
+in the simplest case, $ {T_\nu}$ involves the minimum non-trivial dimer dynamics that preserve the constraint.
 Similarly, the potential energy term provides an energy cost for states with these local configurations:

### 2017-02-26 qdpm_paper.tex
fixed S_d axis (real and positive) and removed note from tex file.
Minor changes
minor fixes to tex and peak_scalling figure

@@
 By doping the QDPM RK state with a pair of monomers, we demonstrate that $Z_3$ electric charges are deconfined.
-Additionally, we introduce a $Z_3$ magnetic string operator which shows no signatures of magnetic vortex condensation also decay exponentially.
+Additionally, we introduce a $Z_3$ magnetic string operator which shows no signatures of magnetic vortex condensation and with correlations that decay exponentially.
 These numerical results suggest that the ground state of the QDPM is a dimer liquid with $Z_3$ topological order.
@@
 One class of such quantum phases of matter are topologically ordered quantum liquids; their non-trivial topological order can not be identified by a local order parameter as these phases of matter don't break conventional symmetries~\cite{Wen1990,Nayak2008}.
-Both because of of the exotic nature of topological phases and their potential use for quantum information processing~\cite{Freedman2001,Kitaev2003}, there is great interest in the development of theoretical models which display these phases and potentially could provide candidate experimental systems in which to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Fowler2012a}.
+Both because of of the exotic nature of topological phases and their potential use for quantum information processing~\cite{Freedman2001,Kitaev2003}, there is great interest in the development of theoretical models which display these phases and potentially could provide candidate experimental systems to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Fowler2012a}.
 
@@
 While on non-bipartite two-dimensionsal lattices, the QDM has a topologically ordered ground state~\cite{Moessner2001a,Fendley2002}, on the square lattice there is only a symmetric liquid ground state at an isolated critical quantum point~\cite{Leung1996,Syljuasen2006}.
-If the hard-core constraint of the QDM is relaxed such that only the parity of the number of dimer touching each vertex is fixed, the simplest non-trivial dynamics leads to a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
+If the hard-core constraint of the square lattice QDM is relaxed such that only the parity of the number of dimer touching each vertex is fixed, the simplest non-trivial dynamics leads to a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
 The existence of topologically ordered ground states in these models is intimately related to the local constraint which imposes a local gauge symmetry in the Hilbert space; the topological order that arises is directly related to a discrete gauge theory with the appropriate local gauge constraint~\cite{Moessner2001}.
@@
 Given that these models with dimer degrees of freedom and local constraints posses the simplest non-trivial local Hilbert space at each link, they provide a potentially simpler route to engineering exotic phases.
-The local constraints can be enforced by a local potential energy penalty and the minimal dynamics are often arise at the lowest order non-trivial order in perturbation theory from a related spin model.
+The local constraints can be enforced by a local potential energy penalty and the minimal dynamics often arise at the lowest non-trivial order in perturbation theory from a related spin model.
 We will refer to such models with dimer degrees of freedom on links and local constraints as \emph{generalized quantum dimer modes} (GQDMs).
@@
 
-Additionally we present a numerical study of the ground state of the QDPM at an exactly soluble point.
+Additionally, we present a numerical study of the ground state of the QDPM at an exactly soluble point.
 Using Monte Carlo calculations, we explicitly demonstrate the absence of symmetry breaking order and the exponential decay of correlation functions.
@@
 In \secref{sec:Background} we provide relevant background for the QDM and related models.
-In \secref{sec:QDPM} we present the details of the QPDM.
+In \secref{sec:QDPM} we present the details of the QDPM.
 \secref{sec:numerics} provides the results of a Monte Carlo study of the ground state of the QDPM at its exactly soluble point.
@@
 \end{equation}
- In general the $[T_\nu, T_{\nu'}] \neq 0 $ and $[T_\nu,V_{\nu'}]\neq0$ when $\nu$ and $\nu'$ share links, and thus the ground state of $H_{\rm{GQDM}}$ is not explicitly known.
+ In general, $[T_\nu, T_{\nu'}] \neq 0 $ and $[T_\nu,V_{\nu'}]\neq0$ when $\nu$ and $\nu'$ share links, and thus the ground state of $H_{\rm{GQDM}}$ is not explicitly known.
 
@@
 \end{equation}
-where all $h_\nu$ are projectors with eigenvalues $\{0,1\}$, the exact ground state is known to be the zero energy state of \Eqref{eq:HRK} that is simultaneously annihilated by all ${h}_\nu$.
+where all $h_\nu$ are projectors with eigenvalues $\{0,1\}$, the exact ground state is known to be
+the zero energy state of \Eqref{eq:HRK} that is simultaneously annihilated by all ${\bar{h}}_\nu$.
 Such a zero energy state, known as the RK state, may be formed from an equal superposition of all dimerizations that are connected by $\{T_\nu\}$:
@@
 
-Because of the local constraints, all states $\ket{\psi}$ in the Hilbert space of a GQDM are invariant under local gauge transformations $G_v \ket{\psi} = \ket{\psi}$ a the vertices, $G_v$ of the general form~\cite{Moessner2001}
+Because of the local constraints, all states $\ket{\psi}$ in the Hilbert space of a GQDM are invariant under local gauge transformations $G_v \ket{\psi} = \ket{\psi}$ the vertices, $G_v$ of the general form~\cite{Moessner2001}
 \begin{equation}
@@
 \end{equation}
-where $n_\ell$ is the number operator for a static background dimer configuration which is chosen to fix the gauge.
+where $\tilde{n}_\ell$ is the number operator for a static background dimer configuration which is chosen to fix the gauge.
 With this gauge fixing, the total charge enclosed in a closed loop $\Gamma$ is $Q_\Gamma = \Phi_\Gamma- \tilde{\Phi}_\Gamma$.
@@
 
-The two unique fixed-number constraints on the square lattice are lead to QDM in the odd sector ($n_v = 1$) and the quantum full-packed loop model (QFPLM) in the even sector ($n_v = 2$).
-For configurations that satisfy these a number constraints, $Q_v$ strictly vanishes, and thus all states in the Hilbert space are invariant under $G_v$ for $0 \leq \alpha_v \leq 2 \pi$ in \Eqref{eq:Gv}; this represents a local $U(1)$ gauge symmetry~\cite{Moessner2001}.
+The two unique fixed-number constraints on the square lattice lead to QDM in the odd sector ($n_v = 1$) and the quantum full-packed loop model (QFPLM) in the even sector ($n_v = 2$).
+For configurations that satisfy these number constraints, $Q_v$ strictly vanishes, and thus all states in the Hilbert space are invariant under $G_v$ for $0 \leq \alpha_v \leq 2 \pi$ in \Eqref{eq:Gv}; this represents a local $U(1)$ gauge symmetry~\cite{Moessner2001}.
 
@@
 \begin{equation}
-\left[ \Phi_\Gamma, \HQDM \right] = 0
-\end{equation}
-and therefore we can define two conserved topological winding numbers $\Phi_{X}$ \& $\Phi_{Y}$ which are the dimer flux through topologically non-trivial loops that wind around each axis of the lattice when the system has periodic boundary conditions (see \figref{fig:orientedSL}).
-On an lattice of dimensions $L_x\times L_y$, the eigenvalues of $\Phi_X$ and $\Phi_Y$ are integers in the range
+\left[ \Phi_\Gamma, \HQDM \right] = 0,
+\end{equation}
+We can define two conserved topological winding numbers $\Phi_{X}$ \& $\Phi_{Y}$ which are the dimer flux through topologically non-trivial loops that wind around each axis of the lattice when the system has periodic boundary conditions (see \figref{fig:orientedSL}).
+On a lattice of dimensions $L_x\times L_y$, the eigenvalues of $\Phi_X$ and $\Phi_Y$ are integers in the range
 \begin{equation}
@@
 
-Defects in these models that violate the local dimer number constraint and thus carry non-zero U(1) electric charge.
+Defects in these models violate the local dimer number constraint and thus carry non-zero U(1) electric charge.
 \tabref{tab:defects} lists all the possible defects and their associated U(1) charges in QDM and QFPLM.
@@
 \end{align}
-where we implicitly include symmetry related resonances. We will limit or discussion to $v_\bplqt=0$ such that the corresponding Hamiltonian is
+where we implicitly include symmetry related resonances. We will limit our discussion to $v_\bplqt=0$ such that the corresponding Hamiltonian is
 \begin{equation}
@@
 \end{equation}
-In this case the equal superposition RK wavefunction is the exact ground state occurs in the absence of a potential energy term, as we can define a projection operator on each plaquette
+In this case the equal superposition RK wavefunction is the exact ground state and occurs in the absence of a potential energy term, as we can define a projection operator on each plaquette
 \begin{equation}
@@
 We may understand the emergence of the $Z_2$ topologically ordered phase of IGTs from the QDM and QFPLM from the following picture.
-The additional vertex configurations that are allowed in the IGTs relative to the models with a dimer number constraint  have charge U(1) charge $Q_v = \pm 2$ (see \tabref{tab:defects}).
-It is known that coupling a $U(1)$ gauge field to a dynamics charge $q$ matter field can result in an $Z_q$ gauge theory~\cite{Fradkin1979}; as in the IGT's we have added dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result.
+The additional vertex configurations that are allowed in the IGTs relative to the models with a dimer number constraint  have U(1) charge $Q_v = \pm 2$ (see \tabref{tab:defects}).
+It is known that coupling a $U(1)$ gauge field to a dynamic charge $q$ matter field can result in a $Z_q$ gauge theory~\cite{Fradkin1979}; as in the IGT's we have added dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result.
 We note that pentamers are charge $\pm3$ objects in the QDM (see \tabref{tab:defects}); thus below we investigate whether introducing pentamers into the QDM leads to an effective $Z_3$ gauge theory (see \appref{sec:Z3GT} for a review of $Z_3$ gauge theory).
@@
 We will now present a numerical study of the dimer density correlations in the RK ground state of the QDPM.
-In \figref{fig:dimer_3way} (a) we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on a $L=32$ lattice; here the origin $\bm{0}$ represents the orange link, and $\bm{r}$ varies over all other links of the lattice.
-These bare dimer correlations display only short range correlations no obvious symmetry breaking.
+In \figref{fig:dimer_3way} (a) we plot the bare dimer-dimer density correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on a $L=32$ lattice; here the origin $\bm{0}$ is represented by the orange link, and $\bm{r}$ varies over all other links of the lattice.
+These bare dimer correlations display only short range correlations with no obvious symmetry breaking.
 In \figref{fig:dimer_3way} (b) we show the equal-time dimer-dimer structure factor,
@@
 where we restrict the sum to horizontal links, for a $L=64$ lattice. 
-\figref{fig:dimer_3way} (c) shows the magnitude \note{(Owen: Is $S_d$ real \& positive?)} of $S_d(\bm{k})$ for a particular path through the Brillouin zone.
+\figref{fig:dimer_3way} (c) shows $S_d(\bm{k})$ for a particular path through the Brillouin zone.
 The dimer structure factor displays broad maxima at $\bm{k} = (0, \pm \pi)$ and $\bm{k} = (\pm \pi, \pm \pi)$.
@@
 In \appref{sec:dimer_order_parameters} we additionally have plotted order parameters that specifically test for rotational and translational symmetry breaking; in all cases we find no symmetry breaking in the thermodynamic limit.
-Thus we see no evidence of symmetry breaking in the thermodynamic limit.
 
@@
 In \figref{fig:spatial_dmr_cor}, $C_d$ between parallel links is plotted as a function of separation, for $\bm{r}$ perpendicular to the orientation of the dimers for a $L=64$ lattice.
-We find that $C_d$ decays exponentially with distance having a correlations length  $\chi\approx 1$.
+We find that $C_d$ decays exponentially with distance having a correlation length  $\chi\approx 1$.
 Additionally, $C_d$ displays a sub-lattice oscillation that is consistent with the finite-size maximum in $S_d$ at $(0,\pi)$.
@@
 We have plotted the finite-size scaling of these peaks in \figref{fig:bragg_scaling} which demonstrates that these peaks vanish in the thermodynamic limit.
-We have additionally studied $S_M$ using different background dimerization and find that the location of the finite-size peaks depend on the gauge choice; however in cases we find that these peaks vanish in the thermodynamic limit.
+We have additionally studied $S_M$ using different background dimerization and find that the location of the finite-size peaks depend on the gauge choice; however in all cases we find that these peaks vanish in the thermodynamic limit.
 The vanishing of the $(0,\pi)$ peak demonstrates the restoration of rotational and translational symmetries in the thermodynamic limit, and the additional vanishing of the $(0,0)$ peak demonstrates the lack of magnetic vortex condensation, which is a mechanism for destroying topological order and breaking lattice symmetries~\cite{Jalabert1991,Ralko2007,Huh2011}.
@@
 We find that the dimer correlations decay exponentially with distance in contrast to the power-law decay of dimer correlations in the QDM.
-Additionally we also have demonstrated that monomer defects are deconfined in the QDPM, in contrast with the critical confinement of monomers in the QDM.
+Additionally, we also have demonstrated that monomer defects are deconfined in the QDPM, in contrast with the critical confinement of monomers in the QDM.
 Finally, we find that the $Z_3$ magnetic string correlations decay exponentially and display no evidence of $Z_3$ vortex condensation; this is consistent with $Z_3$ vortices being gapped quasiparticles excitations above the QDPM ground state.
 These results suggest a the low energy physics of the QDPM is described by a $Z_3$ gauge theory with a $Z_3$ topological ordered ground state.
-Thus we have demonstrated that systems with Ising degrees of freedom and local constraints can lead to $Z_N$ topological order for $N>2$, providing the a new stable phase of matter beyond the commonly seen $Z_2$ topological spin liqud.
+Thus we have demonstrated that systems with Ising degrees of freedom and local constraints can lead to $Z_N$ topological order for $N>2$, providing the a new stable phase of matter beyond the commonly seen $Z_2$ topological spin liquid.
 

### 2017-03-10 qdpm_paper.tex
Incorporating Ty's comment

@@
 Given an Ising spin $\sigma_\ell$ on each link $\ell$ we define the number of dimers on the link $n_\ell \equiv 1/2+\sigma_\ell^z$, where $\sigma_\ell^i$ are the associated Pauli matrices.
-The Hilbert space consists of configurations of dimers on the square lattice that satisfy a local constraint at each vertex.
+The Hilbert space is spanned by an orthonormal basis of dimerizations of the square lattice that satisfy a local constraint at each vertex.
 We define a $U(1)$ charge $Q_v$ at each vertex $v$ of the lattice in terms of the number of dimers touching $v$, $n_v\equiv \sum_{\ell \in v}n_\ell$:
@@
 where all $h_\nu$ are projectors with eigenvalues $\{0,1\}$, the exact ground state is known to be
-the zero energy state of \Eqref{eq:HRK} that is simultaneously annihilated by all ${\bar{h}}_\nu$.
+the zero energy state of \Eqref{eq:HRK} that is simultaneously annihilated by all ${h}_\nu$.
 Such a zero energy state, known as the RK state, may be formed from an equal superposition of all dimerizations that are connected by $\{T_\nu\}$:
@@
 \begin{equation}
-\left[ \Phi_\Gamma, \HQDM \right] = 0,
+\left[ \Phi_\Gamma, \HQDM \right] = 0.
 \end{equation}
@@
 
-At the Rokhsar-Kivelson point $t=v$, we may write $\HQDM$ in the form of \Eqref{eq:HRK} by defining projection operators  $ {h}_\nu \equiv  {P}^\dagger_{\nu} {P}_{\nu}$, with
-\begin{equation}
- {P}^\dagger_\nu \equiv \biggl( \eket{ c_\nu} - \eket{\bar{c}_\nu} \biggr).
+At the Rokhsar-Kivelson point $t=v$, we may write $\HQDM$ in the form of \Eqref{eq:HRK} by defining projection operators  $ {h}_\nu $:
+\begin{equation}
+ {h}_\nu \equiv \biggl( \eket{ c_\nu} - \eket{\bar{c}_\nu} \biggr)\biggl( \ebra{ c_\nu} - \ebra{\bar{c}_\nu} \biggr).
 \end{equation} 
@@
 
-The increased dynamics of $\HIGT$ vs.
+The additional dynamics of $\HIGT$ vs.
 $\HQDM$ no longer conserve the dimer flux $\Phi_\Gamma$ through a closed curve; only $\Phi_\Gamma \mod 2$ is preserved by $\HIGT$.
@@
 We have demonstrated that ground state at the RK point of the QDPM has an exact $Z_3$ gauge symmetry and a corresponding $9$-fold topological degeneracy on the torus.
-We emphasize that despite the exact $Z_3$ local gauge symmetry of the QDPM, there is not an exact mapping to a $Z_3$ gauge theory on the square lattice, as the QDPM has Ising degrees of freedom on the links, rather than the 3 dimensional local Hilbert space of a $Z_3$ gauge theory (see \ref{sec:Z3GT} for details of $Z_3$ gauge theory).
+We emphasize that despite the exact $Z_3$ local gauge symmetry of the QDPM, there is not an exact mapping to a $Z_3$ gauge theory on the square lattice, as the QDPM has Ising degrees of freedom on the links, rather than the 3 dimensional local Hilbert space of a $Z_3$ gauge theory (see \appref{sec:Z3GT} for details of $Z_3$ gauge theory).
 It remains to address whether this RK state is in the deconfined $Z_3$ topologically ordered phase of a $Z_3$ gauge theory, or a confined symmetry broken or critical state, which we discuss below.
@@
 
-Computations were performed on the Vermont Advanced Computing Core supported by NASA (NNX-08AO96G).
+We thank T. J. Volkoff for discussions and a careful reading of the manuscript. Computations were performed on the Vermont Advanced Computing Core supported by NASA (NNX-08AO96G).
 

### 2017-03-10 qdpm_paper.tex
Updated section II based on Ty's comments

@@
 The additional vertex configurations that are allowed in the IGTs relative to the models with a dimer number constraint  have U(1) charge $Q_v = \pm 2$ (see \tabref{tab:defects}).
-It is known that coupling a $U(1)$ gauge field to a dynamic charge $q$ matter field can result in a $Z_q$ gauge theory~\cite{Fradkin1979}; as in the IGT's we have added dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result.
+It is known that when a $U(1)$ gauge field is coupled to a dynamic charge $q$ matter field, this results in a $Z_q$ gauge theory when the matter field condenses~\cite{Fradkin1979}; as in the IGT's we have added dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result.
 We note that pentamers are charge $\pm3$ objects in the QDM (see \tabref{tab:defects}); thus below we investigate whether introducing pentamers into the QDM leads to an effective $Z_3$ gauge theory (see \appref{sec:Z3GT} for a review of $Z_3$ gauge theory).

### 2017-03-15 qdpm_paper.tex
some minor changes. mostly fixed some typos.

@@
 \end{equation}
-where ${T}_\nu$ are off-diagonal kinetic energy operators, ${V}_\nu$ are diagonal potential energy operators, $t_\nu$ and $v_\nu$ parametrize the strength of these terms, and each $\nu$ and represents a set of  neighboring links.
+where ${T}_\nu$ are off-diagonal kinetic energy operators, ${V}_\nu$ are diagonal potential energy operators, $t_\nu$ and $v_\nu$ parametrize the strength of these terms, and each $\nu$ represents a set of  neighboring links.
 We will limit our discussion to $t_\nu >0$.
@@
 
-Because of the local constraints, all states $\ket{\psi}$ in the Hilbert space of a GQDM are invariant under local gauge transformations $G_v \ket{\psi} = \ket{\psi}$ the vertices, $G_v$ of the general form~\cite{Moessner2001}
+Because of the local constraints, all states $\ket{\psi}$ in the Hilbert space of a GQDM are invariant under local gauge transformations $G_v \ket{\psi} = \ket{\psi}$, $G_v$ of the general form~\cite{Moessner2001}
 \begin{equation}
@@
 \end{equation}
-where $\mathrm{sgn}(\ell,\gamma)$ is positive (negative) if $\ell$ is oriented to the right with respect to the orientation of $\gamma$. Additionally, we define background flux $\tilde{\Phi}_\ell$
+where $\mathrm{sgn}(\ell,\gamma)$ is positive (negative) if $\ell$ is oriented to the right (left) with respect to the orientation of $\gamma$.
+Additionally, we define background flux $\tilde{\Phi}_\ell$
 \begin{equation}
@@
 
-The two unique fixed-number constraints on the square lattice lead to QDM in the odd sector ($n_v = 1$) and the quantum full-packed loop model (QFPLM) in the even sector ($n_v = 2$).
+The two unique fixed-number constraints on the square lattice lead to the QDM in the odd sector ($n_v = 1$) and the quantum full-packed loop model (QFPLM) in the even sector ($n_v = 2$).
 For configurations that satisfy these number constraints, $Q_v$ strictly vanishes, and thus all states in the Hilbert space are invariant under $G_v$ for $0 \leq \alpha_v \leq 2 \pi$ in \Eqref{eq:Gv}; this represents a local $U(1)$ gauge symmetry~\cite{Moessner2001}.
@@
 
-We have demonstrated that ground state at the RK point of the QDPM has an exact $Z_3$ gauge symmetry and a corresponding $9$-fold topological degeneracy on the torus.
+We have demonstrated that the ground state at the RK point of the QDPM has an exact $Z_3$ gauge symmetry and a corresponding $9$-fold topological degeneracy on the torus.
 We emphasize that despite the exact $Z_3$ local gauge symmetry of the QDPM, there is not an exact mapping to a $Z_3$ gauge theory on the square lattice, as the QDPM has Ising degrees of freedom on the links, rather than the 3 dimensional local Hilbert space of a $Z_3$ gauge theory (see \appref{sec:Z3GT} for details of $Z_3$ gauge theory).
@@
     \includegraphics[width=1.0\linewidth]{u1_wind_qdpm.pdf}
-    \caption{The histogram of the $U(1)$ topological winding numbers $\Phi_X$ and $\Phi_Y$ as measured in for the ground state of the RK point of the QDPM for three different lattice sizes.
+    \caption{The histogram of the $U(1)$ topological winding numbers $\Phi_X$ and $\Phi_Y$ as measured in the ground state of the RK point of the QDPM for three different lattice sizes.
 The colors correspond to calculations initialized to different topological sectors $(\Phi_X,\Phi_Y)$: blue $(0,0)$, red $(1,1)$, and purple $(-1,-1)$.
@@
 Note that while $C_M$ depends on the choice of the background dimerization which fixes the gauge, $|C_M|$ is independent of the background dimerization.
-We find only short range magnetic string correlations correlations that display no obvious symmetry breaking.
+We find only short range magnetic string correlations that display no obvious symmetry breaking.
 
@@
     \includegraphics[width=1.0\columnwidth]{spatial_cors_z3_vis.pdf}
-    \caption{ The magnitude of the $Z_3$ magnetic string correlation $|C_M|$ along along one axis of the dual lattice of a $L=64$ lattice.
+    \caption{ The magnitude of the $Z_3$ magnetic string correlation $|C_M|$ along one axis of the dual lattice of a $L=64$ lattice.
 The line corresponds to an exponential fit with correlations length $\chi\approx 3$.}
@@
         \includegraphics[width=1.0\columnwidth]{monomer_cor_log.pdf}
-        \caption{ The monomer-monomer correlations function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ along a coordinate axis in the QDPM RK ground state doped with a single pair of monomers on lattices up to $L=64$.
+        \caption{ The monomer-monomer correlation function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ along a coordinate axis in the QDPM RK ground state doped with a single pair of monomers on lattices up to $L=64$.
 The horizontal lines correspond to $L^{-4}$ for the system size corresponding to the color.}
@@
 We have introduced the quantum dimer-pentamer model on the square lattice and studied the ground state at the RK point.
-Using numerical calculations, we have demonstrated that the RK state of the QDPM is a dimer liquid, without spontaneously broken symmetry.
+Using numerical calculations, we have demonstrated that the RK state of the QDPM is a dimer liquid without spontaneously broken symmetry.
 Our numerical calculations explicitly show how the extensive topological degeneracy of the square lattice QDM has been reduced to a finite 9-fold degeneracy in the QDPM on a torus.
@@
 While the Monte Carlo techniques used in this manuscript are limited to the RK point, the phase diagram near the RK point can be explored in future work using quantum Monte Carlo methods, as the QDPM has no sign problem.
-Away from the RK point, the condensation of $Z_3$ magnetic vortices could drive a continuous phase transition out of the topologically order phase, analogous to vison condensation in $Z_2$ spin liquids~\cite{Jalabert1991,Ralko2007,Huh2011,Hao2014,Slagle2014}; if such a continuous transition exists in the QDPM it may provide access to a new universality of class of quantum transitions~\cite{XU2012}.
+Away from the RK point, the condensation of $Z_3$ magnetic vortices could drive a continuous phase transition out of the topologically order phase, analogous to vison condensation in $Z_2$ spin liquids~\cite{Jalabert1991,Ralko2007,Huh2011,Hao2014,Slagle2014}; if such a continuous transition exists in the QDPM it may provide access to a new universality class of quantum transitions~\cite{XU2012}.
 
@@
 \label{sec:Z3GT}
-Here we will review a string-net implementation of $Z_3$ gauge theory on the square lattice~\cite{Horn1979}.
-We define a three -dimensional Hilbert space on each link, corresponding to the presence or absence of an oriented string segment that carries $Z_3$ electric flux which are eigenstates of the Hermitian $Z_3$ electric flux operator $E_{vv'}$
+Here we will review a string-net implementation of $Z_3$ gauge theory on the square
+lattice~\cite{Horn1979}.
+We define a three -dimensional Hilbert space on each link, corresponding to the presence or absence of an oriented string segment that carries $Z_3$ electric flux, which are eigenstates of the Hermitian $Z_3$ electric flux operator $E_{vv'}$
 \begin{align}
@@
     \caption{ ({\it left}) An example of a charge free $Z_3$ electric string configuration.
-The electric string operator $S_\gamma^e$ represented by the thick gray line, oriented from the white to black vertex.
+The electric string operator $S_\gamma^e$ is represented by the thick gray line, oriented from the white to black vertex.
 ({\it right}) An example of a $Z_3$ electric string configuration with a $+1$ ($-1$) electric charge at the red (blue) vertex; this string configuration results form the action of $S_\gamma^e$ on the left panel.
@@
 
-Note that  $S_e$ and $S_m$ do not commute if their corresponding strings intersect--this underlies the non-trivial statics of electric charges and magnetic vortices.
+Note that  $S_e$ and $S_m$ do not commute if their corresponding strings intersect--this underlies the non-trivial statistics of electric charges and magnetic vortices.
 Consider the magnetic string operator $S_m(\tilde{\Gamma})$ defined by an oriented \emph{closed} loop $\tilde{\Gamma}$ on the dual lattice.
@@
 A state with definite electric charge inside $\tilde{\Gamma}$ will be an eigenstate of $S_m(\tilde{\Gamma})$, with eigenvalue $e^{ i 2 \pi/3 q}$, where $q=0,\pm1$ is the net $Z_3$ electric charge (modulo 3) inside $\tilde{\Gamma}$.
-Thus for $\tilde{\Gamma}$ winding around an isolated electric charge, we see that electric charges and magnetic vortices are anyons with relative braiding statics with a statistical phase of $e^{\pm i 2\pi/3}$.
+Thus for $\tilde{\Gamma}$ winding around an isolated electric charge, we see that electric charges and magnetic vortices are anyons with relative braiding statistics with a statistical phase of $e^{\pm i 2\pi/3}$.
 

### 2017-04-05 qdpm_paper.tex
Worked on manuscript

@@
 We introduce the quantum dimer-pentamer model (QDPM) on the square lattice.
-This model is a generalization of the square lattice quantum dimer model (QDM) as its configuration space comprises fully-packed hard-core dimer coverings as well as dimer configurations containing pentamers, where four dimers touch a vertex.
-Thus in the QDPM, the fully-packed, hard-core constraint of the QDM is relaxed such that the local dimer number at each vertex is fixed modulo 3; correspondingly, the local $U(1)$ gauge symmetry of the QDM Hilbert space is reduced to a local $Z_3$ gauge symmetry in the QDPM.
+This model is a generalization of the square lattice quantum dimer model as its configuration space comprises fully-packed hard-core dimer coverings as well as dimer configurations containing pentamers, where four dimers touch a vertex.
+Thus in the QDPM, the fully-packed, hard-core constraint of the quantum dimer model is relaxed such that the local dimer number at each vertex is fixed modulo 3, resulting in an exact local $Z_3$ gauge symmetry.
 We construct a local Hamiltonian for which the Rokhsar-Kivelson (RK) equal superposition state is the exact ground state and has a 9-fold topological degeneracy on the torus.
@@
 By doping the QDPM RK state with a pair of monomers, we demonstrate that $Z_3$ electric charges are deconfined.
-Additionally, we introduce a $Z_3$ magnetic string operator which shows no signatures of magnetic vortex condensation and with correlations that decay exponentially.
+Additionally, we introduce a $Z_3$ magnetic string operator that we find decays exponentially and shows no signatures of magnetic vortex condensation and with correlations.
 These numerical results suggest that the ground state of the QDPM is a dimer liquid with $Z_3$ topological order.
@@
 Strongly interacting quantum many-body systems are known to support a variety of exotic quantum phases of matter with no classical analogue.
-One class of such quantum phases of matter are topologically ordered quantum liquids; their non-trivial topological order can not be identified by a local order parameter as these phases of matter don't break conventional symmetries~\cite{Wen1990,Nayak2008}.
-Both because of of the exotic nature of topological phases and their potential use for quantum information processing~\cite{Freedman2001,Kitaev2003}, there is great interest in the development of theoretical models which display these phases and potentially could provide candidate experimental systems to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Fowler2012a}.
+Among these are topologically ordered quantum liquids; their non-trivial topological order can not be identified by a local order parameter as these phases of matter don't break conventional symmetries~\cite{Wen1990,Nayak2008}.
+Both because of of the exotic nature of topological phases and their potential use for quantum information processing~\cite{Freedman2001,Kitaev2003}, there is great interest in the development of theoretical models which display these phases and could provide candidate experimental systems to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Fowler2012a}.
 
 A variety of exactly soluble lattice models are known to support ground states with topological order that ranges from the simplest variety, $Z_2$ topological order~\cite{Kitaev2003,Wen2003}, to those with non-Abelian anyonic excitations~\cite{Levin2005a,Kitaev2006a}; such models generally involve complex many-body interactions, and thus it is desirable to find simpler models supporting topological order that are closer to what is accessible experimentally.
-Among the simplest class of models displaying topological quantum liquid phases are those with local geometric constraints; the constraints inhibit the formation of symmetry breaking local order and given sufficient dynamics, may lead to a symmetric liquid ground state.
-One of the most basic of these is the quantum dimer model (QDM) describing dimer degrees of freedom living on the links of a lattice~\cite{Rokhsar1988,Moessner2008}; the hard-core, fully-packed QDM has a local constraint that requires exactly one dimer touching each vertex.
+Among the simplest classes of models displaying topological quantum liquid phases are those with local geometric constraints; the constraints inhibit the formation of symmetry breaking local order and given sufficient dynamics, may lead to a symmetric liquid ground state.
+The quantum dimer model (QDM) describing dimer degrees of freedom living on the links of a lattice is one of the most basic locally constrained models~\cite{Rokhsar1988,Moessner2008}; the hard-core, fully-packed QDM has a local constraint that requires that exactly one dimer touches each vertex.
 
@@
 Given that these models with dimer degrees of freedom and local constraints posses the simplest non-trivial local Hilbert space at each link, they provide a potentially simpler route to engineering exotic phases.
-The local constraints can be enforced by a local potential energy penalty and the minimal dynamics often arise at the lowest non-trivial order in perturbation theory from a related spin model.
+The local constraints can be enforced by a local potential energy penalty and the minimal dynamics often arise at the lowest non-trivial order in perturbation theory from a related spin model\cite{Albuquerque2008}.
 We will refer to such models with dimer degrees of freedom on links and local constraints as \emph{generalized quantum dimer modes} (GQDMs).
 Previous work has demonstrated that GQDMs on the square lattice support gapped $Z_2$ topologically ordered phases as well as gapless quantum critical points.
-On non-bipartite lattices, GQDMs support $Z_2$ topological order~\cite{Moessner2001a,Misguich2002} as well as doubled-semion phases~\cite{Qi2014,Buerschaper2014a}.
+On non-bipartite lattices, GQDMs support $Z_2$ topological order~\cite{Moessner2001a,Misguich2002} as well as doubled-semion phases~\cite{Qi2015,Buerschaper2014}.
 A full characterization of all exotic phases that can exist within this framework is thus desirable.
@@
 With this gauge fixing, the total charge enclosed in a closed loop $\Gamma$ is $Q_\Gamma = \Phi_\Gamma- \tilde{\Phi}_\Gamma$.
-An alternative physical picture is that there are static charges of charge $+c_0$ ($-c_0$) sitting at the vertices of the $A$($B$) sub-lattice, which are the source of the non-vanishing $\Phi_\Gamma$ flux through a closed loop.
+An alternative physical picture is that there are static charges of charge $+c_P$ ($-c_P$) sitting at the vertices of the $A$($B$) sub-lattice, which are the source of the non-vanishing $\Phi_\Gamma$ flux through a closed loop.
 
@@
 \begin{equation}
-W_{X,Y} \left( \alpha \right) \equiv S_{\Gamma_{X,Y}} \left( \alpha \right)
-\end{equation}
-where $\Gamma_{X,Y}$ are topologically non-trivial closed loops that wind once about the $X$ and $Y$ directions of the torus, respectively.
-Since $W_{X,Y} (\alpha)$ commute with the Hamiltonian, we may use their eigenvalues to label the ground states.
+W_{X} \left( \alpha \right) \equiv S_{\Gamma_{X}} \left( \alpha \right)
+\end{equation}
+where $\Gamma_{X}$ is a topologically non-trivial closed loop that winds once about the $x$ axis; we define $W_Y$ similarly.
+Since $W_{X} (\alpha)$ and $W_{Y} (\alpha)$ commute with the Hamiltonian, we may use their eigenvalues to label the ground states.
 
@@
 
-The Hamiltonian for these models gives dynamics to parallel dimers on the plaquettes $\bplqt$ of the lattice:
+The Hamiltonian for these models gives dynamics to parallel dimers on the plaquettes of the lattice:
 \begin{equation}
@@
 \end{equation} 
-Since the plaquette flip term in \Eqref{eq:HQDM} is ergodic in each of topological sector $(\Phi_x,\Phi_y)$ on the square lattice~\cite{????}, each topological sector corresponds to a unique RK ground state where $\Omega$ is labeled by $(\Phi_x,\Phi_y)$.
+Since the plaquette flip term in \Eqref{eq:HQDM} is believed to be ergodic in each of topological sector $(\Phi_x,\Phi_y)$ on the square lattice, each topological sector corresponds to a unique RK ground state where $\Omega$ is labeled by $(\Phi_x,\Phi_y)$.
 Thus the  RK points of the QDM and QFPLM have an \emph{extensively} degenerate ground states.
@@
 When a defect lives on sublattice A, it has the opposite charge that the same defect on sublattice B has.
-Note that in the QDM, the maximum charge is $\pm 3$, and there are six distinct possible non-trivial electric charges of defects.
+Note that in the QDM, the maximum charge is $\pm 3$.
 
@@
 Thus, such fixed number constrained models on bipartite lattices are expected to have an isolated unstable gapless critical quantum liquid points with logarithmically confined defect and an extensive topological degeneracy.
-These features of fixed number constrained models are consistent with the effective U(1) gauge theory description of the RK point~\cite{Fradkin2004,Fradkin1990,Moessner2001}; in 2+1D pure U(1) gauge theories are confining and thus the lack of an extended deconfined topologically ordered phase near the RK point~\cite{PolyakovBook}.
+These features of fixed number constrained models are consistent with the effective U(1) gauge theory description of the RK point~\cite{Fradkin2004,Fradkin1990,Moessner2001}; in 2+1D pure U(1) gauge theories are confining and thus the lack of an extended deconfined topologically ordered phase near the RK point~\cite{Polyakov1987}.
 
@@
 \begin{equation}
-S_\gamma^{Z_2} \equiv S_\gamma \left( \pi \right), \quad W_{X,Y}^{Z_2} \equiv W_{X,Y} \left( \pi \right).
-\end{equation}
-Thus the $W_{X,Y}^{Z_2}$ have two eigenvalues $\pm 1$, and the topological sectors on the torus can be labeled as~$\Omega= (\pm 1,\pm1)$; consequently the extensive degeneracy of the fixed number constrained models has been reduced to a finite ground state degeneracy in the fixed parity models.
+S_\gamma^{Z_2} \equiv S_\gamma \left( \pi \right), \quad W_{X}^{Z_2} \equiv W_{X} \left( \pi \right), \notag
+\end{equation}
+and $W_Y^{Z_2}$ is defined similarly.
+Thus the $W_{X}^{Z_2}$ and $W_{Y}^{Z_2}$ have two eigenvalues $\pm 1$, and the topological sectors on the torus can be labeled as~$\Omega= (\pm 1,\pm1)$; consequently the extensive degeneracy of the fixed number constrained models has been reduced to a finite ground state degeneracy in the fixed parity models.
 
@@
     \caption{Finite-size scaling of the maxima in the dimer ($S_d$) and magnetic string ($S_M$) structure factors.
+The lines are fits to $L^{-2}$ scaling.
 All maxima vanish in the thermodynamic limit, indicating that the RK state of the QDPM is a symmetric dimer liquid.
@@
 Future work could directly probe the existence of a finite gap above the RK point by studying the imaginary time dynamics of correlations functions using Monte Carlo methods similar to those used in here~\cite{Henley1997,Henley2004a}; such an approach could be used to explore if the low energy excitations are best described by $Z_3$ magnetic vorticies~\cite{Ivanov2004,Ralko2007,Misguich2008d}.
-Additionally, one could conclusively demonstrate the existence of $Z_3$ topological order by computing the topological entanglement entropy in the QDPM ground state Monte Carlo methods~\cite{Levin2005a,Kitaev2006b,Hastings2010}.
+Additionally, one could conclusively demonstrate the existence of $Z_3$ topological order by computing the topological entanglement entropy in the QDPM ground state using Monte Carlo methods~\cite{Levin2005a,Kitaev2006b,Hastings2010}.
 
@@
 \begin{equation}
-    S_m \left( \tilde{\gamma}_{vv'} \right) \equiv \prod_{l \perp \tilde{\gamma}_{pp'}} P_{v_l v_l'}^\dagger
+    S_m \left( \tilde{\gamma}_{pp'} \right) \equiv \prod_{l \perp \tilde{\gamma}_{pp'}} P_{v_l v_l'}^\dagger
 \end{equation}
@@
 ({\it right}) An example of a $Z_3$ electric string configuration with a $+1$ ($-1$) electric charge at the red (blue) vertex; this string configuration results form the action of $S_\gamma^e$ on the left panel.
+The magnetic loop operator $S_m (\tilde{\Gamma})$ can detect the presence of the electric charges.
 }
@@
 For example, consider the charge free sector on a torus.
-We can consider two topologically non-trivial closed loops $\tilde{\Gamma}_{x}$ \& $\tilde{\Gamma}_{Y}$ which have a single winding around the $x$ or $y$ directions of the torus.
+We can consider two topologically non-trivial closed loops $\tilde{\Gamma}_{X}$ \& $\tilde{\Gamma}_{Y}$ which have a single winding around the $x$ or $y$ directions of the torus.
 Since $S_m(\tilde{\Gamma}_{X})$ commutes with $H_{Z_3}$, we can label the energy eigenstates by the eigenvalues of $S_m(\tilde{\Gamma}_{X})$, and similarly for $\tilde{\Gamma}_Y$: $\{1,e^{ i 2\pi/3},e^{- i 2\pi/3}\}$.
@@
     \caption{Symmetry breaking order parameters defined in the text computed for the RK point of the QDPM.
+The lines are fits to $L^{-1}$ scaling.
 In all cases we find they vanish in the thermodynamic limit, demonstrating the lack of symmetry breaking.}

### 2017-07-07 qdpm_paper.tex
Removed unecessary equation tags
Removed comments for arXiv
Added citation to trimer paper and submission letter
Worked on referee response

@@
 
-%\newcommand*\bplqt{\includegraphics[height=1.6ex] {Symbols/blank_plqt}}
-%\newcommand*\bhrzmv{\includegraphics[height=1.6ex]{Symbols/blank_hrzmv}}
-%\newcommand*\bdiag{\includegraphics[height=1.6ex] {Symbols/blank_diag}}
-%\newcommand*\bstr{\includegraphics[height=1.6ex] {Symbols/blank_str}}
-
 \newcommand{\figref}[1]{Fig. \ref{#1}}
@@
 
-%\newcommand*{\hprs}{%
-%  \text{% change size in subscripts or superscripts
-%    \includegraphics[
-%      height=1.2ex,% adjust to suit
-%      valign=M,% center vertically
-%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-%    ]{Symbols/hrzprestar} }
-%}
-%\newcommand*{\hspr}{%
-%  \text{% change size in subscripts or superscripts
-%    \includegraphics[
-%      height=1.2ex,% adjust to suit
-%      valign=M,% center vertically
-%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-%    ]{Symbols/hrzstarpair} }
-%}
-
 \newcommand*{\bplqt}{%
@@
 }
-%\newcommand*{\bhrzmv}{%
-%  \text{% change size in subscripts or superscripts
-%    \includegraphics[
-%      height=1.2ex,% adjust to suit
-%      valign=M,% center vertically
-%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-%    ]{Symbols/blank_hrzmv} }
-%}
-%\newcommand*{\bdiag}{%
-%  \text{% change size in subscripts or superscripts
-%    \includegraphics[
-%      height=1.2ex,% adjust to suit
-%      valign=M,% center vertically
-%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-%    ]{Symbols/blank_diag} }
-%}
-%\newcommand*{\bstr}{%
-%  \text{% change size in subscripts or superscripts
-%    \includegraphics[
-%      height=1.2ex,% adjust to suit
-%      valign=M,% center vertically
-%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-%    ]{Symbols/blank_str} }
-%}
 \newcommand*{\vvemptylink}{%
@@
 }
-%\newcommand*{\threedownplqt}{%
-%  \text{% change size in subscripts or superscripts
-%    \includegraphics[
-%      height=1.5ex,% adjust to suit
-%      valign=M,% center vertically
-%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-%    ]{Symbols/threedownplqt.pdf} }
-%}
-%\newcommand*{\threeupplqt}{%
-%  \text{% change size in subscripts or superscripts
-%    \includegraphics[
-%      height=1.5ex,% adjust to suit
-%      valign=M,% center vertically
-%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-%    ]{Symbols/threeupplqt.pdf} }
-%}
-%\newcommand*{\threerightplqt}{%
-%  \text{% change size in subscripts or superscripts
-%    \includegraphics[
-%      height=1.5ex,% adjust to suit
-%      valign=M,% center vertically
-%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-%    ]{Symbols/threerightplqt.pdf} }
-%}
 \newcommand*{\threeleftplqt}{%
@@
 }
-%\newcommand*{\onedownplqt}{%
-%  \text{% change size in subscripts or superscripts
-%    \includegraphics[
-%      height=1.5ex,% adjust to suit
-%      valign=M,% center vertically
-%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-%    ]{Symbols/onedownplqt.pdf} }
-%}
-%\newcommand*{\oneupplqt}{%
-%  \text{% change size in subscripts or superscripts
-%    \includegraphics[
-%      height=1.5ex,% adjust to suit
-%      valign=M,% center vertically
-%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-%    ]{Symbols/oneupplqt.pdf} }
-%}
-%\newcommand*{\onerightplqt}{%
-%  \text{% change size in subscripts or superscripts
-%    \includegraphics[
-%      height=1.5ex,% adjust to suit
-%      valign=M,% center vertically
-%      raise=\fontdimen22\textfont2,% but raise it to the formula axis
-%    ]{Symbols/onerightplqt.pdf} }
-%}
 \newcommand*{\oneleftplqt}{%
@@
 Among these are topologically ordered quantum liquids; their non-trivial topological order can not be identified by a local order parameter as these phases of matter don't break conventional symmetries~\cite{Wen1990,Nayak2008}.
-Both because of of the exotic nature of topological phases and their potential use for quantum information processing~\cite{Freedman2001,Kitaev2003}, there is great interest in the development of theoretical models which display these phases and could provide candidate experimental systems to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Fowler2012a}.
+Both because of the exotic nature of topological phases and their potential use for quantum information processing~\cite{Freedman2001,Kitaev2003}, there is great interest in the development of theoretical models which display these phases and could provide candidate experimental systems to constructively engineer topological order~\cite{Duan2003,Jaksch2005,Lewenstein2007,Jiang2008d,Weimer2010a,Herdman2010c,Fowler2012a}.
 
@@
 While on non-bipartite two-dimensionsal lattices, the QDM has a topologically ordered ground state~\cite{Moessner2001a,Fendley2002}, on the square lattice there is only a symmetric liquid ground state at an isolated critical quantum point~\cite{Leung1996,Syljuasen2006}.
-If the hard-core constraint of the square lattice QDM is relaxed such that only the parity of the number of dimer touching each vertex is fixed, the simplest non-trivial dynamics leads to a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
+If the hard-core constraint of the square lattice QDM is relaxed such that only the parity of the number of dimers touching each vertex is fixed, the simplest non-trivial dynamics leads to a $Z_2$ topologically ordered ground state~\cite{Kitaev2003,Wen2003}.
 The existence of topologically ordered ground states in these models is intimately related to the local constraint which imposes a local gauge symmetry in the Hilbert space; the topological order that arises is directly related to a discrete gauge theory with the appropriate local gauge constraint~\cite{Moessner2001}.
@@
 On non-bipartite lattices, GQDMs support $Z_2$ topological order~\cite{Moessner2001a,Misguich2002} as well as doubled-semion phases~\cite{Qi2015,Buerschaper2014}.
+Additionally, recent work on a trimer resonating valence bond state suggests that it may be described by a $Z_3$ gauge theory~\cite{Lee2017}.
 A full characterization of all exotic phases that can exist within this framework is thus desirable.
@@
 We consider systems with Ising-like dimer degrees of freedom on each link, such that each link is either unoccupied or occupied by a single dimer.
-Given an Ising spin $\sigma_\ell$ on each link $\ell$ we define the number of dimers on the link $n_\ell \equiv 1/2+\sigma_\ell^z$, where $\sigma_\ell^i$ are the associated Pauli matrices.
+Given an Ising spin $\sigma_\ell$ on each link $\ell$ we define the number of dimers on the link $n_\ell \equiv 1/2(1+\sigma_\ell^z)$, where $\sigma_\ell^i$ are the associated Pauli matrices.
 The Hilbert space is spanned by an orthonormal basis of dimerizations of the square lattice that satisfy a local constraint at each vertex.
@@
 \begin{equation}
-Q_v \equiv \pm \left( n_v - c_P \right)
-\end{equation}
-where $c_P = 2$, ($c_P=1$) for models in the even (odd) sector of the constraint, and the $+$($-$) sign corresponds to vertices on the $A$($B$) sublattice.
-A local dimer number constraint requires $Q_v$ to vanish for all vertices; a dimer parity constraint requires $(Q_v\mod 2)$ to vanish.
+Q_v \equiv \pm \left( n_v - c_P \right) \notag
+\end{equation}
+where $c_p$ is a constant, and we define the even (odd) sector of the constraint to have $c_P = 2$ ($c_P=1$); the $+$($-$) sign corresponds to vertices on the $A$($B$) sublattice (see \tabref{tab:defects}).
+A local dimer number constraint requires $Q_v$ to vanish for all vertices; a dimer parity constraint requires $(Q_v\mod 2)$ to vanish (see \figref{fig:example_local_constraints}).
 
@@
 \begin{equation}
- {T}_{\nu} = \eket{c_\nu}\ebra{\bar{c}_\nu} + h.c.;
+ {T}_{\nu} = \eket{c_\nu}\ebra{\bar{c}_\nu} + h.c.;  \notag
 \end{equation}
@@
 \begin{equation}
- {V}_{\nu} = \eket{c_\nu}\ebra{c_\nu} +  \eket{\bar{c}_\nu}\ebra{\bar{c}_\nu}.
+ {V}_{\nu} = \eket{c_\nu}\ebra{c_\nu} +  \eket{\bar{c}_\nu}\ebra{\bar{c}_\nu}.  \notag
 \end{equation}
@@
 \begin{equation}
-\HGQDM \biggl( \bigl\{\left(c_\nu,\bar{c}_\nu\right)\},\{\left(t_\nu,v_\nu\right)\bigr\}\biggr).
+\HGQDM \biggl( \bigl\{\left(c_\nu,\bar{c}_\nu\right)\},\{\left(t_\nu,v_\nu\right)\bigr\}\biggr).  \notag
 \end{equation}
@@
 \begin{equation}
-\eket{\Phi_{\RK}^{\Omega}} = \sum_{C \in \Omega} \eket{C}
+\eket{\Phi_{\RK}^{\Omega}} = \sum_{C \in \Omega} \eket{C}  \notag
 \end{equation} 
@@
 \begin{equation}
-W_{X} \left( \alpha \right) \equiv S_{\Gamma_{X}} \left( \alpha \right)
+W_{X} \left( \alpha \right) \equiv S_{\Gamma_{X}} \left( \alpha \right)  \notag
 \end{equation}
@@
 where we have chosen $t_\bplqt = t$, $v_\bplqt =v, \forall \bplqt$.
-%\begin{align}
-%    \label{}
-%   \HQDM = &-t\sum_{\bplqt} \biggl( \eket{\vrtplqt} \ebra{\hrzplqt} +h.c. \biggr) \notag\\
-%    					&+v\sum_{\bplqt} \biggl( \eket{\vrtplqt} \ebra{\vrtplqt} +\eket{\hrzplqt} \ebra{\hrzplqt} \biggr). \label{eq:HQDM}
-%\end{align}
 In this case of a fixed number constraint, the Hamiltonian conserves $Q_v$ and therefore the dimer flux through any closed loop such that:
 \begin{equation}
-\left[ \Phi_\Gamma, \HQDM \right] = 0.
+\left[ \Phi_\Gamma, \HQDM \right] = 0.  \notag
 \end{equation}
@@
 \begin{equation}
--L_{x}/2 \leq  \Phi_{X} \leq L_{x}/2,
+-L_{x}/2 \leq  \Phi_{X} \leq L_{x}/2,  \notag
 \end{equation}
@@
 \begin{equation}
- {h}_\nu \equiv \biggl( \eket{ c_\nu} - \eket{\bar{c}_\nu} \biggr)\biggl( \ebra{ c_\nu} - \ebra{\bar{c}_\nu} \biggr).
+ {h}_\nu \equiv \biggl( \eket{ c_\nu} - \eket{\bar{c}_\nu} \biggr)\biggl( \ebra{ c_\nu} - \ebra{\bar{c}_\nu} \biggr).  \notag
 \end{equation} 
@@
 \begin{equation}
-\HIGT\left(t\right) \equiv \HGQDM \biggl( \mathcal{C}_{\rm{IGT}},\bigl\{ \left(t,0\right) \bigr\} \biggr).
+\HIGT\left(t\right) \equiv \HGQDM \biggl( \mathcal{C}_{\rm{IGT}},\bigl\{ \left(t,0\right) \bigr\} \biggr).  \notag
 \end{equation}
@@
 \begin{equation}
-h_\Box \equiv \frac{1}{2} \left( \mathbb{1} - \sum_i \eket{c_{\Box,i}}\ebra{\bar{c}_{\Box,i}} + h.c. \right)
+h_\Box \equiv \frac{1}{2} \left( \mathbb{1} - \sum_i \eket{c_{\Box,i}}\ebra{\bar{c}_{\Box,i}} + h.c. \right)  \notag
 \end{equation}
@@
 \begin{equation}
-Q_v^{Z_3} \equiv \left(Q_v~\rm{mod}~3\right)
+Q_v^{Z_3} \equiv \left(Q_v~\rm{mod}~3\right)  \notag
 \end{equation}
@@
 The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice; these local dynamics involving pentamers are illustrated in  \tabref{tab:pentamer_moves}.
-Note that pentamers give dynamics to ``staggered" regions with no flippable plaquettes; thus we expect the QDPM to have weaker correlations that the QDM, where the dynamics are more constrained.
+Note that pentamers give dynamics to ``staggered" regions with no flippable plaquettes; thus we expect the QDPM to have weaker correlations than the QDM, where the dynamics are more constrained.
 We may write $\HQDPM$ as the following:
 \begin{equation}
-\HQDPM \equiv \HQDM + H_{\rm{pen}}
+\HQDPM \equiv \HQDM + H_{\rm{pen}}  \notag
 \end{equation}
@@
 \begin{equation}
-\Omega = \left(W_X^{Z_3},W_Y^{Z_3} \right).
+\Omega = \left(W_X^{Z_3},W_Y^{Z_3} \right).  \notag
 \end{equation}
@@
 The histogram $P(\Phi)$ has a Gaussian shape with a width that increases with system size; this is expected as $\Phi = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
-We find no evidence of a lack of ergodicity within each of the 9 topological sectors.
+We find no evidence of a lack of ergodicity within each of the 9 topological sectors, although we cannot rule out the possibility of isolated ``frozen" configurations which are not accessed by the dynamics described in \tabref{tab:pentamer_moves}; in particular we note that the QDPM gives dynamics to ``staggered" dimer configurations that are frozen in the QDM~\cite{Moessner2008}.
 For the remainder of the paper we present results in the $(0,0)$ topological sector, but we see no qualitative dependence between topological sectors for any of the results presented here.
@@
 \begin{equation}
-S_d\left( \bm{k} \right) \equiv \frac{1}{ L^4} \sum_{i,j} e^{-i \bm{k} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_{\bm{r}_i} n_{\bm{r}_j} \right \rangle
+S_d\left( \bm{k} \right) \equiv \frac{1}{ L^4} \sum_{i,j} e^{-i \bm{k} \cdot \left(\bm{r}_i - \bm{r}_j\right)} \left \langle n_{\bm{r}_i} n_{\bm{r}_j} \right \rangle  \notag
 \end{equation}
@@
   \begin{equation}
-    C_{\mathrm{d}} \left(r\right) \equiv \langle n_{\bm{0}} n_{\bm{r}} \rangle - \langle n_{\bm{0}} \rangle   \langle n_{\bm{r}} \rangle   
+    C_{\mathrm{d}} \left(r\right) \equiv \langle n_{\bm{0}} n_{\bm{r}} \rangle - \langle n_{\bm{0}} \rangle   \langle n_{\bm{r}} \rangle   \notag
 \end{equation}
@@
 \begin{equation}
-C_M \left( \bm{r}_{pp'} \right) \equiv \left \langle \exp \left[ \frac{2 \pi}{3} i \left( \Phi_{\gamma_{pp'}} -\tilde{\Phi}_{\gamma_{pp'}} \right) \right] \right \rangle
+C_M \left( \bm{r}_{pp'} \right) \equiv \left \langle \exp \left[ \frac{2 \pi}{3} i \left( \Phi_{\gamma_{pp'}} -\tilde{\Phi}_{\gamma_{pp'}} \right) \right] \right \rangle  \notag
 \end{equation}
@@
 \begin{equation}
-S_M\left( \bm{k} \right) \equiv \frac{1}{ L^4} \sum_{p,p'} e^{-i \bm{k} \cdot \bm{r}_{pp'}} C_M\left( \bm{r}_{pp'}\right)
+S_M\left( \bm{k} \right) \equiv \frac{1}{ L^4} \sum_{p,p'} e^{-i \bm{k} \cdot \bm{r}_{pp'}} C_M\left( \bm{r}_{pp'}\right)  \notag
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-    \begin{figure}[t]
+    \begin{figure}
         \centering
@@
 \begin{equation}
-\monomermvA  \Longleftrightarrow \monomermvB
+\monomermvA  \Longleftrightarrow \monomermvB  \notag
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-%\begin{table}
-%    \begin{tabular}{| l | c | c |}
-%  	\hline
-%     & $c$ & $\bar{c}$ \\
-%	\hline
-%    $i$ & $\monomermvA$ &  $\monomermvB$  \\
-%    \hline
-%  \end{tabular}
-%  \caption{The pair of local dimer \& monomer configurations $c\leftrightarrow\bar{c}$ generate
-%  minimal local monomer dynamics. Monomers always remain on their origonal sublattice. }
-%  \label{tab:pentamerMoves}
-%\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 Finally, we find that the $Z_3$ magnetic string correlations decay exponentially and display no evidence of $Z_3$ vortex condensation; this is consistent with $Z_3$ vortices being gapped quasiparticles excitations above the QDPM ground state.
-These results suggest a the low energy physics of the QDPM is described by a $Z_3$ gauge theory with a $Z_3$ topological ordered ground state.
+These results suggest that the low energy physics of the QDPM is described by a $Z_3$ gauge theory with a $Z_3$ topological ordered ground state.
 Thus we have demonstrated that systems with Ising degrees of freedom and local constraints can lead to $Z_N$ topological order for $N>2$, providing the a new stable phase of matter beyond the commonly seen $Z_2$ topological spin liquid.
@@
 \begin{equation}
-G_v \equiv \prod_{v'} P^\dagger_{vv'}
+G_v \equiv \prod_{v'} P^\dagger_{vv'}  \notag
 \end{equation}
@@
 \begin{equation}
-P_{vv'}^\dagger \equiv e^{i 2\pi/3 E_{vv'}}.
+P_{vv'}^\dagger \equiv e^{i 2\pi/3 E_{vv'}}.  \notag
 \end{equation}
@@
 \begin{equation}
-G_v \eket{\psi} = \eket{\psi} \quad \forall v.
+G_v \eket{\psi} = \eket{\psi} \quad \forall v.  \notag
 \end{equation}
@@
 \begin{equation}
-G_v \ket{\psi} = e^{\pm 2\pi/3 i} \ket{\psi}
+G_v \ket{\psi} = e^{\pm 2\pi/3 i} \ket{\psi}  \notag
 \end{equation}
@@
 \begin{equation}
-H_{Z_3} = - J  \sum_p  \left( Q^\dagger_{v_1^pv_2^p} Q^\dagger_{v_2^pv_3^p} Q^\dagger_{v_3^pv_4^p} Q^\dagger_{v_4^pv_1^p} + h.c. \right)
+H_{Z_3} = - J  \sum_p  \left( Q^\dagger_{v_1^pv_2^p} Q^\dagger_{v_2^pv_3^p} Q^\dagger_{v_3^pv_4^p} Q^\dagger_{v_4^pv_1^p} + h.c. \right)  \notag
 \end{equation}
@@
 \begin{equation}
-    S_e \left( \gamma_{vv'} \right) \equiv \prod_{l \in \gamma_{vv'}} Q_{v_l v_l'}^\dagger
+    S_e \left( \gamma_{vv'} \right) \equiv \prod_{l \in \gamma_{vv'}} Q_{v_l v_l'}^\dagger  \notag
 \end{equation}
@@
 \begin{equation}
-    S_m \left( \tilde{\gamma}_{pp'} \right) \equiv \prod_{l \perp \tilde{\gamma}_{pp'}} P_{v_l v_l'}^\dagger
+    S_m \left( \tilde{\gamma}_{pp'} \right) \equiv \prod_{l \perp \tilde{\gamma}_{pp'}} P_{v_l v_l'}^\dagger  \notag
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=1.0\columnwidth]{spatial_cors_perp.pdf}
-%    \caption{Correlation function between perpendicular dimers on the same (blue) and different (red) 
-%    sub-lattice for a $L=64$ lattice.}
-%    \label{fig:spatial_dmr_cor}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %
-%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=1.0\columnwidth]{spatial_cors_end_to_end_parallel.pdf}
-%    \caption{Correlation function between parallel dimers (end-to-end) on the same (blue) and different (red) 
-%    sub-lattice for a $L=64$ lattice.}
-%    \label{fig:spatial_dmr_cor}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-07-07 Referee_Response.txt
Added referee response

Dear Editor,

We are resubmitting our manuscript "$Z_3$ topological order in the quantum dimer-pentamer model". We thank the referees for the constructive comments, corrections and suggestions, which we have responded to below. We also have included a list of changes to the manuscript. We hope that you agree that with these changes our manuscript is now suitable for publication in Physical Review B.

sincerely,
O. Meyers
C. M. Herdman

Responses to First Referee:

We thank the First Referee for his/her comments. Here we directly respond to the following particular comments (with the referee's comment in quotes):

"Definition of Q_v and c_P It is quite difficult to see what the 
authors mean by $Q_v$ and $c_P$ from the text. I guess the definition 
of $n_\ell$ in page 2 should read $n_\ell = (1+\sigma^z_\ell)/2$ if 
$\sigma^z_\ell$ takes value $\pm 1$."

Yes, we appreciate the referee catching this error.

"The definition of $c_P$ is 
cryptic because "the even (odd) sector of the constraint" seems not 
defined. I was only able to see the assignment of $Q_v$ to each 
configuration from TABLE I. It would be better to touch on TABLE I 
earlier."

We have clarified the definition of the even and odd sectors of the constraint and the choice of $c_P$ in the text.

"The authors conclude that the processes involved in the QDPM 
Hamiltonian are ergodic in each topological sector. This is in marked 
contrast to the QDM on either bipartite or non-bipartite lattice, in 
which we usually have staggered configurations that cannot be reached 
by applying local Hamiltonians repeatedly. Such staggered 
configurations also appear in a recently proposed quantum trimer model 
on a square lattice that exhibits $Z_3$ topological order. I just 
wonder why the authors can exclude such "frozen" configurations from 
the ground states of QDPM. For instance, the state in which all the 
bonds are occupied (all the vertices are of pentamer type) is an 
allowed configuration and does not cost any energy."

We did not intend to claim that we have proven the the QDPM is ergodic in each topological sector, but simply that our numerics are consistent with such ergodicity, as we see no evidence of a lack of ergodicity. We have clarified this in the text by explicitly acknowledging the possibility of "frozen" configurations. However, the particular configurations the referee mentions (all links occupied--i.e. pentamers on each vertex) does indeed have dynamics in the QDPM (refer to Table II, move "\nu_1"). Additionally, as mentioned in the manuscript, the "staggered" configuration which are frozen in the QDM do have dynamics in the QDPM (notice all moves in Table II involve staggered regions).

"The authors discuss that the monomer-monomer correlation decays 
algebraically as $<m_0 m_r> \sim L^{-4}$ with the data in Fig. 10. But 
it is not easy to see this power from the figure. I also wonder 
whether the coefficient of $L^{-4}$ is independent of $L$ or not."

To be clear: the horizontal lines in Fig. 10 are exactly $L^{-4}$ for each system size with a coefficient of unity. This figure demonstrates that the monomer-monomer correlations decay to the exact constant $N^{-2}$ (with $N=L^2$) as $r \rightarrow \infty$, which corresponds to completely uncorrelated monomers on a lattice with $N$ sites, and thus demonstrates monomer deconfinement.

Responses to Second Referee:

We thank the Second Referee for his/her comments. Here we directly respond to the following particular comments (with the referee's comment in quotes):

"I found several minor typos or grammar errors. I think the authors could revise them and polish the manuscript."

We have corrected several typos based on the referees comments--these corrections are listed below.

"I am a little bit worried about "ergodicity" of the model. For example, a staggered region can hop into a pair pentamer (Table II, v1 case). But, again this pair can not be split into or hop into another configuration including some "flippable" plaquettes in the same topological sector. Therefore, the dynamics still seems to happen only between several (maybe quite a lot in large system sizes, but still does not connect to others) configurations and thus not ergodic. If the authors have concrete answer or evidence, they may add some discussion in details in the manuscript."

Owen: Can we include a figure regarding this?

List of Changes:

Page 1: Sec. I 1st Paragraph: Both because of of the exotic ... -> Both because of the exotic ...

Page 2: Sec. II A. 1st Paragraph:

--$n_\ell \equiv 1/2+\sigma_\ell^z$ ==> $n_\ell \equiv 1/2(1+\sigma_\ell^z)$

--Definition of even/odd sectors clarified to read:"...where $c_p$ is a constant, and we define the even (odd) sector of the constraint to have $c_P = 2$ ($c_P=1$); the $+$($-$) sign..."

--References to Tab. I and Fig. 1 added

Page 5: Sec. II 2nd Paragraph: ... weaker correlations that the QDM, -> ... weaker correlations than the QDM,

Page 6: Sec. IV A

--Clarified the discussion of ergodicity as follows:

"We find no evidence of a lack of ergodicity within each of the 9 topological sectors, although we cannot rule out the possibility of isolated ``frozen" configurations which are not accessed by the dynamics described in \tabref{tab:pentamer_moves}; in particular we note that the QDPM gives dynamics to ``staggered" dimer configurations that are frozen in the QDM."

Page 9: Sec. V, 2nd Paragraph: These results suggest a the low energy physics ... -> These results suggest that the low energy physics ...

### 2017-07-26 Referee_Response.txt
Last name in ref responce.
Added Fig. 4, and Referee response

@@
 pentamers on each vertex) does indeed have dynamics in the QDPM (refer to Table II, move "\nu_1").
-Additionally, as mentioned in the manuscript, the "staggered" configuration which are frozen in the QDM do have dynamics in the QDPM (notice all moves in Table II involve staggered regions).
+Additionally, as mentioned in the manuscript, the "staggered" configuration which are frozen in the QDM do have dynamics in the QDPM (see Fig.
+4 in the new version of the manuscript).
 
@@
 
-Owen: Can we include a figure regarding this?
+We have added a new figure (Fig.
+4 in the new manuscript) that illustrates how pentamers can give dynamics to staggered regions, and convert regions with no flippable plaquettes to maximally flippable columnar configurations.
+While we cannot prove ergodicity, or rule out other "frozen" configurations, we hope this new figure helps illustrate the increased dynamics of the QDPM over the QDM.
 
@@
 
+Page 6. Right column: Figure 4 added.
+
 Page 6: Sec. IV A

### 2017-07-26 qdpm_paper.tex
Added Fig. 4, and Referee response

@@
 The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice; these local dynamics involving pentamers are illustrated in  \tabref{tab:pentamer_moves}.
-Note that pentamers give dynamics to ``staggered" regions with no flippable plaquettes; thus we expect the QDPM to have weaker correlations than the QDM, where the dynamics are more constrained.
+Note that pentamers give dynamics to ``staggered" regions with no flippable plaquettes (see \figref{fig:stag_to_flip} for an illustration of this); thus we expect the QDPM to have weaker correlations than the QDM, where the dynamics are more constrained.
 We may write $\HQDPM$ as the following:
@@
 It remains to address whether this RK state is in the deconfined $Z_3$ topologically ordered phase of a $Z_3$ gauge theory, or a confined symmetry broken or critical state, which we discuss below.
+
+ %%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.75\linewidth]{StagToFlip.pdf}
+    \caption{ An illustration of how the QDPM gives dynamics to dimer configurations that are frozen in the QDM; in the QDPM, ``staggered" configurations with no flippable plaquettes can be transformed into columnar regions with the maximum number of flippable plaquettes.
+The transitions from panels (a)-(d) involve the pentamer moves $\nu_1$ and $\nu_2$ from \tabref{tab:pentamer_moves}; the transitions from (d)-(g) involve flipping dimers around the highlighted plaquettes.
+}
+    \label{fig:stag_to_flip}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 In \figref{fig:order_params} we have plotted the finite-size scaling of these order parameters; we find in all cases that while finite size systems display symmetry breaking due to finite-size effects, these order parameters all vanish in the thermodynamic limit, as demonstrated by the extrapolation shown in \figref{fig:order_params}.
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t!]
+
+\vspace{1pt}
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
     \centering
@@
 
-\FloatBarrier
+%\FloatBarrier
 

### 2017-07-27 qdpm_paper.tex
Added new version of Fig. 4, moved figures around, added citation to PRB

--- 2017-07-07 qdpm_paper.tex
@@
 It is known that when a $U(1)$ gauge field is coupled to a dynamic charge $q$ matter field, this results in a $Z_q$ gauge theory when the matter field condenses~\cite{Fradkin1979}; as in the IGT's we have added dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result.
-We note that pentamers are charge $\pm3$ objects in the QDM (see \tabref{tab:defects}); thus below we investigate whether introducing pentamers into the QDM leads to an effective $Z_3$ gauge theory (see \appref{sec:Z3GT} for a review of $Z_3$ gauge theory).
+We note that pentamers are charge $\pm3$ objects in the QDM (see \tabref{tab:defects}); thus below we investigate whether introducing pentamers into the QDM leads to an effective $Z_3$ gauge theory, as suggested in Ref.
+\onlinecite{Herdman2013} (see \appref{sec:Z3GT} for a review of $Z_3$ gauge theory).
 
@@
 The Hamiltonian of the QDPM is defined by \Eqref{eq:HGQDM} including both plaquette flips as well as local dimer resonances that create and destroy pairs of pentamers, and allow single pentamers to translate on the same sub-lattice; these local dynamics involving pentamers are illustrated in  \tabref{tab:pentamer_moves}.
-Note that pentamers give dynamics to ``staggered" regions with no flippable plaquettes; thus we expect the QDPM to have weaker correlations than the QDM, where the dynamics are more constrained.
+Note that pentamers give dynamics to ``staggered" regions with no flippable plaquettes that are frozen in the QDM (see \figref{fig:stag_to_flip} for an illustration of this); thus we expect the QDPM to have weaker correlations than the QDM, where the dynamics are more constrained.
 We may write $\HQDPM$ as the following:
@@
 
+ %%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[]
+    \centering
+    \includegraphics[width=1\linewidth]{StagToFlip.pdf}
+    \caption{ An illustration of how the QDPM gives dynamics to dimer configurations that are frozen in the QDM.
+The transitions from panels (a)-(e) involve the pentamer moves $\nu_1$ and $\nu_2$ from \tabref{tab:pentamer_moves}; the transitions from (e)-(g) involve flipping dimers around the highlighted plaquettes.
+}
+    \label{fig:stag_to_flip}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 Because of the terms involving pentamers, $\HQDPM$ conserves $Q_v^{Z_3}$ rather than $Q_v$, and thus $\Phi_\Gamma$ does not commute with the Hamiltonian for closed loops $\Gamma$.
@@
 The histogram $P(\Phi)$ has a Gaussian shape with a width that increases with system size; this is expected as $\Phi = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
-We find no evidence of a lack of ergodicity within each of the 9 topological sectors, although we cannot rule out the possibility of isolated ``frozen" configurations which are not accessed by the dynamics described in \tabref{tab:pentamer_moves}; in particular we note that the QDPM gives dynamics to ``staggered" dimer configurations that are frozen in the QDM~\cite{Moessner2008}.
+We find no evidence of a lack of ergodicity within each of the 9 topological sectors, although we cannot rule out the possibility of isolated ``frozen" configurations which are not accessed by the dynamics described in \tabref{tab:pentamer_moves}; in particular we note that the QDPM gives dynamics to ``staggered" dimer configurations that are frozen in the QDM (see \figref{fig:stag_to_flip}).
 For the remainder of the paper we present results in the $(0,0)$ topological sector, but we see no qualitative dependence between topological sectors for any of the results presented here.
 Thus we find that the QDPM has a \emph{finite} $9$-fold degeneracy on the torus, where the topological sectors are labeled $(W_X^{Z_3},W_Y^{Z_3})$, in contrast with the extensive degeneracy of the QDM.
+
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 In \appref{sec:dimer_order_parameters} we additionally have plotted order parameters that specifically test for rotational and translational symmetry breaking; in all cases we find no symmetry breaking in the thermodynamic limit.
-
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure}[h!]
     \centering
@@
 Thus we find that the RK point of the QDPM is a symmetric dimer liquid with exponentially decaying dimer correlations, in contrast with the power-law decaying correlations of the QDM.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h]
     \centering
@@
 We find only short range magnetic string correlations that display no obvious symmetry breaking.
+%%%%%%%%%%%%%%%%%%%%%%%
+    \begin{figure}
+        \centering
+        \includegraphics[width=1.0\columnwidth]{vison_3way.pdf}
+        \caption
+        {
+            (a) Color scale of the $Z_3$ magnetic string correlation function $|C_M(\bm{r}_{\bm{0}p})|$,
+            on a $L=32$ lattice where $\bm{0}$ corresponds to plaquette represented by the orange circle.
+            (b) The magnitude of the $Z_3$ magnetic string structure factor $S_M$ for a $L=64$ lattice, using a columnar background dimerization as shown in \figref{fig:orientedSL}.             
+            (c) $|S_M|$ shown along a path in $k$ space. Statistical errors are smaller than the symbols.
+        }
+        \label{fig:vison_3way}
+    \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 These exponentially decaying magnetic string correlations are therefore consistent with a symmetric dimer liquid with no magnetic vortex condensation.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-    \begin{figure}
-        \centering
-        \includegraphics[width=1.0\columnwidth]{vison_3way.pdf}
-        \caption
-        {
-            (a) Color scale of the $Z_3$ magnetic string correlation function $|C_M(\bm{r}_{\bm{0}p})|$,
-            on a $L=32$ lattice where $\bm{0}$ corresponds to plaquette represented by the orange circle.
-            (b) The magnitude of the $Z_3$ magnetic string structure factor $S_M$ for a $L=64$ lattice, using a columnar background dimerization as shown in \figref{fig:orientedSL}.             
-            (c) $|S_M|$ shown along a path in $k$ space. Statistical errors are smaller than the symbols.
-        }
-        \label{fig:vison_3way}
-    \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[]
     \centering
@@
 We then can test for the confinement of monomers by studying the monomer-monomer density correlation function $\langle m_{\bm{0}} m_{\bm{r}} \rangle$, which is plotted in \figref{fig:monomer_correlations}.
-If the monomers are confined, we expect $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ to decay to zero at large distances; conversely if monomers are deconfined, we expect the monomers to be randomly distributed on the lattice, such that $\langle m_{\bm{0}} m_{\bm{r}} \rangle \sim L^{-4}$ at large separations.
+If the monomers are confined, we expect $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ to decay to zero at large distances; conversely if monomers are deconfined, we expect the monomers to be randomly distributed on the lattice, such that $\langle m_{\bm{0}} m_{\bm{r}} \rangle \simeq L^{-4}$ at large separations.
 \figref{fig:monomer_correlations} demonstrates that $\langle m_{\bm{0}} m_{\bm{r}} \rangle$ decays to $L^{-4}$ for each system size, indicating a deconfinement of monomers.
@@
 Thus we find that $Z_3$ electric charges are deconfined in the QDPM.
-
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t!]
+\begin{figure}[b]
     \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-
-\FloatBarrier
+%\FloatBarrier
 

### 2017-08-01 Referee_Response.txt
2nd referee response

@@
 sincerely,
-O. Meyers
+O. Myers
 C. M. Herdman
@@
 
-Yes, we appreciate the referee catching this error.
+Yes this is correct--we appreciate the referee for catching this error.
 
@@
 
-We did not intend to claim that we have proven the the QDPM is ergodic in each topological sector, but simply that our numerics are consistent with such ergodicity, as we see no evidence of a lack of ergodicity.
-We have clarified this in the text by explicitly acknowledging the possibility of "frozen" configurations.
-However, the particular configurations the referee mentions (all links occupied--i.e.
-pentamers on each vertex) does indeed have dynamics in the QDPM (refer to Table II, move "\nu_1").
+We appreciate the referee for pointing our the lack of clarity on this point in the original version of the manuscript.
+We did not intend to claim that we have proven the the QDPM is ergodic in each topological sector, but simply that our numerics are consistent with the QDPM dynamics connecting disconnected topological sectors in the QDM.
+We have clarified this in the text by explicitly acknowledging such "frozen" configurations.
 Additionally, as mentioned in the manuscript, the "staggered" configuration which are frozen in the QDM do have dynamics in the QDPM (see Fig.
@@
 4 in the new manuscript) that illustrates how pentamers can give dynamics to staggered regions, and convert regions with no flippable plaquettes to maximally flippable columnar configurations.
-While we cannot prove ergodicity, or rule out other "frozen" configurations, we hope this new figure helps illustrate the increased dynamics of the QDPM over the QDM.
+We hope this new figure helps illustrate the increased dynamics of the QDPM over the QDM.
 
@@
 
-Page 5: Sec. II 2nd Paragraph: ... weaker correlations that the QDM, -> ... weaker correlations than the QDM,
+Page 5: Sec. III 2nd Paragraph: ... weaker correlations that the QDM, -> ... weaker correlations than the QDM,
 
-Page 6. Right column: Figure 4 added.
+Page 6. Left column: Figure 4 added.
+
+Page 6: Sec III: Rephrased statement about ergodicity: "Our numerical simulations (discussed below in Sec.
+IV) suggest that the dynamics of $H_{QDPM}$ are ergodic in..." ==> "With the exception isolated ``frozen" configurations (e.g.
+pentamers occupying all vertices), our numerical simulations (discussed below in Sec.
+IV) suggest that the dynamics of the $H_{QDPM}$ access a substantial region of configuration space in..."
 
@@
 
-"We find no evidence of a lack of ergodicity within each of the 9 topological sectors, although we cannot rule out the possibility of isolated ``frozen" configurations which are not accessed by the dynamics described in \tabref{tab:pentamer_moves}; in particular we note that the QDPM gives dynamics to ``staggered" dimer configurations that are frozen in the QDM."
+"Although we cannot rule out the possibility of a variety of isolated ``frozen" configurations (e.g.
+pentamers occupying all sites) which are not accessed by the dynamics described in \tabref{tab:pentamer_moves}, we find that the increased dynamics of the QDPM connect $U(1)$ topological sectors that are disconnected in the QDM; in particular we note that the QDPM gives dynamics to ``staggered" dimer configurations that are frozen in the QDM (see Fig.
+4)."
+
+Page 9: Sec. IV D, 1st paragraph: Removed the following statement: "which appear to provide ergodic dynamics in the monomer-dimer-pentamer configuration space."
 

### 2017-08-01 qdpm_paper.tex
2nd referee response

@@
 
-Our numerical simulations (discussed below in \secref{sec:numerics}) suggest that the dynamics of $\HQDPM$ are ergodic in each topological sector $\Omega$ that are labeled by the topological loop operators:
+With the exception isolated ``frozen" configurations (e.g.
+pentamers occupying all vertices), our numerical simulations (discussed below in \secref{sec:numerics}) suggest that the dynamics of the $\HQDPM$ access a substantial region of configuration space in each topological sector $\Omega$ that are labeled by the topological loop operators:
 \begin{equation}
@@
 The histogram $P(\Phi)$ has a Gaussian shape with a width that increases with system size; this is expected as $\Phi = \pm L/2$ correspond to ordered configurations and thus there are fewer dimer configurations near these limits.
-We find no evidence of a lack of ergodicity within each of the 9 topological sectors, although we cannot rule out the possibility of isolated ``frozen" configurations which are not accessed by the dynamics described in \tabref{tab:pentamer_moves}; in particular we note that the QDPM gives dynamics to ``staggered" dimer configurations that are frozen in the QDM (see \figref{fig:stag_to_flip}).
+Although we cannot rule out the possibility of a variety of isolated ``frozen" configurations (e.g.
+pentamers occupying all sites) which are not accessed by the dynamics described in \tabref{tab:pentamer_moves}, we find that the increased dynamics of the QDPM connect $U(1)$ topological sectors that are disconnected in the QDM; in particular we note that the QDPM gives dynamics to ``staggered" dimer configurations that are frozen in the QDM (see \figref{fig:stag_to_flip}).
 For the remainder of the paper we present results in the $(0,0)$ topological sector, but we see no qualitative dependence between topological sectors for any of the results presented here.
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h]
+\begin{figure}[]
     \centering
@@
 \begin{equation}
-\monomermvA  \Longleftrightarrow \monomermvB  \notag
-\end{equation}
-which appear to provide ergodic dynamics in the monomer-dimer-pentamer configuration space.
+\monomermvA  \Longleftrightarrow \monomermvB.  \notag
+\end{equation}
 Notice that monomers remain on the same sub-lattice, which is consistent with their assignment of a $Z_3$ electric charge of $\pm1$ (see \tabref{tab:defects}) and the positive and negative monomers live on different sub-lattices.
